---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  out.width = "100%",
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# ggstatsplot: `ggplot2` Based Plots with Statistical Details

[![CRAN_Release_Badge](http://www.r-pkg.org/badges/version-ago/ggstatsplot)](https://CRAN.R-project.org/package=ggstatsplot)
[![CRAN Checks](https://cranchecks.info/badges/summary/ggstatsplot)](https://cran.r-project.org/web/checks/check_results_ggstatsplot.html)
[![packageversion](https://img.shields.io/badge/Package%20version-0.0.3.9000-orange.svg?style=flat-square)](commits/master)
[![Coverage Status](https://img.shields.io/codecov/c/github/IndrajeetPatil/ggstatsplot/master.svg)](https://codecov.io/github/IndrajeetPatil/ggstatsplot?branch=master)
[![Daily downloads badge](https://cranlogs.r-pkg.org/badges/last-day/ggstatsplot?color=blue)](https://CRAN.R-project.org/package=ggstatsplot)
[![Weekly downloads badge](https://cranlogs.r-pkg.org/badges/last-week/ggstatsplot?color=blue)](https://CRAN.R-project.org/package=ggstatsplot)
[![Monthly downloads badge](https://cranlogs.r-pkg.org/badges/last-month/ggstatsplot?color=blue)](https://CRAN.R-project.org/package=ggstatsplot)
[![Total downloads badge](https://cranlogs.r-pkg.org/badges/grand-total/ggstatsplot?color=blue)](https://CRAN.R-project.org/package=ggstatsplot)
[![Travis Build Status](https://travis-ci.org/IndrajeetPatil/ggstatsplot.svg?branch=master)](https://travis-ci.org/IndrajeetPatil/ggstatsplot) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/IndrajeetPatil/ggstatsplot?branch=master&svg=true)](https://ci.appveyor.com/project/IndrajeetPatil/ggstatsplot) 
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-green.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.3.0-6666ff.svg)](https://cran.r-project.org/)

<!-- 
[![Open issues](http://img.shields.io/github/issues/badges/ggstatsplot.svg)](https://github.com/IndrajeetPatil/ggstatsplot/issues/)
[![Dependency Status](http://img.shields.io/gemnasium/IndrajeetPatil/ggstatsplot.svg)](https://gemnasium.com/IndrajeetPatil/ggstatsplot) 
-->

## Overview

[`ggstatsplot`](https://indrajeetpatil.github.io/ggstatsplot/) is an extension
of [`ggplot2`](https://github.com/tidyverse/ggplot2) package for creating
graphics with details from statistical tests included in the plots themselves
and targeted primarily at behavioral sciences community to provide a one-line
code to produce information-rich plots. Currently, it supports only the most
common types of statistical tests (**parametric**, **nonparametric**, and
**robust** versions of **t-tets/anova**, **correlation**, and **contingency tables** analyses). 

It, therefore, produces a limited kinds of plots for the supported analyses:

  - **violin plots** (for comparisons between groups or conditions), 
  - **pie charts** (for categorical data),
  - **scatterplots** (for correlations between two variables),
  - **correlation matrices** (for correlations between multiple variables),
  - **histograms** (for hypothesis about distributions), and
  - **dot-and-whisker plots** (for regression models).

In addition to these basic plots, `ggstatsplot` also provides `grouped_`
versions of all functions that makes it easy to repeat the same anlysis for any
grouping variable.

Future versions will include other types of analyses and plots as well.

## Installation

To get the latest, stable CRAN release:
```{r installationCRAN, eval = FALSE}
utils::install.packages(pkgs = "ggstatsplot")
```

You can get the **development** version from GitHub. If you are in hurry and
want to reduce the time of installation, prefer-

```{r installation1, eval = FALSE}
# needed package to download from GitHub repo
utils::install.packages(pkgs = "devtools")   

# downloading the package from GitHub
devtools::install_github(
  repo = "IndrajeetPatil/ggstatsplot", # package path on GitHub
  dependencies = FALSE,                # assumes that you already have all packages installed needed for this package to work
  quick = TRUE                         # skips docs, demos, and vignettes
)                        
```

If time is not a constraint-
```{r installation2, eval = FALSE}
devtools::install_github(
  repo = "IndrajeetPatil/ggstatsplot", # package path on GitHub
  dependencies = TRUE,                 # installs packages which ggstatsplot depends on
  upgrade_dependencies = TRUE          # updates any out of date dependencies
)
```

If you are not using the [RStudio IDE](https://www.rstudio.com/) and you get an
error related to "pandoc" you will either need to remove the argument
`build_vignettes = TRUE` (to avoid building the vignettes) or install
[pandoc](http://pandoc.org/). If you have the `rmarkdown` R package installed
then you can check if you have pandoc by running the following in R:

```{r pandoc}
rmarkdown::pandoc_available()
```
## Citation

If you want to cite this package in a scientific journal or in any other
context, run the following code in your R console:

```{r citation, eval = FALSE}
utils::citation(package = "ggstatsplot")
```

## Help

There is a dedicated website to `ggstatplot`, which is updated after every new
commit: <https://indrajeetpatil.github.io/ggstatsplot/>.

In `R`, documentation for any function can be accessed with the standard `help` command-
```{r help, eval = FALSE}
?ggbetweenstats
?ggscatterstats
?gghistostats
?ggpiestats
?ggcorrmat
?ggcoefstats
?combine_plots
?grouped_ggbetweenstats
?grouped_ggscatterstats
?grouped_gghistostats
?grouped_ggpiestats
?grouped_ggcorrmat
```

## Usage

`ggstatsplot` relies on [non-standard evaluation](http://adv-r.had.co.nz/Computing-on-the-language.html), which means you **shouldn't** enter arguments in the following manner: `data = NULL, x = data$x, y = data$y`. This may work well for most of the functions most of the time, but is highly discouraged. You should always specify `data` argument for all functions. 

Additionally, `ggstatsplot` is a very chatty package and will by default output
information about references for tests, notes on assumptions about linear
models, and warnings. If you don't want your console to be cluttered with such
messages, they can be turned off by setting argument `messages = FALSE` in the
function call.

Here are examples of the main functions currently supported in `ggstatsplot`.
**Note**: The documentation below is for the **development** version of the package.
So you may see some features available here that are not currently present in the
stable version of this package on **CRAN**:
<https://cran.r-project.org/web/packages/ggstatsplot/index.html>

* `ggbetweenstats`

This function creates either a violin plot, a box plot, or a mix of two for
**between**-group or **between**-condition comparisons with results from
statistical tests in the subtitle. The simplest function call looks like this-

```{r ggbetweenstats1, message = FALSE, warning = FALSE}
ggstatsplot::ggbetweenstats(
  data = datasets::iris, 
  x = Species, 
  y = Sepal.Length,
  messages = FALSE
)
```

Number of other arguments can be specified to make this plot even more
informative and, additionally, this function returns a `ggplot2` object and thus
any of the graphics layers can be further modified:

```{r ggbetweenstats2, message = FALSE, warning = FALSE}
library(ggplot2)

ggstatsplot::ggbetweenstats(
  data = datasets::iris,
  x = Species,
  y = Sepal.Length,
  notch = TRUE,                                   # show notched box plot
  mean.plotting = TRUE,                           # whether mean for each group id to be displayed 
  type = "parametric",                            # which type of test is to be run
  outlier.tagging = TRUE,                         # whether outliers need to be tagged
  outlier.label = Sepal.Width,                    # variable to be used for the outlier tag
  xlab = "Type of Species",                       # label for the x-axis variable
  ylab = "Attribute: Sepal Length",               # label for the y-axis variable
  title = "Dataset: Iris flower data set",        # title text for the plot
  caption = expression(                           # caption text for the plot 
    paste(italic("Note"), ": this is a demo")
  ),
  ggtheme = ggplot2::theme_grey(),                # choosing a different theme
  palette = "Set1",                               # choosing a different color palette
  messages = FALSE
) +                                               # further modification outside of ggstatsplot
  ggplot2::coord_cartesian(ylim = c(3, 8)) + 
  ggplot2::scale_y_continuous(breaks = seq(3, 8, by = 1)) 
```

The `type` (of test) argument also accepts the following abbreviations: `"p"`
(for *parametric*), `"np"` (for *nonparametric*), `"r"` (for *robust*).
Additionally, the type of plot to be displayed can also be modified (`"box"`,
`"violin"`, or `"boxviolin"`).

Variant of this function `ggwithinstats` is currently under work. You *can*
still use this function just to prepare the **plot** for exploratory data
analysis, but the statistical details displayed in the subtitle will be
incorrect. You can remove them by adding `+ ggplot2::labs(subtitle = NULL)`.

For more, see the `ggbetweenstats` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggbetweenstats.html>

* `ggscatterstats`

This function creates a scatterplot with marginal histograms/boxplots/density/violin plots from \code{\link[ggExtra]{ggMarginal}} and results from statistical tests in the subtitle:

```{r ggscatterstats1, message = FALSE, warning = FALSE}
ggstatsplot::ggscatterstats(
  data = datasets::iris, 
  x = Sepal.Length, 
  y = Petal.Length,
  title = "Dataset: Iris flower data set",
  messages = FALSE
)
```

Number of other arguments can be specified to modify this basic plot-

```{r ggscatterstats2, message = FALSE, warning = FALSE}
library(datasets)

ggstatsplot::ggscatterstats(
  data = subset(datasets::iris, iris$Species == "setosa"),
  x = Sepal.Length,
  y = Petal.Length,
  type = "robust",                               # type of test that needs to be run
  xlab = "Attribute: Sepal Length",              # label for x axis
  ylab = "Attribute: Petal Length",              # label for y axis 
  line.color = "black",                         # changing regression line color line
  title = "Dataset: Iris flower data set",       # title text for the plot
  caption = expression(                          # caption text for the plot
    paste(italic("Note"), ": this is a demo")
  ),
  marginal.type = "density",                     # type of marginal distribution to be displayed
  xfill = "blue",                                # color fill for x-axis marginal distribution 
  yfill = "red",                                 # color fill for y-axis marginal distribution
  centrality.para = "median",                    # which type of central tendency lines are to be displayed  
  width.jitter = 0.2,                            # amount of horizontal jitter for data points
  height.jitter = 0.4,                           # amount of vertical jitter for data points
  messages = FALSE                               # turn off messages and notes
) 
```

For more, see the `ggscatterstats` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggscatterstats.html>

* `ggpiestats`

This function creates a pie chart for categorical variables with results from
contingency table analysis included in the subtitle of the plot. If only one
categorical variable is entered, results from one-sample **proportion test**
will be displayed as a subtitle.

```{r ggpiestats1, message = FALSE, warning = FALSE}
ggstatsplot::ggpiestats(
  data = datasets::iris,
  main = Species,
  messages = FALSE
)
```

This function can also be used to study an interaction between two categorical
variables. Additionally, as with the other functions in `ggstatsplot`, this
function returns a `ggplot2` object and can further be modified with `ggplot2`
syntax (e.g., we can change the color palette *after* `ggstatsplot` has produced
the plot)-

```{r ggpiestats2, message = FALSE, warning = FALSE}
library(ggplot2)

ggstatsplot::ggpiestats(
  data = datasets::mtcars,
  main = cyl,
  condition = am,
  title = "Dataset: Motor Trend Car Road Tests",      
  messages = FALSE
) + # further modification outside of ggstatsplot to change the default palette as an example 
  ggplot2::scale_fill_brewer(palette = "Set1")     
```

As with the other functions, this basic plot can further be modified with
additional arguments:

```{r ggpiestats3, message = FALSE, warning = FALSE}
library(ggplot2)

ggstatsplot::ggpiestats(
  data = datasets::mtcars,
  main = am,
  condition = cyl,
  title = "Dataset: Motor Trend Car Road Tests",      # title for the plot
  stat.title = "interaction effect",                  # title for the results from Pearson's chi-squared test
  legend.title = "Transmission",                      # title for the legend
  factor.levels = c("1 = manual", "0 = automatic"),   # renaming the factor level names for 'main' variable 
  facet.wrap.name = "No. of cylinders",               # name for the facetting variable
  facet.proptest = FALSE,                             # turning of facetted proportion test results
  caption = expression(                               # text for the caption
    paste(italic("Note"), ": this is a demo")
  ),
  messages = FALSE                                    # turn off messages and notes
) 
```

For more, including information about the variant of this function
`grouped_ggpiestats`, see the `ggpiestats` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggpiestats.html>

* `gghistostats`

In case you would like to see the distribution of one variable and check if it
is significantly different from a specified value with a one sample test, this
function will let you do that.

```{r gghistostats1, message = FALSE, warning = FALSE}
library(datasets)

ggstatsplot::gghistostats(
  data = datasets::iris,
  x = Sepal.Length,
  title = "Distribution of Iris sepal length",
  type = "parametric",               # one sample t-test
  test.value = 3,                    # default value is 0
  centrality.para = "mean",          # which measure of central tendency is to be plotted
  centrality.color = "darkred",     # decides color of vertical line representing central tendency
  binwidth = 0.10,                   # binwidth value (needs to be toyed around with until you find the best one)
  messages = FALSE                   # turn off the messages
) 
```

The `type` (of test) argument also accepts the following abbreviations: `"p"` (for
*parametric*) or `"np"` (for *nonparametric*) or `"bf"` (for *Bayes Factor*). 

```{r gghistostats2, message = FALSE, warning = FALSE}
ggstatsplot::gghistostats(
  data = NULL,
  title = "Distribution of variable x",
  x = stats::rnorm(n = 1000, mean = 0, sd = 1),
  test.value = 1,
  test.value.line = TRUE,
  test.value.color = "black",
  centrality.para = "mean",
  type = "bf",
  bf.prior = 0.8,
  messages = FALSE,
  caption = expression(                              
    paste(italic("Note"), ": black line - test value; blue line - observed mean")
  )
)
```

As seen here, by default, Bayes Factor quantifies the support for the
alternative hypothesis (H1) over the null hypothesis (H0) (i.e., BF10 is
displayed). In case you run parametric t-test and the effect is not significant,
caption will be displayed containing information about evidence in favor of the
null hypothesis (H0). This is not recommended, but if you want to turn off this
behavior, you can use the argument `bf.message = FALSE`.

```{r gghistostats3, message = FALSE, warning = FALSE}
ggstatsplot::gghistostats(
  data = datasets::ToothGrowth,
  x = len,
  title = "Distribution of tooth length",
  centrality.para = "mean",
  test.value = 20,
  test.value.line = TRUE,
  xlab = "Tooth length",
  caption = expression(                              
    paste(italic("Note"), ": black line - test value; blue line - observed mean")
  ),
  messages = FALSE
)
```

For more, including information about the variant of this function
`grouped_gghistostats`, see the `gghistostats` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/gghistostats.html>

* `ggcorrmat`

`ggcorrmat` makes correlalograms with minimal amount of code. Just sticking
to the defaults itself produces publication-ready correlation matrices.
 (Wrapper around [`ggcorrplot`](https://github.com/kassambara/ggcorrplot))

```{r ggcorrmat1, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 6}
# as a default this function outputs a correlalogram plot
ggstatsplot::ggcorrmat(
  data = datasets::iris,
  corr.method = "spearman",                # correlation method
  sig.level = 0.005,                       # threshold of significance
  cor.vars = Sepal.Length:Petal.Width,     # a range of variables can be selected  
  cor.vars.names = c("Sepal Length", "Sepal Width", "Petal Length", "Petal Width"),
  title = "Correlalogram for length measures for Iris species",
  subtitle = "Iris dataset by Anderson",
  caption = expression(
    paste(
      italic("Note"),
      ": X denotes correlation non-significant at ",
      italic("p "),
      "< 0.005; adjusted alpha"
    )
  )
)
```

Multiple arguments can be modified to change the appearance of the correlation
matrix. 

Alternatively, you can use it just to get the correlation matrices and their
corresponding *p*-values (in a [tibble](http://tibble.tidyverse.org/) format).
This is especially useful for robust correlation coefficient, which is not
currently supported in `ggcorrmat` plot.

```{r ggcorrmat3, message = FALSE, warning = FALSE}
# getting the correlation coefficient matrix
ggstatsplot::ggcorrmat(
  data = datasets::iris,
  cor.vars = Sepal.Length:Petal.Width,
  corr.method = "robust",
  output = "correlations",             # specifying the needed output
  digits = 3                           # number of digits to be dispayed for correlation coefficient
)

# getting the p-value matrix
ggstatsplot::ggcorrmat(
  data = datasets::iris,
  cor.vars = Sepal.Length:Petal.Width,
  corr.method = "robust",
  output = "p-values"
)
```

For examples and more information, see the `ggcorrmat` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggcorrmat.html>

* `ggcoefstats`

`ggcoefstats` creates a lot with the regression coefficients' point estimates as
dots with confidence interval whiskers. This is a wrapper function around
`GGally::ggcoef`.

```{r ggcoefstats1, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 8, out.width = "80%"}
ggstatsplot::ggcoefstats(x = stats::lm(formula = mpg ~ am * cyl,
                                       data = mtcars)) 
```

The basic can be further modified to one's liking with additional arguments:
```{r ggcoefstats2, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 8, out.width = "80%"}
ggstatsplot::ggcoefstats(
  x = stats::lm(formula = mpg ~ am * cyl,
                data = mtcars),
  point.color = "red",
  stats.label.size = 3.5,
  stats.label.color = c("#0072B2", "#D55E00", "#CC79A7"),
  title = "Car performance predicted by transmission and cylinder count",
  subtitle = "Source: 1974 Motor Trend US magazine"
) +                                    
  # further modification with the ggplot2 commands
  # note the order in which the labels are entered
  ggplot2::scale_y_discrete(labels = c("transmission", "cylinders", "interaction")) +
  ggplot2::labs(x = "regression coefficient",
                y = NULL)
```

All the regression model classes that are supported in the `broom` package with
`tidy` and `glance` methods
(<https://broom.tidyverse.org/articles/available-methods.html>) are also
supported by `ggcoefstats`. Let's see few examples:

```{r ggcoefstats3, message = FALSE, warning = FALSE, fig.height = 10, fig.width = 10, out.width = "100%"}
library(dplyr)
library(lme4)

# for reproducibility
set.seed(200)

# creating dataframes needed for the analysis below
d <- as.data.frame(Titanic)

# combining plots together
ggstatsplot::combine_plots(
  # general linear model
  ggstatsplot::ggcoefstats(
    x = stats::glm(
      formula = Survived ~ Sex + Age,
      data = d,
      weights = d$Freq,
      family = "binomial"
    ),
    exponentiate = TRUE,
    exclude.intercept = FALSE
  ),
  # nonlinear least squares
  ggstatsplot::ggcoefstats(
    x = stats::nls(
      formula = mpg ~ k / wt + b,
      data = mtcars,
      start = list(k = 1, b = 0)
    ),
    point.color = "darkgreen"
  ),
  # linear mmodel
  ggstatsplot::ggcoefstats(
    x = lme4::lmer(
      formula = Reaction ~ Days + (Days | Subject),
      data = lme4::sleepstudy
    ),
    point.color = "red",
    exclude.intercept = TRUE
  ),
  # generalized linear mixed-effects model
  ggstatsplot::ggcoefstats(
    x = lme4::glmer(
      formula = cbind(incidence, size - incidence) ~ period + (1 | herd),
      data = lme4::cbpp,
      family = binomial
    ),
    exclude.intercept = FALSE
  ),
  labels = c("(a)", "(b)", "(c)", "(d)"),
  nrow = 2,
  ncol = 2
)
```

* `combine_plots`

`ggstatsplot` also contains a helper function `combine_plots` to combine
multiple plots. This is a wrapper around \code{\link[cowplot]{plot_grid}} 
and lets you combine multiple plots and add combination of title, caption, and
annotation texts with suitable default parameters.

The full power of `ggstatsplot` can be leveraged with a functional programming
package like [`purrr`](http://purrr.tidyverse.org/) that replaces many for loops
with code that is both more succinct and easier to read and, therefore, `purrr`
should be preferrred.

For more, see the associated vignette-
<https://indrajeetpatil.github.io/ggstatsplot/articles/combine_plots.html>

* `theme_mprl`

All plots from `ggstatsplot` have a default theme: `theme_mprl`. For more on how
to modify it, see the associated vignette-
<https://indrajeetpatil.github.io/ggstatsplot/articles/theme_mprl.html>
