---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

  ```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# ggstatsplot: `ggplot2` Based Plots with Statistical Details

[![Travis Build Status](https://travis-ci.org/IndrajeetPatil/ggstatsplot.svg?branch=master)](https://travis-ci.org/IndrajeetPatil/ggstatsplot)

## Overview

ggstatsplot is an extension of `ggplot2` package for creating graphics with details from statistical tests included
in the plots themselves and targeted primarily at behavioral sciences community to provide a one-line code to produce information-rich figures. Currently, it supports only the most common types of tests used in analysis (**parametric**, **nonparametric**, and **robust** versions of **t-tets/anova**, **correlation**, and **contingency tables** analyses). 
Future versions will include other types of analyses as well.

## Installation

```{r, eval = FALSE}
# You can get the development version from GitHub:
# install.packages("devtools")
devtools::install_github("IndrajeetPatil/ggstatsplot")
```
## Usage

Here are examples of the three main functions currently supported in `ggstatsplot`:

* `ggbetweenstats`

This function creates a violin plot for **between**-group or **between**-condition comparisons with results from statistical tests in the subtitle:
```{r message = FALSE}
ggstatsplot::ggbetweenstats(data = iris, 
                            x = Species, 
                            y = Sepal.Length)
```

Number of other arguments can be specified to make this plot even more informative and, additionally, this function returns a `ggplot2` object and thus any of the graphics layers can be further modified:
```{r message = FALSE}
library(ggplot2)
ggstatsplot::ggbetweenstats(
  data = iris,
  x = Species,
  y = Sepal.Length,
  mean.plotting = TRUE,
  type = "robust",
  outlier.tagging = TRUE,
  xlab = "Type of Species",
  ylab = "Attribute: Sepal Length",
  title = "Dataset: Iris flower data set",
  caption = expression(paste(italic("Note"), ": this is a demo"))
  ) +
  coord_cartesian(ylim = c(3, 8)) + 
  scale_y_continuous(breaks = seq(3, 8, by = 1))
```

Variant of this function `ggwithinstats` is currently under work.

* `ggscatterstats`

This function creates a scatterplot with marginal histograms/boxplots/density/violin plots from `ggExtra::ggMarginal()` and results from statistical tests in subtitle:
```{r message = FALSE}
ggstatsplot::ggscatterstats(data = iris, 
                            x = Sepal.Length, 
                            y = Petal.Length)
```

Number of other arguments can be specified to modify this basic plot-
```{r message = FALSE}
ggstatsplot::ggscatterstats(
  data = subset(iris, iris$Species == "setosa"),
  x = Sepal.Length,
  y = Petal.Length,
  test = "robust",
  xlab = "Attribute: Sepal Length",
  ylab = "Attribute: Petal Length",
  title = "Dataset: Iris flower data set",
  caption = expression(paste(italic("Note"), ": this is a demo")),
  marginal.type = "density",
  xfill = "blue",
  yfill = "red",
  intercept = "median",
  width.jitter = 0.2,
  height.jitter = 0.4
  ) 
```

**Important**: In contrast to all other functions in this package, the `ggscatterstats` function returns object that is **not** further modifiable with `ggplot2`. This can be avoided by not plotting the marginal distributions (`marginal = FALSE`). Currently trying to find a workaround this problem.

* `ggpiestats`

This function creates a pie chart for categorical variables with results from contingency table analysis included in the subtitle of the plot. If only one categorical variable is entered, proportion test will be carried out.
```{r message = FALSE}
ggstatsplot::ggpiestats(data = iris,
                        main = Species)
```

This function can also be used to study an interaction between two categorical variables. Additionally, as with the other functions in `ggstatsplot`, this function returns a `ggplot2` object and can further be modified with `ggplot2` syntax (e.g., we can change the color palette *after* `ggstatsplot` has produced the plot)-
```{r message = FALSE}
library(ggplot2)
ggstatsplot::ggpiestats(data = mtcars,
                        main = am,
                        condition = cyl) +
  scale_fill_brewer(palette = "Dark2")
```

As with the other functions, this basic plot can further be modified with additional arguments:
```{r message = FALSE}
library(ggplot2)
ggstatsplot::ggpiestats(
data = mtcars,
main = am,
condition = cyl,
title = "Dataset: Motor Trend Car Road Tests",
stat.title = "interaction effect",
legend.title = "Transmission",
factor.levels = c("0 = automatic", "1 = manual"),
facet.wrap.name = "No. of cylinders",
caption = expression(paste(italic("Note"), ": this is a demo"))
) 
```
