---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 150,
  out.width = "100%",
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ggstatsplot: `ggplot2` Based Plots with Statistical Details

[![CRAN_Release_Badge](http://www.r-pkg.org/badges/version-ago/ggstatsplot)](https://CRAN.R-project.org/package=ggstatsplot)
[![CRAN Checks](https://cranchecks.info/badges/summary/ggstatsplot)](https://cran.r-project.org/web/checks/check_results_ggstatsplot.html)
[![packageversion](https://img.shields.io/badge/Package%20version-0.0.6.9000-orange.svg?style=flat-square)](https://github.com/IndrajeetPatil/ggstatsplot/)
[![Coverage Status](https://img.shields.io/codecov/c/github/IndrajeetPatil/ggstatsplot/master.svg)](https://codecov.io/github/IndrajeetPatil/ggstatsplot?branch=master)
[![Daily downloads badge](https://cranlogs.r-pkg.org/badges/last-day/ggstatsplot?color=blue)](https://CRAN.R-project.org/package=ggstatsplot)
[![Weekly downloads badge](https://cranlogs.r-pkg.org/badges/last-week/ggstatsplot?color=blue)](https://CRAN.R-project.org/package=ggstatsplot)
[![Monthly downloads badge](https://cranlogs.r-pkg.org/badges/last-month/ggstatsplot?color=blue)](https://CRAN.R-project.org/package=ggstatsplot)
[![Total downloads badge](https://cranlogs.r-pkg.org/badges/grand-total/ggstatsplot?color=blue)](https://CRAN.R-project.org/package=ggstatsplot)
[![Travis Build Status](https://travis-ci.org/IndrajeetPatil/ggstatsplot.svg?branch=master)](https://travis-ci.org/IndrajeetPatil/ggstatsplot) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/IndrajeetPatil/ggstatsplot?branch=master&svg=true)](https://ci.appveyor.com/project/IndrajeetPatil/ggstatsplot) 
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-green.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.3.0-6666ff.svg)](https://cran.r-project.org/)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Pending Pull-Requests](http://githubbadges.herokuapp.com/IndrajeetPatil/ggstatsplot/pulls.svg?style=flat)](https://github.com/IndrajeetPatil/ggstatsplot/pulls)
[![Github Issues](http://githubbadges.herokuapp.com/IndrajeetPatil/ggstatsplot/issues.svg)](https://github.com/IndrajeetPatil/ggstatsplot/issues)

<!--
[![Dependency Status](http://img.shields.io/gemnasium/IndrajeetPatil/ggstatsplot.svg)](https://gemnasium.com/IndrajeetPatil/ggstatsplot) 
-->

# Overview

[`ggstatsplot`](https://indrajeetpatil.github.io/ggstatsplot/) is an extension
of [`ggplot2`](https://github.com/tidyverse/ggplot2) package for creating
graphics with details from statistical tests included in the plots themselves
and targeted primarily at behavioral sciences community to provide a one-line
code to produce information-rich plots. In a typical exploratory data analysis
workflow, data visualization and statistical modelling are two different phases:
visualization informs modelling, and modelling in its turn can suggest a
different visualization method, and so on and so forth. The central idea of
*ggstatsplot* is simple: combine these two phases into one in the form of
graphics with statistical details, which makes data exploration simpler and
faster.

Currently, it supports only the most
common types of statistical tests (**parametric**, **nonparametric**, and
**robust** versions of **t-test**, **anova**, and **correlation** analyses,
**contingency table** analysis, and **regression** analyses).

It, therefore, produces a limited kinds of plots for the supported analyses:

  - **violin plots** (for comparisons *between* groups or conditions), 
  - **pie charts** (for categorical data),
  - **scatterplots** (for correlations between two variables),
  - **correlation matrices** (for correlations between multiple variables),
  - **histograms** (for hypothesis about distributions), and
  - **dot-and-whisker plots** (for regression models).

In addition to these basic plots, `ggstatsplot` also provides **`grouped_`**
versions for most functions that makes it easy to repeat the same analysis for any
grouping variable.

Future versions will include other types of statistical analyses and plots as well.

# Installation

To get the latest, stable CRAN release (`0.0.6`):
```{r installationCRAN, eval = FALSE}
utils::install.packages(pkgs = "ggstatsplot")
```

You can get the **development** version of the package from GitHub
(`0.0.6.9000`). To see what new changes (and bug fixes) have been made to the
package since the last release on `CRAN`, you can check the detailed log of
changes here: <https://indrajeetpatil.github.io/ggstatsplot/news/index.html>

If you are in hurry and want to reduce the time of installation,
prefer-

```{r installation1, eval = FALSE}
# needed package to download from GitHub repo
utils::install.packages(pkgs = "devtools")   

# downloading the package from GitHub
devtools::install_github(
  repo = "IndrajeetPatil/ggstatsplot", # package path on GitHub
  dependencies = FALSE,                # assumes that you already have all packages installed needed for this package to work
  quick = TRUE                         # skips docs, demos, and vignettes
)                        
```

If time is not a constraint-
```{r installation2, eval = FALSE}
devtools::install_github(
  repo = "IndrajeetPatil/ggstatsplot", # package path on GitHub
  dependencies = TRUE,                 # installs packages which ggstatsplot depends on
  upgrade_dependencies = TRUE          # updates any out of date dependencies
)
```

If you are not using the [RStudio IDE](https://www.rstudio.com/) and you get an
error related to "pandoc" you will either need to remove the argument
`build_vignettes = TRUE` (to avoid building the vignettes) or install
[pandoc](http://pandoc.org/). If you have the `rmarkdown` R package installed
then you can check if you have pandoc by running the following in R:

```{r pandoc}
rmarkdown::pandoc_available()
```

# Citation

If you want to cite this package in a scientific journal or in any other
context, run the following code in your `R` console:

```{r citation, eval = FALSE}
utils::citation(package = "ggstatsplot")
```

There is currently a publication in preparation corresponding this package and
the citation will be updated once it's published.

# Documentation and Examples

To see the detailed documentation for each function in the stable **CRAN**
version of the package, see:

  - README:
    <https://cran.r-project.org/web/packages/ggstatsplot/readme/README.html>
  - Vignettes: <https://cran.r-project.org/web/packages/ggstatsplot/vignettes/>

To see the documentation relevant for the **development** version of the package,
see the dedicated website for `ggstatplot`, which is updated after every new
commit: <https://indrajeetpatil.github.io/ggstatsplot/>.

## Help

In `R`, documentation for any function can be accessed with the standard `help`
command-

```{r help, eval = FALSE}
# primary functions
?ggbetweenstats
?ggscatterstats
?gghistostats
?ggpiestats
?ggcorrmat
?ggcoefstats

# grouped variants of primary functions
?grouped_ggbetweenstats
?grouped_ggscatterstats
?grouped_gghistostats
?grouped_ggpiestats
?grouped_ggcorrmat

# helper functions
?combine_plots
?theme_ggstatsplot
```

Another handy tool to see arguments to any of the functions is `args`. For
example-

```{r args}
args(name = ggstatsplot::ggscatterstats)
```

In case you want to look at the function body for any of the functions, just
type the name of the function without the parentheses:

```{r funbody}
ggstatsplot::theme_ggstatsplot
```

If you are not familiar either with what the namespace `::` does or how to use
pipe operator `%>%`, something this package and its documentation relies a lot
on, you can check out these links-

  - <http://r-pkgs.had.co.nz/namespace.html>
  - <http://r4ds.had.co.nz/pipes.html>

## Usage

`ggstatsplot` relies on [non-standard evaluation](http://adv-r.had.co.nz/Computing-on-the-language.html), which means you **shouldn't** enter arguments in the following manner: `data = NULL, x = data$x, y = data$y`. You **must** always specify the `data` argument for all functions. 

Additionally, `ggstatsplot` is a very chatty package and will by default output
information about references for tests, notes on assumptions about linear
models, and warnings. If you don't want your console to be cluttered with such
messages, they can be turned off by setting argument `messages = FALSE` in the
function call.

Here are examples of the main functions currently supported in `ggstatsplot`.

**Note**: The documentation below is for the **development** version of the
package. So you may see some features available here that are not currently
present in the stable version of this package on **CRAN**. For documentation
relevant for the CRAN version, see the vignettes on the site:
<https://cran.r-project.org/web/packages/ggstatsplot/vignettes/>

## `ggbetweenstats`

This function creates either a violin plot, a box plot, or a mix of two for
**between**-group or **between**-condition comparisons with results from
statistical tests in the subtitle. The simplest function call looks like this-

```{r ggbetweenstats1, message = FALSE, warning = FALSE}
# loading needed libraries
library(ggstatsplot)

# for reproducibility
set.seed(123)

# plot
ggstatsplot::ggbetweenstats(
  data = datasets::iris, 
  x = Species, 
  y = Sepal.Length,
  messages = FALSE
) +                                               # further modification outside of ggstatsplot
  ggplot2::coord_cartesian(ylim = c(3, 8)) + 
  ggplot2::scale_y_continuous(breaks = seq(3, 8, by = 1)) 
```

Note that this function returns a `ggplot2` object and thus any of the graphics
layers can be further modified.

The `type` (of test) argument
also accepts the following abbreviations: `"p"` (for *parametric*) or `"np"`
(for *nonparametric*) or `"r"` (for *robust*) or `"bf"` (for *Bayes Factor*).
Additionally, the type of plot to be displayed can also be modified (`"box"`,
`"violin"`, or `"boxviolin"`).

A number of other arguments can be specified to make this plot even more
informative or change some of the default options. 

```{r ggbetweenstats2, message = FALSE, warning = FALSE}
library(ggplot2)

# for reproducibility
set.seed(123)

# let's leave out one of the factor levels and see if instead of anova, a t-test will be run
iris2 <- dplyr::filter(.data = datasets::iris, Species != "setosa")

# let's change the levels of our factors, a common routine in data analysis
# pipeline, to see if this function respects the new factor levels
iris2$Species <-
  base::factor(x = iris2$Species,
               levels = c("virginica" , "versicolor"))

# plot
ggstatsplot::ggbetweenstats(
  data = iris2,                                    
  x = Species,
  y = Sepal.Length,
  notch = TRUE,                                   # show notched box plot
  mean.plotting = TRUE,                           # whether mean for each group is to be displayed 
  mean.ci = TRUE,                                 # whether to display confidence interval for means
  mean.label.size = 2.5,                          # size of the label for mean
  type = "p",                                     # which type of test is to be run
  bf.message = TRUE,                              # add a message with bayes factor in favor of the null
  k = 2,                                          # number of decimal places for statistical results
  outlier.tagging = TRUE,                         # whether outliers need to be tagged
  outlier.label = Sepal.Width,                    # variable to be used for the outlier tag
  outlier.label.color = "darkgreen",              # changing the color for the text label
  xlab = "Type of Species",                       # label for the x-axis variable
  ylab = "Attribute: Sepal Length",               # label for the y-axis variable
  title = "Dataset: Iris flower data set",        # title text for the plot
  ggtheme = ggthemes::theme_fivethirtyeight(),    # choosing a different theme
  ggstatsplot.layer = FALSE,                      # turn off ggstatsplot theme layer
  package = "wesanderson",                        # package from which color palette is to be taken
  palette = "Darjeeling1",                        # choosing a different color palette
  messages = FALSE
) 
```

In case of a parametric t-test, setting `bf.message = TRUE` will also attach
results from Bayesian Student's *t*-test. That way, if the null hypothesis can't
be rejected with the NHST approach, the Bayesian approach can help index
evidence in favor of the null hypothesis (i.e., `BF01`).

By default, Bayes Factor quantifies the support for the
alternative hypothesis (H1) over the null hypothesis (H0) (i.e., `BF10` is
displayed). Natural logarithms are shown because BF values can be pretty large.
This also makes it easy to compare evidence in favor alternative (`BF10`) versus
null (`BF01`) hypotheses (since `log(BF10) = - log(BF01)`).

Additionally, there is also a `grouped_` variant of this function that makes it
easy to repeat the same operation across a **single** grouping variable:

```{r ggbetweenstats3, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::grouped_ggbetweenstats(
  data = ggstatsplot::movies_long, 
  x = mpaa, 
  y = length,
  grouping.var = genre,            # grouping variable
  title.prefix = "Movie genre",
  palette = "default_jama",
  package = "ggsci",
  messages = FALSE,
  nrow = 2,
  ncol = 2,
  title.text = "Differences in movie length by mpaa ratings for different genres"
)
```

For more, see the `ggbetweenstats` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggbetweenstats.html>

** This function is not appropriate for within-subjects designs.**

Variant of this function `ggwithinstats` is currently under work. You *can*
still use this function just to prepare the **plot** for exploratory data
analysis, but the statistical details displayed in the subtitle will be
incorrect. You can remove them by adding `+ ggplot2::labs(subtitle = NULL)` to
your function call.

As a **temporary solution**, you can use the helper function from `ggstatsplot`
to display results from within-subjects version of the test in question. Here is
an example-

```{r ggbetweenstats4, message = FALSE, warning = FALSE}
# for reproducibility
set.seed(123)

# creating a smaller dataframe
intent_short <- ggstatsplot::intent_morality %>%
  dplyr::filter(.data = ., condition %in% c("accidental", "attempted")) 

# getting text results using with a helper function
results_subtitle <- ggstatsplot::subtitle_ggbetween_t_parametric(
  data = intent_short,
  x = condition,
  y = rating,
  paired = TRUE
)

# displaying the subtitle on the plot
ggstatsplot::ggbetweenstats(
  data = intent_short,
  x = condition,
  y = rating,
  messages = FALSE
) +
  ggplot2::labs(subtitle = results_subtitle)
```


## `ggscatterstats`

This function creates a scatterplot with marginal
histograms/boxplots/density/violin/densigram plots from `ggExtra::ggMarginal`
and results from statistical tests in the subtitle:

```{r ggscatterstats1, message = FALSE, warning = FALSE}
ggstatsplot::ggscatterstats(
  data = ggplot2::msleep, 
  x = sleep_rem, 
  y = awake,
  xlab = "REM sleep (in hours)",
  ylab = "Amount of time spent awake (in hours)",
  title = "Understanding mammalian sleep",
  messages = FALSE
)
```

Number of other arguments can be specified to modify this basic plot-

```{r ggscatterstats2, message = FALSE, warning = FALSE}
library(datasets)

# for reproducibility
set.seed(123)

# plot
ggstatsplot::ggscatterstats(
  data = dplyr::filter(.data = ggstatsplot::movies_long, genre == "Action"),
  x = budget,
  y = rating,
  type = "robust",                                # type of test that needs to be run
  xlab = "Movie budget (in million/ US$)",        # label for x axis
  ylab = "IMDB rating",                           # label for y axis 
  label.var = "title",                            # variable for labeling data points
  label.expression = "rating < 5 & budget > 150", # expression that decides which points to label
  line.color = "yellow",                          # changing regression line color line
  title = "Movie budget and IMDB rating (action)",# title text for the plot
  caption = expression(                           # caption text for the plot
    paste(italic("Note"), ": IMDB stands for Internet Movie DataBase")
  ),
  ggtheme = hrbrthemes::theme_ipsum_ps(),         # choosing a different theme
  ggstatsplot.layer = FALSE,                      # turn off ggstatsplot theme layer
  marginal.type = "density",                      # type of marginal distribution to be displayed
  xfill = "#0072B2",                              # color fill for x-axis marginal distribution 
  yfill = "#009E73",                              # color fill for y-axis marginal distribution
  xalpha = 0.6,                                   # transparency for x-axis marginal distribution
  yalpha = 0.6,                                   # transparency for y-axis marginal distribution
  centrality.para = "median",                     # which type of central tendency lines are to be displayed  
  point.width.jitter = 0.2,                       # amount of horizontal jitter for data points
  point.height.jitter = 0.4,                      # amount of vertical jitter for data points
  messages = FALSE                                # turn off messages and notes
) 
```

Additionally, there is also a `grouped_` variant of this function that makes it
easy to repeat the same operation across a **single** grouping variable:

```{r ggscatterstats3, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::grouped_ggscatterstats(
  data = ggstatsplot::movies_long, 
  x = rating, 
  y = length,
  xfill = "#E69F00", 
  yfill = "#8b3058",
  xlab = "IMDB rating",
  grouping.var = genre,            # grouping variable
  title.prefix = "Movie genre",
  ggtheme = ggplot2::theme_grey(),
  messages = FALSE,
  nrow = 2,
  ncol = 2,
  title.text = "Relationship between movie length by IMDB ratings for different genres"
)
```

For more, see the `ggscatterstats` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggscatterstats.html>

## `ggpiestats`

This function creates a pie chart for categorical or nominal variables with
results from contingency table analysis (Pearson's chi-squared test for
between-subjects design and McNemar's test for within-subjects design) included
in the subtitle of the plot. If only one categorical variable is entered,
results from one-sample **proportion test** will be displayed as a subtitle.

```{r ggpiestats1, message = FALSE, warning = FALSE}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::ggpiestats(
  data = ggplot2::msleep,
  main = vore,
  title = "Composition of vore types among mammals",
  messages = FALSE
)
```

This function can also be used to study an interaction between two categorical
variables. Additionally, this basic plot can further be modified with additional
arguments and the function returns a `ggplot2` object that can further be
modified with `ggplot2` syntax:

```{r ggpiestats2, message = FALSE, warning = FALSE}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::ggpiestats(
  data = datasets::mtcars,
  main = am,
  condition = cyl,
  title = "Dataset: Motor Trend Car Road Tests",      # title for the plot
  stat.title = "interaction: ",                       # title for the results from Pearson's chi-squared test
  legend.title = "Transmission",                      # title for the legend
  factor.levels = c("1 = manual", "0 = automatic"),   # renaming the factor level names for 'main' variable 
  facet.wrap.name = "No. of cylinders",               # name for the facetting variable
  facet.proptest = FALSE,                             # turning of facetted proportion test results
  package = "ggsci",                                  # package from which color palette is to be taken
  palette = "default_jama",                           # choosing a different color palette 
  caption = expression(                               # text for the caption
    paste(italic("Note"), ": this is a demo")
  ),
  messages = FALSE                                    # turn off messages and notes
) 
```

In case of within-subjects designs, setting `paired = TRUE` will produce results
from McNemar test-

```{r ggpiestats3, message = FALSE, warning = FALSE}
# for reproducibility
set.seed(123)

# data
survey.data <- data.frame(
  `1st survey` = c('Approve', 'Approve', 'Disapprove', 'Disapprove'),
  `2nd survey` = c('Approve', 'Disapprove', 'Approve', 'Disapprove'),
  `Counts` = c(794, 150, 86, 570),
  check.names = FALSE
)

# plot
ggstatsplot::ggpiestats(
  data = survey.data,
  main = `1st survey`,
  condition = `2nd survey`,
  counts = Counts,
  paired = TRUE,                      # within-subjects design
  stat.title = "McNemar Test: ",
  package = "wesanderson",
  palette = "Royal1"
)
```

Additionally, there is also a `grouped_` variant of this function that makes it
easy to repeat the same operation across a **single** grouping variable:

```{r ggpiestats4, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 8}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::grouped_ggpiestats(
  data = ggstatsplot::movies_long, 
  main = mpaa,
  grouping.var = genre,            # grouping variable
  title.prefix = "Movie genre",
  palette = "BrightPastel",
  package = "quickpalette",
  messages = FALSE,
  nrow = 2,
  ncol = 2,
  title.text = "Composition of MPAA ratings for different genres"
)
```

For more, including information about the variant of this function
`grouped_ggpiestats`, see the `ggpiestats` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggpiestats.html>

## `gghistostats`

In case you would like to see the distribution of one variable and check if it
is significantly different from a specified value with a one sample test, this
function will let you do that. 

The `type` (of test) argument also accepts the following abbreviations: `"p"`
(for *parametric*) or `"np"` (for *nonparametric*) or `"r"` (for *robust*) or
`"bf"` (for *Bayes Factor*).

```{r gghistostats1, message = FALSE, warning = FALSE}
ggstatsplot::gghistostats(
  data = datasets::ToothGrowth,             # dataframe from which variable is to be taken
  x = len,                                  # numeric variable whose distribution is of interest
  title = "Distribution of Sepal.Length",   # title for the plot
  fill.gradient = TRUE,                     # use color gradient
  test.value = 10,                          # the comparison value for t-test
  test.value.line = TRUE,                   # display a vertical line at test value
  type = "bf",                              # bayes factor for one sample t-test
  bf.prior = 0.8,                           # prior width for calculating the bayes factor
  messages = FALSE                          # turn off the messages
)
```

The aesthetic defaults can be easily modified-

**Note**: To use `bar.measure = "mix"` option, you will need to get the
development version of `ggplot2` from GitHub.

```{r gghistostats2, message = FALSE, warning = FALSE}
# getting development version of ggplot2
# devtools::install_github(repo = "tidyverse/ggplot2", dependencies = FALSE)

# plot
ggstatsplot::gghistostats(
  data = datasets::iris,                         # dataframe from which variable is to be taken
  x = Sepal.Length,                              # numeric variable whose distribution is of interest
  title = "Distribution of Iris sepal length",   # title for the plot
  type = "parametric",                           # one sample t-test
  bar.measure = "mix",                           # what does the bar length denote
  test.value = 5,                                # default value is 0
  test.value.line = TRUE,                        # display a vertical line at test value
  test.value.color = "#0072B2",                  # color for the line for test value
  centrality.para = "mean",                      # which measure of central tendency is to be plotted
  centrality.color = "darkred",                  # decides color of vertical line representing central tendency
  binwidth = 0.10,                               # binwidth value (experiment until you find the best one)
  bf.message = TRUE,                             # display bayes factor for null over alternative
  bf.prior = 0.8,                                # prior width for computing bayes factor
  messages = FALSE,                              # turn off the messages
  ggtheme = hrbrthemes::theme_ipsum_tw(),        # choosing a different theme
  ggstatsplot.layer = FALSE                      # turn off ggstatsplot theme layer
) 
```

As can be seen from the plot, bayes factor can be attached (using `bf.message =
TRUE`) to assess evidence in favor of the null hypothesis.


Additionally, there is also a `grouped_` variant of this function that makes it
easy to repeat the same operation across a **single** grouping variable:

```{r gghistostats4, message = FALSE, warning = FALSE, fig.height = 10, fig.width = 10}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::grouped_gghistostats(
  data = ggstatsplot::movies_long, 
  x = budget,
  xlab = "Movies budget (in million US$)",
  grouping.var = genre,            # grouping variable
  title.prefix = "Movie genre",
  ggtheme = ggthemes::theme_tufte(),
  messages = FALSE,
  nrow = 2,
  ncol = 2,
  title.text = "Movies budgets for different genres"
)
```

For more, including information about the variant of this function
`grouped_gghistostats`, see the `gghistostats` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/gghistostats.html>

## `ggcorrmat`

`ggcorrmat` makes a correlalogram (a matrix of correlation coefficients) with
minimal amount of code. Just sticking to the defaults itself produces
publication-ready correlation matrices. But, for the sake of exploring the
available options, let's change some of the defaults.

```{r ggcorrmat1, message = FALSE, warning = FALSE}
# as a default this function outputs a correlalogram plot
ggstatsplot::ggcorrmat(
  data = ggplot2::msleep,
  corr.method = "robust",                    # correlation method
  sig.level = 0.001,                         # threshold of significance
  p.adjust.method = "holm",                  # p-value adjustment method for multiple comparisons
  cor.vars = c(sleep_rem, awake:bodywt),     # a range of variables can be selected  
  cor.vars.names = c("REM sleep",            # variable names
                     "time awake", 
                     "brain weight", 
                     "body weight"), 
  matrix.type = "upper",                     # type of visualization matrix
  colors = c("#B2182B", "white", "#4D4D4D"), 
  title = "Correlalogram for mammals sleep dataset",
  subtitle = "sleep units: hours; weight units: kilograms"
)
```

Note that if there are `NA`s present in the selected dataframe, the legend will
display minimum, median, and maximum number of pairs used for correlation
matrices.

Multiple aesthetics-related arguments can be modified to change the appearance
of the correlation matrix.

Alternatively, you can use it just to get the correlation matrices and their
corresponding *p*-values (in a `tibble` format).

```{r ggcorrmat2, message = FALSE, warning = FALSE}
# show four digits in a tibble
options(pillar.sigfig = 4)

# getting the correlation coefficient matrix
ggstatsplot::ggcorrmat(
  data = datasets::iris,
  cor.vars = Sepal.Length:Petal.Width,
  corr.method = "robust",
  output = "correlations",             # specifying the needed output ("r" or "corr" will also work)
  digits = 3                           # number of digits to be dispayed for correlation coefficient
)

# getting the p-value matrix
ggstatsplot::ggcorrmat(
  data = ggplot2::msleep,
  cor.vars = sleep_total:bodywt,
  corr.method = "robust",
  output = "p.values",                  # only "p" or "p-values" will also work
  p.adjust.method = "holm"
)

# getting the sample sizes for all pairs
ggstatsplot::ggcorrmat(
  data = ggplot2::msleep,
  cor.vars = sleep_total:bodywt,
  corr.method = "robust",
  output = "n"
)
```

Additionally, there is also a `grouped_` variant of this function that makes it
easy to repeat the same operation across a **single** grouping variable:

```{r ggcorrmat3, message = FALSE, warning = FALSE, fig.height = 10, fig.width = 10}
# for reproducibility
set.seed(123)

# plot
# let's use only 50% of the data to speed up the process
ggstatsplot::grouped_ggcorrmat(
  data = dplyr::sample_frac(ggstatsplot::movies_long, size = 0.5),
  cor.vars = length:votes,
  corr.method = "np",
  colors = c("#cbac43", "white", "#550000"),
  grouping.var = genre,                      # grouping variable
  title.prefix = "Movie genre",
  messages = FALSE,
  nrow = 2,
  ncol = 2
)
```

For examples and more information, see the `ggcorrmat` vignette:
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggcorrmat.html>

## `ggcoefstats`

`ggcoefstats` creates a lot with the regression coefficients' point estimates as
dots with confidence interval whiskers. 

```{r ggcoefstats1, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 8, out.width = "80%"}
ggstatsplot::ggcoefstats(x = stats::lm(formula = mpg ~ am * cyl,
                                       data = datasets::mtcars)) 
```

The basic can be further modified to one's liking with additional arguments
(also, let's use a robust linear model instead of a simple linear model now):

```{r ggcoefstats2, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 8, out.width = "80%"}
ggstatsplot::ggcoefstats(
  x = MASS::rlm(formula = mpg ~ am * cyl,
                data = datasets::mtcars),
  point.color = "red",                
  point.shape = 15,
  vline.color = "#CC79A7",
  vline.linetype = "dotdash",
  stats.label.size = 3.5,
  stats.label.color = c("#0072B2", "#D55E00", "darkgreen"),
  title = "Car performance predicted by transmission & cylinder count",
  subtitle = "Source: 1974 Motor Trend US magazine",
  ggtheme = ggthemes::theme_stata(),
  ggstatsplot.layer = FALSE
) +                                    
  # further modification with the ggplot2 commands
  # note the order in which the labels are entered
  ggplot2::scale_y_discrete(labels = c("transmission", "cylinders", "interaction")) +
  ggplot2::labs(x = "regression coefficient",
                y = NULL)
```

All the regression model classes that are supported in the `broom` package with
`tidy` and `glance` methods
(<https://broom.tidyverse.org/articles/available-methods.html>) are also
supported by `ggcoefstats`. Additionally, we can make a number of aesthetic
modifications by changing the defaults for theme and palette.

Let's see a couple more examples:

```{r ggcoefstats3, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 6}
library(dplyr)
library(lme4)
library(quantreg)

# for reproducibility
set.seed(200)

# creating dataframe needed for one of the analyses below
d <- as.data.frame(Titanic)
data(stackloss)

# combining plots together
ggstatsplot::combine_plots(
  # quantile regression
ggstatsplot::ggcoefstats(
  x = quantreg::rq(
    formula = stack.loss ~ stack.x,
    data = stackloss,
    method = "br"
  ),
  se.type = "iid",
  title = "quantile regression"
),
  # linear mmodel
  ggstatsplot::ggcoefstats(
    x = lme4::lmer(
      formula = Reaction ~ Days + (Days | Subject),
      data = lme4::sleepstudy
    ),
    point.color = "red",
    stats.label.color = "black",
    ggtheme = hrbrthemes::theme_ipsum_ps(),
    ggstatsplot.layer = FALSE,
    exclude.intercept = FALSE,
    title = "linear mixed-effects model"
  ),
  labels = c("(a)", "(b)"),
  nrow = 2,
  ncol = 1
)
```

This is by no means an exhaustive list of models supported by `ggcoefstats`. For
a more thorough discussion about all regression models supported, see the
associated vignette-
<https://indrajeetpatil.github.io/ggstatsplot/articles/ggcoefstats.html>


## `combine_plots`

The full power of `ggstatsplot` can be leveraged with a functional programming
package like [`purrr`](http://purrr.tidyverse.org/) that replaces `for` loops
with code that is both more succinct and easier to read and, therefore, `purrr`
should be preferrred `r emo::ji("heart_eyes_cat")`. (Another old school option
to do this effectively is using the `plyr` package.)

In such cases, `ggstatsplot` contains a helper function `combine_plots` to
combine multiple plots, which can be useful for combining a list of plots
produced with `purrr`. This is a wrapper around `cowplot::plot_grid` and lets
you combine multiple plots and add a combination of title, caption, and
annotation texts with suitable defaults.

For examples (both with `plyr` and `purrr`), see the associated vignette-
<https://indrajeetpatil.github.io/ggstatsplot/articles/combine_plots.html>

## `theme_ggstatsplot`

All plots from `ggstatsplot` have a default theme: `theme_ggstatsplot`. You can
change this theme by using the argument `ggtheme` for all functions.

It is important to note that irrespective of which `ggplot` theme you choose,
`ggstatsplot` in the backdrop adds a new layer with its idiosyncratic theme
settings, chosen to make the graphs more readable or aesthetically pleasing.
Let's see an example with `gghistostats` and see how a certain theme from
`hrbrthemes` package looks with and without the `ggstatsplot` layer.

```{r theme_ggstatsplot, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 12}
# to use hrbrthemes themes, first make sure you have all the necessary fonts
library(hrbrthemes)
# extrafont::ttf_import()
# extrafont::font_import()

# try this yourself
ggstatsplot::combine_plots(
  # with the ggstatsplot layer
  ggstatsplot::gghistostats(
    data = datasets::iris,
    x = Sepal.Width,
    messages = FALSE,
    title = "Distribution of Sepal Width",
    test.value = 5,
    ggtheme = hrbrthemes::theme_ipsum(),
    ggstatsplot.layer = TRUE
  ),
  # without the ggstatsplot layer
  ggstatsplot::gghistostats(
    data = datasets::iris,
    x = Sepal.Width,
    messages = FALSE,
    title = "Distribution of Sepal Width",
    test.value = 5,
    ggtheme = hrbrthemes::theme_ipsum_ps(),
    ggstatsplot.layer = FALSE
  ),
  nrow = 1,
  labels = c("(a)", "(b)"),
  title.text = "Behavior of ggstatsplot theme layer with chosen ggtheme"
)
```

For more on how to modify it, see the associated vignette-
<https://indrajeetpatil.github.io/ggstatsplot/articles/theme_ggstatsplot.html>

## Using `ggstatsplot` helpers to display text results

Sometimes you may not like the default plot produced by `ggstatsplot`. In such
cases, you can use other custom plots (from `ggplot2` or other plotting
packages) and still use `ggstatsplot` (subtitle) helper functions to display
results from relevant statistical test. For example, in the following chunk, we
will use pirateplot from `yarrr` package and use `ggstatsplot` helper function
to display the results.

```{r pirateplot, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 8}

# for reproducibility
set.seed(123)

# loading the needed libraries
library(yarrr)
library(ggstatsplot)

# using `ggstatsplot` to prepare text with statistical results
stats_results <-
  ggstatsplot::subtitle_ggbetween_anova_parametric(
    data = ChickWeight,
    x = Time,
    y = weight,
    messages = FALSE
  )

# using `yarrr` to create plot
yarrr::pirateplot(
  formula = weight ~ Time,
  data = ChickWeight,
  theme = 1,
  main = stats_results
)
```

# Code coverage

As the code stands right now, here is the code coverage for all primary
functions involved:
<https://codecov.io/gh/IndrajeetPatil/ggstatsplot/tree/master/R>

# Contributing

I'm happy to receive bug reports, suggestions, questions, and (most of all)
contributions to fix problems and add features. I personally prefer using the
Github issues system over trying to reach out to me in other ways (personal
e-mail, Twitter, etc.). Pull requests for contributions are encouraged.

Please note that this project is released with a 
[Contributor Code of Conduct](CONDUCT.md). By participating in this project
you agree to abide by its terms.
