---
  output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

  ```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# ggstatsplot: `ggplot2` Based Plots with Statistical Details

[![packageversion](https://img.shields.io/badge/Package%20version-0.0.1-orange.svg?style=flat-square)](commits/master)
[![Travis Build Status](https://travis-ci.org/IndrajeetPatil/ggstatsplot.svg?branch=master)](https://travis-ci.org/IndrajeetPatil/ggstatsplot) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/IndrajeetPatil/ggstatsplot?branch=master&svg=true)](https://ci.appveyor.com/project/IndrajeetPatil/ggstatsplot) 
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.3.3-6666ff.svg)](https://cran.r-project.org/)
<!-- [![Coverage Status](https://img.shields.io/codecov/c/github/IndrajeetPatil/ggstatsplot/master.svg)](https://codecov.io/github/IndrajeetPatil/ggstatsplot?branch=master)
[![Dependency Status](http://img.shields.io/gemnasium/IndrajeetPatil/ggstatsplot.svg)](https://gemnasium.com/IndrajeetPatil/ggstatsplot) -->

## Overview

`ggstatsplot` is an extension of [`ggplot2`](https://github.com/tidyverse/ggplot2)
package for creating graphics with details from statistical tests included in
the plots themselves and targeted primarily at behavioral sciences community
to provide a one-line code to produce information-rich figures. Currently, it
supports only the most common types of tests used in analysis (**parametric**,
**nonparametric**, and **robust** versions of **t-tets/anova**, **correlation**,
and **contingency tables** analyses). Future versions will include other types
of analyses as well.

## Installation

You can get the development version from GitHub. If you are in hurry and want to reduce the time of installation, prefer-

```{r installation1, eval = FALSE}
# install.packages("devtools")                                # needed package to download from GitHub repo
devtools::install_github(repo = "IndrajeetPatil/ggstatsplot", # package path on GitHub
                         quick = TRUE)                        # skips docs, demos, and vignettes
```

If time is not a constraint-
```{r installation2, eval = FALSE}
devtools::install_github(repo = "IndrajeetPatil/ggstatsplot", # package path on GitHub
                         dependencies = TRUE,                 # installs packages which ggstatsplot depends on
                         upgrade_dependencies = TRUE          # updates any out of date dependencies
)
```

## Help

Documentation for any function can be accessed with the standard `help` command-
```{r help, eval = FALSE}
?ggbetweenstats
?ggscatterstats
?gghistostats
?ggpiestats
?ggcorrmat
?combine_plots
```

## Usage

`ggstatsplot` relies on [non-standard evaluation](http://adv-r.had.co.nz/Computing-on-the-language.html), which means you **can't** enter arguments in the following manner: `x = data$x, y = data$y`. This may work well for most of the functions most of the time, but is highly discouraged. You should always specify `data` argument for all functions. 

Additionally, `ggstatsplot` is a very chatty package and will by default output
information about references for tests, notes on assumptions about linear
models, and warnings. If you don't want your console to be cluttered with such
messages, they can be turned off by setting `messages = FALSE`.

Here are examples of the main functions currently supported in `ggstatsplot`:

* `ggbetweenstats`

This function creates a violin plot for **between**-group or **between**-condition comparisons with results from statistical tests in the subtitle:

```{r ggbetweenstats1, message = FALSE, warning = FALSE, dpi = 300}
ggstatsplot::ggbetweenstats(data = iris, 
                            x = Species, 
                            y = Sepal.Length)
```

Number of other arguments can be specified to make this plot even more
informative and, additionally, this function returns a `ggplot2` object and thus
any of the graphics layers can be further modified:

```{r ggbetweenstats2, message = FALSE, warning = FALSE, dpi = 300}
library(ggplot2)

ggstatsplot::ggbetweenstats(
  data = iris,
  x = Species,
  y = Sepal.Length,
  mean.plotting = TRUE,                           # whether mean for each group id to be displayed 
  type = "robust",                                # which type of test is to be run
  outlier.tagging = TRUE,                         # whether outliers need to be tagged
  outlier.label = Sepal.Width,                    # variable to be used for the outlier tag
  xlab = "Type of Species",                       # label for the x-axis variable
  ylab = "Attribute: Sepal Length",               # label for the y-axis variable
  title = "Dataset: Iris flower data set",        # title text for the plot
  caption = expression(                           # caption text for the plot 
    paste(italic("Note"), ": this is a demo")
    )
  ) +                                             # further modifcation outside of ggstatsplot
  ggplot2::coord_cartesian(ylim = c(3, 8)) + 
  ggplot2::scale_y_continuous(breaks = seq(3, 8, by = 1)) 
```

The `type` (of test) argument also accepts the following abbreviations:
"p" (for *parametric*), "np" (for *nonparametric*), "r" (for
*robust*).

For example,
```{r ggbetweenstats3, message = FALSE, warning = FALSE, dpi = 300, fig.height = 10, fig.width = 6}
library(ggplot2)
library(cowplot)

# parametric t-tet 
p1 <- ggstatsplot::ggbetweenstats(
  data = mtcars,
  x = am,
  y = mpg, 
  type = "p"
)

# Mann-Whitney U-test
p2 <- ggstatsplot::ggbetweenstats(
  data = mtcars,
  x = am,
  y = mpg, 
  type = "np"
)

# robust t-test
p3 <- ggstatsplot::ggbetweenstats(
  data = mtcars,
  x = am,
  y = mpg, 
  type = "r"
)

# combining the individual plots into a single plot
cowplot::plot_grid(p1, p2, p3, 
                   nrow = 3, 
                   ncol = 1, 
                   labels = c("(a)", "(b)", "(c)")
)
```

Variant of this function `ggwithinstats` is currently under work.

* `ggscatterstats`

This function creates a scatterplot with marginal histograms/boxplots/density/violin plots from [`ggExtra::ggMarginal()`](https://cran.r-project.org/web/packages/ggExtra/vignettes/ggExtra.html) and results from statistical tests in the subtitle:

```{r ggscatterstats1, message = FALSE, warning = FALSE, dpi = 300}
ggstatsplot::ggscatterstats(data = iris, 
                            x = Sepal.Length, 
                            y = Petal.Length,
                            title = "Dataset: Iris flower data set")
```

Number of other arguments can be specified to modify this basic plot-

```{r ggscatterstats2, message = FALSE, warning = FALSE, dpi = 300}
library(datasets)

ggstatsplot::ggscatterstats(
  data = subset(iris, iris$Species == "setosa"),
  x = Sepal.Length,
  y = Petal.Length,
  type = "robust",                               # type of test that needs to be run
  xlab = "Attribute: Sepal Length",              # label for x axis
  ylab = "Attribute: Petal Length",              # label for y axis 
  line.colour = "black",                         # changing regression line colour line
  title = "Dataset: Iris flower data set",       # title text for the plot
  caption = expression(                          # caption text for the plot
    paste(italic("Note"), ": this is a demo")
    ),
  marginal.type = "density",                     # type of marginal distribution to be displayed
  xfill = "blue",                                # colour fill for x-axis marginal distribution 
  yfill = "red",                                 # colour fill for y-axis marginal distribution
  intercept = "median",                          # which type of intercept line is to be displayed  
  width.jitter = 0.2,                            # amount of horizontal jitter for data points
  height.jitter = 0.4                            # amount of vertical jitter for data points
  ) 
```

The `type` (of test) argument also accepts the following abbreviations:
"p" (for *parametric*/pearson's), "np" (for *nonparametric*/spearman), "r" (for
*robust*).

**Important**: In contrast to all other functions in this package, the
`ggscatterstats` function returns object that is **not** further modifiable
with `ggplot2`. This can be avoided by not plotting the marginal distributions
(`marginal = FALSE`). Currently trying to find a workaround this problem.

* `ggpiestats`

This function creates a pie chart for categorical variables with results from
contingency table analysis included in the subtitle of the plot. If only one
categorical variable is entered, proportion test will be carried out.

```{r ggpiestats1, message = FALSE, warning = FALSE, dpi = 300}
ggstatsplot::ggpiestats(data = iris,
                        main = Species)
```

This function can also be used to study an interaction between two categorical
variables. Additionally, as with the other functions in `ggstatsplot`, this
function returns a `ggplot2` object and can further be modified with `ggplot2`
syntax (e.g., we can change the color palette *after* `ggstatsplot` has produced
the plot)-

```{r ggpiestats2, message = FALSE, warning = FALSE, dpi = 300}
library(ggplot2)

ggstatsplot::ggpiestats(data = mtcars,
                        main = cyl,                
                        condition = am) +
  ggplot2::scale_fill_brewer(palette = "Dark2")   # further modifcation outside of ggstatsplot    
```

As with the other functions, this basic plot can further be modified with additional arguments:

```{r ggpiestats3, message = FALSE, warning = FALSE, dpi = 300}
library(ggplot2)

ggstatsplot::ggpiestats(
  data = mtcars,
  main = am,
  condition = cyl,
  title = "Dataset: Motor Trend Car Road Tests",      # title for the plot
  stat.title = "interaction effect",                  # title for the results from Pearson's chi-squared test
  legend.title = "Transmission",                      # title for the legend
  factor.levels = c("0 = automatic", "1 = manual"),   # renaming the factor level names for main variable 
  facet.wrap.name = "No. of cylinders",               # name for the facetting variable
  facet.proptest = FALSE,                             # turning of facetted proportion test results
  caption = expression(                               # text for the caption
    paste(italic("Note"), ": this is a demo")
    )
) 
```

* `gghistostats`

In case you would like to see the distribution of one variable and check if it
is significantly different from a specified value with a one sample test, this
function will let you do that.


```{r gghistostats, message = FALSE, warning = FALSE, dpi = 300}
library(datasets)
library(viridis)

ggstatsplot::gghistostats(
  data = iris,
  x = Sepal.Length,
  title = "Distribution of Iris sepal length",
  type = "parametric",            # one sample t-test
  test.value = 3,                 # default value is 0
  centrality.para = "mean",       # which measure of central tendency is to be plotted
  centrality.colour = "red",      # decides colour of vertical line representing central tendency
  density.plot = TRUE,            # whether density plot is to be overlayed on a histogram
  binwidth.adjust = TRUE,         # whether binwidth needs to be adjusted
  binwidth = 0.10                 # binwidth value (needs to be toyed around with until you find the best one)
) +              
  viridis::scale_fill_viridis()   # further modifcation outside of ggstatsplot
```

The `type` (of test) argument also accepts the following abbreviations:
"p" (for *parametric*) or "np" (for *nonparametric*).

* `ggcorrmat`

`ggcorrmat` makes correlalograms with minimal amount of code. Just sticking
to the defaults itself produces publication-ready correlation matrices.
 (Wrapper around [`ggcorrplot`](https://github.com/kassambara/ggcorrplot))

```{r ggcorrmat1, message = FALSE, warning = FALSE, dpi = 300, fig.height = 6, fig.width = 6}
# as a default this function outputs a correlalogram plot
ggstatsplot::ggcorrmat(
  data = iris,
  corr.method = "spearman",      # correlation method
  sig.level = 0.005,              # threshold of significance
  cor.vars = c(Sepal.Length, Sepal.Width, Petal.Length, Petal.Width),
  cor.vars.names = c("Sepal Length", "Sepal Width", "Petal Length", "Petal Width"),
  title = "Correlalogram for length measures for Iris species",
  subtitle = "Iris dataset by Anderson",
  caption = expression(
    paste(
      italic("Note"),
      ": X denotes correlation non-significant at ",
      italic("p "),
      "< 0.005; adjusted alpha"
    )
  )
)
```

Alternatively, you can use it just to get the correlation matrices and their
corresponding p-values (in a [tibble](http://tibble.tidyverse.org/) format).

```{r ggcorrmat2, message = FALSE, warning = FALSE}
# getting correlations 
ggstatsplot::ggcorrmat(
  data = iris,
  cor.vars = c(Sepal.Length, Sepal.Width, Petal.Length, Petal.Width),
  output = "correlations"
)

# getting p-values
ggstatsplot::ggcorrmat(
  data = iris,
  cor.vars = c(Sepal.Length, Sepal.Width, Petal.Length, Petal.Width),
  output = "p-values"
)
```

* `combine_plots`

`ggstatsplot` also contains a helper function `combine_plots` to combine
multiple plots. This is a wrapper around [`cowplot::plot_grid`](https://cran.r-project.org/web/packages/cowplot/vignettes/plot_grid.html)
and lets you combine multiple plots and add combination of title, caption, and
annotation texts with suitable default parameters.

The full power of `ggstatsplot` can be leveraged with a functional programming
package like [`purrr`](http://purrr.tidyverse.org/) that replaces many for loops
with code that is both more succinct and easier to read and, therefore, `purrr`
should be preferrred.

An example is provided below. Notice how little code is needed not only to
prepare the plots but also to plot the statistical test results.

```{r combine_plots_purrr1, message = FALSE, warning = FALSE, dpi = 300, fig.height = 12, fig.width = 8}

library(glue)
library(tidyverse)

### creating a list column with `ggstatsplot` plots
plots <- datasets::iris %>%
  dplyr::mutate(.data = ., Species2 = Species) %>% # just creates a copy of this variable
  dplyr::group_by(.data = ., Species) %>%                
  tidyr::nest(data = .) %>%                        # creates a nested dataframe with list column called `data`
  dplyr::mutate(                                   # creating a new list column of ggstatsplot outputs
    .data = .,
    plot = data %>%
      purrr::map(
        .x = .,
        .f = ~ ggstatsplot::ggscatterstats(
          data = .,
          x = Sepal.Length,
          y = Sepal.Width,
          messages = FALSE,                        # turns off all the warnings, notes, and reference messages   
          marginal.type = "boxplot",
          title =
            glue::glue("Species: {.$Species2} (n = {length(.$Sepal.Length)})")
        )
      )
  )

### display the new object (notice that the class of the `plot` list column is S3: gg)
plots

### creating a grid with cowplot
ggstatsplot::combine_plots(
  plotlist = plots$plot,                           # list column containing all ggstatsplot objects
  labels = c("(a)", "(b)", "(c)"),
  nrow = 3,
  ncol = 1,
  title.text = "Relationship between sepal length and width for all Iris species",
  title.size = 14,
  title.colour = "blue",
  caption.text = expression(
    paste(
      italic("Note"),
      ": Iris flower dataset was collected by Edgar Anderson."
    ),
    caption.size = 10
  )
)
```

Here is another example with `ggbetweenstats`-

```{r combine_plots_purrr2, message = FALSE, warning = FALSE, dpi = 300, fig.height = 13, fig.width = 6}
library(tidyverse)
library(glue)

### creating a list column with `ggstatsplot` plots
plots <- datasets::mtcars %>%
  dplyr::mutate(.data = ., cyl2 = cyl) %>%        # just creates a copy of this variable
  dplyr::group_by(.data = ., cyl) %>%             # 
  tidyr::nest(data = .) %>%                       # creates a nested dataframe with list column called `data`
  dplyr::mutate(                                  # creating a new list column of ggstatsplot outputs
    .data = .,
    plot = data %>%
      purrr::map(
        .x = .,
        .f = ~ ggstatsplot::ggbetweenstats(
          data = .,
          x = am,
          y = mpg,
          messages = FALSE,                       # turns off all the warnings, notes, and reference messages
          xlab = "Transmission",
          ylab = "Miles/(US) gallon",
          title = glue::glue(
            "Number of cylinders: {.$cyl2}"       # this is where the duplicated cyl2 column is useful
            ) 
        )
      )
  )

### display the new object (notice that the class of the `plot` list column is S3: gg)
plots

### creating a grid with cowplot
ggstatsplot::combine_plots(plotlist = plots$plot,       # list column containing all ggstatsplot objects
                           nrow = 3,
                           ncol = 1,
                           labels = c("(a)","(b)","(c)"),
                           title.text = "MPG and car transmission relationship (for each cylinder count)",
                           title.size = 13,
                           title.colour = "blue",
                           caption.text = expression(
                             paste(
                               italic("Transmission"),
                               ": 0 = automatic, 1 = manual"
                             ),
                             caption.size = 10
                           ))
```

* `theme_mprl`

`ggstatsplot` uses a default theme `theme_mprl()` that can be used with any `ggplot2` objects.

```{r theme_mprl, message = FALSE, warning = FALSE, dpi = 200, fig.height = 3, fig.width = 3}
library(ggplot2)

# Basic scatter plot
ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_point()
# Basic scatter plot with theme_mprl() added
ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_point() + 
  ggstatsplot::theme_mprl()

```

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/IndrajeetPatil/ggstatsplot/blob/master/CONDUCT.md). By participating in this project you agree to
abide by its terms.
