---
title: "Benchmarking"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    toc_depth: 3
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{Benchmarking}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
options(
  tibble.width = Inf,
  pillar.bold = TRUE,
  pillar.neg = TRUE,
  pillar.subtle_num = TRUE,
  pillar.min_chars = Inf
)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  out.width = "100%",
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

# Introduction

This is mostly to keep track of how the performance of different functions
changes across time.

# `ggbetweenstats`

```{r ggbetweenstats}
library(ggstatsplot)

set.seed(123)
bench::mark(
  ggbetweenstats(
    data = dplyr::filter(
      .data = movies_long,
      genre %in% c("Action", "Action Comedy", "Action Drama", "Comedy")
    ),
    x = mpaa,
    y = length
  )
) %>%
  dplyr::select(-expression)

set.seed(123)
bench::mark(
  grouped_ggbetweenstats(
    data = dplyr::filter(
      .data = movies_long,
      genre %in% c("Action", "Action Comedy", "Action Drama", "Comedy")
    ),
    x = mpaa,
    y = length,
    grouping.var = genre
  )
) %>%
  dplyr::select(-expression)
```

# `ggwithinstats`

```{r ggwithinstats}
library(ggstatsplot)

set.seed(123)
bench::mark(
  ggwithinstats(
    data = bugs_long,
    x = condition,
    y = desire
  )
) %>%
  dplyr::select(-expression)

set.seed(123)
bench::mark(
  grouped_ggwithinstats(
    data = bugs_long,
    x = condition,
    y = desire,
    grouping.var = gender
  )
) %>%
  dplyr::select(-expression)
```

# `gghistostats`

```{r gghistostats}
library(ggstatsplot)

set.seed(123)
bench::mark(gghistostats(mtcars, wt, test.value = 3)) %>%
  dplyr::select(-expression)

set.seed(123)
bench::mark(gghistostats(mtcars, wt, test.value = 3, grouping.var = am)) %>%
  dplyr::select(-expression)
```

# `ggdotplotstats`

```{r ggdotplotstats}
library(ggstatsplot)

set.seed(123)
bench::mark(ggdotplotstats(ggplot2::mpg, cty, manufacturer, test.value = 15)) %>%
  dplyr::select(-expression)

set.seed(123)
bench::mark(ggdotplotstats(ggplot2::mpg, cty, manufacturer, test.value = 15, grouping.var = cyl)) %>%
  dplyr::select(-expression)
```

# `ggscatterstats`

```{r ggscatterstats}
library(ggstatsplot)

set.seed(123)
bench::mark(ggscatterstats(mtcars, wt, mpg)) %>%
  dplyr::select(-expression)

set.seed(123)
bench::mark(ggscatterstats(mtcars, wt, mpg, grouping.var = am)) %>%
  dplyr::select(-expression)
```

# `ggcorrmat`

```{r ggcorrmat}
library(ggstatsplot)

set.seed(123)
bench::mark(ggcorrmat(iris)) %>%
  dplyr::select(-expression)

set.seed(123)
bench::mark(ggcorrmat(iris, grouping.var = Species)) %>%
  dplyr::select(-expression)
```

# `ggpiestats`

```{r ggpiestats}
library(ggstatsplot)

set.seed(123)
bench::mark(ggpiestats(mtcars, cyl)) %>%
  dplyr::select(-expression)

set.seed(123)
bench::mark(ggpiestats(mtcars, cyl, grouping.var = am)) %>%
  dplyr::select(-expression)
```

# `ggbarstats`

```{r ggbarstats}
library(ggstatsplot)

set.seed(123)
bench::mark(ggbarstats(ggplot2::mpg, fl, class)) %>%
  dplyr::select(-expression)

set.seed(123)
bench::mark(ggbarstats(ggplot2::mpg, fl, class, grouping.var = drv)) %>%
  dplyr::select(-expression)
```

# `ggcoefstats`

```{r ggcoefstats}
library(ggstatsplot)

set.seed(123)
bench::mark(ggcoefstats(stats::lm(formula = wt ~ am * cyl, data = mtcars))) %>%
  dplyr::select(-expression)
```

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>
