---
title: "combine_plots"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{combine_plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

# Combining plots with `combine_plots`

`ggstatsplot` contains a "helper" function named `combine_plots` to help you
combine several plots into one plot or add a combination of title, caption, and
annotation texts with suitable default parameters. It is a wrapper around
`cowplot::plot_grid()`. Some examples below.

**Note Before**: If you have just one grouping variable and you'd like a plot
for each `factor` of this variable the `grouped_` variants
(<https://indrajeetpatil.github.io/ggstatsplot/reference/index.html>) of all
`ggstatsplot` functions will allow you do to this. They specifically use the
`combine_plots` function under the covers.

## Combining multiple plots: Example-1 using `dplyr::group_map`

The easiest way to run the same `ggstatsplot` operation across multiple grouping
variables is by using `dplyr::group_map` functions and then - of course - one
would like to combine these plots in a single plot.

```{r ggscatterstats_groupmap, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 10}
# libraries
set.seed(123)
library(tidyverse)

# creating a list of plots
p_list <- mtcars %>%
  dplyr::filter(.data = ., cyl != 4) %>%
  dplyr::group_by(.data = ., cyl) %>%
  dplyr::group_map(
    .data = .,
    .f = ~ ggstatsplot::ggbetweenstats(
    data = .,
    x = am,
    y = wt,
    messages = FALSE
  ))

# combining plots
cowplot::plot_grid(
  plotlist = p_list,
  labels = rlang::set_names(levels(as.factor(mtcars$cyl)))
)
```


## Combining multiple plots: Example-2 using `purrr`

The full power of `ggstatsplot` can be leveraged with a functional programming
package like [`purrr`](http://purrr.tidyverse.org/) which can replace many `for`
loops, is more succinct, and easier to read. Consider `purrr` as your first
choice for combining multiple plots.

An example using the `iris` dataset is provided below.  Imagine that we want to
separately plot the linear relationship between sepal length and sepal width for
each of the three species but combine them into one consistent plot with common
labeling and as one plot.  Rather than call `ggscatterstats` three times and
gluing the results or using `cowplot` directly, we'll create a `tibble` called
`plots` using `purrr::map` then feed that to `combine_plots` to get our combined
plot.

```{r ggscatterstats_purrr, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 8}
library(ggstatsplot)

# for reproducibility
set.seed(123)

# creating a list column with `ggstatsplot` plots
plots <- iris %>%
  dplyr::mutate(.data = ., Species2 = Species) %>% # just creates a copy of this variable
  dplyr::group_by(.data = ., Species) %>%
  tidyr::nest(.) %>% # a nested dataframe with list column called `data`
  dplyr::mutate( # creating a new list column of ggstatsplot outputs
    .data = .,
    plot = data %>%
      purrr::map(
        .x = .,
        .f = ~ ggstatsplot::ggscatterstats(
          data = .,
          x = Sepal.Length,
          y = Sepal.Width,
          xfill = "#0072B2",
          yfill = "#009E73",
          ggtheme = ggthemes::theme_fivethirtyeight(),
          ggstatsplot.layer = FALSE,
          messages = FALSE, # turns off warnings and notes messages
          marginal.type = "boxplot",
          title =
            glue::glue("Species: {.$Species2} (n = {length(.$Sepal.Length)})")
        )
      )
  )

# display the new object (notice that the class of the `plot` list column is
# S3: ggExtraPlot)
plots

# creating a grid with cowplot
ggstatsplot::combine_plots(
  plotlist = plots$plot, # list column containing all ggstatsplot objects
  nrow = 3,
  ncol = 1,
  title.text = "Relationship between sepal length and width for each Iris species",
  title.size = 14,
  caption.text = expression(
    paste(
      italic("Note"),
      ": Iris flower dataset was collected by Edgar Anderson.",
      sep = ""
    ),
    caption.size = 12
  )
)
```

## Combining multiple plots: Example-3 with `plyr`

Another popular package for handling big datasets is `plyr`, which allows us to
repeatedly apply a common function on smaller pieces and then combine the
results into a larger whole.

In this example we'll start with the `gapminder` dataset.  We're interested in
the linear relationship between Gross Domestic Product (per capita) and life
expectancy in the year 2007, for all the continents except Oceania. We'll use
`dplyr` to filter to the right rows then use `plyr` to repeat the
`ggscatterstats` function across each of the 4 continents remaining.  The result
is of that is a list of plots called `plots`.  We then feed `plots` to the
`combine_plots` function to merge them into one plot. We will call attention to
the countries which have very low life expectancy (< 45 years) by labeling those
countries when they occur.

```{r ggscatterstats_plyr, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}
library(plyr)
library(gapminder)

# for reproducibility
set.seed(123)

# let's have a look at the structure of the data
dplyr::glimpse(gapminder::gapminder)

# creating a list of plots
plots <- plyr::dlply(
  .data = dplyr::filter(
    gapminder::gapminder,
    year == 2007, continent != "Oceania"
  ),
  .variables = .(continent),
  .fun = function(data) {
    ggstatsplot::ggscatterstats(
      data = data,
      x = gdpPercap,
      y = lifeExp,
      xfill = "#0072B2",
      yfill = "#009E73",
      label.var = "country",
      label.expression = "lifeExp < 45",
      title = glue::glue("Continent: {data$continent}"),
      marginal = FALSE
    ) +
      ggplot2::scale_x_continuous(labels = scales::comma)
  }
)

# combining individual plots
ggstatsplot::combine_plots(
  plotlist = plots,
  title.text = "Relationship between GDP (per capita) and life expectancy",
  nrow = 2
)
```

# Adding additional details to plots

The `combine_plots` function can also be useful for adding additional textual
information that can not be added by making a single call to a `ggstatsplot`
function via the title, subtitle, or caption options. For this example let's
assume we want to assess the relationship between a movie's rating and its
budget from the **Internet Movie Database** using polynomial regression.

`ggcoefstats` will do most of the work, including the title, subtitle, and
caption. But we want to add at the bottom an annotation to show the formula we
are using for our regression.  `combine_plots` allows us to add `sub.text =` to
accomplish that task as shown in the resulting plot.

```{r ggbetweenstats_subtext, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 8}
library(ggstatsplot)

ggstatsplot::combine_plots(
  # preparing the plot with ggstatsplot function
  # let's use only 20% of data to speed up the process
  ggstatsplot::ggcoefstats(
    x = stats::lm(
      formula = rating ~ stats::poly(budget, degree = 3),
      data = dplyr::sample_frac(tbl = ggstatsplot::movies_long, size = 0.2),
      na.action = na.omit
    ),
    exclude.intercept = FALSE,
    title = "Relationship between movie budget and IMDB rating",
    subtitle = "Source: Internet Movie Database",
    ggtheme = ggplot2::theme_gray(),
    stats.label.color = c("#CC79A7", "darkgreen", "#0072B2", "red")
  ) +
    # modifying the plot outside of ggstatsplot using ggplot2 functions
    ggplot2::scale_y_discrete(
      labels = c(
        "Intercept (c)",
        "1st degree (b1)",
        "2nd degree (b2)",
        "3rd degree (b3)"
      )
    ) +
    ggplot2::labs(y = "term (polynomial regression)"),
  # adding additional text element to the plot since title, subtitle, caption are all already occupied
  sub.text = expression(
    paste(
      "linear model: ", bolditalic(y),
      " ~ ",
      italic(c) + italic(b)[1] * bolditalic(x) + italic(b)[2] * bolditalic(x)^
        2 + italic(b)[3] * bolditalic(x)^3,
      sep = ""
    )
  ),
  sub.size = 12
)
```

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on `GitHub`: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>
