---
title: "Frequently Asked Questions (FAQ)"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Frequently Asked Questions (FAQ)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE

source("../setup.R")
```

```{r}
#| label = "suggested_pkgs",
#| include = FALSE

pkgs <- "PMCMRplus"

successfully_loaded <- purrr::map_lgl(pkgs, requireNamespace, quietly = TRUE)
can_evaluate <- all(successfully_loaded)

if (can_evaluate) {
  purrr::walk(pkgs, library, character.only = TRUE)
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

<!-- Give every question an explicit, stable anchor ID so that links to it -->
<!-- survive rewording, reordering, and adding or removing other questions. -->

---

Following are a few of the common questions asked in GitHub issues and on social
media platforms.

## Statistical details {#statistical-details}

### I just want the plot, not the statistical details. How can I turn them off? {#turn-off-details}

All functions in `{ggstatsplot}` that display results from statistical analysis in
a subtitle have argument `results.subtitle`. Setting it to `FALSE` will return
only the plot.

For parametric tests, the Bayes Factor shown in the caption is controlled
separately by the `bf.message` argument. Set it to `FALSE` to drop the caption:

```{r}
#| label = "no_caption"

ggbetweenstats(mtcars, am, mpg, bf.message = FALSE)
```

Your own `subtitle` text is used only when `results.subtitle = FALSE`.

### Why do I get only the plot but not the subtitle/caption? {#missing-subtitle}

In order to prevent the entire plotting function from failing when statistical
analysis fails, functions in `{ggstatsplot}` default to first attempting to run
the analysis and if they fail, then return empty (`NULL`) subtitle/caption. In
such cases, if you wish to diagnose why the analysis is failing, you will have
to do so using the underlying function used to carry out statistical analysis.

For example, the following returns only the plot but not the statistical details
in a subtitle or caption, because the outcome is constant within each group.

```{r}
#| label = "null_subtitle"

df <- data.frame(x = c("a", "a", "b", "b"), y = c(1, 1, 2, 2))
ggbetweenstats(df, x, y)
```

To see why the statistical analysis failed, you can look at the error from the
underlying function:

```{r}
#| label = "null_subtitle_error",
#| error = TRUE

library(statsExpressions)
two_sample_test(df, x, y)
```

### What statistical test was carried out? {#which-test}

In case you are not sure what was the statistical test that produced the results
shown in the subtitle of the plot, the best way to get that information is to
either look at the documentation for the function used or check out the
associated vignette.

All statistical analyses are carried out by `{statsExpressions}`, and a summary
of every supported test and effect size is available in its
[documentation](https://www.indrapatil.com/statsExpressions/articles/stats_details.html).

You can also check the `method` column of the data frames returned by
`extract_stats()` (see [below](#extract-stats)).

### How can I access the data frames with the statistical results? {#extract-stats}

`{ggstatsplot}` displays expressions in the subtitle and caption, but you can
get back the underlying data frames with the `extract_stats()` helper function.
It returns a list with the following components (`NULL` when not relevant for a
given plot): `subtitle_data`, `caption_data`, `pairwise_comparisons_data`,
`descriptive_data`, `one_sample_data`, `tidy_data`, and `glance_data`.

```{r}
#| label = "extract_stats"

p <- ggbetweenstats(mtcars, cyl, wt)

# data frame with results from pairwise comparisons
extract_stats(p)$pairwise_comparisons_data
```

For `grouped_` plots, `extract_stats()` returns one such list per group.
`extract_subtitle()` and `extract_caption()` return just the expressions.

If you only need the results and not the plot, you can call the functions from
the source package `{statsExpressions}` directly (see
[examples](https://www.indrapatil.com/statsExpressions/articles/web_only/dataframe_outputs.html)).

### Does `{ggstatsplot}` carry out assumption checks? {#assumption-checks}

No, `{ggstatsplot}` does not carry out any analysis of whether assumptions are
met or not. It will just carry out whatever test you ask it to carry out.

To check these assumptions, you can use a different package called
[`{performance}`](https://easystats.github.io/performance/reference/index.html#check-model-assumptions-or-data-properties).

### How are missing values handled? {#missing-values}

Rows with missing values (`NA`) in the variables of interest are removed before
the analysis, and the subtitle reports the sample size that was actually used.
Other columns in the data are ignored.

- In `ggwithinstats()`, specify `subject.id`: any subject with a missing value
  in *any* condition is then excluded from the statistical analysis, so that
  only complete pairs are analyzed (the subtitle reports
  *n*<sub>pairs</sub>). The subject's non-missing observations are still
  shown in the plot.
- In `ggcorrmat()`, missing values are removed separately for each pair of
  variables, and the legend shows the minimum, mode, and maximum sample sizes
  across pairs.
- In `grouped_` functions, rows with missing values in `grouping.var` are
  dropped.

```{r}
#| label = "missing_values"

# 5 of the 93 subjects in `bugs_long` have a missing value, so n_pairs = 88
ggwithinstats(bugs_long, condition, desire, subject.id = subject)
```

### Is there a way to adjust my alpha level? {#alpha-level}

Within a single plot, some functions let you choose the cutoff used to decide
what is displayed as significant:

- `pairwise.alpha` in `ggbetweenstats()` and `ggwithinstats()` (together with
  `p.adjust.method` for multiple comparisons correction).
- `sig.level` in `ggcorrmat()`.
- `conf.level` (in all functions) sets the width of the confidence intervals.

But there is no way to adjust alpha *across* the plots produced by `grouped_`
functions, since each group is analyzed independently. You will have to report
the adjusted alpha yourself (e.g., with 2 tests, only consider `p < 0.025` as
significant).

### The statistical analysis I want to carry out is not available. What can I do? {#custom-test}

Since `{ggstatsplot}` always allows just **one** type of test per statistical
approach, sometimes your favorite test might not be available. For
example, `{ggstatsplot}` provides only Spearman's $\rho$, but not Kendall's
$\tau$ as a non-parametric correlation test.

In such cases, you can override the defaults and use `{statsExpressions}` to
create custom expressions to display in the plot. But be forewarned that the
expression building function in `{statsExpressions}` is not stable yet.

```{r}
#| label = "custom_test",
#| fig.width = 6,
#| fig.height = 6

library(correlation)
library(statsExpressions)
library(ggplot2)

# data with two variables of interest
df <- dplyr::select(mtcars, wt, mpg)

# correlation results
results <- correlation(df, method = "kendall") |>
  insight::standardize_names(style = "broom")

# creating expression out of these results
df_results <- statsExpressions::add_expression_col(
  data           = results,
  no.parameters  = 0L,
  statistic.text = list(quote(italic("T"))),
  effsize.text   = list(quote(widehat(italic(tau))["Kendall"])),
  n              = results$n.obs[[1]]
)

# using custom expression in plot
ggscatterstats(df, wt, mpg, results.subtitle = FALSE) +
  labs(subtitle = df_results$expression[[1]])
```

### How should I cite and report the results? {#cite-report}

You can cite the package with `citation("ggstatsplot")` (see top of this
article). For reporting, the expressions shown in the plots follow a standard
template (see the
[principles article](https://www.indrapatil.com/ggstatsplot/articles/web_only/principles.html#statistical-reporting)),
and all numbers can be retrieved as data frames with
[`extract_stats()`](#extract-stats). For interpreting logged Bayes Factors, see
[this article](https://www.indrapatil.com/ggstatsplot/articles/web_only/interpretation.html).

## Subtitle and caption {#subtitle-caption}

### How can I customize the details contained in the subtitle? {#custom-subtitle}

Sometimes you may not wish to include so many details in the subtitle. In that
case, you can extract the expression and copy-paste only the part you wish to
include. For example, here only statistic and *p*-values are included:

```{r}
#| label = "custom_expr"

library(ggplot2)
library(statsExpressions)

# extracting detailed expression
data_results <- oneway_anova(iris, Species, Sepal.Length)
data_results$expression[[1]]

# adapting the details to your liking
ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot() +
  labs(subtitle = ggplot2::expr(paste(
    italic("F"), "(", "2", ",", "147", ")=", "119.26", ", ",
    italic("p"), "<", "0.001"
  )))
```

The extracted expression can also be put on any other plot with
`labs(subtitle = extract_subtitle(p))`.

### How can I change the size or position of the subtitle? {#subtitle-style}

The statistical results appear as a standard `{ggplot2}` subtitle (and,
when Bayes Factor is shown, as a caption). You can restyle and reposition them
using `theme()` via the `ggplot.component` argument:

```{r}
#| label = "subtitle_style",
#| fig.width = 7,
#| fig.height = 5

library(ggplot2)

ggbetweenstats(
  mtcars, am, mpg,
  ggplot.component = list(
    theme(
      plot.subtitle = element_text(size = 10, face = "bold", hjust = 0),
      plot.caption = element_text(size = 8, hjust = 0)
    )
  )
)
```

### How can I turn off scientific notation in expressions? {#scientific-notation}

Increase the number of digits with the `digits` argument. Note that very small
*p*-values can still be shown in scientific notation if they would otherwise be
rounded to zero.

```{r}
#| label = "digits"

library(WRS2)

ggwithinstats(
  WineTasting,
  Wine,
  Taste,
  subject.id = Taster,
  digits = 4L
)
```

## Pairwise comparisons {#pairwise-comparisons}

### How can I show only some of the pairwise comparisons? {#custom-pairwise}

Currently, for `ggbetweenstats` and `ggwithinstats`, you can either display all
**significant** comparisons, all **non-significant** comparisons, or **all**
comparisons. But what if I am only interested in just one particular comparison?

Here is a workaround using `{ggsignif}`:

```{r}
#| label = "custom_pairwise",
#| fig.width = 7,
#| fig.height = 6

library(ggsignif)

ggbetweenstats(mtcars, cyl, wt, pairwise.display = "none") +
  geom_signif(comparisons = list(c("4", "6")), test.args = list(exact = FALSE))
```

### How can I change the annotation in pairwise comparisons? {#pairwise-annotation}

`{ggstatsplot}` defaults to displaying exact *p*-values or logged Bayes Factor
values for pairwise comparisons. But what if you wish to adopt different
annotation labels, such as asterisks? You will have to customize them yourself:

```{r}
#| label = "comp_asterisks"

library(ggplot2)
library(ggsignif)

# converting to factor
mtcars$cyl <- as.factor(mtcars$cyl)

# creating the base plot
p <- ggbetweenstats(mtcars, cyl, wt, pairwise.display = "none")

# using `statsExpressions::pairwise_comparisons()` function to create a data frame with results
df <- statsExpressions::pairwise_comparisons(mtcars, cyl, wt) |>
  dplyr::mutate(groups = purrr::pmap(.l = list(group1, group2), .f = c)) |>
  dplyr::arrange(group1) |>
  dplyr::mutate(asterisk_label = dplyr::case_when(
    p.value < 0.001 ~ "***",
    p.value < 0.01 ~ "**",
    p.value < 0.05 ~ "*",
    .default = "ns"
  ))

df

# adding pairwise comparisons using `{ggsignif}` package
p +
  ggsignif::geom_signif(
    comparisons = df$groups,
    map_signif_level = TRUE,
    annotations = df$asterisk_label,
    y_position = c(5.5, 5.75, 6.0),
    test = NULL,
    na.rm = TRUE
  )
```

### Why do pairwise comparison brackets disappear when I restrict the Y-axis? {#brackets-disappear}

This is a common `{ggplot2}` footgun. There are two ways to restrict the visible
y-range, and they behave very differently:

- `scale_y_continuous(limits = c(a, b))` — **modifies the data**, setting any
  values outside `[a, b]` to `NA` before rendering. Because pairwise comparison
  brackets from `{ggsignif}` are positioned *above* the maximum observed value,
  they often fall outside a tight limit and are silently dropped.
- `coord_cartesian(ylim = c(a, b))` — **zooms the viewport** without touching
  the underlying data. The brackets are still computed from the full data range
  and remain fully intact.

The fix is to replace `scale_y_continuous(limits = ...)` with
`coord_cartesian(ylim = ...)`:

```{r}
#| label = "coord_cartesian_pairwise",
#| fig.width = 7,
#| fig.height = 6

library(ggplot2)

ggbetweenstats(mtcars, cyl, wt) +
  coord_cartesian(ylim = c(1, 4))
```

## Plot appearance {#plot-appearance}

### How can I change the theme, color palette, or colors? {#theme-palette}

Use the `ggtheme` argument to supply any `{ggplot2}` theme (the default is
`theme_ggstatsplot()`), and the `palette` argument to choose any discrete
palette from `{paletteer}` in the `"package::palette"` format. Run
`View(paletteer::palettes_d_names)` to see all available palettes.

```{r}
#| label = "theme_palette"

ggbetweenstats(
  mtcars,
  cyl,
  wt,
  ggtheme = ggplot2::theme_classic(),
  palette = "ggsci::nrc_npg"
)
```

The palette must have at least as many colors as there are levels in the
grouping variable; otherwise an error is thrown. `ggscatterstats()`,
`gghistostats()`, `ggdotplotstats()`, and `ggcorrmat()` don't have a `palette`
argument; use the relevant `*.args` arguments (or `colors` in `ggcorrmat()`)
instead.

If none of the palettes suit you, specify the colors manually with the usual
`{ggplot2}` scales:

```{r}
#| label = "manual_colors"

library(ggplot2)

ggbarstats(mtcars, am, cyl, results.subtitle = FALSE) +
  scale_fill_manual(values = c("#E7298A", "#66A61E"))
```

### How can I remove a particular `geom` layer from the plot? {#remove-layer}

Sometimes you may not want a particular `geom` layer to be displayed. You can
remove it by setting transparency (`alpha`) for that layer to 0 via the
corresponding `*.args` argument. For example, to remove the points from a
`ggwithinstats()` plot:

```{r}
#| label = "geom_removal",
#| fig.width = 7,
#| fig.height = 5

ggwithinstats(
  data = bugs_long,
  x = condition,
  y = desire,
  subject.id = subject,
  point.args = list(alpha = 0),
  results.subtitle = FALSE,
  pairwise.display = "none"
)
```

The same works for other layers, e.g. `sample.size.label.args = list(alpha = 0)`
removes the sample size labels in `ggbarstats()`.

## `grouped_` functions and programmatic use {#grouped-functions}

### How can I modify `grouped_` outputs using `{ggplot2}` functions? {#grouped-modify}

All `{ggstatsplot}` plots are `ggplot` objects, which can be further modified,
just like any other `ggplot` object. The exception is plots returned by
`grouped_` functions, which are `{patchwork}` objects combining several plots.
To modify each of the individual plots, use the `ggplot.component` argument
(present in all functions except `ggcoefstats()`). For example, this gives all
plots the same color scale and Y-axis range:

```{r}
#| label = "grouped_modify"

library(ggplot2)

grouped_ggbetweenstats(
  mtcars,
  cyl,
  wt,
  grouping.var = am,
  results.subtitle = FALSE,
  pairwise.display = "none",
  ggplot.component = list(
    scale_color_manual(values = paletteer::paletteer_c("viridis::viridis", 3)),
    scale_y_continuous(limits = c(1, 6))
  ),
  # arguments given to `{patchwork}` for annotating the combined plot
  annotation.args = list(
    title = "Weight by number of cylinders",
    theme = theme(plot.title = element_text(size = 20))
  )
)
```

Alternatively, `{patchwork}`'s `&` operator applies a `{ggplot2}` component to
all plots in a `grouped_` output:

```{r}
#| label = "grouped_modify_patchwork",
#| eval = FALSE

grouped_ggbetweenstats(mtcars, cyl, wt, grouping.var = am) &
  theme(axis.text.x = element_text(angle = 90))
```

### How can I go beyond what `grouped_` functions support? {#beyond-grouped}

The `grouped_` functions only repeat the analysis across a _single_ grouping
variable, and they don't let you create group-specific titles or subtitles.
For anything else, split the data yourself, create one plot per group with
`{purrr}`, and combine them with `combine_plots()` (see also
[this article](https://www.indrapatil.com/ggstatsplot/articles/web_only/purrr_examples.html)).
For example, to repeat the analysis across two grouping variables with a
title for each group:

```{r}
#| label = "beyond_grouped",
#| fig.width = 8,
#| fig.height = 8

ggplot2::mpg |>
  dplyr::filter(drv %in% c("4", "f"), fl %in% c("p", "r")) |>
  (\(d) split(d, f = list(d$drv, d$fl), drop = TRUE))() |>
  purrr::imap(\(data, group) {
    ggscatterstats(
      data = data,
      x = displ,
      y = hwy,
      title = paste0("Drive and fuel type: ", group),
      results.subtitle = FALSE
    )
  }) |>
  combine_plots(plotgrid.args = list(nrow = 2L))
```

### How can I use `{ggstatsplot}` functions in a `for` loop? {#for-loop}

Given that all functions in `{ggstatsplot}` use tidy evaluation, running these
functions in a `for` loop requires minor adjustment to how inputs are entered:

```{r}
#| label = "loop",
#| eval = FALSE

col.name <- colnames(mtcars)
plot_list <- list()

# executing the function in a `for` loop
for (i in 3:length(col.name)) {
  plot_list[[col.name[i]]] <- ggbetweenstats(
    data = mtcars,
    x = cyl,
    y = !!col.name[i]
  )
}
```

Note that plots created inside a `for` loop are not printed automatically;
either store them (as above) or wrap the call in `print()`.

That said, if repeating function execution across multiple columns in a
data frame is what you want to do, I will recommend a
[`{purrr}`-based solution](https://www.indrapatil.com/ggstatsplot/articles/web_only/purrr_examples.html#repeating-function-execution-across-multiple-columns-in-a-data-frame).

This solution would work for `x` and `y` arguments, but not for the
`grouping.var` argument, which first needs to be converted to a symbol:

```{r}
#| label = "tidyeval-grouping-var",
#| eval = FALSE

df <- dplyr::filter(movies_long, genre == "Comedy" | genre == "Drama")

grouped_ggscatterstats(
  data = df,
  x = !!colnames(df)[3],
  y = !!colnames(df)[5],
  grouping.var = !!rlang::sym(colnames(df)[8]),
  results.subtitle = FALSE
)
```

## Suggestions {#suggestions}

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
