---
title: "Frequently asked questions"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{Frequently asked questions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
# show me all columns
options(tibble.width = Inf, pillar.bold = TRUE, pillar.subtle_num = TRUE)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  warning = FALSE,
  message = FALSE,
  out.width = "100%",
  comment = "#>"
)
```

Here are some of the common questions that have been asked in GitHub issues and
on social media platforms.  

# I just want the plot, not the statistical details. How can I turn them off?

All functions in `ggstatsplot` that display results from statistical analysis in
a subtitle have argument `results.subtitle`. Setting it to `FALSE` will return
only the plot.

# How can I customize the details contained in the subtitle?

Sometimes you may not wish include so many details in the subtitle. In that
case, you can extract the expression and copy-paste only the part you wish to
include. For example, here only statistic and *p*-values are included:

```{r custom_expr}
# setup
set.seed(123)
library(ggstatsplot)
library(ggplot2)
library(statsExpressions)

# extracting detailed expression
(res_expr <- expr_anova_parametric(iris, Species, Sepal.Length, var.equal = TRUE))

# adapting the details to your liking
ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot() +
  labs(subtitle = ggplot2::expr(paste(
    NULL, italic("F"), "(", "2",
    ",", "147", ") = ", "119.26", ", ",
    italic("p"), " = ", "1.67e-31"
  )))
```

# I am getting `Error in grid.Call` error

Sometimes, if you are working in `RStudio`, you might see the following error-

```r
Error in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, :
polygon edge not found
```

There is no unique solution for this. Just Google this error and see if any of
those solutions solve your problem.

If not, pray to the old and the new gods, and try again. It might just solve
your problem. `r emo::ji("shrug")`

# What statistical test was carried out?

In case you are not sure what was the statistical test that produced the results
shown in the subtitle of the plot, the best way to get that information is to
either look at the documentation for the function used or check out the
associated vignette. 

Summary of all analysis is handily available in `README`: 
<https://github.com/IndrajeetPatil/ggstatsplot/blob/master/README.md>

# How can I use `ggstatsplot` functions in a `for` loop?

Given that all functions in `ggstatsplot` use tidy evaluation, running these
functions in a `for` loop requires minor adjustment to how inputs are entered:

```{r loop, eval=FALSE}
# setup
data(mtcars)
library(ggstatsplot)
col.name <- colnames(mtcars)

# executing the function in a `for` loop
for (i in 3:length(col.name)) {
  ggbetweenstats(
    data = mtcars,
    x = cyl,
    y = !!col.name[i]
  )
}
```

That said, if repeating function execution across multiple columns in a
dataframe in what you want to do, I will recommend you to have a look at
`purrr`-based solution:

<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html#repeating-function-execution-across-multiple-columns-in-a-dataframe-1>

# How can I have uniform Y-axes ranges in `grouped_` functions?

```{r grouped_y_axes, fig.height=10, fig.width=8}
# setup
set.seed(123)
library(ggstatsplot)

combine_plots2(
  list(
  # with unequal Y-axes ranges
  grouped_ggscatterstats(
    mtcars,
    disp,
    hp,
    grouping.var = am,
    results.subtitle = FALSE,
    title.text = "before"
  ),
  # with equal Y-axes ranges
  grouped_ggscatterstats(
    mtcars,
    disp,
    hp,
    grouping.var = am,
    results.subtitle = FALSE,
    ggplot.component =
      list(ggplot2::scale_y_continuous(breaks = seq(50, 350, 50), limits = (c(50, 350)))),
    title.text = "after"
  )),
  plotgrid.args = list(nrow = 2)
)
```

# Does `ggstatsplot` work with `plotly`?

The `plotly` R graphing library makes it easy to produce interactive web
graphics via `plotly.js`. 

The `ggstatsplot` functions are compatible with `plotly`.
 
```{r plotly, fig.width = 4, fig.height = 4}
# for reproducibility
set.seed(123)
library(ggstatsplot)
library(plotly)

# creating ggplot object with `ggstatsplot`
p <-
  ggstatsplot::ggbetweenstats(
    data = mtcars,
    x = cyl,
    y = mpg
  )

# converting to plotly object
plotly::ggplotly(p, width = 480, height = 480)
```

# How can I use `grouped_` functions with more than one group?

Currently, the `grouped_` variants of functions only support repeating the
analysis across a _single_ grouping variable. Often, you have to run the same
analysis across a combination of more than two grouping variables. This can be
easily achieved using `purrr` package. 

Here is an example-

```{r grouped_2, fig.width = 6, fig.height = 6}
# setup
set.seed(123)
library(ggstatsplot)

# creating a list by splitting dataframe by combination of two different
# grouping variables
df_list <-
  mpg %>%
  dplyr::filter(drv %in% c("4", "f"), fl %in% c("p", "r")) %>%
  split(x = ., f = list(.$drv, .$fl), drop = TRUE)

# checking if the length of the list is 4
length(df_list)

# running correlation analyses between
# this will return a *list* of plots
plot_list <-
  purrr::pmap(
    .l = list(
      data = df_list,
      x = "displ",
      y = "hwy",
      results.subtitle = FALSE,
      marginal.type = "densigram"
    ),
    .f = ggstatsplot::ggscatterstats
  )

# arragen the list in a single plot
ggstatsplot::combine_plots(
  plotlist = plot_list,
  nrow = 2,
  labels = c("(i)", "(ii)", "(iii)", "(iv)")
)
```

# How can I include statistical expressions in facet labels?

```{r facet_expr, fig.width = 6, fig.height = 8}
set.seed(123)
library(ggplot2)
library(ggstatsplot)

# data
mtcars1 <- mtcars
statistics <-
  grouped_ggbetweenstats(
    data = mtcars1,
    x = cyl,
    y = mpg,
    grouping.var = am,
    output = "subtitle"
  )
mtcars1$am <- factor(mtcars1$am, levels = c(0, 1), labels = statistics)

# plot
mtcars1 %>%
  ggplot(aes(x = cyl, y = mpg)) +
  geom_jitter() +
  facet_wrap(
    vars(am),
    ncol = 1,
    strip.position = "top",
    labeller = ggplot2::label_parsed
  )
```

# Can you customize which pairs are shown in pairwise comparisons?

Currently, for `ggbetweenstats` and `ggwithinstats`, you can either display all
**significant** comparisons, all **non-significant** comparisons, or **all**
comparisons. But what if I am only interested in just one particular comparison?

Here is a workaround using `ggsignif`:

```{r custom_pairwise, fig.width = 7, fig.height = 6}
set.seed(123)
library(ggstatsplot)
library(ggsignif)

# displaying only one comparison
ggbetweenstats(mtcars, cyl, wt, pairwise.comparisons = FALSE) +
  geom_signif(comparisons = list(c("4", "6")))
```

# How to access dataframe with results from pairwise comparisons?

```{r}
library(ggstatsplot)
library(ggplot2)

# way-1

p <- ggbetweenstats(mtcars, cyl, wt)

pb <- ggplot_build(p)

pb$plot$plot_env$df_pairwise

# way-2

library(pairwiseComparisons)

pairwise_comparisons(mtcars, cyl, wt)
```

# How to access dataframe with results from `ggpiestats` and `ggbarstats`?

```{r proptest_df}
# setup
set.seed(123)
library(ggplot2)

# plot
p <- ggpiestats(mtcars, am, cyl)

# build ggplot object
pb <- ggplot2::ggplot_build(p)

# dataframe with proportion test results
pb$plot$plot_env$df_proptest

# dataframe with counts and proportions details
pb$plot$plot_env$df_descriptive
```

# How can I remove a a particular `geom` layer from the plot?

Sometimes you may not want a particular `geom` layer to be displayed. You can
remove them using `gginnards`. 

For example, let's say we want to remove the `geom_point()` from
`ggwithinstats` default plot.

```{r gginnards, fig.width = 7, fig.height = 5}
# needed libraries
library(ggstatsplot)
library(gginnards)

# plot with all geoms
p <-
  ggwithinstats(
    data = bugs_long,
    x = condition,
    y = desire,
    results.subtitle = FALSE,
    pairwise.comparisons = FALSE
  )

# delete `geom` corresponding to violin
gginnards::delete_layers(x = p, match_type = "GeomViolin")
```

This can be helpful to add a new layer with aesthetic specifications of your
liking.

```{r gginnards2, fig.width = 7, fig.height = 5}
# needed libraries
set.seed(123)
library(ggstatsplot)
library(gginnards)
library(ggplot2)

# basic plot without mean tagging
p <-
  ggwithinstats(
    data = bugs_long,
    x = condition,
    y = desire,
    mean.plotting = FALSE
  )

# delete the geom_point layer
p <- gginnards::delete_layers(x = p, match_type = "GeomPoint")

# add a new layers for points with a different shape
p + geom_point(shape = 23, aes(color = condition))
```

# How can I modify the fill colors with custom values?

Sometimes you may not be satisfied with the available color palette values. In
this case, you can also change the colors by manually specifying these values.

```{r ggbar_colors, fig.width = 6, fig.height = 6}
# needed libraries
set.seed(123)
library(ggstatsplot)
library(ggplot2)

ggbarstats(mtcars, am, cyl, results.subtitle = FALSE) +
  scale_fill_manual(values = c("#E7298A", "#66A61E"))
```

The same can also be done for `grouped_` functions:

```{r ggpie_colors, fig.width = 12, fig.height = 6}
ggstatsplot::grouped_ggpiestats(
  data = mtcars,
  grouping.var = am,
  x = cyl,
  ggplot.component = ggplot2::scale_fill_grey()
)
```

# How can I modify `grouped_` outputs using `ggplot2` functions?

All `ggstatsplot` are `ggplot` objects, which can be further modified, just like
any other `ggplot` object. But exception to these are all plots returned by
`grouped_` functions, but there is a way to tackle this.

```{r grouped_modify, fig.width = 12, fig.height = 6}
# needed libraries
set.seed(123)
library(ggstatsplot)
library(paletteer)
library(ggplot2)
library(palmerpenguins)

# plot
grouped_ggbetweenstats(
  penguins,
  species,
  body_mass_g,
  grouping.var = sex,
  type = "np",
  ggplot.component =
    # modify further with `ggplot2` functions
  list(
    scale_color_manual(values = paletteer::paletteer_c("viridis::viridis", 3)),
    theme(axis.text.x = element_text(angle = 90))
  )
)
```

# How can I extract dataframe containing results from `ggstatsplot`?

`ggstatsplot` can return expressions in the subtitle and caption, but what if
you want to actually get back dataframe containing the results?

This is possible via `statsExpressions`:
<https://indrajeetpatil.github.io/statsExpressions/articles/dataframe_outputs.html>

# Test I need is not available. What can I do?

By default, since `ggstatsplot` always allows just **one** type of test per
statistical approach, sometimes your favorite test might not be available. For
example, `ggstatsplot` provides only Spearman's $\rho$, but not Kendall's
$\tau$ as a non-parametric correlation test. 

In such cases, you can override the defaults and use `statsExpressions` to
create custom expressions to display in the plot.

```{r custom_test, fig.width = 5, fig.height = 5}
# setup
set.seed(123)
library(ggstatsplot)
library(correlation)
library(statsExpressions)
library(ggplot2)

# data with two variables of interest
df <- dplyr::select(mtcars, wt, mpg)

# correlation results
results <-
  correlation(df, method = "kendall") %>%
  parameters::standardize_names(., "broom")

# creating expression out of these results
expr_results <-
  statsExpressions::expr_template(
    no.parameters = 0L,
    statistic.text = quote(italic("T")),
    effsize.text = quote(widehat(italic(tau))["Kendall"]),
    stats.df = results,
    n = results$n.obs[[1]]
  )

# plot (overriding defaults and using custom expression)
ggscatterstats(
  df, wt, mpg,
  results.subtitle = FALSE,
  ggplot.component = list(labs(subtitle = expr_results))
)
```

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>
