---
title: "Frequently asked questions"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{Frequently asked questions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  dpi = 300,
  out.width = "100%",
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)
```

# FAQ

Here are some of the common questions that have been asked in GitHub issues and
on social media platforms.  

## I just want the plot, not the statistical details. How can I turn them off?

All functions in `ggstatsplot` that display results from statistical analysis in
a subtitle have argument `results.subtitle`. Setting it to `FALSE` will return
only the plot.

## How can I customize the details contained in the subtitle?

Sometimes you may not wish include so many details in the subtitle. In that
case, you can extract the expression and copy-paste only the part you wish to
include. For example, here only statistic and *p*-values are included:

```{r custom_expr}
# setup
set.seed(123)
library(ggplot2)
library(statsExpressions)

# extracting detailed expression
(res_expr <- expr_anova_parametric(iris, Species, Sepal.Length, var.equal = TRUE))

# adapting the details to your liking
ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot() +
  labs(subtitle = ggplot2::expr(paste(
    NULL, italic("F"), "(", "2",
    ",", "147", ") = ", "119.26", ", ",
    italic("p"), " = ", "1.67e-31"
  )))
```

## What statistical test was carried out?

In case you are not sure what was the statistical test that produced the results
shown in the subtitle of the plot, the best way to get that information is to
either look at the documentation for the function used or check out the
associated vignette. 

Summary table: 
<https://indrajeetpatil.github.io/statsExpressions/articles/stats_details.html>

## Does `ggstatsplot` work with `plotly`?

The `plotly` R graphing library makes it easy to produce interactive web
graphics via `plotly.js`. 

The `ggstatsplot` functions are compatible with `plotly`.
 
```{r plotly, fig.width = 4, fig.height = 4}
# for reproducibility
set.seed(123)
library(ggstatsplot)
library(plotly)

# creating ggplot object with `ggstatsplot`
p <-
  ggstatsplot::ggbetweenstats(
    data = mtcars,
    x = cyl,
    y = mpg
  )

# converting to plotly object
plotly::ggplotly(p, width = 480, height = 480)
```

## How can I use `grouped_` functions with more than one group?

Currently, the `grouped_` variants of functions only support repeating the
analysis across a _single_ grouping variable. Often, you have to run the same
analysis across a combination of more than two grouping variables. This can be
easily achieved using `purrr` package. 

Here is an example-

```{r grouped_2, fig.width = 6, fig.height = 6}
# setup
set.seed(123)
library(tidyverse, warn.conflicts = FALSE)
library(ggstatsplot)

# creating a list by splitting dataframe by combination of two different
# grouping variables
df_list <-
  mpg %>%
  dplyr::filter(drv %in% c("4", "f"), fl %in% c("p", "r")) %>%
  split(x = ., f = list(.$drv, .$fl), drop = TRUE)

# checking if the length of the list is 4
length(df_list)

# running correlation analyses between
# this will return a *list* of plots
plot_list <-
  purrr::pmap(
    .l = list(
      data = df_list,
      x = "displ",
      y = "hwy",
      results.subtitle = FALSE,
      marginal.type = "densigram"
    ),
    .f = ggstatsplot::ggscatterstats
  )

# arragen the list in a single plot
ggstatsplot::combine_plots(
  plotlist = plot_list,
  nrow = 2,
  labels = c("(i)", "(ii)", "(iii)", "(iv)")
)
```

## How can I include statistical expressions in facet labels?

```{r facet_expr, fig.width = 6, fig.height = 8}
set.seed(123)
library(ggplot2)
library(ggstatsplot)

# data
mtcars1 <- mtcars
statistics <-
  grouped_ggbetweenstats(
    data = mtcars1,
    x = cyl,
    y = mpg,
    grouping.var = am,
    output = "subtitle"
  )
mtcars1$am <- factor(mtcars1$am, levels = c(0, 1), labels = statistics)

# plot
mtcars1 %>%
  ggplot(aes(x = cyl, y = mpg)) +
  geom_jitter() +
  facet_wrap(
    vars(am),
    ncol = 1,
    strip.position = "top",
    labeller = ggplot2::label_parsed
  )
```

## Can you customize which pairs are shown in pairwise comparisons?

Currently, for `ggbetweenstats` and `ggwithinstats`, you can either display all
**significant** comparisons, all **non-significant** comparisons, or **all**
comparisons. But what if I am only interested in just one particular comparison?

Here is a workaround using `ggsignif`:

```{r custom_pairwise, fig.width = 7, fig.height = 6}
set.seed(123)
library(ggstatsplot)
library(ggsignif)

# displaying only one comparison
ggbetweenstats(mtcars, cyl, wt) +
  geom_signif(comparisons = list(c("4", "6")))
```

## How to access dataframe with results from pairwise comparisons?

```{r}
library(ggstatsplot)
library(ggplot2)

# way-1

p <- ggbetweenstats(mtcars, cyl, wt, pairwise.comparisons = TRUE)

pb <- ggplot_build(p)

pb$plot$plot_env$df_pairwise

# way-2

library(pairwiseComparisons)

pairwise_comparisons(mtcars, cyl, wt)
```

## How can I remove a a particular `geom` layer from the plot?

Sometimes you may not want a particular `geom` layer to be displayed. You can
remove them using `gginnards`. 

For example, let's say we want to remove the `geom_point()` from
`ggbetweenstats` default plot.

```{r gginnards, fig.width = 7, fig.height = 5}
# needed libraries
library(ggstatsplot)
library(gginnards)

# plot with all geoms
p <-
  ggbetweenstats(
    data = iris,
    x = Species,
    y = Sepal.Length,
    mean.plotting = FALSE
  )

# delete geom corresponding to points
gginnards::delete_layers(x = p, match_type = "GeomPoint")
```

This can be helpful to add a new layer with aesthetic specifications of your
liking.

```{r gginnards2, fig.width = 7, fig.height = 5}
set.seed(123)

# needed libraries
library(ggstatsplot)
library(gginnards)
library(ggplot2)

# basic plot without mean tagging
p <-
  ggwithinstats(
    data = bugs_long,
    x = condition,
    y = desire,
    mean.plotting = FALSE
  )

# delete the geom_point layer
p <- gginnards::delete_layers(x = p, match_type = "GeomPoint")

# add a new layers for points with a different shape
p + geom_point(shape = 23, aes(color = condition))
```

## How can I modify `grouped_` outputs using `ggplot2` functions?

All `ggstatsplot` are `ggplot` objects, which can be further modified, just like
any other `ggplot` object. But exception to these are all plots returned by
`grouped_` functions, but there is a way to tackle this.

```{r grouped_modify, fig.width = 12, fig.height = 6}
# needed libraries
set.seed(123)
library(ggstatsplot)
library(paletteer)
library(ggplot2)
library(palmerpenguins)

# plot
grouped_ggbetweenstats(
  penguins,
  species,
  body_mass_g,
  grouping.var = sex,
  type = "np",
  ggplot.component =
    # modify further with `ggplot2` functions
  list(
    scale_color_manual(values = paletteer::paletteer_c("viridis::viridis", 3)),
    theme(axis.text.x = element_text(angle = 90))
  )
)
```

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>
