---
title: "Frequently Asked Questions (FAQ)"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Frequently Asked Questions (FAQ)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE

source("../setup.R")
```

```{r}
#| label = "suggested_pkgs",
#| include = FALSE

pkgs <- c(
  "PMCMRplus",
  "svglite"
)

successfully_loaded <- purrr::map_lgl(pkgs, requireNamespace, quietly = TRUE)
can_evaluate <- all(successfully_loaded)

if (can_evaluate) {
  purrr::walk(pkgs, library, character.only = TRUE)
  knitr::opts_chunk$set(eval = TRUE, dev = "svglite")
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

<!-- The sections are numbered manually because `pkgdown` doesn't render -->
<!-- numbered sections for `rmarkdown::html_vignette` format -->

---

Following are a few of the common questions asked in GitHub issues and on social
media platforms.

## 1. I just want the plot, not the statistical details. How can I turn them off?

All functions in `{ggstatsplot}` that display results from statistical analysis in
a subtitle have argument `results.subtitle`. Setting it to `FALSE` will return
only the plot.

## 2. How can I customize the details contained in the subtitle?

Sometimes you may not wish include so many details in the subtitle. In that
case, you can extract the expression and copy-paste only the part you wish to
include. For example, here only statistic and *p*-values are included:

```{r}
#| label = "custom_expr"

library(ggplot2)
library(statsExpressions)

# extracting detailed expression
data_results <- oneway_anova(iris, Species, Sepal.Length, var.equal = TRUE)
data_results$expression[[1]]

# adapting the details to your liking
ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot() +
  labs(subtitle = ggplot2::expr(paste(
    italic("F"), "(", "2", ",", "147", ")=", "119.26", ", ",
    italic("p"), "<", "0.001"
  )))
```

## 3. I am getting `Error in grid.Call` error

Sometimes, if you are working in `RStudio`, you might see the following error-

```r
Error in grid.Call(C_textBounds, as.graphicsAnnot(x$label), x$x, x$y, :
polygon edge not found
```

This can possibly be solved by increasing the size of RStudio viewer pane.

## 4. Why do I get only plot in return but not the subtitle/caption?

In order to prevent the entire plotting function from failing when statistical
analysis fails, functions in `{ggstatsplot}` default to first attempting to run
the analysis and if they fail, then return empty (`NULL`) subtitle/caption. In
such cases, if you wish to diagnose why the analysis is failing, you will have
to do so using the underlying function used to carry out statistical analysis.

For example, the following returns only the plot but not the statistical details
in a subtitle.

```{r}
#| label = "null_subtitle"

df <- data.frame(x = 1, y = 2)
ggscatterstats(df, x, y, type = "robust")
```

To see why the statistical analysis failed, you can look at the error from the
underlying function:

```{r}
#| error = TRUE
library(statsExpressions)
df <- data.frame(x = 1, y = 2)
corr_test(df, x, y, type = "robust")
```

## 5. What statistical test was carried out?

In case you are not sure what was the statistical test that produced the results
shown in the subtitle of the plot, the best way to get that information is to
either look at the documentation for the function used or check out the
associated vignette. 

Summary of all analysis is handily available in `README`: 
<https://github.com/IndrajeetPatil/ggstatsplot/blob/master/README.md>

## 6. How can I use `{ggstatsplot}` functions in a `for` loop?

Given that all functions in `{ggstatsplot}` use tidy evaluation, running these
functions in a `for` loop requires minor adjustment to how inputs are entered:

```{r}
#| label = "loop",
#| eval = FALSE
col.name <- colnames(mtcars)

# executing the function in a `for` loop
for (i in 3:length(col.name)) {
  ggbetweenstats(
    data = mtcars,
    x = cyl,
    y = !!col.name[i]
  )
}
```

That said, if repeating function execution across multiple columns in a
data frame in what you want to do, I will recommend `{purrr}`-based solution:

<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html#repeating-function-execution-across-multiple-columns-in-a-data frame-1>

## 7. How can I have uniform Y-axes ranges in `grouped_` functions?

Across different facets of a `grouped_` plot, the axes ranges might sometimes
differ. You can use the `ggplot.component` parameter (present in all functions)
to have the same scale across the individual plots:

```{r}
#| label = "grouped_y_axes",
#| fig.height = 6,
#| fig.width = 8

# provide a list of further `{ggplot2}` modifications using `ggplot.component`
grouped_ggscatterstats(
  mtcars,
  disp,
  hp,
  grouping.var = am,
  results.subtitle = FALSE,
  ggplot.component = list(ggplot2::scale_y_continuous(
    breaks = seq(50, 350, 50),
    limits = (c(50, 350))
  ))
)
```

## 8. Does `{ggstatsplot}` work with `plotly`?

The `plotly` R graphing library makes it easy to produce interactive web
graphics via `plotly.js`. 

The `{ggstatsplot}` functions are compatible with `plotly`.
 
```r
library(plotly)

# creating ggplot object with `{ggstatsplot}`
p <- ggbetweenstats(mtcars, cyl, mpg)

# converting to plotly object
plotly::ggplotly(p, width = 480, height = 480)
```

## 9. How can I use `grouped_` functions with more than one group?

Currently, the `grouped_` variants of functions only support repeating the
analysis across a _single_ grouping variable. Often, you have to run the same
analysis across a combination of more than two grouping variables. This can be
easily achieved using `{purrr}` package. 

Here is an example-

```{r}
#| label = "grouped_2",
#| fig.width = 6,
#| fig.height = 6



# creating a list by splitting data frame by combination of two different
# grouping variables
df_list <- mpg %>%
  dplyr::filter(drv %in% c("4", "f"), fl %in% c("p", "r")) %>%
  split(f = list(.$drv, .$fl), drop = TRUE)

# checking if the length of the list is 4
length(df_list)

# running correlation analyses between; this will return a *list* of plots
plot_list <- purrr::pmap(
  .l = list(
    data = df_list,
    x = "displ",
    y = "hwy",
    results.subtitle = FALSE
  ),
  .f = ggscatterstats
)

# arrange the list in a single plot grid
combine_plots(
  plotlist = plot_list,
  plotgrid.args = list(nrow = 2),
  annotation.args = list(tag_levels = "i")
)
```

## 10. How can I include statistical expressions in facet labels?

```{r}
#| label = "facet_expr",
#| fig.width = 6,
#| fig.height = 8

library(ggplot2)

# data
mtcars1 <- mtcars

p <- grouped_ggbetweenstats(
  data = mtcars1,
  x = cyl,
  y = mpg,
  grouping.var = am
)

expr1 <- extract_subtitle(p[[1L]])
expr2 <- extract_subtitle(p[[2L]])

mtcars1$am <- factor(mtcars1$am, levels = c(0, 1), labels = c(expr1, expr2))

mtcars1 %>%
  ggplot(aes(x = cyl, y = mpg)) +
  geom_jitter() +
  facet_wrap(
    vars(am),
    ncol = 1,
    strip.position = "top",
    labeller = ggplot2::label_parsed
  )
```

## 11. How to customize which pairs are shown in pairwise comparisons?

Currently, for `ggbetweenstats` and `ggwithinstats`, you can either display all
**significant** comparisons, all **non-significant** comparisons, or **all**
comparisons. But what if I am only interested in just one particular comparison?

Here is a workaround using `{ggsignif}`:

```{r}
#| label = "custom_pairwise",
#| fig.width = 7,
#| fig.height = 6

library(ggsignif)

## displaying only one comparison
ggbetweenstats(mtcars, cyl, wt, pairwise.comparisons = FALSE) +
  geom_signif(comparisons = list(c("4", "6")), test.args = list(exact = FALSE))
```

## 12. How to access data frame with results from pairwise comparisons?

Behind the scenes, `{ggstatsplot}` uses `statsExpressions::pairwise_comparisons()` function. 

You can use it to extract actual data frames used in `{ggstatsplot}` functions.

```{r}
library(ggplot2)

pairwise_comparisons(mtcars, cyl, wt)
```

## 13. How can I change annotation in pairwise comparisons?

`{ggstatsplot}` defaults to displaying exact p-values or logged Bayes Factor
values for pairwise comparisons. But what if you wish to adopt a different
annotation labels?

You will have to customize them yourself:

```{r}
#| label = "comp_asterisks"

library(ggplot2)
library(ggsignif)

# converting to factor
mtcars$cyl <- as.factor(mtcars$cyl)

# creating the base plot
p <- ggbetweenstats(mtcars, cyl, wt, pairwise.comparisons = FALSE)

# using `pairwise_comparisons()` function to create a data frame with results
(df <- pairwise_comparisons(mtcars, cyl, wt) %>%
  dplyr::mutate(groups = purrr::pmap(.l = list(group1, group2), .f = c)) %>%
  dplyr::arrange(group1) %>%
  dplyr::mutate(asterisk_label = c("**", "***", "**")))

# adding pairwise comparisons using `{ggsignif}` package
p +
  ggsignif::geom_signif(
    comparisons = df$groups,
    map_signif_level = TRUE,
    annotations = df$asterisk_label,
    y_position = c(5.5, 5.75, 6.0),
    test = NULL,
    na.rm = TRUE
  )
```

## 14. How to access data frame containing statistical analyses?

You can use the `extract_stats()` helper function for this.

```{r}
#| label = "onesample_df"

library(ggplot2)

p <- ggpiestats(mtcars, am, cyl)

# data frame with results
extract_stats(p)
```

## 15. How can I remove a particular `geom` layer from the plot?

Sometimes you may not want a particular `geom` layer to be displayed. You can
remove them by setting transparency (`alpha`) for that layer to 0.

For example, let's say I want to remove the points from `ggwithintstats()` plot:

```{r}
#| label = "geom_removal",
#| fig.width = 7,
#| fig.height = 5


# before
ggwithinstats(
  data = bugs_long,
  x = condition,
  y = desire,
  results.subtitle = FALSE,
  pairwise.comparisons = FALSE
)

# after
ggwithinstats(
  data = bugs_long,
  x = condition,
  y = desire,
  point.args = list(alpha = 0),
  results.subtitle = FALSE,
  pairwise.comparisons = FALSE
)
```

## 16. How can I modify the fill colors with custom values?

Sometimes you may not be satisfied with the available color palette values. In
this case, you can also change the colors by manually specifying these values.

```{r}
#| label = "ggbar_colors"

library(ggplot2)

ggbarstats(mtcars, am, cyl, results.subtitle = FALSE) +
  scale_fill_manual(values = c("#E7298A", "#66A61E"))
```

The same can also be done for `grouped_` functions:

```{r}
#| label = "ggpie_colors",
#| fig.width = 12,
#| fig.height = 6
grouped_ggpiestats(
  data = mtcars,
  grouping.var = am,
  x = cyl,
  ggplot.component = ggplot2::scale_fill_grey()
)
```

## 17. How can I modify `grouped_` outputs using `{ggplot2}` functions?

All `{ggstatsplot}` are `ggplot` objects, which can be further modified, just like
any other `ggplot` object. But exception to these are all plots returned by
`grouped_` functions, but there is a way to tackle this.

```{r}
#| label = "grouped_modify"

library(paletteer)
library(ggplot2)

grouped_ggbetweenstats(
  mtcars,
  cyl,
  wt,
  grouping.var = am,
  results.subtitle = FALSE,
  pairwise.comparisons = FALSE,
  ggplot.component =
  # modify further with `{ggplot2}` functions
    list(
      scale_color_manual(values = paletteer::paletteer_c("viridis::viridis", 3)),
      theme(axis.text.x = element_text(angle = 90))
    )
)
```

## 18. How can I extract data frame containing results from `{ggstatsplot}`?

`{ggstatsplot}` can return expressions in the subtitle and caption, but what if
you want to actually get back data frame containing the results?

You have two options:

- Use `ggstatsplot::extract_stats()` function
- Or go to the source package `{statsExpressions}` (see [examples](https://indrajeetpatil.github.io/statsExpressions/articles/dataframe_outputs.html))

## 19. How can I remove sample size labels for `ggbarstats`?

```
library(gginnards)

## create a plot
p <- ggbarstats(mtcars, am, cyl)

## remove layer corresponding to sample size
delete_layers(p, "GeomText")
```

## 20. Statistical analysis I want to carry out is not available. What can I do?

By default, since `{ggstatsplot}` always allows just **one** type of test per
statistical approach, sometimes your favorite test might not be available. For
example, `{ggstatsplot}` provides only Spearman's $\rho$, but not Kendall's
$\tau$ as a non-parametric correlation test. 

In such cases, you can override the defaults and use `{statsExpressions}` to
create custom expressions to display in the plot. But be forewarned that the
expression building function in `{statsExpressions}` is not stable yet.

```{r}
#| label = "custom_test",
#| fig.width = 6,
#| fig.height = 6

library(correlation)
library(statsExpressions)
library(ggplot2)

# data with two variables of interest
df <- dplyr::select(mtcars, wt, mpg)

# correlation results
results <- correlation(df, method = "kendall") %>%
  insight::standardize_names(style = "broom")

# creating expression out of these results
df_results <- statsExpressions::add_expression_col(
  data           = results,
  no.parameters  = 0L,
  statistic.text = list(quote(italic("T"))),
  effsize.text   = list(quote(widehat(italic(tau))["Kendall"])),
  n              = results$n.obs[[1]]
)

# using custom expression in plot
ggscatterstats(df, wt, mpg, results.subtitle = FALSE) +
  labs(subtitle = df_results$expression[[1]])
```

## 21. Is there way to adjust my alpha level?

No, there is no way to adjust alpha if you use `grouped_` functions (e.g.,
`grouped_ggwithinstats`). You will have to just report in the
paper/article/report, what your adjusted alpha is.

So, for example, iif 2 tests are being carried out, the alpha is going to be
`0.05/2 = 0.025`. So, when you describe the _Methods_ section, you can mention
that only those tests should be considered significant where `p < 0.025`. Or you
can even mention this in the caption.

## 22. How can I build a `Shiny` app using `{ggstatsplot}` functions?

Below is an example using `ggbetweenstats` function.

```r
library(shiny)
library(rlang)

ui <- fluidPage(
  headerPanel("Example - ggbetweenstats"),
  sidebarPanel(
    selectInput("x", "xcol", "X Variable", choices = names(iris)[5]),
    selectInput("y", "ycol", "Y Variable", choices = names(iris)[1:4])
  ),
  mainPanel(plotOutput("plot"))
)

server <- function(input, output) {
  output$plot <- renderPlot({
    ggbetweenstats(iris, !!input$x, !!input$y)
  })
}

shinyApp(ui, server)
```

## 23. How to change size of annotations for combined plot in `grouped_*` functions?

```{r}
library(ggplot2)

grouped_ggbetweenstats(
  data = dplyr::filter(ggplot2::mpg, drv != "4"),
  x = year,
  y = hwy,
  grouping.var = drv,
  results.subtitle = FALSE,
  ## arguments given to `{patchwork}` for combining plots
  annotation.args = list(
    title = "this is my title",
    subtitle = "this is my subtitle",
    theme = ggplot2::theme(
      plot.subtitle = element_text(size = 20),
      plot.title = element_text(size = 30)
    )
  )
)
```

## 24. How to change size of text in the subtitle?

```{r}
ggbetweenstats(
  data = iris,
  x = Species,
  y = Sepal.Length,
  ggplot.component = list(theme(plot.subtitle = element_text(size = 20, face = "bold")))
)
```

## 25. How to display pairwise comparison letter in a plot?

This is not possible out of the box, but see [this](https://github.com/IndrajeetPatil/ggstatsplot/issues/654#issuecomment-948862514) comment.

## 26. Does `{ggstatsplot}` carry out assumption checks?

No, `{ggstatsplot}` does not carry out any analysis of whether assumptions are
met or not. It will just carry out whatever test you ask it to carry out.

To check these assumptions, you can use a different package called `{performance}`:

<https://easystats.github.io/performance/reference/index.html#check-model-assumptions-or-data-properties>

## 27. I am on Ubuntu and have trouble installing `{PMCMRplus}`?

Linux users may encounter some installation problems. In particular, the
`{ggstatsplot}` package depends on the `{PMCMRplus}` package.

```r
ERROR: dependencies ‘gmp’, ‘Rmpfr’ are not available for package ‘PMCMRplus’
```

This means that your operating system lacks `gmp` and `Rmpfr` libraries.

If you use `Ubuntu`, you can install these dependencies:

```
sudo apt-get install libgmp3-dev
sudo apt-get install libmpfr-dev
```

The following `README` file briefly describes the installation procedure:
<https://CRAN.R-project.org/package=PMCMRplus/readme/README.html>

For MacOS, have a look at this [post](https://stackoverflow.com/questions/35360885/installing-finding-gmp-under-osx).

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
