---
title: "Gallery of ggstatsplot examples"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{Gallery of ggstatsplot examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  dpi = 300,
  out.width = "100%",
  collapse = TRUE,
  comment = "#>"
)
```

# Gallery of examples

Here are few examples that demonstrate how the basic plots generated by
`ggstatsplot` can be further modified with either with `ggplot2` functions or
other additional `geoms`, `themes`, etc. from `ggplot2` extensions. This is because
the class of the object from all functions is still `ggplot`.

## Example-1: `ggscatterstats`

```{r gallery1, message = FALSE, warning = FALSE, fig.height = 10, fig.width = 10}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::ggscatterstats(
  data = ggplot2::msleep,
  x = brainwt,
  y = sleep_total,
  xlab = "Brain weight (in kilograms)",
  ylab = "Total amount of sleep (in hours)",
  label.var = "name",
  title = "Mammalian sleep",
  marginal = FALSE,
  type = "robust"
) + # further modifications with `ggplot2`
  ggplot2::geom_rug(sides = "b") +
  ggplot2::scale_x_log10()
```

## Example-2: `ggbetweenstats`

```{r gallery2, message = FALSE, warning = FALSE, fig.height = 10, fig.width = 10}
# for reproducibility
set.seed(123)

# needed library (download from GitHub)
# devtools::install_github("gadenbuie/ggpomological")
library(ggpomological)

# plot
ggpomological::paint_pomological(
  pomo_gg = ggstatsplot::ggbetweenstats(
    data = dplyr::filter(.data = ggstatsplot::movies_long,
                         genre %in% c("Action", "Action Comedy", "Action Drama", "Comedy")), 
    x = genre,
    y = rating,
    messages = FALSE,
    xlab = "movie genre",
    ylab = "IMDB rating",
    title = "Differences in IMDB ratings by genre"
  ) + # further modifications with `ggplot2`
    ggpomological::theme_pomological_fancy() +
    ggplot2::theme(legend.position = "none"),
  res = 110,
  width = 1000,
  height = 700
)
```

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>

