---
title: "ggcoefstats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggcoefstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
# show me all columns
options(tibble.width = Inf)
options(mc.cores = parallel::detectCores())   # use max # CPUs

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)

library(future)
plan("multicore")
```

The function `ggstatsplot::ggcoefstats` generates **dot-and-whisker plots** for
regression models saved in a tidy data frame. The tidy dataframes are prepared
using the following packages: `broom`, `broom.mixed`, and `parameters`.
Additionally, if available, the model summary indices are also extracted from
the following packages: `broom`, `broom.mixed`, and `performance`.

In this vignette, we will see examples of how to use this function. We will try
to cover as many classes of objects as possible. Unfortunately, there is no
single dataset that will be helpful for carrying out all types of regression
analyses and, therefore, we will use various datasets to explore data-specific
hypotheses using regression models.

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

# General structure of the plots

Although the statistical models displayed in the plot may differ based on the
class of models being investigated, there are few aspects of the plot that will
be invariant across models:

  - The dot-whisker plot contains a dot representing the **estimate** and their
    **confidence intervals** (`95%` is the default). The estimate can either be
    effect sizes (for tests that depend on the `F` statistic) or regression
    coefficients (for tests with `t` and `z` statistic), etc. The function will,
    by default, display a helpful `x`-axis label that should clear up what
    estimates are being displayed. The confidence intervals can sometimes be
    asymmetric if bootstrapping was used.

  - The caption will always contain diagnostic information, if available, about
    models that can be useful for model selection: The smaller the Akaike's
    Information Criterion (**AIC**) and the Bayesian Information Criterion
    (**BIC**) values, the "better" the model is.

  - The output of this function will be a `ggplot2` object and, thus, it can be
    further modified (e.g., change themes, etc.) with `ggplot2` functions.

# Supported models

Most of the regression models that are supported in the underlying packages are
also supported by `ggcoefstats`. For example-

`aareg`, `anova`, `aov`, `aovlist`, `Arima`, `BBreg`, `bcplm`, `bglmerMod`,
`bife`, `bigglm`, `biglm`, `blavaan`, `bmlm`, `blmerMod`, `bracl`, `brglm2`,
`brmsfit`, `brmultinom`, `btergm`, `cch`, `cgam`, `cgamm`, `cglm`, `clm`,
`clmm`, `coeftest`, `complmrob`, `confusionMatrix`, `coxme`, `coxph`, `cpglm`,
`cpglmm`, `crch`, `DirichReg`, `drc`, `emmGrid`, `epi.2by2`, `ergm`, `feis`,
`felm`, `fitdistr`, `flexsurvreg`, `glmc`, `glmerMod`, `glmmTMB`, `gls`, `gam`,
`Gam`, `gamlss`, `garch`, `glm`, `glmmadmb`, `glmmPQL`, `glmRob`, `glmrob`,
`glmx`, `gmm`, `hurdle`, `ivreg`, `iv_robust`, `lavaan`, `lm`, `lm.beta`,
`lmerMod`, `lmerModLmerTest`, `lmodel2`, `lmRob`, `lmrob`, `LORgee`, `lrm`, `mcmc`,
`MCMCglmm`, `mclogit`, `mmclogit`, `mediate`, `mixor`, `mjoint`, `mle2`, `mlm`,
`multinom`, `negbin`, `nlmerMod`, `nlrq`, `nlreg`, `nls`, `orcutt`, `plm`,
`polr`, `ridgelm`, `rjags`, `rlm`, `rlmerMod`, `rq`, `rqss`, `slm`, `speedglm`,
`speedlm`, `stanfit`, `stanreg`, `survreg`, `svyglm`, `svyolr`, `svyglm`,
`tobit`, `truncreg`, `vgam`, `wbgee`, `wblm`, `zcpglm`, `zeroinfl`, etc.

In the following examples, we will try out a number of regression models and,
additionally, we will also see how we can change different aspects of the plot
itself.

## omnibus ANOVA (`aov`)

For this analysis, let's use the `movies_long` dataset, which provides
information about IMDB ratings, budget, length, MPAA ratings (R-rated, PG, or
PG-13), and genre for a number of movies. Let's say our hypothesis is that the
IMDB ratings for a movie are predicted by a multiplicative effect of the genre
and the MPAA rating it got. Let's carry out an omnibus ANOVA to see if this is
the case.

```{r aov1, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8}
# loading needed libraries
library(ggstatsplot)
library(ggplot2)

# for reproducibility
set.seed(123)

# to speed up the calculation, let's use only 10% of the data
movies_10 <- dplyr::sample_frac(tbl = ggstatsplot::movies_long, size = 0.1)

# plot
ggstatsplot::ggcoefstats(
  x = stats::aov(
    formula = rating ~ mpaa * genre,
    data = movies_10
  ),
  effsize = "eta", # changing the effect size estimate being displayed
  partial = FALSE, # just eta-squared
  point.args = list(color = "red", size = 4, shape = 15), # changing the point geom
  package = "dutchmasters", # package from which color paletter is to be taken
  palette = "milkmaid", # color palette for labels
  title = "omnibus ANOVA" # title for the plot
) +
  # further modification with the ggplot2 commands
  # note the order in which the labels are entered
  ggplot2::scale_y_discrete(labels = c("MPAA", "Genre", "Interaction term")) +
  ggplot2::labs(
    x = "effect size estimate (partial omega-squared)",
    y = NULL
  )
```

As this plot shows, there is no interaction effect between these two factors.

Note that we can also use this function for model selection. You can try out
different models with the code below and see how the AIC, BIC, and
log-likelihood values change. Looking at the model diagnostics, you should be
able to see that the model with only `genre` as the predictor of ratings seems
to perform almost equally well as more complicated additive and multiplicative
models. Although there is certainly some improvement with additive and
multiplicative models, it is by no means convincing enough for us to abandon a
simpler model.

```{r aov2, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10}
library(ggstatsplot)

# to speed up the calculation, let's use only 10% of the data
movies_10 <- dplyr::sample_frac(tbl = ggstatsplot::movies_long, size = 0.1)

# for reproducibility
set.seed(123)

# plot
ggstatsplot::combine_plots(
  # model 1
  ggstatsplot::ggcoefstats(
    x = stats::aov(
      formula = rating ~ mpaa,
      data = movies_10
    ),
    stats.label.color = "black",
    title = "1. Only MPAA ratings"
  ), # model 2
  ggstatsplot::ggcoefstats(
    x = stats::aov(
      formula = rating ~ genre,
      data = movies_10
    ),
    stats.label.color = "black",
    title = "2. Only genre"
  ), # model 3
  ggstatsplot::ggcoefstats(
    x = stats::aov(
      formula = rating ~ mpaa + genre,
      data = movies_10
    ),
    stats.label.color = "black",
    title = "3. Additive effect of MPAA and genre"
  ), # model 4
  ggstatsplot::ggcoefstats(
    x = stats::aov(
      formula = rating ~ mpaa * genre,
      data = movies_10
    ),
    stats.label.color = "black",
    title = "4. Multiplicative effect of MPAA and genre"
  ),
  title.text = "Model selection using ggcoefstats",
  labels = c("(a)", "(b)", "(c)", "(d)")
)
```

## linear model (`lm`)

Now that we have figured out that the movie's `genre` explains a fair amount of
the variation in how people rate the movie on IMDB, let's run a linear
regression model to see how different types of genres compare with each other
using **Action** movies as our comparison point.

```{r lm, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 8}
# plot
ggstatsplot::ggcoefstats(
  x = stats::lm(
    formula = rating ~ genre,
    data = dplyr::filter(
      .data = ggstatsplot::movies_long,
      genre %in% c(
        "Action",
        "Action Comedy",
        "Action Drama",
        "Comedy",
        "Drama",
        "Comedy Drama"
      )
    )
  ),
  conf.level = 0.99, # changing the confidence levels for confidence intervals
  sort = "ascending", # sorting the terms of the model based on estimate values
  label.direction = "both", # direction in which to adjust position of labels (both x and y)
  ggtheme = ggplot2::theme_gray(), # changing the default theme
  stats.label.color = c("#CC79A7", "darkgreen", "#0072B2", "black", "red"),
  title = "Movie ratings by their genre",
  subtitle = "Source: www.imdb.com"
) +
  # further modification with the ggplot2 commands
  # note the order in which the labels are entered
  ggplot2::scale_y_discrete(labels = c("Comedy", "Action Comedy", "Action Drama", "Comedy Drama", "Drama")) +
  ggplot2::labs(y = "Genre compared to Action movies)") +
  ggplot2::theme(axis.title.y = ggplot2::element_text(size = 14, face = "bold"))
```

As can be seen from the regression coefficients, compared to action movies,
comedies and action comedies are not rated significantly better. All three of
the "drama" types (pure, action or comedy dramas) have statistical significantly
higher regression coefficients. This finding occurs even with our more
conservative `0.99` confidence interval.

## linear mixed-effects model (`lmer`/`lmerMod`)

Now let's say we want to see how movie's budget relates to how good the movie is
rated to be on IMDB (e.g., more money, better ratings?). But we have reasons to
believe that the relationship between these two variables might be different for
different genres (e.g., budget might be a good predictor of how good the movie
is rated to be for animations or actions movies as more money can help with
better visual effects and animations, but this may not be true for dramas, so we
don't want to use `stats::lm`. In this case, therefore, we will be running a
linear mixed-effects model (using `lme4::lmer` and *p*-values generated using
the `parameters::p_values` function) with a random slope for the genre variable.

```{r lmer1, warning = FALSE, message = FALSE, fig.height = 12, fig.width = 7}
# set up
library(lme4)
library(ggstatsplot)
set.seed(123)

# to speed up the calculation, let's use only 10% of the data
movies_10 <- dplyr::sample_frac(tbl = ggstatsplot::movies_long, size = 0.1)

# combining the two different plots
ggstatsplot::combine_plots(
  # model 1: simple linear model
  ggstatsplot::ggcoefstats(
    x = stats::lm(
      formula = scale(rating) ~ scale(budget),
      data = movies_10
    ),
    title = "linear model",
    stats.label.color = "black",
    exclude.intercept = FALSE # show the intercept
  ) +
    ggplot2::labs(x = parse(text = "'standardized regression coefficient' ~italic(beta)")),
  # model 2: linear mixed-effects model
  ggstatsplot::ggcoefstats(
    x = lme4::lmer(
      formula = scale(rating) ~ scale(budget) + (budget | genre),
      data = movies_10,
      control = lme4::lmerControl(calc.derivs = FALSE)
    ),
    title = "linear mixed-effects model",
    stats.label.color = "black",
    exclude.intercept = FALSE
  ) +
    ggplot2::labs(
      x = parse(text = "'standardized regression coefficient' ~italic(beta)"),
      y = "fixed effects"
    ),
  labels = c("(a)", "(b)"),
  nrow = 2,
  ncol = 1,
  title.text = "Relationship between movie budget and its IMDB rating"
)
```

As can be seen from these plots, although there seems to be a really small
correlation between budget and rating in a linear model, this effect is not
significant once we take into account the hierarchical structure of the data.

Note that for mixed-effects models, only the *fixed* effects are shown because
there are no confidence intervals for *random* effects terms. In case, you would
like to see these terms, you can enter the same object you entered as `x`
argument to `ggcoefstats` in `broom::tidy`:

```{r lmer2, warning = FALSE, message = FALSE}
set.seed(123)

# to speed up the calculation, let's use only 10% of the data
movies_10 <- dplyr::sample_frac(tbl = ggstatsplot::movies_long, size = 0.1)

# tidy output
broom.mixed::tidy(
  x = lme4::lmer(
    formula = scale(rating) ~ scale(budget) + (budget | genre),
    data = movies_10,
    control = lme4::lmerControl(calc.derivs = FALSE)
  ),
  conf.int = TRUE,
  conf.level = 0.95
)
```

## robust linear mixed-effects models (`rlmer`)

Robust version of `lmer` (as implemented in `robustlmm` package) is also
supported-

```{r rlmer, warning = FALSE, message = FALSE, width = 5, height = 5}
# setups
set.seed(123)
library(robustlmm)

# model
roblmm.mod <-
  robustlmm::rlmer(
    formula = scale(Reaction) ~ scale(Days) + (Days | Subject),
    data = sleepstudy,
    rho.sigma.e = psi2propII(smoothPsi, k = 2.28),
    rho.sigma.b = chgDefaults(smoothPsi, k = 5.11, s = 10)
  )

# plot
ggstatsplot::ggcoefstats(
  x = roblmm.mod,
  title = "robust estimation of linear mixed-effects model",
  conf.level = 0.90
)
```

## linear mixed-effects models with `lmerTest` (`lmerModLmerTest`)

```{r lmerModLmerTest, warning = FALSE, message = FALSE, width = 6, height = 10}
# setup
set.seed(123)
library(lmerTest)

# fit linear mixed model to the ham data:
fm <-
  lmerTest::lmer(
    formula = Informed.liking ~ Gender + Information * Product + (1 | Consumer) +
      (1 | Consumer:Product),
    data = ham
  )

# plot
ggstatsplot::ggcoefstats(
  x = fm,
  title = "linear mixed-effects models with `lmerTest`"
)
```

## non-linear mixed-effects model (`nlmer`/`nlmerMod`)

```{r nlmer, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# data
library(lme4)
set.seed(123)
startvec <- c(Asym = 200, xmid = 725, scal = 350)

# model
nm1 <-
  lme4::nlmer(
    formula = circumference ~ SSlogis(age, Asym, xmid, scal) ~ Asym | Tree,
    data = Orange,
    start = startvec
  )

# plot
ggstatsplot::ggcoefstats(
  x = nm1,
  title = "non-linear mixed-effects model"
)
```

## non-linear least-squares model (`nls`)

So far we have been assuming a linear relationship between movie budget and
rating. But what if we want to also explore the possibility of a non-linear
relationship? In that case, we can run a non-linear least squares regression.
Note that you need to choose some non-linear function, which will be based on
prior exploratory data analysis (`y ~ k/x + c` implemented here, but you can try
out other non-linear functions, e.g. `Y ~ k * exp(-b*c)`).

```{r nls, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
library(ggstatsplot)

# to speed up the calculation, let's use only 10% of the data
movies_10 <- dplyr::sample_frac(tbl = ggstatsplot::movies_long, size = 0.1)

# model
mod <-
  stats::nls(
    formula = rating ~ k / budget + c, # try toying around with the form of non-linear function
    data = movies_10,
    start = list(k = 1, c = 0)
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "non-linear least squares regression",
  subtitle = "Non-linear relationship between budget and rating"
)
```

This analysis shows that there is indeed a possible non-linear association
between rating and budget (non-linear regression term `k` is significant), at
least with the particular non-linear function we used.

## stationary linear model (`slm`)

```{r slm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
# setup
set.seed(123)
library(slm)
data("shan")

# model
mod <-
  slm(
    myformula = shan$PM_Xuhui ~ .,
    data = shan,
    method_cov_st = "fitAR",
    model_selec = -1
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  conf.level = 0.90,
  title = "stationary linear models",
  package = "rcartocolor",
  palette = "Vivid"
)
```

## generalized linear model (`glm`)

In all the analyses carried out thus far, the outcome variable (`y` in `y ~ x`)
has been continuous. In case the outcome variable is nominal/categorical/factor,
we can use the **generalized** form of linear model that works even if the
response is a numeric vector or a factor vector, etc.

To explore this model, we will use the Titanic dataset, which tabulates
information on the fate of passengers on the fatal maiden voyage of the ocean
liner *Titanic*, summarized according to economic status (class), sex, age, and
survival. Let's say we want to know what was the strongest predictor of whether
someone survived the Titanic disaster-

```{r glm1, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
library(ggstatsplot)

# having a look at the Titanic dataset
df <- as.data.frame(x = Titanic)
str(df)

# model
mod <-
  stats::glm(
    formula = Survived ~ Sex + Age,
    data = df,
    weights = df$Freq,
    family = stats::binomial(link = "logit")
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  exponentiate = TRUE,
  ggtheme = ggthemes::theme_economist_white(),
  title = "generalized linear model (glm)",
  vline.color = "red",
  vline.linetype = "solid",
  label.segment.color = "red",
  stats.label.color = c("orangered", "dodgerblue")
)
```

As can be seen from the regression coefficients, all entered predictors were
significant predictors of the outcome. More specifically, being a female was
associated with higher likelihood of survival (compared to male). On other hand,
being an adult was associated with decreased likelihood of survival (compared to
child).

**Note**: Few things to keep in mind for `glm` models,

  - The exact statistic will depend on the family used. Below we will see a host
    of different function calls to `glm` with a variety of different families.

  - Some families will have a `t` statistic associated with them, while others a
    `z` statistic. The function will figure this out for you.

```{r glm_full, warning = FALSE, message = FALSE, fig.height = 13, fig.width = 10}
# creating dataframes to use for regression analyses
library(ggstatsplot)

# dataframe #1
df.counts <-
  base::data.frame(
    treatment = gl(n = 3, k = 3, length = 9),
    outcome = gl(n = 3, k = 1, length = 9),
    counts = c(18, 17, 15, 20, 10, 20, 25, 13, 12)
  ) %>%
  tibble::as_tibble(.)

# dataframe #2
df.clotting <-
  data.frame(
    u = c(5, 10, 15, 20, 30, 40, 60, 80, 100),
    lot1 = c(118, 58, 42, 35, 27, 25, 21, 19, 18),
    lot2 = c(69, 35, 26, 21, 18, 16, 13, 12, 12)
  ) %>%
  tibble::as_tibble(.)

# dataframe #3
x1 <- stats::rnorm(50)
y1 <- stats::rpois(n = 50, lambda = exp(1 + x1))
df.3 <- data.frame(x = x1, y = y1) %>%
  tibble::as_tibble(.)

# dataframe #4
x2 <- stats::rnorm(50)
y2 <- rbinom(
  n = 50,
  size = 1,
  prob = stats::plogis(x2)
)

df.4 <- data.frame(x = x2, y = y2) %>%
  tibble::as_tibble(.)

# combining all plots in a single plot
ggstatsplot::combine_plots(
  # Family: Poisson
  ggstatsplot::ggcoefstats(
    x = stats::glm(
      formula = counts ~ outcome + treatment,
      data = df.counts,
      family = stats::poisson(link = "log")
    ),
    title = "Family: Poisson",
    stats.label.color = "black"
  ),
  # Family: Gamma
  ggstatsplot::ggcoefstats(
    x = stats::glm(
      formula = lot1 ~ log(u),
      data = df.clotting,
      family = stats::Gamma(link = "inverse")
    ),
    title = "Family: Gamma",
    stats.label.color = "black"
  ),
  # Family: Quasi
  ggstatsplot::ggcoefstats(
    x = stats::glm(
      formula = y ~ x,
      family = quasi(variance = "mu", link = "log"),
      data = df.3
    ),
    title = "Family: Quasi",
    stats.label.color = "black"
  ),
  # Family: Quasibinomial
  ggstatsplot::ggcoefstats(
    x = stats::glm(
      formula = y ~ x,
      family = stats::quasibinomial(link = "logit"),
      data = df.4
    ),
    title = "Family: Quasibinomial",
    stats.label.color = "black"
  ),
  # Family: Quasipoisson
  ggstatsplot::ggcoefstats(
    x = stats::glm(
      formula = y ~ x,
      family = stats::quasipoisson(link = "log"),
      data = df.4
    ),
    title = "Family: Quasipoisson",
    stats.label.color = "black"
  ),
  # Family: Gaussian
  ggstatsplot::ggcoefstats(
    x = stats::glm(
      formula = Sepal.Length ~ Species,
      family = stats::gaussian(link = "identity"),
      data = iris
    ),
    title = "Family: Gaussian",
    stats.label.color = "black"
  ),
  labels = c("(a)", "(b)", "(c)", "(d)", "(e)", "(f)"),
  ncol = 2,
  title.text = "Exploring models with different `glm` families",
  title.color = "blue"
)
```

## modified fitting for generalized linear models (`glm2`)

```{r glm2, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# setup
library(glm2)
y <- c(1, 1, 1, 0)

# model
fit1 <- glm2::glm2(
  formula = y ~ 1,
  family = binomial(link = "logit"),
  control = glm.control(trace = FALSE)
)

# plot
ggstatsplot::ggcoefstats(
  x = fit1,
  title = "greater stability for fitting \ngeneralized linear models",
  exclude.intercept = FALSE
)
```

## logistic regression model (`lrm`)

```{r lrm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 7}
# setup
library(rms)
set.seed(123)

# data
n <- 500
x1 <- runif(n, -1, 1)
x2 <- runif(n, -1, 1)
x3 <- sample(0 : 1, n, TRUE)
y <- x1 + 0.5 * x2 + x3 + rnorm(n)
y <- as.integer(cut2(y, g=10))
dd <- datadist(x1, x2, x3); options(datadist='dd')

# model
f <- rms::lrm(y ~ x1 + pol(x2, 2) + x3, eps = 1e-7) # eps to check against rstan

# plot
ggstatsplot::ggcoefstats(
  x = f, 
  title = "Logistic Regression Model",
  package = "ggsci",
  palette = "category20c_d3"
)
```

## Two-Stage Least Squares Instrumental Variables Regression (`iv_robust`)

```{r iv_robust, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 7}
# setup
set.seed(123)
library(fabricatr)
library(estimatr)

# data
dat <- fabricate(
  N = 40,
  Y = rpois(N, lambda = 4),
  Z = rbinom(N, 1, prob = 0.4),
  D = Z * rbinom(N, 1, prob = 0.8),
  X = rnorm(N),
  G = sample(letters[1:4], N, replace = TRUE)
)

# instrument for treatment `D` with encouragement `Z`
mod <- estimatr::iv_robust(formula = Y ~ D + X | Z + X, data = dat)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  exclude.intercept = FALSE,
  title = "Two-Stage Least Squares Instrumental Variables Regression"
)
```

## fitting negative binomial GLM (`negbin`)

Just to demonstrate that this can be done, let's also flip the axes:

```{r negbin, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8}
# setup
library(MASS)
library(lme4)
set.seed(101)

# data
dd <- expand.grid(
  f1 = factor(1:3),
  f2 = LETTERS[1:2],
  g = 1:9,
  rep = 1:15,
  KEEP.OUT.ATTRS = FALSE
)
mu <- 5 * (-4 + with(dd, as.integer(f1) + 4 * as.numeric(f2)))
dd$y <- rnbinom(nrow(dd), mu = mu, size = 0.5)

# model
m.glm <- MASS::glm.nb(formula = y ~ f1 * f2, data = dd)

# plot
ggstatsplot::ggcoefstats(
  x = m.glm,
  title = "generalized linear model (GLM)\n for the negative binomial family",
  exclude.intercept = FALSE,
  only.significant = TRUE,
  stats.label.args = list(size = 2.5, direction = "x")
) +
  ggplot2::coord_flip()
```

## generalized linear mixed-effects model (`glmer`/`glmerMod`)

In the previous example, we saw how being a female and being a child was
predictive of surviving the Titanic disaster. But in that analysis, we didn't
take into account one important factor: the passenger class in which people were
traveling. Naively, we have reasons to believe that the effects of sex and age
might be dependent on the class (maybe rescuing passengers in the first class
were given priority?). To take into account this hierarchical structure of the
data, we can run generalized linear mixed effects model with a random slope for
class.

```{r glmer, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(lme4)

# model
mod <- lme4::glmer(
  formula = Survived ~ Sex + Age + (Sex + Age | Class),
  # select 20% of the sample to reduce the time of execution
  data = dplyr::sample_frac(tbl = ggstatsplot::Titanic_full, size = 0.2),
  family = stats::binomial(link = "logit"),
  control = lme4::glmerControl(
    optimizer = "Nelder_Mead",
    calc.derivs = FALSE,
    boundary.tol = 1e-7
  )
)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "generalized linear mixed-effects model",
  exponentiate = TRUE,
  stats.label.color = "black"
)
```

As we had expected, once we take into account the differential relationship that
might exist between survival and predictors across different passenger classes,
only the sex factor remain a significant predictor. In other words, being a
female was the strongest predictor of whether someone survived the tragedy that
befell the Titanic.

## fitting negative binomial GLMM (`glmer.nb`)

```{r glmer.nb, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 6}
# setup
library(MASS)
library(lme4)
set.seed(101)

# data
dd <-
  expand.grid(
    f1 = factor(1:3),
    f2 = LETTERS[1:2],
    g = 1:9,
    rep = 1:15,
    KEEP.OUT.ATTRS = FALSE
  )
mu <- 5 * (-4 + with(dd, as.integer(f1) + 4 * as.numeric(f2)))
dd$y <- rnbinom(nrow(dd), mu = mu, size = 0.5)

# model
m.nb <- lme4::glmer.nb(formula = y ~ f1 * f2 + (1 | g), data = dd)

# plot
ggstatsplot::ggcoefstats(
  x = m.nb,
  title = "generalized linear mixed-effects model (GLMM)\n for the negative binomial family",
  exclude.intercept = FALSE
)
```

## Compound Poisson Generalized Linear Models (`cpglm`)

```{r cpglm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10}
# set up
set.seed(123)
library(cplm)

# model
mod <- cplm::cpglm(
  formula = RLD ~ factor(Zone) * factor(Stock),
  data = FineRoot
)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Compound Poisson Generalized Linear Models"
)
```

## Compound Poisson Generalized Linear Mixed Models (`cpglmm`)

```{r cpglmm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10}
# set up
set.seed(123)
library(cplm)

# model
mod <- cpglmm(formula = RLD ~ Stock + Spacing + (1 | Plant), data = FineRoot)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Compound Poisson Generalized Linear Mixed Models"
)
```

## Bayesian Compound Poisson Linear Models (`bcplm`)

```{r bcplm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10}
# set up
set.seed(123)
library(cplm)

# model
mod <-
  bcplm(
    formula = RLD ~ factor(Zone) * factor(Stock),
    data = FineRoot,
    tune.iter = 2000,
    n.iter = 6000,
    n.burnin = 1000,
    n.thin = 5
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Bayesian Compound Poisson Linear Models"
)
```

## Zero-inflated Compound Poisson Generalized Linear Models (`zcpglm`)

```{r zcpglm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10}
# set up
set.seed(123)
library(cplm)
da <- subset(AutoClaim, IN_YY == 1) # use data in the Yip and Yau paper
da <- transform(da, CLM_AMT5 = CLM_AMT5 / 1000, INCOME = INCOME / 10000)

# model
mod <- zcpglm(
  formula = CLM_AMT5 ~ CAR_USE + MARRIED + AREA + MVR_PTS || MVR_PTS + INCOME,
  data = da
)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Zero-inflated Compound Poisson \nGeneralized Linear Models"
)
```

## Zero-Inflated Count Data Regression (`zeroinfl`)

```{r zeroinfl, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
# setup
set.seed(123)
library(pscl)

# data
data("bioChemists", package = "pscl")

# model
mod <-
  pscl::zeroinfl(
    formula = art ~ . | 1,
    data = bioChemists,
    dist = "negbin"
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  exclude.intercept = FALSE,
  title = "Zero-Inflated Count Data Regression"
)
```

## Vector Generalized Linear Models (`vgam`)

```{r vgam, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6}
# setup
set.seed(123)
library(VGAM)
pneumo <- transform(pneumo, let = log(exposure.time))

# model
mod <-
  vglm(
    formula = cbind(normal, mild, severe) ~ let,
    family = multinomial,
    data = pneumo
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Vector Generalized Linear Models",
  exclude.intercept = FALSE
)
```

## Constrained Generalized Additive Model Fitting (`cgam`)

```{r cgam, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6}
# setup
set.seed(123)
library(cgam)
data(cubic)

# model
m <- cgam(formula = y ~ incr.conv(x), data = cubic)

# plot
ggstatsplot::ggcoefstats(
  x = m,
  title = "Constrained Generalized Additive Model Fitting",
  exclude.intercept = FALSE
)
```

## Constrained Generalized Additive Mixed-Effects Model Fitting (`cgamm`)

```{r cgamm, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 7}
# setup
set.seed(123)
library(cgam)

# simulate a balanced data set with 30 clusters
# each cluster has 30 data points
n <- 30
m <- 30

# the standard deviation of between cluster error terms is 1
# the standard deviation of within cluster error terms is 2
sige <- 1
siga <- 2

# generate a continuous predictor
x <- 1:(m * n)
for (i in 1:m) {
  x[(n * (i - 1) + 1):(n * i)] <- round(runif(n), 3)
}
# generate a group factor
group <- trunc(0:((m * n) - 1) / n) + 1

# generate the fixed-effect term
mu <- 10 * exp(10 * x - 5) / (1 + exp(10 * x - 5))

# generate the random-intercept term asscosiated with each group
avals <- rnorm(m, 0, siga)

# generate the response
y <- 1:(m * n)
for (i in 1:m) {
  y[group == i] <- mu[group == i] + avals[i] + rnorm(n, 0, sige)
}

# use REML method to fit the model
ans <- cgamm(formula = y ~ s.incr(x) + (1 | group), reml = TRUE)

# plot
ggstatsplot::ggcoefstats(
  x = ans,
  title = "Constrained Generalized Additive Mixed-Effects Model Fitting",
  exclude.intercept = FALSE
)
```

## Hurdle Models for Count Data Regression (`hurdle`)

```{r hurdle, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 8}
# setup
set.seed(123)
library(pscl)
data("bioChemists", package = "pscl")

# geometric-poisson
fm_hp2 <-
  pscl::hurdle(
    formula = art ~ .,
    data = bioChemists,
    zero = "geometric"
  )

# plot
ggstatsplot::ggcoefstats(
  x = fm_hp2,
  only.significant = TRUE,
  exclude.intercept = FALSE,
  conf.level = 0.99,
  title = "Hurdle Models for Count Data Regression"
)
```

## beta-binomial logistic regression model (`BBreg`)

```{r BBreg, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(18)
library(PROreg)

# We simulate a covariate, fix the paramters of the beta-binomial
# distribution and simulate a response variable.
# Then we apply the model, and try to get the same values.
k <- 1000
m <- 10
x <- rnorm(k, 5, 3)
beta <- c(-10, 2)
p <- 1 / (1 + exp(-(beta[1] + beta[2] * x)))
phi <- 1.2
y <- rBB(k, m, p, phi)

# model
model <- BBreg(y ~ x, m)

# plot
ggstatsplot::ggcoefstats(
  x = model,
  exclude.intercept = FALSE,
  title = "beta-binomial logistic regression model"
)
```

## binary choice models with fixed effects (`bife`)

```{r bife, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 8}
# setup
set.seed(123)
library(bife)
dataset <- psid

# binary choice models with fixed effects
mod <-
  bife(
    LFP ~ I(AGE^2) + log(INCH) + KID1 + KID2 + KID3 + factor(TIME) | ID,
    dataset
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "binary choice models with fixed effects"
)
```

## Dirichlet regression model (`DirichReg`)

```{r DirichReg, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(DirichletReg)

# data
ALake <- ArcticLake
ALake$Y <- DR_data(ALake[, 1:3])

# fit a quadratic Dirichlet regression models ("common")
mod <- DirichReg(Y ~ depth + I(depth^2), ALake)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Dirichlet Regression"
)
```

## Generalized Linear Models with Extra Parameters (`glmx`)

```{r glmx, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10}
# setup
library(glmx)
library(MASS)
set.seed(1)
d <- data.frame(x = runif(200, -1, 1))
d$y <- rnbinom(200, mu = exp(0 + 3 * d$x), size = 1)

# model
m_nb1 <-
  glmx(
    formula = y ~ x,
    data = d,
    family = negative.binomial,
    xlink = "log",
    xstart = 0
  )

ggstatsplot::ggcoefstats(
  x = m_nb1,
  title = "Generalized Linear Models with Extra Parameters"
)
```

## generalized linear mixed model trees (`glmertree`)

```{r glmertree, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10}
# setup
set.seed(123)
library(glmertree)
data("DepressionDemo", package = "glmertree")

# fit normal linear regression LMM tree for continuous outcome
lt <- glmertree::lmertree(
  formula = depression ~ treatment | cluster | age + anxiety + duration,
  data = DepressionDemo
)

# fit logistic regression GLMM tree for binary outcome
gt <- glmertree::glmertree(
  formula = depression_bin ~ treatment | cluster | age + anxiety + duration,
  data = DepressionDemo
)

# plot
ggstatsplot::combine_plots(
  ggstatsplot::ggcoefstats(
    x = lt$lmer,
    title = "normal linear regression \nLMM tree for continuous outcome"
  ),
  ggstatsplot::ggcoefstats(
    x = lt$lmer,
    title = "logistic regression \nGLMM tree for binary outcome"
  ),
  labels = c("(a)", "(b)")
)
```

## generalized linear mixed models using Penalized Quasi-Likelihood (`glmmPQL`)

```{r glmmPQL, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# setup
set.seed(123)
library(MASS)
library(nlme)

# model
mod <-
  MASS::glmmPQL(
    fixed = y ~ trt + I(week > 2),
    random = ~ 1 | ID,
    family = binomial,
    data = bacteria,
    verbose = FALSE
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "generalized linear mixed models \n using Penalized Quasi-Likelihood",
  exclude.intercept = FALSE
)
```

## generalized linear mixed models using Template Model Builder (`glmmTMB`)

`glmmTMB` package allows for flexibly fitting generalized linear mixed models
(GLMMs) and extensions. Model objects from this package are also supported.

```{r glmmTMB, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# set up
library(glmmTMB)
library(lme4)
set.seed(123)

# model
mod <-
  glmmTMB::glmmTMB(
    formula = Reaction ~ Days + (Days | Subject),
    data = sleepstudy,
    family = glmmTMB::truncated_poisson()
  )

# plotting the model
ggstatsplot::ggcoefstats(
  x = mod,
  conf.method = "uniroot",
  title = "generalized linear mixed models \nusing Template Model Builder"
)
```

Another example (given the number of terms, let's only display labels for
significant effects):

```{r glmmTMB2, warning = FALSE, message = FALSE, fig.height = 14, fig.width = 8}
# setup
set.seed(123)
library(glmmTMB)
data(Salamanders)

# model
zipm3 <-
  glmmTMB(count ~ spp * mined + (1 | site),
    zi = ~ spp * mined,
    data = Salamanders,
    family = "poisson"
  )

# plot
ggstatsplot::ggcoefstats(
  x = zipm3,
  package = "palettesForR",
  palette = "Inkscape",
  only.significant = TRUE
)
```

## generalized linear mixed models using AD Model Builder (`glmmadmb`)

Another option is to use `glmmadmb` package.

```{r glmmadmb, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
library(glmmADMB)

# simulate values
set.seed(101)
d <- data.frame(f = factor(rep(LETTERS[1:10], each = 10)), x = runif(100))
u <- rnorm(10, sd = 2)
d$eta <- with(d, u[f] + 1 + 4 * x)
pz <- 0.3
zi <- rbinom(100, size = 1, prob = pz)
d$y <- ifelse(zi, 0, rpois(100, lambda = exp(d$eta)))

# fit
zipmodel <-
  glmmADMB::glmmadmb(
    formula = y ~ x + (1 | f),
    data = d,
    family = "poisson",
    zeroInflation = TRUE
  )

# plotting the model
ggstatsplot::ggcoefstats(
  x = zipmodel,
  title = "generalized linear mixed models \nusing AD Model Builder"
)
```

## cumulative link models (`clm`)

So far we have dealt either with continuous or nominal/factor responses (or
output variables), but sometimes we will encounter **ordinal** data (e.g.,
Likert scale measurement in behavioral sciences). In these cases, ordinal
regression models are more suitable. To study these models, we will use
`intent_morality` dataset included in the `ggstatsplot` package. This dataset
contains moral judgments ("how wrong was this behavior?", "how much punishment
does the agent deserve?"; on a Likert scale of 1-7) by participants about
third-party actors who harmed someone. There are four different conditions
formed out of belief (neutral, negative) and outcome (neutral, negative) for
four different vignettes, each featuring a different type of harm. The question
we are interested in is what explains variation in participants' rating:
information about intentionality, consequences, or their interaction?

```{r clm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8}
# for reproducibility
set.seed(123)

# model (to speed up calculations, we will use just 10% of the dataset)
mod <- ordinal::clm(
  formula = as.factor(rating) ~ belief * outcome,
  link = "logit",
  data = dplyr::sample_frac(tbl = ggstatsplot::intent_morality, size = 0.10),
  control = ordinal::clm.control(
    maxIter = 50,
    convergence = "silent"
  )
)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  stats.label.color = "black",
  title = "cumulative link model (clm)",
  subtitle = "(using `ordinal` package)"
) +
  ggplot2::labs(x = "logit regression coefficient", y = NULL)
```

As can be seen from this plot, both factors (intentionality and consequences)
were significant, and so was their interaction.

## cumulative link models (`clm2`)

```{r clm2, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6, eval = FALSE}
# for reproducibility
set.seed(123)
library(ordinal)
library(MASS)
data(housing, package = "MASS")

# data
tab26 <- with(soup, table("Product" = PROD, "Response" = SURENESS))
dimnames(tab26)[[2]] <- c("Sure", "Not Sure", "Guess", "Guess", "Not Sure", "Sure")
dat26 <- expand.grid(sureness = as.factor(1:6), prod = c("Ref", "Test"))
dat26$wghts <- c(t(tab26))

# model
mod <-
  clm2(
    location = sureness ~ prod,
    scale = ~prod,
    data = dat26,
    weights = wghts,
    link = "logistic"
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "older version of `clm`"
)
```

## cumulative link mixed models (`clmm`)

In the previous analysis, we carried out a single ordinal regression models to
see the effects intent and outcome information on moral judgments. But what if
we also want to account for item level differences (since different items had
different types of harm)? For this, we can use ordinal mixed-effects regression
model (with random effects for type of harm) to see how intent and outcome
contribute towards variation in moral judgment ratings-

```{r clmm1, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
# for reproducibility
set.seed(123)

# to speed up calculations, we will use just 10% of the dataset
ggstatsplot::ggcoefstats(
  x = ordinal::clmm(
    formula = as.factor(rating) ~ belief * outcome + (belief + outcome |
      harm),
    data = dplyr::sample_frac(tbl = ggstatsplot::intent_morality, size = 0.10),
    control = ordinal::clmm.control(
      method = "nlminb",
      maxIter = 50,
      gradTol = 1e-4,
      innerCtrl = "noWarn"
    )
  ),
  title = "cumulative link mixed model (clmm)",
  subtitle = "(using `ordinal` package)"
) +
  ggplot2::labs(
    x = "coefficient from ordinal mixed-effects regression",
    y = "fixed effects"
  )
```

Mixed effects regression didn't reveal any interaction effect. That is, most of
the variance was accounted for by the information about whether there was
harmful intent and whether there was harm, at least this is the effect we found
with these four types of (minor) harms.

Note that, by default, `beta` parameters are shown for `clm` and `clmm` models,
but you can also plot either just `alpha` or `both` using `ggcoefstats`.

```{r clmm2, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
# for reproducibility
set.seed(123)

# model
mod <-
  ordinal::clmm(
    formula = as.factor(rating) ~ belief * outcome + (belief + outcome | harm),
    link = "logit",
    data = dplyr::sample_frac(tbl = ggstatsplot::intent_morality, size = 0.10),
    control = ordinal::clmm.control(
      maxIter = 50,
      gradTol = 1e-4,
      innerCtrl = "noWarn"
    )
  )

# plot
ggstatsplot::ggcoefstats(mod) +
  ggplot2::labs(
    x = "logit regression coefficients",
    y = "threshold parameters",
    title = "cumulative link mixed models"
  )
```

## Mixed-Effects Ordinal Regression Analysis (`mixor`)

```{r mixor, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(mixor)
data("SmokingPrevention")

# data frame must be sorted by id variable
SmokingPrevention <- SmokingPrevention[order(SmokingPrevention$class), ]

# school model
mod <-
  mixor(
    formula = thksord ~ thkspre + cc + tv + cctv,
    data = SmokingPrevention,
    id = school,
    link = "logit"
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Mixed-Effects Ordinal Regression Analysis",
  exclude.intercept = FALSE
)
```

## bias reduction in generalized linear models (`brglm2`)

Note that we can also choose to display labels only for the significant effects.
This can be helpful when a large number of regression coefficients are to be
displayed in a single plot and we would like to focus only on the significant
ones.

```{r brglm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 5}
# setup
set.seed(123)
library(brglm2)
data("lizards")

# fit the model using maximum likelihood mean bias-reduced fit:
lizardsBR_mean <-
  stats::glm(
    formula = cbind(grahami, opalinus) ~ height + diameter + light + time,
    family = binomial(logit),
    data = lizards,
    method = "brglmFit"
  )

# plot
ggstatsplot::ggcoefstats(
  x = lizardsBR_mean,
  only.significant = TRUE,
  title = "bias reduction in generalized linear models"
)
```

## Bias Reduction For Multinomial Response Models Using The Poisson Trick (`brmultinom`)

```{r brmultinom, warning = FALSE, message = FALSE, fig.height = 12, fig.width = 7, eval=FALSE}
# setup
set.seed(123)
library(MASS)
library(brglm2)
data("housing", package = "MASS")

# Maximum likelihood using brmultinom with baseline category 'Low'
houseML1 <- 
  brglm2::brmultinom(
  formula = Sat ~ Infl + Type + Cont,
  weights = Freq,
  data = housing,
  type = "ML",
  ref = 1
)

# plot
ggstatsplot::ggcoefstats(
  x = houseML1,
  title = "Bias Reduction For Multinomial Response Models \nUsing The Poisson Trick"
)
```

## bias reduction for adjacent category logit models (`bracl`)

```{r bracl, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 7, eval=FALSE}
# setup
set.seed(123)
library(brglm2)
data("stemcell")

# bias reduction for adjacent category logit models
# for ordinal responses using the Poisson trick
fit_bracl <-
  brglm2::bracl(
    formula = research ~ as.numeric(religion) + gender,
    weights = frequency,
    data = stemcell,
    type = "ML"
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit_bracl,
  conf.int = FALSE,
  title = "bias reduction for adjacent category logit models"
)
```

## generalized linear models subject to population constraints

```{r glmc, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# setup
set.seed(123)
library(glmc)

# data
n <- rbind(c(5903, 230), c(5157, 350))
mat <- matrix(0, nrow = sum(n), ncol = 2)
mat <-
  rbind(
    matrix(1, nrow = n[1, 1], ncol = 1) %*% c(0, 0),
    matrix(1, nrow = n[1, 2], ncol = 1) %*% c(0, 1),
    matrix(1, nrow = n[2, 1], ncol = 1) %*% c(1, 0),
    matrix(1, nrow = n[2, 2], ncol = 1) %*% c(1, 1)
  )

# specifying the population constraints
gfr <- .06179 * matrix(1, nrow = nrow(mat), ncol = 1)
g <- matrix(1, nrow = nrow(mat), ncol = 1)
amat <- matrix(mat[, 2] * g - gfr, ncol = 1)

# defining constraints in the data frame.
hrh <- data.frame(birth = mat[, 2], child = mat[, 1], constraints = amat)

# model
gfit <-
  glmc::glmc(
    formula = birth ~ child,
    data = hrh,
    family = "binomial",
    emplik.method = "Owen",
    control = glmc::glmc.control(
      trace.optim = 0,
      trace.glm = FALSE,
      maxit.glm = 10,
      maxit.weights = 200,
      itertrace.weights = TRUE,
      gradtol.weights = 10^(-6)
    )
  )

# plot
ggstatsplot::ggcoefstats(
  x = gfit,
  title = "generalized linear models \nsubject to population constraints",
  exclude.intercept = FALSE
)
```

## Bayesian linear linear mixed-effects models (`blmerMod`)

```{r blmerMod, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# for reproducibility
set.seed(123)
library(blme)

# data
data(sleepstudy)
sleepstudy$mygrp <- sample(1:5, size = 180, replace = TRUE)
sleepstudy$mysubgrp <- NA
for (i in 1:5) {
  filter_group <- sleepstudy$mygrp == i
  sleepstudy$mysubgrp[filter_group] <-
    sample(1:30, size = sum(filter_group), replace = TRUE)
}

# model
mod <-
  blme::blmer(
    formula = scale(Reaction) ~ scale(Days) + (1 + Days | Subject),
    data = sleepstudy,
    cov.prior = NULL,
    REML = FALSE
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Bayesian linear mixed-effects models",
  exclude.intercept = FALSE
)
```

## Bayesian generalized linear mixed-effects models (`bglmerMod`)

```{r bglmerMod, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# for reproducibility
set.seed(123)
library(blme)

# model
mod <-
  blme::bglmer(
    formula = Survived ~ Sex + Age + (Sex + Age | Class),
    # select 20% of the sample to reduce the time of execution
    data = dplyr::sample_frac(tbl = ggstatsplot::Titanic_full, size = 0.2),
    family = stats::binomial(link = "logit"),
    control = lme4::glmerControl(
      optimizer = "Nelder_Mead",
      calc.derivs = FALSE,
      boundary.tol = 1e-7
    )
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Bayesian generalized linear mixed-effects models"
)
```

## ordered logistic or probit regression (`polr`)

```{r polr, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8}
# polr model
set.seed(123)
library(MASS)
polr.mod <-
  MASS::polr(
    formula = Sat ~ Infl + Type + Cont,
    weights = Freq,
    data = housing
  )

# plot
ggstatsplot::ggcoefstats(
  x = polr.mod,
  coefficient.type = "both",
  title = "ordered logistic or probit regression",
  subtitle = "using `MASS` package"
)
```

## multiple linear regression models (`mlm`)

```{r mlm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# model (converting all numeric columns in data to z-scores)
mod <-
  stats::lm(
    formula = cbind(mpg, disp) ~ wt,
    data = purrr::modify_if(.x = mtcars, .p = is.numeric, ~ {
      as.numeric(scale(.x))
    })
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "multiple linear regression models",
  exclude.intercept = FALSE
)
```

## multinomial logistic regression models (`multinom`)

```{r multinom, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(nnet)
library(MASS)
utils::example(topic = birthwt, echo = FALSE)

# model
bwt.mu <-
  nnet::multinom(
    formula = low ~ .,
    data = bwt,
    trace = FALSE
  )

# plot
ggstatsplot::ggcoefstats(
  x = bwt.mu,
  title = "multinomial logistic regression models",
  package = "ggsci",
  palette = "default_ucscgb"
)
```

## multilevel mediation model (`bmlm`)

```{r bmlm, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 5}
# setup
set.seed(123)
library(bmlm)

# model
fit <- bmlm::mlm(BLch9, verbose = FALSE)

# exctrating summary
df_summary <-
  bmlm::mlm_summary(fit) %>%
  dplyr::rename(
    .data = .,
    estimate = Mean,
    term = Parameter,
    std.error = SE,
    conf.low = `2.5%`,
    conf.high = `97.5%`
  )

# plot
ggstatsplot::ggcoefstats(
  x = df_summary,
  title = "Bayesian multilevel mediation models with Stan"
)
```

## proportional odds and related models (`svyolr`)

```{r svyolr, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(survey)
data(api)

# preparing data
dclus1 <-
  survey::svydesign(
    id = ~dnum,
    weights = ~pw,
    data = apiclus1,
    fpc = ~fpc
  )

# update
dclus1 <- update(dclus1, mealcat = cut(meals, c(0, 25, 50, 75, 100)))

# model
m <- survey::svyolr(formula = mealcat ~ avg.ed + mobility + stype, design = dclus1)

# plot
ggstatsplot::ggcoefstats(
  x = m,
  title = "proportional odds and related models",
  coefficient.type = "both"
)
```

## survey-weighted generalized linear models (`svyglm`)

```{r svyglm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# data
library(survey)
set.seed(123)
data(api)
dstrat <-
  survey::svydesign(
    id = ~1,
    strata = ~stype,
    weights = ~pw,
    data = apistrat,
    fpc = ~fpc
  )

# model
mod <-
  survey::svyglm(
    formula = sch.wide ~ ell + meals + mobility,
    design = dstrat,
    family = quasibinomial()
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "survey-weighted generalized linear model"
)
```

## repeated measures ANOVA (`aovlist`)

Let's now consider an example of a repeated measures design where we want to run
omnibus ANOVA with a specific error structure. To carry out this analysis, we
will first have to convert the iris dataset from wide to long format such that
there is one column corresponding to `attribute` (which part of the calyx of a
flower is being measured: `sepal` or `petal`?) and one column corresponding to
`measure` used (`length` or `width`?). Note that this is within-subjects design
since the same flower has both measures for both attributes. The question we are
interested in is how much of the variance in measurements is explained by both
of these factors and their interaction.

```{r aovlist1, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8}
# for reproducibility
set.seed(123)

# having a look at iris before converting to long format
dplyr::glimpse(ggstatsplot::iris_long)

# let's use 20% of the sample to speed up the analysis
iris_long_20 <- dplyr::sample_frac(tbl = ggstatsplot::iris_long, size = 0.20)

# specifying the model (note the error structure)
ggstatsplot::ggcoefstats(
  x = stats::aov(
    formula = value ~ attribute * measure + Error(id / (attribute * measure)),
    data = iris_long_20
  ),
  effsize = "eta",
  partial = FALSE,
  nboot = 50,
  ggtheme = ggthemes::theme_fivethirtyeight(),
  ggstatsplot.layer = FALSE,
  stats.label.color = c("#0072B2", "#D55E00", "darkgreen"),
  title = "Variation in measurements for Iris species",
  subtitle = "Source: Iris data set (by Fisher or Anderson)",
  caption = "Results from 2 by 2 RM ANOVA"
) +
  ggplot2::theme(plot.subtitle = ggplot2::element_text(size = 11, face = "plain"))
```

As revealed by this analysis, all effects of this model are significant. But
most of the variance is explained by the `attribute`, with the next important
explanatory factor being the `measure` used. A very little amount of variation
in measurement is accounted for by the interaction between these two factors.

## robust regression with `robust` package (`lmRob`, `glmRob`)

The robust regression models, as implemented in the `robust` package are also
supported.

```{r robust, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 6}
ggstatsplot::combine_plots(
  # plot 1: glmRob
  ggstatsplot::ggcoefstats(
    x = robust::glmRob(
      formula = Survived ~ Sex,
      data = dplyr::sample_frac(tbl = ggstatsplot::Titanic_full, size = 0.20),
      family = stats::binomial(link = "logit")
    ),
    title = "generalized robust linear model",
    package = "dichromat",
    palette = "BrowntoBlue.10",
    ggtheme = ggthemes::theme_fivethirtyeight(),
    ggstatsplot.layer = FALSE
  ),
  # plot 2: lmRob
  ggstatsplot::ggcoefstats(
    x = robust::lmRob(
      formula = Sepal.Length ~ Sepal.Width * Species,
      data = iris
    ),
    title = "robust linear model",
    package = "awtools",
    palette = "a_palette",
    ggtheme = ggthemes::theme_tufte(),
    ggstatsplot.layer = FALSE
  ),
  # arguments relevant for `combine_plots` function
  labels = c("(a)", "(b)"),
  title.text = "Robust variants of `lmRob` and `glmRob` \n(from`robust` package)",
  nrow = 2
)
```

## robust regression with `robustbase` package (`lmrob`, `glmrob`)

Another alternative is to use robust models, as implemented in the `robustbase`
package.

```{r robustbase, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 6, eval=FALSE}
# setup
set.seed(123)
library(robustbase)

# dataframe
data(coleman)
clotting <- data.frame(
  u = c(5, 10, 15, 20, 30, 40, 60, 80, 100),
  lot1 = c(118, 58, 42, 35, 27, 25, 21, 19, 18),
  lot2 = c(69, 35, 26, 21, 18, 16, 13, 12, 12)
)

# combined plot for both generalized and simple robust models
ggstatsplot::combine_plots(
  # plot 1: glmrob
  ggstatsplot::ggcoefstats(
    x = robustbase::glmrob(
      formula = lot1 ~ log(u),
      data = clotting,
      family = Gamma
    ),
    title = "generalized robust linear model"
  ),
  # plot 2: lmrob
  ggstatsplot::ggcoefstats(
    x = robustbase::lmrob(formula = Y ~ ., data = coleman),
    title = "robust linear model"
  ),
  # arguments relevant for `combine_plots` function
  labels = c("(i)", "(ii)"),
  title.text = "Robust variants of `lmRob` and `glmRob` \n(from`robustbase` package)",
  nrow = 2
)
```

## MM-type estimators for linear regression on compositional data (`complmrob`)

```{r complmrob, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 6}
# setup
set.seed(123)
library(complmrob)

# data
crimes <- data.frame(
  lifeExp = state.x77[, "Life Exp"],
  USArrests[, c("Murder", "Assault", "Rape")]
)

# model
mUSArr <- complmrob(formula = lifeExp ~ ., data = crimes)

# plot
ggstatsplot::ggcoefstats(
  x = mUSArr,
  title = "MM-type estimators for linear regression on compositional data"
)
```

## fit a nonlinear heteroscedastic model via maximum likelihood (`nlreg`)

```{r nlreg, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
set.seed(123)
library(nlreg)
library(boot)
data(calcium)

# homoscedastic model fit
calcium.nl <-
  nlreg::nlreg(
    formula = cal ~ b0 * (1 - exp(-b1 * time)),
    start = c(b0 = 4, b1 = 0.1),
    data = calcium
  )

# plot
ggstatsplot::ggcoefstats(
  x = calcium.nl,
  conf.int = FALSE,
  title = "fit a nonlinear heteroscedastic model \nvia maximum likelihood"
)
```

## fit a linear model with multiple group fixed effects (`felm`)

Models of class `felm` from `lfe` package are also supported. This method is
used to fit linear models with multiple group fixed effects, similarly to `lm`.
It uses the Method of Alternating projections to sweep out multiple group
effects from the normal equations before estimating the remaining coefficients
with OLS.

```{r felm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(lfe)

# create covariates
x <- rnorm(1000)
x2 <- rnorm(length(x))

# individual and firm
id <- factor(sample(20, length(x), replace = TRUE))
firm <- factor(sample(13, length(x), replace = TRUE))

# effects for them
id.eff <- rnorm(nlevels(id))
firm.eff <- rnorm(nlevels(firm))

# left hand side
u <- rnorm(length(x))
y <- x + 0.5 * x2 + id.eff[id] + firm.eff[firm] + u

# estimate and print result
est <- lfe::felm(formula = y ~ x + x2 | id + firm)

# plot
ggstatsplot::ggcoefstats(
  x = est,
  title = "linear model with multiple group fixed effects"
)
```

## linear models for panel data (`plm`)

```{r plm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# data
set.seed(123)
library(plm)
data("Produc", package = "plm")

# model
plm.mod <-
  plm::plm(
    formula = log(gsp) ~ log(pcap) + log(pc) + log(emp) + unemp,
    data = Produc,
    index = c("state", "year")
  )

# plot
ggstatsplot::ggcoefstats(
  x = plm.mod,
  title = "linear models for panel data"
)
```

## analysis of factorial experiments (`mixed`)

```{r mixed, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 8}
# setup
set.seed(123)
library(afex)
data(sleepstudy)

# data
sleepstudy$mygrp <- sample(1:5, size = 180, replace = TRUE)
sleepstudy$mysubgrp <- NA
for (i in 1:5) {
  filter_group <- sleepstudy$mygrp == i
  sleepstudy$mysubgrp[filter_group] <-
    sample(1:30, size = sum(filter_group), replace = TRUE)
}

# linear model
m1 <- afex::mixed(
  formula = Reaction ~ Days + (1 + Days | Subject),
  data = sleepstudy
)

# linear mixed-effects model
m2 <- afex::mixed(
  formula = Reaction ~ Days + (1 | mygrp / mysubgrp) + (1 | Subject),
  data = sleepstudy
)

# plot
ggstatsplot::combine_plots(
  ggstatsplot::ggcoefstats(m1, title = "linear model (`afex` package)"),
  ggstatsplot::ggcoefstats(m2, title = "linear mixed-effects model (`afex` package)"),
  labels = c("(a)", "(b)")
)
```

## multinomial logit model (`mlogit`)

```{r mlogit, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 7}

# setup
set.seed(123)
library(mlogit)

# data
data("Fishing", package = "mlogit")
Fish <- mlogit.data(Fishing, varying = c(2:9), shape = "wide", choice = "mode")

# a "mixed" model
m <- mlogit(mode ~ price + catch | income, data = Fish)

# plot
ggstatsplot::ggcoefstats(
  x = m,
  title = "multinomial logit model"
)
```

## conditional logit models (`mclogit`)

```{r mclogit, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# setup
set.seed(123)
library(mclogit)
data(Transport)

# model
mod <-
  mclogit::mclogit(
    formula = cbind(resp, suburb) ~ distance + cost,
    data = Transport,
    control = mclogit.control(trace = FALSE)
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Conditional Logit Models"
)
```

## mixed conditional logit models (`mmclogit`)

```{r mmclogit, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 7}
# setup
set.seed(123)
library(mclogit)
data(electors)

# model
mod <-
  mclogit::mclogit(
    formula = cbind(Freq, interaction(time, class)) ~ econ.left / class + welfare / class + auth / class,
    random = ~ 1 | party.time,
    control = mclogit.control(trace = FALSE),
    data = within(electors, party.time <- interaction(party, time))
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Mixed Conditional Logit Models"
)
```

## conditional generalized linear models for clustered data (`cglm`)

```{r cglm, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(cglm)
data(teenpov)

# model
fit.ide <-
  cglm::cglm(
    method = "ts",
    formula = hours ~ nonpov + inschool + spouse + age + mother,
    data = teenpov,
    id = "ID",
    link = "identity"
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit.ide,
  title = "conditional generalized linear models\n for clustered data"
)
```

## Cox proportional hazards regression model (`coxph`)

Fitted proportional hazards regression model - as implemented in the `survival`
package - can also be displayed in a dot-whisker plot.

```{r coxph, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# for reproducibility
set.seed(123)
library(survival)

# create the simplest test data set
test1 <- list(
  time = c(4, 3, 1, 1, 2, 2, 3),
  status = c(1, 1, 1, 0, 1, 1, 0),
  x = c(0, 2, 1, 1, 1, 0, 0),
  sex = c(0, 0, 0, 0, 1, 1, 1)
)

# fit a stratified model
mod <-
  survival::coxph(
    formula = Surv(time, status) ~ x + strata(sex),
    data = test1
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  exponentiate = TRUE,
  title = "Cox proportional hazards regression model"
)
```

## mixed effects Cox model (`coxme`)

```{r coxme, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# setup
set.seed(123)
library(survival)
library(coxme)

# model
fit <- coxme(Surv(y, uncens) ~ trt + (1 | center), eortc)

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  exclude.intercept = FALSE,
  title = "mixed effects Cox model"
)
```

## truncated Gaussian Regression Models (`truncreg`)

```{r truncreg, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 5}
# setup
set.seed(123)
library(truncreg)
library(survival)

# data
data("tobin", package = "survival")

# model
cragg_trunc <-
  truncreg(
    formula = durable ~ age + quant,
    data = tobin,
    subset = durable > 0
  )

# plot
ggstatsplot::ggcoefstats(
  x = cragg_trunc,
  title = "Truncated Gaussian Regression Models"
)
```

## autoregressive integrated moving average (`Arima`)

```{r arima, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# for reproducibility
set.seed(123)

# model
fit <- stats::arima(x = lh, order = c(1, 0, 0))

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  title = "autoregressive integrated moving average"
)
```

## high performance linear model (`speedlm`/`speedglm`)

Example of high performance linear model-

```{r speedlm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
library(speedglm)
set.seed(123)

# model
mod <-
  speedglm::speedlm(
    formula = mpg ~ wt + qsec,
    data = mtcars,
    fitted = TRUE
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "high performance linear model",
  exclude.intercept = FALSE
)
```

Example of high performance generalized linear model-

```{r speedglm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(speedglm)

# data
n <- 50000
k <- 5
y <- rgamma(n, 1.5, 1)
x <- round(matrix(rnorm(n * k), n, k), digits = 3)
colnames(x) <- paste("s", 1:k, sep = "")
da <- data.frame(y, x)
fo <- as.formula(paste("y~", paste(paste("s", 1:k, sep = ""), collapse = "+")))

# model
mod <- speedglm::speedglm(
  formula = fo,
  data = da,
  family = stats::Gamma(log)
)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "high performance generalized linear model"
)
```

## bounded memory linear regression (`biglm`)

```{r biglm, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6}
# setup
set.seed(123)
library(biglm)

# model
bfit1 <- biglm(
  formula = scale(mpg) ~ scale(wt) + scale(disp),
  data = mtcars
)

# plot
ggstatsplot::ggcoefstats(
  x = bfit1,
  title = "bounded memory simple linear regression",
  exclude.intercept = FALSE
)
```

## bounded memory general linear regression (`bigglm`)

```{r bigglm, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6}
# setup
set.seed(123)
library(biglm)
data(trees)

# model
mod <-
  biglm::bigglm(
    formula = log(Volume) ~ log(Girth) + log(Height),
    data = trees,
    chunksize = 10,
    sandwich = TRUE
  )
# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "bounded memory general linear regression"
)
```

## parametric survival regression model (`survreg`)

```{r survreg, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(survival)

# model
mod <-
  survival::survreg(
    formula = Surv(futime, fustat) ~ ecog.ps + rx,
    data = ovarian,
    dist = "logistic"
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  exclude.intercept = FALSE,
  ggtheme = hrbrthemes::theme_ipsum_rc(),
  package = "ggsci",
  palette = "legacy_tron",
  title = "parametric survival regression model"
)
```

## Fixed Effects Individual Slope Estimator (`feis`)

```{r feis, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(feisr)
data("mwp", package = "feisr")

# model
feis.mod <-
  feis(
    formula = lnw ~ marry + enrol + as.factor(yeargr) | exp + I(exp^2),
    data = mwp,
    id = "id",
    robust = TRUE
  )

# plot
ggstatsplot::ggcoefstats(
  x = feis.mod,
  title = "Fixed Effects Individual Slope Estimator"
)
```

## tobit regression (`tobit`)

```{r tobit, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(AER)
data("Affairs", package = "AER")

# model
m1 <-
  AER::tobit(
    formula = affairs ~ age + yearsmarried + religiousness + occupation + rating,
    data = Affairs
  )

# plot
ggstatsplot::ggcoefstats(
  x = m1,
  title = "tobit regression"
)
```

## Aalen's additive regression model for censored data (`aareg`)

```{r aareg, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# model
library(survival)
set.seed(123)
afit <- survival::aareg(
  formula = Surv(time, status) ~ age + sex + ph.ecog,
  data = lung,
  dfbeta = TRUE
)

# plot
ggstatsplot::ggcoefstats(
  x = afit,
  title = "Aalen's additive regression model",
  subtitle = "(for censored data)",
  k = 3
)
```

## relative risk regression model for case-cohort studies (`cch`)

```{r cch, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
# setup
set.seed(123)
library(survival)

# examples come from cch documentation
subcoh <- nwtco$in.subcohort
selccoh <- with(nwtco, rel == 1 | subcoh == 1)
ccoh.data <- nwtco[selccoh, ]
ccoh.data$subcohort <- subcoh[selccoh]

## central-lab histology
ccoh.data$histol <- factor(ccoh.data$histol, labels = c("FH", "UH"))

## tumour stage
ccoh.data$stage <-
  factor(ccoh.data$stage, labels = c("I", "II", "III", "IV"))
ccoh.data$age <- ccoh.data$age / 12 # Age in years

# model
fit.ccP <-
  survival::cch(
    formula = Surv(edrel, rel) ~ stage + histol + age,
    data = ccoh.data,
    subcoh = ~subcohort,
    id = ~seqno,
    cohort.size = 4028
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit.ccP,
  title = "relative risk regression model",
  subtitle = "(for case-cohort studies)",
  conf.level = 0.99
)
```

## ridge regression (`ridgelm`)

For ridge regression, neither statistic values nor confidence intervals for
estimates are available, so only estimates will be displayed.

```{r ridgelm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(MASS)

# model
names(longley)[1] <- "y"
mod <- MASS::lm.ridge(formula = y ~ ., data = longley)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "ridge regression"
)
```

## generalized additive models with integrated smoothness estimation (`gam`)

**Important**: These model outputs contains both parametric and smooth terms.
`ggcoefstats` only displays the parametric terms.

```{r gam_mgcv, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(mgcv)

# model
g <-
  mgcv::gam(
    formula = mpg ~ s(hp) + am + qsec,
    family = stats::quasi(),
    data = mtcars
  )

# plot
ggstatsplot::ggcoefstats(
  x = g,
  title = "generalized additive models \nwith integrated smoothness estimation",
  subtitle = "using `mgcv` package"
)
```

## generalized additive model (`Gam`)

```{r Gam, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(gam)

# model
g <- gam::gam(
  formula = mpg ~ s(hp, 4) + am + qsec,
  data = mtcars
)

# plot
ggstatsplot::ggcoefstats(
  x = g,
  title = "generalized additive model",
  subtite = "(using `gam` package)"
)
```

## linear mixed-effects models (`lme`)

```{r lme, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# for reproducibility
set.seed(123)
library(lme4)
library(nlme)
data("sleepstudy")

# model
mod <-
  nlme::lme(
    fixed = Reaction ~ Days,
    random = ~ 1 + Days | Subject,
    data = sleepstudy
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "linear mixed-effects models (`lme`)"
)
```

## linear model using generalized least squares (`gls`)

The `nlme` package provides a function to fit a linear model using generalized
least squares. The errors are allowed to be correlated and/or have unequal
variances.

```{r gls, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# for reproducibility
set.seed(123)
library(nlme)

# model
mod <-
  nlme::gls(
    model = follicles ~ sin(2 * pi * Time) + cos(2 * pi * Time),
    data = Ovary,
    correlation = corAR1(form = ~ 1 | Mare)
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  stats.label.color = "black",
  ggtheme = hrbrthemes::theme_ipsum_ps(),
  ggstatsplot.layer = FALSE,
  exclude.intercept = FALSE,
  title = "generalized least squares model"
)
```

## ordinary least squares with robust standard errors (`lm_robust`)

```{r lm_robust, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# for reproducibility
set.seed(123)
library(estimatr)

# model
mod <- lm_robust(
  formula = mpg ~ gear + wt + cyl,
  data = mtcars
)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "ordinary least squares \nwith robust standard errors"
)
```

## inference for estimated coefficients (`coeftest`)

```{r coeftest, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# setup
set.seed(123)
library(lmtest)

# load data and fit model
data("Mandible", package = "lmtest")
fm <- stats::lm(formula = length ~ age, data = Mandible, subset = (age <= 28))

# the following commands lead to the same tests:
ct <- lmtest::coeftest(fm)

# plot
ggstatsplot::ggcoefstats(
  x = ct,
  plot = "inference for estimated coefficients",
  conf.level = 0.99
)
```

## robust regression using an M estimator (`rlm`)

```{r rlm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# for reproducibility
set.seed(123)

# model
mod <- MASS::rlm(formula = mpg ~ am * cyl, data = mtcars)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  point.args = list(color = "red", shape = 15),
  vline.args = list(size = 1, color = "#CC79A7", linetype = "dotdash"),
  stats.label.color = c("#0072B2", "#D55E00", "darkgreen"),
  title = "robust regression using an M estimator",
  ggtheme = ggthemes::theme_stata(),
  ggstatsplot.layer = FALSE
)
```

## quantile regression (`rq`)

```{r rq, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# for reproducibility
set.seed(123)
library(quantreg)

# loading dataframe needed for the analyses below
data(stackloss)

# plot
ggstatsplot::ggcoefstats(
  x = quantreg::rq(
    formula = stack.loss ~ stack.x,
    data = stackloss,
    method = "br"
  ),
  se.type = "iid",
  title = "quantile regression"
)
```

## nonlinear quantile regression estimates (`nlrq`)

```{r nlrq, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
library(quantreg)

# preparing data
Dat <- NULL
Dat$x <- rep(1:25, 20)
set.seed(123)
Dat$y <- stats::SSlogis(Dat$x, 10, 12, 2) * rnorm(500, 1, 0.1)

# then fit the median using nlrq
Dat.nlrq <-
  quantreg::nlrq(
    formula = y ~ SSlogis(x, Asym, mid, scal),
    data = Dat,
    tau = 0.5,
    trace = FALSE
  )

# plot
ggstatsplot::ggcoefstats(
  x = Dat.nlrq,
  title = "non-linear quantile regression",
  se.type = "nid"
)
```

## additive quantile regression (`rqss`)

```{r rqss, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# setup
set.seed(123)
library(quantreg)
data(CobarOre)

# model
fCO <- rqss(formula = z ~ qss(cbind(x, y), lambda = .08), data = CobarOre)

# model info
ggstatsplot::ggcoefstats(
  x = fCO,
  title = "Additive Quantile Regression",
  exclude.intercept = FALSE
)
```

## instrumental-variable regression (`ivreg`)

```{r ivreg, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
suppressPackageStartupMessages(library(AER))
set.seed(123)
data("CigarettesSW", package = "AER")

# model
ivr <- AER::ivreg(
  formula = log(packs) ~ income | population,
  data = CigarettesSW,
  subset = year == "1995"
)

# plot
ggstatsplot::ggcoefstats(
  x = ivr,
  title = "instrumental-variable regression"
)
```

## causal mediation analysis (`mediate`)

```{r mediate, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(mediation)
data(jobs)

# base models
b <-
  stats::lm(
    formula = job_seek ~ treat + econ_hard + sex + age,
    data = jobs
  )
c <-
  stats::lm(
    formula = depress2 ~ treat + job_seek + econ_hard + sex + age,
    data = jobs
  )

# mediation model
mod <-
  mediation::mediate(
    model.m = b,
    model.y = c,
    sims = 50,
    treat = "treat",
    mediator = "job_seek"
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "causal mediation analysis"
)
```

## Model II regression (`lmodel2`)

```{r lmodel2, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(lmodel2)
data(mod2ex2)

# model
Ex2.res <-
  lmodel2::lmodel2(
    formula = Prey ~ Predators,
    data = mod2ex2,
    range.y = "relative",
    range.x = "relative",
    nperm = 99
  )

# plot
ggstatsplot::ggcoefstats(
  x = Ex2.res,
  exclude.intercept = FALSE,
  title = "Model II regression"
)
```

## generalized additive models for location scale and shape (`gamlss`)

```{r gamlss, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(gamlss)

# model
g <-
  gamlss::gamlss(
    formula = y ~ pb(x),
    sigma.fo = ~ pb(x),
    family = BCT,
    data = abdom,
    method = mixed(1, 20)
  )

# plot
ggstatsplot::ggcoefstats(
  x = g,
  title = "generalized additive models \nfor location scale and shape"
)
```

## generalized method of moment estimation (`gmm`)

```{r gmm, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 5}
# setup
set.seed(123)
library(gmm)

# examples come from the "gmm" package
## CAPM test with GMM
data(Finance)
r <- Finance[1:300, 1:10]
rm <- Finance[1:300, "rm"]
rf <- Finance[1:300, "rf"]

z <- as.matrix(r - rf)
t <- nrow(z)
zm <- rm - rf
h <- matrix(zm, t, 1)
res <- gmm::gmm(z ~ zm, x = h)

# plot
ggstatsplot::ggcoefstats(
  x = res,
  package = "palettetown",
  palette = "victreebel",
  title = "generalized method of moment estimation"
)
```

## fit a GLM with lasso or elasticnet regularization (`glmnet`)

Although these models are not directly supported in `ggcoefstats` because of the
sheer number of terms that are typically present. But this function can still be
used to selectively show few of the terms of interest:

```{r glmnet, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# setup
library(glmnet)
set.seed(2014)

# creating a dataframe
x <- matrix(rnorm(100 * 20), 100, 20)
y <- rnorm(100)
fit1 <- glmnet::glmnet(x, y)
(df <- broom::tidy(fit1))

# displaying only a certain step
ggstatsplot::ggcoefstats(x = dplyr::filter(df, step == 4))
```

## joint model to time-to-event data and multivariate longitudinal data (`mjoint`)

```{r mjoint, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 8}
# setup
set.seed(123)
library(joineRML)
data(heart.valve)

# data
hvd <- heart.valve[!is.na(heart.valve$log.grad) &
  !is.na(heart.valve$log.lvmi) &
  heart.valve$num <= 50, ]

# model
fit <-
  joineRML::mjoint(
    formLongFixed = list(
      "grad" = log.grad ~ time + sex + hs,
      "lvmi" = log.lvmi ~ time + sex
    ),
    formLongRandom = list(
      "grad" = ~ 1 | num,
      "lvmi" = ~ time | num
    ),
    formSurv = Surv(fuyrs, status) ~ age,
    data = hvd,
    inits = list("gamma" = c(0.11, 1.51, 0.80)),
    timeVar = "time"
  )

# extract the survival fixed effects and plot them
ggstatsplot::ggcoefstats(
  x = fit,
  conf.level = 0.99,
  exclude.intercept = FALSE,
  component = "longitudinal",
  package = "yarrr",
  palette = "basel",
  title = "joint model to time-to-event data \nand multivariate longitudinal data"
)
```

## exponential-family random graph models (`ergm`)

```{r ergm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# load the Florentine marriage network data
set.seed(123)
suppressPackageStartupMessages(library(ergm))
data(florentine)

# fit a model where the propensity to form ties between
# families depends on the absolute difference in wealth
gest <- ergm(flomarriage ~ edges + absdiff("wealth"))

# plot
ggstatsplot::ggcoefstats(
  x = gest,
  conf.level = 0.99,
  title = "exponential-family random graph models"
)
```

## TERGM by bootstrapped pseudolikelihood or MCMC MLE (`btergm`)

```{r btergm, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# setup
library(network)
library(btergm)
set.seed(123)

# create 10 random networks with 10 actors
networks <- list()
for (i in 1:10) {
  mat <- matrix(rbinom(100, 1, .25), nrow = 10, ncol = 10)
  diag(mat) <- 0 # loops are excluded
  nw <- network(mat) # create network object
  networks[[i]] <- nw # add network to the list
}

# create 10 matrices as covariate
covariates <- list()
for (i in 1:10) {
  mat <- matrix(rnorm(100), nrow = 10, ncol = 10)
  covariates[[i]] <- mat # add matrix to the list
}

# model
fit <-
  btergm::btergm(
    formula = networks ~ edges + istar(2) + edgecov(covariates),
    parallel = "multicore",
    ncpus = 4,
    R = 100,
    verbose = FALSE
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  title = "Terms used in Exponential Family Random Graph Models",
  subtitle = "by bootstrapped pseudolikelihood or MCMC MLE"
)
```

## generalized autoregressive conditional heteroscedastic (`garch`)

```{r garch, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(tseries)
data(EuStockMarkets)
dax <- diff(log(EuStockMarkets))[, "DAX"]
dax.garch <- tseries::garch(x = dax, trace = FALSE)

# plot
ggstatsplot::ggcoefstats(
  x = dax.garch,
  title = "generalized autoregressive \nconditional heteroscedastic (GARCH)"
)
```

## maximum-likelihood fitting of univariate distributions (`fitdistr`)

```{r fitdistr, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# model
set.seed(123)
library(MASS)
x <- rnorm(100, 5, 2)
fit <- MASS::fitdistr(x, dnorm, list(mean = 3, sd = 1))

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  title = "maximum-likelihood fitting of \nunivariate distributions",
  ggtheme = ggthemes::theme_pander()
)
```

## maximum likelihood estimation (`mle2`)

```{r mle2, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 4}
# setup
set.seed(123)
library(bbmle)

# data
x <- 0:10
y <- c(26, 17, 13, 12, 20, 5, 9, 8, 5, 4, 8)
d <- data.frame(x, y)

# custom function
LL <- function(ymax = 15, xhalf = 6) {
  -sum(stats::dpois(y, lambda = ymax / (1 + x / xhalf), log = TRUE))
}

# use default parameters of LL
fit <- bbmle::mle2(LL, fixed = list(xhalf = 6))

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  title = "maximum likelihood estimation",
  ggtheme = ggthemes::theme_excel_new()
)
```

## summary grid from `emmeans` package (`emmGrid`)

```{r emmGrid, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(emmeans)

# linear model for sales of oranges per day
oranges_lm1 <- stats::lm(
  formula = sales1 ~ price1 + price2 + day + store,
  data = oranges
)

# reference grid; see vignette("basics", package = "emmeans")
oranges_rg1 <- emmeans::ref_grid(oranges_lm1)
marginal <- emmeans::emmeans(oranges_rg1, "day")

# looking at the tidy output (you can do this yourself)
# broom::tidy(marginal)

# plotting it using `ggcoefstats`
# note that since there was column called `term`, the function created one
ggstatsplot::ggcoefstats(
  x = marginal,
  point.args = list(color = "darkgreen", shape = 9),
  title = "summary grid from `emmeans` package"
)
```

## Cochrane-Orcutt estimation (`orcutt`)

```{r orcutt, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# model
library(orcutt)
set.seed(123)
reg <- stats::lm(formula = mpg ~ wt + qsec + disp, data = mtcars)
co <- orcutt::cochrane.orcutt(reg)

# plot
ggstatsplot::ggcoefstats(
  x = co,
  title = "Cochrane-Orcutt estimation"
)
```

## confusion matrix (`confusionMatrix`)

```{r confusionMatrix, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
# setup
library(caret)
set.seed(123)

# setting up confusion matrix
two_class_sample1 <- as.factor(sample(letters[1:2], 100, TRUE))
two_class_sample2 <- as.factor(sample(letters[1:2], 100, TRUE))

two_class_cm <- caret::confusionMatrix(two_class_sample1, two_class_sample2)

# plot
ggstatsplot::ggcoefstats(
  x = two_class_cm,
  by.class = TRUE,
  title = "confusion matrix"
)
```

## dose-response models/curves (`drc`)

```{r drc, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 5}
# setup
set.seed(123)
library(drc)

# model
mod <-
  drc::drm(
    formula = dead / total ~ conc,
    curveid = type,
    weights = total,
    data = selenium,
    fct = LL.2(),
    type = "binomial"
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  conf.level = 0.99,
  title = "Dose-Response Curves"
)
```

## Flexible parametric regression for time-to-event data (`flexsurvreg`)

```{r flexsurvreg, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 7}
# setup
set.seed(123)
library(flexsurv)
data(ovarian)

# compare generalized gamma fit with Weibull
fitg <-
  flexsurvreg(
    formula = Surv(futime, fustat) ~ 1,
    data = ovarian,
    dist = "gengamma"
  )

ggstatsplot::ggcoefstats(
  x = fitg,
  title = "Flexible parametric regression for time-to-event data"
)
```

## panel regression models fit via multilevel modeling (`wblm`)

```{r wblm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 7}
# setup
set.seed(123)
library(panelr)

# data
data("WageData")
wages <- panelr::panel_data(data = WageData, id = id, wave = t)

# model
mod <- wbm(
  formula = lwage ~ lag(union) + wks | blk + fem | blk * lag(union),
  data = wages
)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "panel regression models fit \nvia multilevel modeling"
)
```

## panel regression models fit via generalized estimating equations (`wbgee`)

```{r wbgee, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(panelr)
data("WageData")

# data
wages <- panelr::panel_data(data = WageData, id = id, wave = t)

# model
model <-
  panelr::wbgee(
    formula = lwage ~ lag(union) + wks | blk + fem | blk * lag(union),
    data = wages
  )

# plot
ggstatsplot::ggcoefstats(
  x = model,
  exclude.intercept = FALSE,
  conf.level = 0.99,
  title = "panel regression models fit \nvia generalized estimating equations"
)
```

## Censored Regression with Conditional Heteroscedasticy (`crch`)

```{r crch, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 8}
# setup
set.seed(123)
library(crch)
data("RainIbk")

# mean and standard deviation of square root transformed ensemble forecasts
RainIbk$sqrtensmean <- apply(sqrt(RainIbk[, grep("^rainfc", names(RainIbk))]), 1, mean)
RainIbk$sqrtenssd <- apply(sqrt(RainIbk[, grep("^rainfc", names(RainIbk))]), 1, sd)

# fit linear regression model with Gaussian distribution
CRCH <-
  crch(
    formula = sqrt(rain) ~ sqrtensmean,
    data = RainIbk,
    dist = "gaussian"
  )

# plot
ggstatsplot::ggcoefstats(
  x = CRCH,
  title = "Censored Regression with Conditional Heteroscedasticy"
)
```

## Marginal Models For Correlated Ordinal Multinomial Responses (`LORgee`)

```{r LORgee, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 8}
# setup
set.seed(123)
library(multgee)
data("arthritis")

# model
fit <-
  ordLORgee(
    formula = y ~ factor(time) + factor(trt) + factor(baseline),
    link = "logit",
    id = id,
    repeated = time,
    data = arthritis,
    LORstr = "uniform"
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  title = "Marginal Models For Correlated Ordinal Multinomial Responses",
  package = "ggthemes",
  palette = "Classic 20"
)
```

## summary measures for count data (`epi.2by2`)

```{r epi.2by2, warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6}
# setup
set.seed(123)
library(epiR)

# data
dat <- matrix(c(13, 2163, 5, 3349), nrow = 2, byrow = TRUE)
rownames(dat) <- c("DF+", "DF-")
colnames(dat) <- c("FUS+", "FUS-")

# model
fit <-
  epiR::epi.2by2(
    dat = as.table(dat),
    method = "cross.sectional",
    conf.level = 0.95,
    units = 100,
    outcome = "as.columns"
  )

# tidy dataframe
ggstatsplot::ggcoefstats(
  x = fit,
  parameters = "moa",
  title = "Summary measures for count data \npresented in a 2 by 2 table"
)
```

## Bayesian generalized (non-)linear multivariate multilevel models (`brmsfit`)

```{r brmsfit, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(brms)

# prior
bprior1 <- prior(student_t(5, 0, 10), class = b) + prior(cauchy(0, 2), class = sd)

# model
fit1 <-
  brms::brm(
    formula = count ~ Age + Base * Trt + (1 | patient),
    data = epilepsy,
    family = poisson(),
    prior = bprior1,
    silent = TRUE
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit1,
  exclude.intercept = FALSE,
  conf.method = "HPDinterval",
  title = "Bayesian generalized (non-)linear \nmultivariate multilevel models",
  subtitle = "using `brms` package"
)
```

Let's see another example where we use `brms` to run the same model on multiple
datasets-

```{r brmsfit_multiple, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 7}
# setup
set.seed(123)
library(brms)
library(mice)

# data
imp <- mice::mice(data = nhanes2, print = FALSE)

# fit the model using brms
fit <-
  brms::brm_multiple(
    formula = bmi ~ age + hyp + chl,
    data = imp,
    chains = 1
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  title = "Same `brms` model with multiple datasets",
  conf.level = 0.99
)
```

## Bayesian regression models via Stan (`stanreg`)

```{r stanreg, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# set up
set.seed(123)
library(rstanarm)

# model
fit <-
  rstanarm::stan_glm(
    formula = mpg ~ wt + am,
    data = mtcars,
    chains = 1
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  title = "Bayesian generalized linear models via Stan"
)
```

## Bayesian multivariate generalized linear models via Stan (`stanmvreg`)

```{r stanmvreg, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(rstanarm)
pbcLong$ybern <- as.integer(pbcLong$logBili >= mean(pbcLong$logBili))

# model
mod <-
  rstanarm::stan_mvmer(
    formula = list(
      ybern ~ year + (1 | id),
      albumin ~ sex + year + (year | id)
    ),
    data = pbcLong,
    cores = 4,
    seed = 12345,
    iter = 1000
  )

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  title = "Bayesian multivariate generalized linear models \nvia Stan"
)
```

## Bayesian nonlinear models via Stan (`nlstanreg`)

```{r nlstanreg, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# setup
set.seed(123)
library(rstanarm)
data("Orange", package = "datasets")
Orange$circumference <- Orange$circumference / 100
Orange$age <- Orange$age / 100

# model
fit <-
  rstanarm::stan_nlmer(
    formula = circumference ~ SSlogis(age, Asym, xmid, scal) ~ Asym | Tree,
    data = Orange,
    # for speed only
    chains = 1,
    iter = 1000
  )

# plot
ggstatsplot::ggcoefstats(
  x = fit,
  title = "Bayesian nonlinear models via Stan"
)
```

## multivariate generalized linear mixed models (`MCMCglmm`)

```{r MCMCglmm, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
# setup
set.seed(123)
library(lme4)
library(MCMCglmm)
data(sleepstudy)

# model
mm0 <-
  MCMCglmm::MCMCglmm(
    fixed = scale(Reaction) ~ scale(Days),
    random = ~Subject,
    data = sleepstudy,
    nitt = 4000,
    pr = TRUE,
    verbose = FALSE
  )

# plot
ggstatsplot::ggcoefstats(
  x = mm0,
  title = "multivariate generalized linear mixed model",
  conf.method = "HPDinterval",
  exclude.intercept = FALSE,
  robust = TRUE
)
```

## Markov Chain Monte Carlo objects (`mcmc`)

```{r mcmc, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 5}
# loading the data
set.seed(123)
library(coda)
data(line)

# select first chain
x1 <- line[[1]]

# plot
ggstatsplot::ggcoefstats(
  x = x1,
  title = "Markov Chain Monte Carlo objects",
  robust = TRUE,
  ess = TRUE
)
```

## MCMC with Just Another Gibbs Sampler (`rjags`)

```{r R2jags, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 6}
# setup
set.seed(123)
library(R2jags)

# An example model file is given in:
model.file <- system.file(package = "R2jags", "model", "schools.txt")

# data
J <- 8.0
y <- c(28.4, 7.9, -2.8, 6.8, -0.6, 0.6, 18.0, 12.2)
sd <- c(14.9, 10.2, 16.3, 11.0, 9.4, 11.4, 10.4, 17.6)

# setting up model
jags.data <- list("y", "sd", "J")
jags.params <- c("mu", "sigma", "theta")
jags.inits <- function() {
  list("mu" = rnorm(1), "sigma" = runif(1), "theta" = rnorm(J))
}

# model fitting
jagsfit <-
  R2jags::jags(
    data = list("y", "sd", "J"),
    inits = jags.inits,
    jags.params,
    n.iter = 10,
    model.file = model.file
  )

# plot
ggstatsplot::ggcoefstats(
  x = jagsfit,
  title = "Markov Chain Monte Carlo with\nJust Another Gibbs Sampler"
)
```

## latent variable model (`lavaan`)

```{r lavaan, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 6}
# setup
set.seed(123)
library(lavaan)

# The Holzinger and Swineford (1939) example
HS.model <- " visual =~ x1 + x2 + x3
textual =~ x4 + x5 + x6
speed =~ x7 + x8 + x9 "

# model
fit <-
  lavaan::lavaan(
    HS.model,
    data = HolzingerSwineford1939,
    auto.var = TRUE,
    auto.fix.first = TRUE,
    auto.cov.lv.x = TRUE
  )

# tidy
ggstatsplot::ggcoefstats(
  x = fit,
  title = "latent variable model",
  conf.level = 0.99
)
```

## Bayesian latent variable model (`blavaan`)

```{r blavaan, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 6}
# setup
set.seed(123)
library(blavaan)
future::plan("multiprocess")

# The Holzinger and Swineford (1939) example
HS.model <- " visual =~ x1 + x2 + x3
textual =~ x4 + x5 + x6
speed =~ x7 + x8 + x9 "

# model
fit <-
  blavaan::blavaan(
    HS.model,
    data = HolzingerSwineford1939,
    auto.var = TRUE,
    auto.fix.first = TRUE,
    auto.cov.lv.x = TRUE
  )

# tidy
ggstatsplot::ggcoefstats(
  x = fit,
  title = "Bayesian latent variable model"
)
```

## regression models with `list` outputs

Note that a number of regression models will return an object of class `list`,
in which case this function will fail. But often you can extract the object of
interest from this list and use it to plot the regression coefficients.

```{r list_gamm4, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 10}
# setup
library(gamm4)
set.seed(123)

# data
dat <- gamSim(1, n = 400, scale = 2)

# now add 20 level random effect `fac'...
dat$fac <- fac <- as.factor(sample(1:20, 400, replace = TRUE))
dat$y <- dat$y + model.matrix(~ fac - 1) %*% rnorm(20) * .5

# model object
br <-
  gamm4::gamm4(
    formula = y ~ s(x0) + x1 + s(x2),
    data = dat,
    random = ~ (1 | fac)
  )

# looking at the classes of the objects contained in the list
purrr::map(br, class)

# plotting
ggstatsplot::combine_plots(
  # first object plot (only parametric terms are shown)
  ggstatsplot::ggcoefstats(
    x = br$gam,
    exclude.intercept = FALSE,
    title = "generalized additive model (parametric terms)",
    k = 3
  ),
  # second object plot
  ggstatsplot::ggcoefstats(
    x = br$mer,
    exclude.intercept = FALSE,
    title = "linear mixed-effects model",
    k = 3
  ),
  labels = c("(a)", "(b)"),
  nrow = 1
)
```

# meta-analysis

In case the estimates you are displaying come from multiple studies, you can
also use this function to carry out random-effects meta-analysis (as implemented
in the [metafor](http://www.metafor-project.org/doku.php) package; see
`metafor::rma()`).

The dataframe you enter **must** contain at the minimum the following three
columns- `term`, `estimate`, `std.error`.

### parametric

```{r meta1, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 8}
# setup
set.seed(123)
library(metaplus)

# renaming to what the function expects
df <- dplyr::rename(mag, estimate = yi, std.error = sei, term = study)

# plot
ggstatsplot::ggcoefstats(
  x = df,
  meta.analytic.effect = TRUE,
  meta.type = "parametric",
  title = "parametric random-effects meta-analysis"
)
```

### robust

```{r meta2, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 8}
# plot
ggstatsplot::ggcoefstats(
  x = df,
  meta.analytic.effect = TRUE,
  meta.type = "robust",
  title = "robust random-effects meta-analysis"
)
```

### Bayesian

```{r meta3, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 8}
# plot
ggstatsplot::ggcoefstats(
  x = df,
  meta.analytic.effect = TRUE,
  meta.type = "bayes",
  title = "Bayesian random-effects meta-analysis"
)
```

You can also provide a dataframe containing all the other relevant
information for additionally displaying labels with statistical information.

```{r meta4, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 7}
# let's make up a dataframe (with all available details)
df_full <-
  tibble::tribble(
    ~term, ~statistic, ~estimate, ~std.error, ~p.value, ~df.residual,
    "study1", 0.158, 0.0665, 0.778, 0.875, 5L,
    "study2", 1.33, 0.542, 0.280, 0.191, 10L,
    "study3", 1.24, 0.045, 0.030, 0.001, 12L,
    "study4", 0.156, 0.500, 0.708, 0.885, 8L,
    "study5", 0.33, 0.032, 0.280, 0.101, 2L,
    "study6", 1.04, 0.085, 0.030, 0.001, 3L
  )

# plot
ggstatsplot::ggcoefstats(
  x = df_full,
  meta.analytic.effect = TRUE,
  statistic = "t",
  package = "LaCroixColoR",
  palette = "paired"
)
```

# dataframes

Sometimes you don't have a model object but a custom dataframe that you want
display using this function. If a data frame is to be plotted, it **must**
contain columns named `term` (names of predictors), and `estimate`
(corresponding estimates of coefficients or other quantities of interest). Other
optional columns are `conf.low` and `conf.high` (for confidence intervals), and
`p.value`. You will also have to specify the type of statistic relevant for
regression models (`"t"`, `"z"`, `"f"`) in case you want to display statistical
labels.

```{r dataframe, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
# set up
set.seed(123)
library(ggstatsplot)
library(gapminder)

# data for running regression models
df <- dplyr::filter(.data = gapminder::gapminder, continent != "Oceania")

# saving results from regression
df_results <-
  purrr::pmap(
    .l = list(
      data = list(df),
      formula = list(scale(lifeExp) ~ scale(gdpPercap) + (gdpPercap | country)),
      grouping.vars = alist(continent),
      output = list("tidy", "glance")
    ),
    .f = groupedstats::grouped_lmer
  ) %>%
  dplyr::full_join(x = .[[1]], y = .[[2]], by = "continent")

# modifying the results so to be compatible with the `ggcoefstats` requirement
(df_results %<>% dplyr::filter(.data = ., term != "(Intercept)"))

# plot
ggstatsplot::ggcoefstats(
  x = df_results,
  statistic = "t",
  sort = "ascending",
  title = "Relationship between life expectancy and GDP",
  subtitle = "Source: Gapminder foundation",
  caption = "Data from Oceania continent not included"
)
```

## And much more...

This vignette was supposed to give a comprehensive account of regression models
supported by `ggcoefstats`. The list of supported models will keep expanding as
additional tidiers are added to the `broom`, `broom.mixed`, `parameters`, and
`performance` packages.

Note that not **all** models supported in these packages will be supported by
`ggcoefstats`. In particular, classes of objects for which there is no column
for `estimate` (e.g., `kmeans`, `optim`, `muhaz`, `survdiff`, `zoo`, etc.) are
not supported.

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>
