---
title: "ggcorrmat"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ggcorrmat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE

source("../setup.R")
```

```{r}
#| label = "suggested_pkgs",
#| include = FALSE

pkgs <- c(
  "gapminder",
  "svglite"
)

successfully_loaded <- purrr::map_lgl(pkgs, requireNamespace, quietly = TRUE)
can_evaluate <- all(successfully_loaded)

if (can_evaluate) {
  purrr::walk(pkgs, library, character.only = TRUE)
  knitr::opts_chunk$set(eval = TRUE, dev = "svglite")
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

---

Lifecycle: [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)

The function `ggcorrmat()` provides a quick way to produce **publication-ready correlation matrix** (aka *correlalogram*) plot. The function can also be used
for quick **data exploration**. In addition to the plot, it can also be used to
get a correlation coefficient matrix or the associated *p*-value matrix.
This function is a convenient wrapper around `ggcorrplot::ggcorrplot()`
function with some additional functionality.

We will see examples of how to use this function in this vignette with the
`gapminder` and `diamonds` dataset.

To begin with, here are some instances where you would want to use
`ggcorrmat`-

  - to easily visualize a correlation matrix using `{ggplot2}`
  - to quickly explore correlation between (all) numeric variables in the
  dataset

## Correlation matrix plot with `ggcorrmat()`

For the first example, we will use the `gapminder` dataset (available in
eponymous [package](https://CRAN.R-project.org/package=gapminder) on CRAN)
provides values for life expectancy, Gross Domestic Product (GDP) per capita,
and population, every five years, from 1952 to 2007, for each of 142 countries
and was collected by the Gapminder Foundation. Let's have a look at the data-

```{r}
#| label = "gapminder"
library(gapminder)
library(dplyr)

dplyr::glimpse(gapminder)
```

Let's say we are interested in studying correlation between population of a
country, average life expectancy, and GDP per capita across countries only for
the year 2007.

The simplest way to get a correlation matrix is to stick to the defaults-

```{r}
#| label = "ggcorrmat1",
#| fig.height = 6,
#| fig.width = 6

## select data only from the year 2007
gapminder_2007 <- dplyr::filter(gapminder::gapminder, year == 2007)

## producing the correlation matrix
ggcorrmat(
  data = gapminder_2007, ## data from which variable is to be taken
  cor.vars = lifeExp:gdpPercap ## specifying correlation matrix variables
)
```

This plot can be further modified with additional arguments-

```{r}
#| label = "ggcorrmat2",
#| fig.height = 6,
#| fig.width = 6
ggcorrmat(
  data = gapminder_2007, ## data from which variable is to be taken
  cor.vars = lifeExp:gdpPercap, ## specifying correlation matrix variables
  cor.vars.names = c(
    "Life Expectancy",
    "population",
    "GDP (per capita)"
  ),
  type = "np", ## which correlation coefficient is to be computed
  lab.col = "red", ## label color
  ggtheme = ggplot2::theme_light(), ## selected ggplot2 theme
  ## turn off default ggestatsplot theme overlay
  matrix.type = "lower", ## correlation matrix structure
  colors = NULL, ## turning off manual specification of colors
  palette = "category10_d3", ## choosing a color palette
  package = "ggsci", ## package to which color palette belongs
  title = "Gapminder correlation matrix", ## custom title
  subtitle = "Source: Gapminder Foundation" ## custom subtitle
)
```

As seen from this correlation matrix, although there is no relationship between
population and life expectancy worldwide, at least in 2007, there is a strong
positive relationship between GDP, a well-established indicator of a country's
economic performance.

Given that there were only three variables, this doesn't look that impressive.
So let's work with another example from `{ggplot2}` package: the `diamonds`
[dataset](http://ggplot2.tidyverse.org/reference/diamonds.html). This dataset
contains the prices and other attributes of almost 54,000 diamonds.

Let's have a look at the data-

```{r}
#| label = "diamonds"
library(ggplot2)

dplyr::glimpse(ggplot2::diamonds)
```

Let's see the correlation matrix between different attributes of the diamond and
the price.

```{r}
#| label = "ggcorrmat3",
#| fig.height = 7,
#| fig.width = 7

## let's use just 5% of the data to speed it up
ggcorrmat(
  data = dplyr::sample_frac(ggplot2::diamonds, size = 0.05),
  cor.vars = c(carat, depth:z), ## note how the variables are getting selected
  cor.vars.names = c(
    "carat",
    "total depth",
    "table",
    "price",
    "length (in mm)",
    "width (in mm)",
    "depth (in mm)"
  ),
  ggcorrplot.args = list(outline.color = "black", hc.order = TRUE)
)
```

We can make a number of changes to this basic correlation matrix. For example,
since we were interested in relationship between price and other attributes,
let's make the `price` column to the the first column.

```{r}
#| label = "ggcorrmat4",
#| fig.height = 7,
#| fig.width = 7

## let's use just 5% of the data to speed it up
ggcorrmat(
  data = dplyr::sample_frac(ggplot2::diamonds, size = 0.05),
  cor.vars = c(price, carat, depth:table, x:z), ## note how the variables are getting selected
  cor.vars.names = c(
    "price",
    "carat",
    "total depth",
    "table",
    "length (in mm)",
    "width (in mm)",
    "depth (in mm)"
  ),
  type = "np",
  title = "Relationship between diamond attributes and price",
  subtitle = "Dataset: Diamonds from ggplot2 package",
  colors = c("#0072B2", "#D55E00", "#CC79A7"),
  pch = "square cross",
  ## additional aesthetic arguments passed to `ggcorrmat()`
  ggcorrplot.args = list(
    lab_col = "yellow",
    lab_size = 6,
    tl.srt = 90,
    pch.col = "white",
    pch.cex = 14
  )
) + ## modification outside `{ggstatsplot}` using `{ggplot2}` functions
  ggplot2::theme(
    axis.text.x = ggplot2::element_text(
      margin = ggplot2::margin(t = 0.15, r = 0.15, b = 0.15, l = 0.15, unit = "cm")
    )
  )
```

As seen here, and unsurprisingly, the strongest predictor of the diamond price
is its carat value, which a unit of mass equal to 200 mg. In other words, the
heavier the diamond, the more expensive it is going to be.

## Grouped analysis with `grouped_ggcorrmat`

What if we want to do the same analysis separately for each quality of the
diamond `cut` (Fair, Good, Very Good, Premium, Ideal)? 

`{ggstatsplot}` provides a special helper function for such instances:
`grouped_ggcorrmat()`. This is merely a wrapper function around
`combine_plots()`. It applies `ggcorrmat()` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. 

```{r}
#| label = "ggcorrmat7",
#| fig.height = 16,
#| fig.width = 10

grouped_ggcorrmat(
  ## arguments relevant for `ggcorrmat()`
  data = ggplot2::diamonds,
  cor.vars = c(price, carat, depth),
  grouping.var = cut,
  ## arguments relevant for `combine_plots()`
  plotgrid.args = list(nrow = 3),
  annotation.args = list(
    tag_levels = "a",
    title = "Relationship between diamond attributes and price across cut",
    caption = "Dataset: Diamonds from ggplot2 package"
  )
)
```

Note that this function also makes it easy to run the same correlation matrix
across different levels of a factor/grouping variable.

## Data frame

If you want a data frame of (grouped) correlation matrix, use
`correlation::correlation()` instead. It can also do grouped analysis when 
used with output from `dplyr::group_by()`.

## Grouped analysis with `ggcorrmat()` + `{purrr}`

Although `grouped_` function is good for quickly exploring the data, it reduces
the flexibility with which this function can be used. This is the because the
common parameters used are applied to plots corresponding to all levels of the
grouping variable and there is no way to customize the arguments for different
levels of the grouping variable. We will see how this can be done using the
`{purrr}` package.

See the associated vignette here:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html>

## Summary of graphics and tests

Details about underlying functions used to create graphics and statistical tests carried out can be found in the function documentation:
<https://indrajeetpatil.github.io/ggstatsplot/reference/gghistostats.html>

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
