---
title: "ggdotplotstats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggdotplotstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
# show me all columns
options(tibble.width = Inf, pillar.bold = TRUE, pillar.subtle_num = TRUE)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  warning = FALSE,
  message = FALSE,
  out.width = "100%",
  comment = "#>"
)
```

The function `ggstatsplot::ggdotplotstats` can be used for **data exploration**
and to provide an easy way to make **publication-ready dot plots/charts** with
appropriate and selected statistical details embedded in the plot itself. In
this vignette we will explore several examples of how to use it.

This function is a sister function of `gghistostats` with the difference being
it expects a labeled numeric variable.

## Distribution of a sample with `ggdotplotstats`

Let's begin with a very simple example from the `ggplot2` package
(`ggplot2::mpg`), a subset of the fuel economy data that the EPA makes available
on <http://fueleconomy.gov>.

```{r mpg}
# looking at the structure of the data using glimpse
dplyr::glimpse(x = ggplot2::mpg)
```

Let's say we want to visualize the distribution of mileage by car manufacturer. 

```{r mpg2, fig.height = 7, fig.width = 9}
# for reproducibility
set.seed(123)

# removing factor level with very few no. of observations
df <- dplyr::filter(.data = ggplot2::mpg, cyl %in% c("4", "6"))

# creating a vector of colors using `paletteer` package
paletter_vector <-
  paletteer::paletteer_d(
    palette = "palettetown::venusaur",
    n = nlevels(as.factor(df$manufacturer)),
    type = "discrete"
  )

# plot
ggstatsplot::ggdotplotstats(
  data = df,
  x = cty,
  y = manufacturer,
  xlab = "city miles per gallon",
  ylab = "car manufacturer",
  test.value = 15.5,
  point.args = list(
    shape = 16,
    color = paletter_vector,
    size = 5
  ),
  test.value.line = TRUE,
  title = "Distribution of mileage of cars",
  ggtheme = hrbrthemes::theme_ipsum_ps(),
  ggstatsplot.layer = FALSE
)
```

## Grouped analysis with `grouped_ggdotplotstats`

What if we want to do the same analysis separately for different engines with
different numbers of cylinders?

`ggstatsplot` provides a special helper function for such instances:
`grouped_ggdotplotstats`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `ggdotplotstats` across all **levels** of
a specified **grouping variable** and then combines the individual plots into a
single plot. 

Let's see how we can use this function to apply `ggdotplotstats` to accomplish our
task. 

```{r grouped1, fig.height = 12, fig.width = 7}
# for reproducibility
set.seed(123)

# removing factor level with very few no. of observations
df <- dplyr::filter(.data = ggplot2::mpg, cyl %in% c("4", "6"))

# plot
ggstatsplot::grouped_ggdotplotstats(
  # arguments relevant for ggstatsplot::ggdotplotstats
  data = df,
  x = cty,
  y = manufacturer,
  xlab = "city miles per gallon",
  ylab = "car manufacturer",
  grouping.var = cyl, # grouping variable
  type = "bayes", # bayes factor test
  test.value = 15.5,
  title.prefix = "cylinder count",
  point.args = list(
    color = "red",
    size = 5,
    shape = 13
  ),
  test.value.line = TRUE,
  ggtheme = ggthemes::theme_fivethirtyeight(),
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Fuel economy data",
  plotgrid.args = list(nrow = 2)
)
```

## Grouped analysis with `purrr`

Although this is a quick and dirty way to explore a large amount of data with
minimal effort, it does come with an important limitation: reduced flexibility.
For example, if we wanted to add, let's say, a separate `test.value` argument
for each gender, this is not possible with `grouped_ggdotplotstats`. For cases
like these, or to run separate  kinds of tests (robust for some, parametric for
other, while Bayesian for some other levels of the group) it would be better to
use `purrr`.   

See the associated vignette here:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html>

## Summary of tests

Following tests are carried out for each type of analyses-

Type | Test | Function
------------------ | ------------------------- | -----
Parametric | One-sample Student's *t*-test | `stats::t.test`
Non-parametric | One-sample Wilcoxon test | `stats::wilcox.test`
Robust | One-sample percentile bootstrap | `WRS2::onesampb`
Bayes Factor | One-sample Student's *t*-test | `BayesFactor::ttestBF`

Following effect sizes (and confidence intervals/CI) are available for each type
of test-

Type | Effect size | CI? | Function
------------ | ----------------------- | --- | -----
Parametric | Cohen's *d*, Hedge's *g* | <font color="green">Yes<font> | `effectsize::cohens_d`, `effectsize::hedges_g`
Non-parametric | *r* | <font color="green">Yes<font> | `rcompanion::wilcoxonOneSampleR`
Robust | robust location measure | <font color="green">Yes<font> | `WRS2::onesampb`
Bayes Factor | $\delta_{posterior}$ | <font color="green">Yes<font> | `bayestestR::describe_posterior`


## Effect size interpretation

To see how the effect sizes displayed in these tests can be interpreted, see:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/effsize_interpretation.html>

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>
