---
title: "gghistostats"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{gghistostats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE

source("../setup.R")
```

```{r}
#| label = "suggested_pkgs",
#| include = FALSE

pkgs <- "psych"

successfully_loaded <- purrr::map_lgl(pkgs, requireNamespace, quietly = TRUE)
can_evaluate <- all(successfully_loaded)

if (can_evaluate) {
  purrr::walk(pkgs, library, character.only = TRUE)
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

---

Lifecycle: [![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html)

The function `gghistostats` can be used for **data exploration**
and to provide an easy way to make **publication-ready histograms** with
appropriate and selected statistical details embedded in the plot itself. In
this vignette we will explore several examples of how to use it.

Some instances where you would want to use `gghistostats`-

  - to inspect distribution of a continuous variable
  - to test if the mean of a sample variable is different from a specified value
  (population parameter)

## Statistical analysis with `gghistostats`

Let's begin with a very simple example from the `psych` package
(`psych::sat.act`), a sample of 700 self-reported scores on the SAT Verbal, SAT
Quantitative and ACT tests. ACT composite scores may range from 1 - 36. National
norms have a mean of 20.

```{r}
#| label = "psychact"
## loading needed libraries
library(psych)

## looking at the structure of the data using glimpse
dplyr::glimpse(psych::sat.act)
```

By default, `gghistostats` chooses a binwidth of `(max(x) - min(x)) / sqrt(N)`.
You should always check this value and explore multiple widths (via the
`binwidth` argument) to find the best to illustrate the stories in your data
since histograms are sensitive to binwidth. If you want a simple histogram
without any statistical details, set `results.subtitle = FALSE` (and
`centrality.plotting = FALSE` to also remove the centrality line).

Let's test the hypothesis that our sample mean is the same as our national
population mean of 20 using a parametric one sample *t*-test (the default
`type = "parametric"`).

```{r}
#| label = "psychact3",
#| fig.height = 6,
#| fig.width = 7

gghistostats(
  data = psych::sat.act, ## data from which variable is to be taken
  x = ACT, ## numeric variable
  xlab = "ACT Score", ## x-axis label
  title = "Distribution of ACT Scores", ## title for the plot
  test.value = 20, ## test value
  caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
```

`gghistostats` also computed Bayes Factors to quantify the likelihood of the
**research** (BF10) and the **null** hypothesis (BF01). In our current example,
the Bayes Factor value provides **very strong evidence**
[(Kass and Raftery, 1995)](https://sites.stat.washington.edu/raftery/Research/PDF/kass1995.pdf)
in favor of the research hypothesis: these ACT scores are much higher than the
national average. The natural log of the Bayes factor of 492.5 means the odds
are 7.54e+213:1 that this sample is different.

## Grouped analysis with `grouped_gghistostats`

What if we want to do the same analysis separately for each gender?
`{ggstatsplot}` provides a special helper function for such instances:
`grouped_gghistostats`. This is merely a wrapper function around
`combine_plots`. It applies `gghistostats` across all **levels** of
a specified **grouping variable** and then combines the individual plots into a
single plot. Note that the grouping variable can be anything: conditions in a
given study, groups in a study sample, different studies, etc.

Let's see how we can use this function to apply `gghistostats` to accomplish our
task.

```{r}
#| label = "grouped1",
#| fig.height = 10,
#| fig.width = 7

grouped_gghistostats(
  ## arguments relevant for gghistostats
  data = psych::sat.act,
  x = ACT, ## same outcome variable
  xlab = "ACT Score",
  grouping.var = gender, ## grouping variable males = 1, females = 2
  type = "robust", ## robust test: bootstrap-t test for one-sample trimmed mean
  test.value = 20, ## test value against which sample trimmed mean is to be compared
  centrality.line.args = list(color = "#D55E00", linetype = "dashed"),
  ## arguments relevant for combine_plots
  annotation.args = list(
    title = "Distribution of ACT scores across genders",
    caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
  ),
  plotgrid.args = list(nrow = 2L)
)
```

As can be seen from these plots, the mean value is much higher than the national
norm. Additionally, we see the benefits of plotting this data separately for
each gender. We can *see* the differences in distributions.

## Grouped analysis with `{purrr}`

Although this is a quick and dirty way to explore a large amount of data with
minimal effort, it does come with an important limitation: reduced flexibility.
For example, if we wanted to add, let's say, a separate `test.value` argument
for each gender, this is not possible with `grouped_gghistostats`.

For cases like these, or to run separate kinds of tests (robust for some,
parametric for other, while Bayesian for some other levels of the group) it
would be better to use `{purrr}`.

See the associated vignette here:
<https://www.indrapatil.com/ggstatsplot/articles/web_only/purrr_examples.html>

## Summary of graphics and tests

```{asis, file="../../man/rmd-fragments/gghistostats_graphics.Rmd"}
```

The statistical tests and effect sizes carried out for each `type` are listed
in the function documentation:
<https://www.indrapatil.com/ggstatsplot/reference/gghistostats.html>

## Extracting statistical details

All statistical details shown in the plot are also available as data frames,
which can be extracted with `extract_stats()`. The returned list contains
results from the test in the subtitle (`subtitle_data`) and the Bayesian test in
the caption (`caption_data`).

```{r}
#| label = "extract_stats"
p <- gghistostats(psych::sat.act, ACT, test.value = 20)

extract_stats(p)$subtitle_data
```

For `grouped_gghistostats()` plots, `extract_stats()` returns one such list
for each level of the grouping variable.

## Reporting

```{asis, file="../../man/md-fragments/reporting.md"}
```

For example, let's see the following example:

```{r}
#| label = "reporting"
gghistostats(trees, Height, test.value = 75)
```

The narrative context (assuming `type = "parametric"`) can complement this plot
either as a figure caption or in the main text-

> Student's *t*-test revealed that, across 31 felled black cherry trees,
although the height was higher than expected height of 75 ft., this effect was
not statistically significant. The effect size $(g = 0.15)$ was small, as per
Cohen’s (1988) conventions. The Bayes Factor for the same analysis revealed that
the data were `r round(exp(1.3), 2)` times more probable under the null
hypothesis as compared to the alternative hypothesis. This can be considered
moderate evidence (Jeffreys, 1961) in favor of the null hypothesis.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub:
<https://github.com/IndrajeetPatil/ggstatsplot/issues>
