---
title: "gghistostats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{gghistostats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
## show me all columns
options(tibble.width = Inf, pillar.bold = TRUE, pillar.subtle_num = TRUE)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  warning = FALSE,
  message = FALSE,
  out.width = "100%",
  comment = "#>"
)
```

---

You can cite this package/vignette as:

```{r citation, echo=FALSE, comment = ""}
citation("ggstatsplot")
```

---

Lifecycle: [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)

The function `ggstatsplot::gghistostats` can be used for **data exploration**
and to provide an easy way to make **publication-ready histograms** with
appropriate and selected statistical details embedded in the plot itself. In
this vignette we will explore several examples of how to use it.

Some instances where you would want to use `gghistostats`-

  - to inspect distribution of a continuous variable
  - to test if the mean of a sample variable is different from a specified value
  (population parameter)

## Statistical analysis with `gghistostats`

Let's begin with a very simple example from the `psych` package
(`psych::sat.act`), a sample of 700 self-reported scores on the SAT Verbal, SAT
Quantitative and ACT tests. ACT composite scores may range from 1 - 36. National
norms have a mean of 20.

```{r psychact}
## loading needed libraries
library(ggstatsplot)
library(psych)
library(dplyr)

## looking at the structure of the data using glimpse
dplyr::glimpse(psych::sat.act)
```

To get a simple histogram with no statistics and no special information.
`gghistostats` will by default choose a binwidth `max(x) - min(x) / sqrt(N)`.
You should always check this value and explore multiple widths to find the best
to illustrate the stories in your data since histograms are sensitive to
binwidth.

Let's display the national norms (labeled as "Test") and test the hypothesis
that our sample mean is the same as our national population mean of 20 using a
parametric one sample *t*-test (`type = "p"`).

```{r psychact3, fig.height = 6, fig.width = 7}
set.seed(123)

ggstatsplot::gghistostats(
  data = psych::sat.act, ## data from which variable is to be taken
  x = ACT, ## numeric variable
  xlab = "ACT Score", ## x-axis label
  title = "Distribution of ACT Scores", ## title for the plot
  ggtheme = ggthemes::theme_tufte(), ## changing default theme
  test.value = 20, ## test value
  caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
```

`gghistostats` computed Bayes Factors to quantify the likelihood of the **research** (BF10) and
the **null** hypothesis (BF01). In our current example, the Bayes Factor value provides
**very strong evidence** [(Kass and Rafferty, 1995)](https://www.stat.washington.edu/raftery/Research/PDF/kass1995.pdf)
in favor of the research hypothesis: these ACT scores are much higher than the
national average.  The log(Bayes factor) of 492.5 means the odds are 7.54e+213:1
that this sample is different.

## Grouped analysis with `grouped_gghistostats`

What if we want to do the same analysis separately for each gender? 
`{ggstatsplot}` provides a special helper function for such instances:
`grouped_gghistostats`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `gghistostats` across all **levels** of
a specified **grouping variable** and then combines the individual plots into a
single plot. Note that the grouping variable can be anything: conditions in a
given study, groups in a study sample, different studies, etc.

Let's see how we can use this function to apply `gghistostats` to accomplish our
task. 

```{r grouped1, fig.height = 10, fig.width = 7}
set.seed(123)

ggstatsplot::grouped_gghistostats(
  ## arguments relevant for ggstatsplot::gghistostats
  data = psych::sat.act,
  x = ACT, ## same outcome variable
  xlab = "ACT Score",
  grouping.var = gender, ## grouping variable males = 1, females = 2
  type = "robust", ## robust test: one-sample percentile bootstrap
  test.value = 20, ## test value against which sample mean is to be compared
  centrality.line.args = list(color = "#D55E00", linetype = "dashed"),
  ggtheme = ggthemes::theme_stata(), ## changing default theme
   ## turn off ggstatsplot theme layer
  ## arguments relevant for ggstatsplot::combine_plots
  annotation.args = list(
    title = "Distribution of ACT scores across genders",
    caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
  ),
  plotgrid.args = list(nrow = 2)
)
```

As can be seen from these plots, the mean value is much higher than the national
norm. Additionally, we see the benefits of plotting this data separately for
each gender. We can *see* the differences in distributions.

## Grouped analysis with `purrr`

Although this is a quick and dirty way to explore a large amount of data with
minimal effort, it does come with an important limitation: reduced flexibility.
For example, if we wanted to add, let's say, a separate `test.value` argument
for each gender, this is not possible with `grouped_gghistostats`. 

For cases like these, or to run separate  kinds of tests (robust for some,
parametric for other, while Bayesian for some other levels of the group) it
would be better to use `purrr`.

See the associated vignette here:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html>

## Summary of graphics

graphical element | `geom_` used | argument for further modification
--------- | ------- | --------------------------
histogram bin | `ggplot2::stat_bin` | `bin.args`
centrality measure line | `ggplot2::geom_vline` | `centrality.line.args`
normality curve | `ggplot2::stat_function` | `normal.curve.args`

## Summary of tests

**Central tendency measure**

Type | Measure | Function used
----------- | --------- | ------------------ 
Parametric | mean | `parameters::describe_distribution`
Non-parametric | median | `parameters::describe_distribution`
Robust | trimmed mean | `parameters::describe_distribution`
Bayesian | MAP (maximum *a posteriori* probability) estimate | `parameters::describe_distribution`

**Hypothesis testing**

Type | Test | Function used
------------------ | ------------------------- | -----
Parametric | One-sample Student's *t*-test | `stats::t.test`
Non-parametric | One-sample Wilcoxon test | `stats::wilcox.test`
Robust | Bootstrap-*t* method for one-sample test | `WRS2::trimcibt`
Bayesian | One-sample Student's *t*-test | `BayesFactor::ttestBF`

**Effect size estimation**

Type | Effect size | CI? | Function used
------------ | ----------------------- | --- | -----
Parametric | Cohen's *d*, Hedge's *g* | ✅ | `effectsize::cohens_d`, `effectsize::hedges_g`
Non-parametric | *r* (rank-biserial correlation) | ✅ | `effectsize::rank_biserial`
Robust | trimmed mean | ✅ | `WRS2::trimcibt`
Bayes Factor | $\delta_{posterior}$ | ✅ | `bayestestR::describe_posterior`

## Reporting

If you wish to include statistical analysis results in a publication/report, the
ideal reporting practice will be a hybrid of two approaches:

- the `{ggstatsplot}` approach, where the plot contains both the visual and
numerical summaries about a statistical model, and

- the *standard* narrative approach, which provides interpretive context for the
reported statistics.

For example, let's see the following example:



```{r reporting}
gghistostats(trees, Height, test.value = 75)
```

The narrative context (assuming `type = "parametric"`) can complement this plot
either as a figure caption or in the main text-

> Student's *t*-test revealed that, across 31 felled black cherry trees,
although the height was higher than expected height of 75 ft., this effect was
not statistically significant. The effect size $(g = 0.15)$ was small, as per
Cohen’s (1988) conventions. The Bayes Factor for the same analysis revealed that
the data were `r round(exp(1.3), 2)` times more probable under the null
hypothesis as compared to the alternative hypothesis. This can be considered
moderate evidence (Jeffreys, 1961) in favor of the null hypothesis.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>

