---
title: "ggpiestats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ggpiestats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE
source("../setup.R")
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

---

Lifecycle: [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)

## Introduction to `ggpiestats`

The function `ggpiestats` can be used for quick **data
exploration** and/or to prepare **publication-ready pie charts** to summarize
the statistical relationship(s) among one or more categorical variables. We will
see examples of how to use this function in this vignette.

To begin with, here are some instances where you would want to use
`ggpiestats`-

 - to check if the proportion of observations matches our hypothesized
proportion, this is typically known as a "Goodness of Fit" test

 - to see if the frequency distribution of two categorical variables are
independent of each other using the contingency table analysis

 - to check if the proportion of observations at each level of a categorical
variable is equal

**Note:** The following demo uses the pipe operator (`%>%`), if you are not
familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>.

`ggpiestats` works **only** with data organized in data frames or tibbles. It
will not work with other data structures like base-R tables or matrices. It can
operate on data frames that are organized with one row per observation or
data frames that have one column containing counts. This vignette provides
examples of both (see examples below).

To help demonstrate how `ggpiestats` can be used with categorical (also known as
nominal) data, a modified version of the original `Titanic` dataset (from the
`datasets` library) has been provided in the `{ggstatsplot}` package with the name
`Titanic_full`. The Titanic Passenger Survival Dataset provides information "on
the fate of passengers on the fatal maiden voyage of the ocean liner *Titanic*,
including economic status (class), sex, age, and survival."

Let's have a look at the structure of both.

```{r}
#| label = "titanic1"

# looking at the original data in tabular format
dplyr::glimpse(Titanic)

# looking at the dataset as a tibble or data frame
dplyr::glimpse(Titanic_full)
```

## Goodness of Fit with `ggpiestats`

The simplest use case for `ggpiestats` is that we want to display information
about **one** categorical or nominal variable. As part of that display or plot,
we may also choose to execute a chi-squared goodness of fit test to see whether
the proportions (or percentages) in categories of the single variable appear to
line up with our hypothesis or model. To start simple and then expand, let's say
that we'd like to display a piechart with the percentages of passengers who did
or did not survive. Our initial hypothesis is that it was no different than
flipping a coin. People had a 50/50 chance of surviving.

```{r}
#| label = "ggpiestats3",
#| fig.height = 5,
#| fig.width = 6

ggpiestats(
  data = Titanic_full,
  x = Survived,
  title = "Passenger survival on the Titanic",
  caption = "Source: Titanic survival dataset",
  legend.title = "Survived?"
)
```

**Note:** equal proportions per category are the default, e.g. 50/50, but you
can specify any hypothesized ratio you like with `ratio` so if our hypothesis
was that 80% died and 20% survived we would add `ratio = c(.80,.20)` when we
entered the code.

## Independence (or association) with `ggpiestats`

Let's next investigate whether the passenger's gender was independent of, or
associated with, gender. The test is whether the proportion of people who
survived was different between the sexes using `ggpiestats`.

```{r}
#| label = "ggpiestats1",
#| fig.height = 5,
#| fig.width = 8




ggpiestats(
  data = Titanic_full,
  x = Survived,
  y = Sex
) + # further modification with `{ggplot2}` commands
  ggplot2::theme(
    plot.title = ggplot2::element_text(
      color = "black",
      size = 14,
      hjust = 0
    )
  )
```

The plot clearly shows that survival rates were very different between males and
females. The Pearson's $\chi^2$-test of independence is significant given our
large sample size. Additionally, for both females and males, the survival rates
were significantly different than 50% as indicated by a goodness of fit test for
each gender.

## Grouped analysis with `grouped_ggpiestats`

What if we want to do the same analysis of gender but also factor in the
passenger's age (Age)? We have information that classifies the passengers as
Child or Adult, perhaps that makes a difference to their survival rate? 

`{ggstatsplot}` provides a special helper function for such instances:
`grouped_ggpiestats`. It is a convenient wrapper function around
`combine_plots`. It applies `ggpiestats` across all **levels** of a
specified **grouping variable** and then combines the list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc.

```{r}
#| label = "ggpiestats4",
#| fig.height = 10,
#| fig.width = 8

grouped_ggpiestats(
  # arguments relevant for `ggpiestats()`
  data = Titanic_full,
  x = Survived,
  y = Sex,
  grouping.var = Age,
  perc.k = 1,
  package = "ggsci",
  palette = "category10_d3",
  # arguments relevant for `combine_plots()`
  title.text = "Passenger survival on the Titanic by gender and age",
  caption.text = "Asterisks denote results from proportion tests; \n***: p < 0.001, ns: non-significant",
  plotgrid.args = list(nrow = 2)
)
```

The resulting pie charts and statistics make the story clear. For adults gender
very much matters. Women survived at much higher rates than men. For children
gender is not significantly associated with survival and both male and female
children have a survival rate that is not significantly different from 50/50.

## Grouped analysis with `ggpiestats` + `{purrr}` 

Although `grouped_ggpiestats` provides a quick way to explore the data, it
leaves much to be desired. For example, we may want to add different captions,
titles, themes, or palettes for each level of the grouping variable, etc. For
cases like these, it would be better to use `{purrr}` package.  

See the associated vignette here:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html>

## Working with data organized by `counts` 

`ggpiestats` can also work with data frame containing counts (aka tabled data),
i.e., when each row doesn't correspond to a unique observation. For example,
consider the following notional `fishing` data frame containing data from two
boats (`A` and `B`) about the number of different types fish they caught in the
months of `February` and `March`. In this data frame, each row corresponds to a
unique combination of `Boat` and `Month`.

```{r}
#| label = "ggpiestats7",
#| fig.height = 8,
#| fig.width = 9

# creating a data frame
# (this is completely fictional; I don't know first thing about fishing!)
(
  fishing <- tibble::as_tibble(data.frame(
    Boat = c(rep("B", 4), rep("A", 4), rep("A", 4), rep("B", 4)),
    Month = c(rep("February", 2), rep("March", 2), rep("February", 2), rep("March", 2)),
    Fish = c(
      "Bass",
      "Catfish",
      "Cod",
      "Haddock",
      "Cod",
      "Haddock",
      "Bass",
      "Catfish",
      "Bass",
      "Catfish",
      "Cod",
      "Haddock",
      "Cod",
      "Haddock",
      "Bass",
      "Catfish"
    ),
    SumOfCaught = c(25, 20, 35, 40, 40, 25, 30, 42, 40, 30, 33, 26, 100, 30, 20, 20)
  ))
)
```

When the data is organized this way, we make a slightly different call to the
`ggpiestats()` function: we use the `counts` argument. 

If we want to investigate the relationship of type of fish by month (a test of
independence), our command would be:

```{r}
#| label = "ggpiestats8",
#| fig.height = 5,
#| fig.width = 8

ggpiestats(
  data = fishing,
  x = Fish,
  y = Month,
  counts = SumOfCaught,
  label = "both",
  package = "ggsci",
  palette = "default_jama",
  title = "Type fish caught by month",
  caption = "Source: completely made up",
  legend.title = "Type fish caught: "
)
```

The results support our hypothesis that the type of fish caught is related to
the month in which we're fishing. The $\chi^2$ independence test results at
the top of the plot. In February, we catch significantly more Cod than we
would hypothesize for an equal distribution. Whereas, in March, our results
indicate there's no strong evidence that the distribution isn't equal.

## Within-subjects designs

Let's imagine we're conducting clinical trials for some
new imaginary wonder drug. We have 134 subjects entering the trial. Some of them
enter healthy (*n* = 96), some of them enter the trial already being sick (*n* =
38). All of them receive our treatment or intervention. Then we check back in a
month to see if they are healthy or sick. A classic pre/post experimental
design. We're interested in seeing the change in both groupings. In the case of
within-subjects designs, you can set `paired = TRUE`, which will display results
from **McNemar test** in the subtitle.

(**Note:** If you forget to set `paired = TRUE`, the results will be
inaccurate.)

```{r}
#| label = "ggpiestats9",
#| fig.height = 5,
#| fig.width = 8

# create imaginary data
clinical_trial <- tibble::tribble(
  ~SickBefore, ~SickAfter, ~Counts,
  "No", "Yes", 4,
  "Yes", "No", 25,
  "Yes", "Yes", 13,
  "No", "No", 92
)

ggpiestats(
  data = clinical_trial,
  x = SickAfter,
  y = SickBefore,
  counts = Counts,
  paired = TRUE,
  label = "both",
  title = "Results from imaginary clinical trial",
  package = "ggsci",
  palette = "default_ucscgb"
)
```

The results bode well for our experimental wonder drug. Of the 96 who started
out healthy only 4% were sick after a month. Ideally, we would have hoped for
zero but reality is seldom perfect. On the other side of the 38 who started out
sick that number has reduced to just 13 or 34% which is a marked improvement.

## Summary of graphics and tests

Details about underlying functions used to create graphics and statistical tests carried out can be found in the function documentation:
<https://indrajeetpatil.github.io/ggstatsplot/reference/ggpiestats.html>

## Reporting

If you wish to include statistical analysis results in a publication/report, the
ideal reporting practice will be a hybrid of two approaches:

- the `{ggstatsplot}` approach, where the plot contains both the visual and
numerical summaries about a statistical model, and

- the *standard* narrative approach, which provides interpretive context for the
reported statistics.

For example, let's see the following example:

```{r}
#| label = "reporting"
ggpiestats(mtcars, am, cyl)
```

The narrative context (assuming `type = "parametric"`) can complement this plot
either as a figure caption or in the main text-

> Pearson's $\chi^2$-test of independence revealed that, across 32 automobiles,
showed that there was a significant association between transmission engine and
number of cylinders. The Bayes Factor for the same analysis revealed that the
data were `r round(exp(2.82), 2)` times more probable under the alternative
hypothesis as compared to the null hypothesis. This can be considered strong
evidence (Jeffreys, 1961) in favor of the alternative hypothesis.

Similar reporting style can be followed when the function performs one-sample
goodness-of-fit test instead of a $\chi^2$-test.

Same holds true for `ggbarstats`.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

