---
title: "ggpiestats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggpiestats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction to `ggpiestats`

The function `ggstatsplot::ggpiestats` can be used for quick **data
exploration** and/or to prepare **publication-ready pie charts** to summarize
the statistical relationship(s) among one or more categorical variables. We will
see examples of how to use this function in this vignette.

To begin with, here are some instances where you would want to use
`ggpiestats`-

 - to check if the proportion of observations matches our hypothesized
proportion, this is typically known as a "Goodness of Fit" test

 - to see if the frequency distribution of two categorical variables are
independent of each other using the contingency table analysis

 - to check if the proportion of observations at each level of a categorical
variable is equal

**Note:** The following demo uses the pipe operator (`%>%`), if you are not
familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>.

`ggpiestats` **only** works with data organized in dataframes or tibbles. It
will not work with other data structures like base R tables or matrices. It can
operate on dataframes that are organized with one row per observation or
dataframes that have one column containing counts. This vignette provides
examples of both (see examples below).

To help demonstrate how `ggpiestats` can be used with categorical (also known as
nominal) data, a modified version of the original `Titanic` dataset (from the
`datasets` library) has been provided in the `ggstatsplot` package with the name
`Titanic_full`. The Titanic Passenger Survival Dataset provides information "on
the fate of passengers on the fatal maiden voyage of the ocean liner *Titanic*,
including economic status (class), sex, age, and survival."

Let's have a look at the structure of both.

```{r titanic1, warning = FALSE, message = FALSE}
library(datasets)
library(dplyr)
library(ggstatsplot)

# looking at the original data in tabular format
dplyr::glimpse(x = Titanic)

# looking at the dataset as a tibble or dataframe
dplyr::glimpse(x = ggstatsplot::Titanic_full)
```

## Goodness of Fit with `ggpiestats`

The simplest use case for `ggpiestats` is that we want to display information
about **one** categorical or nominal variable. As part of that display or plot,
we may also choose to execute a chi-squared goodness of fit test to see whether
the proportions (or percentages) in categories of the single variable appear to
line up with our hypothesis or model. To start simple and then expand, let's say
that we'd like to display a piechart with the percentages of passengers who did
or did not survive. Our initial hypothesis is that it was no different than
flipping a coin. People had a 50/50 chance of surviving.

```{r ggpiestats3, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
# since effect size confidence intervals are computed using bootstrapping, let's
# set seed for reproducibility
set.seed(123)

# to speed up the process, let's use only half of the dataset
Titanic_full_50 <- dplyr::sample_frac(tbl = ggstatsplot::Titanic_full, size = 0.5)

# plot
ggstatsplot::ggpiestats(
  data = Titanic_full_50,                          
  main = Survived,
  title = "Passenger survival on the Titanic",       # title for the entire plot
  caption = "Source: Titanic survival dataset",      # caption for the entire plot
  legend.title = "Survived?",                        # legend title
  messages = FALSE                                   # turn off messages
)
```

**Note:** equal proportions per category are the default, e.g. 50/50, but you
can specify any hypothesized ratio you like with `ratio` so if our hypothesis
was that 80% died and 20% survived we would add `ratio = c(.80,.20)` when we
entered the code.

Let's move on to a more complex example statistically and in terms of the
features we will use in `ggpiestats`

## Independence (or association) with `ggpiestats`

Let's next investigate whether the passenger's gender was independent of, or
associated with, gender. The test is whether the proportion of people who
survived was different between the sexes using `ggpiestats`.

We'll modify a number of arguments to change the appearance of this plot and
showcase the flexibility of `ggpiestats`. We will:

1. Change the plot theme to `ggplot2::theme_grey()` 

2. Change our color palette to `category10_d3` from `ggsci` package

3. We'll customize the subtitle by being more precise about which chi 
  squared test this is `stat.title = "chi squared test of independence: "` 

4. Finally, we'll make a call to `ggplot2` to modify the size
   of our plot title and to make it right justified

```{r ggpiestats1, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8}
# since effect size confidence intervals are computed using bootstrapping, let's
# set seed for reproducibility
set.seed(123)

# to speed up the process, let's use only half of the dataset
Titanic_full_50 <- dplyr::sample_frac(tbl = ggstatsplot::Titanic_full, size = 0.5)

# plot
ggstatsplot::ggpiestats(
  data = Titanic_full_50,
  main = Survived,
  condition = Sex,
  title = "Passenger survival on the Titanic by gender",   # title for the entire plot
  caption = "Source: Titanic survival dataset",            # caption for the entire plot
  legend.title = "Survived?",                              # legend title
  bf.message = TRUE,                                       # display bayes factor in favor of null hypothesis
  ggtheme = ggplot2::theme_grey(),                         # changing plot theme 
  palette = "category10_d3",                               # choosing a different color palette
  package = "ggsci",                                       # package to which color palette belongs
  stat.title = "Pearson's chi-squared test: ",             # title for statistical test
  k = 3,                                                   # decimal places in result
  perc.k = 1,                                              # decimal places in percentage labels
  nboot = 10,                                              # no. of bootstrap sample for effect size CI
  messages = FALSE
)  +                                                       # further modification with `ggplot2` commands
  ggplot2::theme(plot.title = ggplot2::element_text(
    color = "black",
    size = 14,
    hjust = 0
  ))
```

The plot clearly shows that survival rates were very different between males and
females. The Pearson's chi-square test of independence is significant given our
large sample size. Additionally, for both females and males, the survival rates
were significantly different than 50% as indicated by the `***` which is
equivalent to a goodness of fit test for each gender.

## Grouped analysis with `grouped_ggpiestats`

What if we want to do the same analysis of gender but also factor in the
passenger's age (Age)? We have information that classifies the passengers as
Child or Adult, perhaps that makes a difference to their survival rate? We could
write a `for` loop or use `purrr`, but `ggstatsplot` provides a special helper
function for such instances: `grouped_ggpiestats`.

It is a convenient wrapper function around `ggstatsplot::combine_plots`. It
applies `ggpiestats` across all **levels** of a specified **grouping variable**
and then combines the list of individual plots into a single plot. Note that the
grouping variable can be anything: conditions in a given study, groups in a
study sample, different studies, etc.

```{r ggpiestats4, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 8}
# since effect size confidence intervals are computed using bootstrapping, let's
# set seed for reproducibility
set.seed(123)

# plot
ggstatsplot::grouped_ggpiestats(
  # arguments relevant for ggstatsplot::gghistostats
  data = ggstatsplot::Titanic_full,
  grouping.var = Age,
  title.prefix = "Child or Adult?",
  main = Survived,
  condition = Sex,
  nboot = 10,
  perc.k = 1,
  package = "ggsci",
  palette = "category10_d3",
  messages = FALSE,
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Passenger survival on the Titanic by gender and age",
  caption.text = "Asterisks denote results from proportion tests; \n***: p < 0.001, ns: non-significant",
  nrow = 2
)
```

The resulting pie charts and statistics make the story clear. For adults gender
very much matters. Women survived at much higher rates than men. For children
gender is not significantly associated with survival and both male and female
children have a survival rate that is not significantly different from 50/50.

## Grouped analysis with `ggpiestats` + `purrr` 

Although `grouped_ggpiestats` provides a quick way to explore the data, it
leaves much to be desired. For example, we may want to add different captions,
titles, themes, or palettes for each level of the grouping variable, etc. For
cases like these, it would be better to use `purrr` package.  

See the associated vignette here:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html>

## Working with data organized by `counts` 

`ggpiestats` can also work with dataframe containing counts (aka tabled data),
i.e., when each row doesn't correspond to a unique observation. For example,
consider the following notional `fishing` dataframe containing data from two
boats (`A` and `B`) about the number of different types fish they caught in the
months of `February` and `March`. In this dataframe, each row corresponds to a
unique combination of `Boat` and `Month`.

```{r ggpiestats7, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 9}
# for reproducibility
set.seed(123)

# creating a dataframe
# (this is completely fictional; I don't know first thing about fishing!)
(
  fishing <- data.frame(
    Boat = c(rep("B", 4), rep("A", 4), rep("A", 4), rep("B", 4)),
    Month = c(rep("February", 2), rep("March", 2), rep("February", 2), rep("March", 2)),
    Fish = c(
      "Bass",
      "Catfish",
      "Cod",
      "Haddock",
      "Cod",
      "Haddock",
      "Bass",
      "Catfish",
      "Bass",
      "Catfish",
      "Cod",
      "Haddock",
      "Cod",
      "Haddock",
      "Bass",
      "Catfish"
    ),
    SumOfCaught = c(25, 20, 35, 40, 40, 25, 30, 42, 40, 30, 33, 26, 100, 30, 20, 20)
  ) %>% # converting to a tibble dataframe
    tibble::as_data_frame(x = .)
)
```

When the data is organized this way, we make a slightly different call to the
`ggpiestats` function: we use the `counts` argument. If we want to investigate
the relationship of type of fish by month (a test of independence), our command
would be:

```{r ggpiestats8, message = FALSE, warning = FALSE, fig.height = 5, fig.width = 8}
# running `ggpiestats` with counts information
ggstatsplot::ggpiestats(
  data = fishing,
  main = Fish,
  condition = Month,
  counts = SumOfCaught,
  slice.label = "both",
  package = "ggsci",
  palette = "default_jama",
  title = "Type fish caught by month",
  caption = "Source: completely made up",
  legend.title = "Type fish caught: ",
  messages = FALSE
)
```

The results support our hypothesis that the type of fish caught is related to
the month in which we're fishing. The chi squared independence test results at
the top of the plot. In February we catch significantly more Haddock than we
would hypothesize for an equal distribution. Whereas in March our results
indicate there's no strong evidence that the distribution isn't equal.

## Within-subjects designs

For our final example let's imagine we're conducting clinical trials for some
new imaginary wonder drug. We have 134 subjects entering the trial. Some of them
enter healthy (N=96), some of them enter the trial already being sick (*n* = 38).
All of them receive our treatment or intervention. Then we check back in a month
to see if they are healthy or sick. A classic pre/post experimental design.
We're interested in seeing the change in both groupings. In the case of
within-subjects designs, you can set `paired = TRUE`, which will display results
from **McNemar test** in the subtitle. 

(**Note:** If you forget to set `paired = TRUE`, the results you get will be
inaccurate.)

```{r ggpiestats9, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8}
# seed for reproducibility
set.seed(123)

# create our imaginary data
clinical_trial <- 
  tibble::tribble(
    ~SickBefore,	~SickAfter,	~Counts,
    "No",	"Yes",	4,
    "Yes",	"No",	25,
    "Yes",	"Yes",	13,
    "No",	"No",	92
  )

# plot
ggstatsplot::ggpiestats(
  data = clinical_trial,
  condition = SickBefore,
  main = SickAfter,
  counts = Counts,
  paired = TRUE,
  slice.label = "both",
  stat.title = "McNemar test: ",
  title = "Results from imaginary clinical trial",
  package = "ggsci",
  palette = "default_ucscgb",
  direction = -1,
  messages = FALSE
) 
```

The results bode well for our experimental wonder drug. Of the 96 who started
out healthy only 4% were sick after a month. Ideally, we would have hoped for
zero but reality is seldom perfect. On the other side of the 38 who started out
sick that number has reduced to just 13 or 34% which is a marked improvement.

## Summary of tests

Following tests are carried out for each type of analyses-

Type of data | Design | Test
----------- | ------------ | -------------------------
Unpaired | $n \times p$ contingency table | Pearson's $\chi^2$ test
Paired | $n \times p$ contingency table | McNemar's test
Frequency | $n \times 1$ contingency table | Goodness of fit

Following effect sizes (and confidence intervals/CI) are available for each type
of test-

Type | Effect size | CI?
--------------- | ------------------------- | --- 
Pearson's $\chi^2$ test | Cramer's $V$ | <font color="green">Yes<font>
McNemar's test | Cohen's $g$ | <font color="green">Yes<font>
Goodness of fit | Cramer's $V$ | <font color="green">Yes<font>

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>

