---
title: "ggscatterstats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ggscatterstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE
source("../setup.R")
```

```{r}
#| label = "suggested_pkgs",
#| include = FALSE
pkgs <- c(
  "ggside"
)

successfully_loaded <- purrr::map_lgl(pkgs, requireNamespace, quietly = TRUE)
can_evaluate <- all(successfully_loaded)

if (can_evaluate) {
  purrr::walk(pkgs, library, character.only = TRUE)
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

Lifecycle: [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)

The function `ggscatterstats` is meant to provide a **publication-ready
scatterplot** with all statistical details included in the plot itself to show
association between two continuous variables. This function is also helpful
during the **data exploration** phase. We will see examples of how to use this
function in this vignette with the `ggplot2movies` dataset.

To begin with, here are some instances where you would want to use
`ggscatterstats`-

  - to check linear association between two continuous variables
  - to check distribution of two continuous variables

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Correlation plot with `ggscatterstats`

To illustrate how this function can be used, we will rely on the `ggplot2movies`
dataset. This dataset provides information about movies scraped from
[IMDB](https://www.imdb.com/). Specifically, we will be using cleaned version of
this dataset included in the `{ggstatsplot}` package itself.

```{r}
#| label = "ggplot2movies1"

## see the selected data (we have data from 1813 movies)
dplyr::glimpse(movies_long)
```

Now that we have a clean dataset, we can start asking some interesting
questions. For example, let's see if the average IMDB rating for a movie has any
relationship to its budget. Additionally, let's also see which movies had a high
budget but low IMDB rating by labeling those data points. 

To reduce the processing time, let's only work with 30% of the dataset.

```{r}
#| label = "ggscatterstats1",
#| fig.height = 6,
#| fig.width = 8

ggscatterstats(
  data = movies_long, ## data frame from which variables are taken
  x = budget, ## predictor/independent variable
  y = rating, ## dependent variable
  xlab = "Budget (in millions of US dollars)", ## label for the x-axis
  ylab = "Rating on IMDB", ## label for the y-axis
  label.var = title, ## variable to use for labeling data points
  label.expression = rating < 5 & budget > 100, ## expression for deciding which points to label
  point.label.args = list(alpha = 0.7, size = 4, color = "grey50"),
  xfill = "#CC79A7", ## fill for marginals on the x-axis
  yfill = "#009E73", ## fill for marginals on the y-axis
  title = "Relationship between movie budget and IMDB rating",
  caption = "Source: www.imdb.com"
)
```

There is indeed a small, but significant, positive correlation between the
amount of money studio invests in a movie and the ratings given by the
audiences.

## Grouped analysis with `grouped_ggscatterstats`

What if we want to do the same analysis do the same analysis for movies with
different MPAA (Motion Picture Association of America) film ratings (NC-17, PG,
PG-13, R)? 

`{ggstatsplot}` provides a special helper function for such instances:
`grouped_ggstatsplot`. This is merely a wrapper function around
`combine_plots`. It applies `{ggstatsplot}` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

Let's see how we can use this function to apply `ggscatterstats` for all MPAA
ratings. Also, let's run a robust test this time.

```{r}
#| label = "grouped1",
#| fig.height = 12,
#| fig.width = 7

grouped_ggscatterstats(
  ## arguments relevant for ggscatterstats
  data = movies_long,
  x = budget,
  y = rating,
  grouping.var = mpaa,
  label.var = title,
  label.expression = rating < 5 & budget > 80,
  type = "r",
  # ggtheme = ggthemes::theme_tufte(),
  ## arguments relevant for combine_plots
  annotation.args = list(
    title = "Relationship between movie budget and IMDB rating",
    caption = "Source: www.imdb.com"
  ),
  plotgrid.args = list(nrow = 3, ncol = 1)
)
```

As seen from the plot, this analysis has revealed something interesting: The
relationship we found between budget and IMDB rating holds only for PG-13 and
R-rated movies. 

## Grouped analysis with `ggscatterstats` + `{purrr}`

Although this is a quick and dirty way to explore large amount of data with
minimal effort, it does come with an important limitation: reduced flexibility.
For example, if we wanted to add, let's say, a separate type of marginal
distribution plot for each MPAA rating or if we wanted to use different types of
correlations across different levels of MPAA ratings (NC-17 has only 6 movies,
so a robust correlation would be a good idea), this is not possible. But this
can be easily done using `{purrr}`.  

See the associated vignette here:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html>

## Summary of graphics and tests

Details about underlying functions used to create graphics and statistical tests carried out can be found in the function documentation:
<https://indrajeetpatil.github.io/ggstatsplot/reference/ggscatterstats.html>

## Reporting

```{asis, file="../../man/md-fragments/reporting.md"}
```

For example, let's see the following example:

```{r}
#| label = "reporting"
ggscatterstats(mtcars, qsec, drat)
```

The narrative context (assuming `type = "parametric"`) can complement this plot
either as a figure caption or in the main text-

> Pearson's correlation test revealed that, across 32 cars, a measure of
acceleration (1/4 mile time; `qsec`) was positively correlated with rear axle
ratio (`drat`), but this effect was not statistically significant. The effect
size $(r = 0.09)$ was small, as per Cohen’s (1988) conventions. The Bayes Factor
for the same analysis revealed that the data were `r round(exp(1.20), 2)` times
more probable under the null hypothesis as compared to the alternative
hypothesis. This can be considered moderate evidence (Jeffreys, 1961) in favor
of the null hypothesis (of absence of any correlation between these two
variables).

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>
