---
title: "ggstatsplot: ggplot2 Based Plots with Statistical Details"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    eval: FALSE
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{ggstatsplot: ggplot2 Based Plots with Statistical Details}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

(**This publication is still a work in progress**)

> "What is to be sought in designs for the display of information is the clear
portrayal of complexity. Not the complication of the simple; rather ... the
revelation of the complex."   
- Edward R. Tufte

# Introduction
   
The `ggstatsplot` package is an opinionated collection of plots made with
`ggplot2` and is designed for exploratory data analysis or for producing
publication-ready statistical graphics. All plots share an underlying principle
of displaying information-rich plots with all necessary statistical details
included in the plots themselves. Although the plots produced by `ggstatsplot`
are still `ggplot` objects and can thus be further modified using `ggplot2`
commands, there is a limit to how many such modifications can be made. That is,
it is less flexible than `ggplot2`, but that's a feature and not a bug. The
original intent behind this package is to offload struggles associated with
*constructing* the plot and focus more on the *interpretation* of that data
displayed in the plot.

# Graphical perception
   
Graphical perception involves visual decoding of the encoded information in
graphs. `ggstatsplot` incorporates the paradigm proposed in Cleveland (1985,
Chapter 4) to facilitate making visual judgments about quantitative information
effortless and almost instantaneous. Based on experiments, Cleveland proposes
that there are ten elementary graphical-perception tasks that we perform to
visually decode quantitative information in graphs (organized from most to least
accurate; Cleveland, 1985, p.254)-
 
  * Position along a common scale
  * Position along identical, non-aligned scales
  * Length
  * Angle (Slope)
  * Area
  * Volume
  * Color hue - Color saturation - Density

So the key principle of Cleveland's paradigm for data display is- 

> "We should encode data on a graph so that the visual decoding involves
[graphical-perception] tasks as high in the ordering as possible."

For example, decoding the data point values in `ggbetweenstats` requires
position judgments along a common scale (Figure-1):

```{r example1, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 10, fig.cap = "**Figure-1**. Note that assessing differences in mean values between groups has been made easier with the help of *position* of data points along a common scale (the Y-axis) and labels."}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::ggbetweenstats(
  data = dplyr::filter(
    .data = ggstatsplot::movies_long,
    genre %in% c("Action", "Action Comedy", "Action Drama", "Comedy")
  ),
  x = genre,
  y = rating,
  title = "Figure-1: IMDB rating by film genre",
  xlab = "Genre",
  ylab = "IMDB rating (average)",
  pairwise.comparisons = TRUE,
  p.adjust.method = "bonferroni",
  ggtheme = hrbrthemes::theme_ipsum_tw(),
  ggstatsplot.layer = FALSE,
  outlier.tagging = TRUE,
  outlier.label = title,
  messages = FALSE
)
```

There are few instances where `ggstatsplot` diverges from recommendations made
in Cleveland's paradigm:

* For the categorical/nominal data, `ggstatsplot` uses pie charts (see Figure-2)
which rely on *angle* judgments, which are less accurate (as compared to bar
graphs, e.g., which require *position* judgments). This shortcoming is assuaged
to some degree by using plenty of labels that describe percentages for all
slices. This makes angle judgment unnecessary and pre-vacates any concerns about
inaccurate judgments about percentages. Additionally, it also provides
alternative function to `ggpiestats` for working with categorical variables:
`ggbarstats`.

```{r example2, fig.height = 6, fig.width = 10, fig.cap = "**Figure-2**. Pie charts don't follow Cleveland's paradigm to data display because they rely on less accurate angle judgments. `ggstatsplot` sidesteps this issue by always labelling percentages for pie slices, which makes angle judgments unnecessary."}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::ggpiestats(
  data = ggstatsplot::movies_long,
  main = genre,
  condition = mpaa,
  title = "Figure-2: Distribution of MPAA ratings by film genre",
  legend.title = "layout",
  caption = substitute(paste(
    italic("MPAA"), ": Motion Picture Association of America"
  )),
  palette = "Paired",
  messages = FALSE
)
```

* Cleveland's paradigm also emphasizes that *superposition* of data is better
than *juxtaposition* (Cleveland, 1985, p.201) because this allows for a more
incisive comparison of the values from different parts of the dataset. This
recommendation is violated in all `grouped_` variants of the function (see
Figure-3). Note that the range for Y-axes are no longer the same across
juxtaposed subplots and so visually comparing the data becomes difficult. On the
other hand, in the superposed plot, all data have the same range and coloring
different parts makes the visual discrimination of different components of the
data, and their comparison, easier. But the goal of `grouped_` variants of
functions is to not only show different aspects of the data but also to run
statistical tests and showing detailed results for all aspects of the data in a
superposed plot is difficult. Therefore, this is a compromise `ggstatsplot` is
comfortable with, at least to produce plots for quick exploration of different
aspects of the data. 

```{r example3, fig.height = 12, fig.width = 10, fig.cap = "**Figure-3**. Comparing different aspects of data is much more accurate in (a) a *superposed* plot, which is recommended in Cleveland's paradigm, than in (b) a *juxtaposed* plot, which is how it is implemented in `ggstatsplot` package. This is because displaying detailed results from statistical tests would be difficult in a superposed plot."}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::combine_plots(
  # plot 1: superposition
  ggplot2::ggplot(
    data = dplyr::filter(ggstatsplot::movies_long, genre == "Comedy" |
      genre == "Drama"),
    mapping = ggplot2::aes(
      x = length,
      y = rating,
      color = genre
    )
  ) +
    ggplot2::geom_jitter(size = 3, alpha = 0.5) +
    ggplot2::geom_smooth(method = "lm") +
    ggplot2::labs(title = "superposition (recommended in Cleveland's paradigm)") +
    ggstatsplot::theme_ggstatsplot(),
  # plot 2: juxtaposition
  ggstatsplot::grouped_ggscatterstats(
    data = dplyr::filter(ggstatsplot::movies_long, genre == "Comedy" |
      genre == "Drama"),
    x = length,
    y = rating,
    grouping.var = genre,
    marginal = FALSE,
    messages = FALSE,
    title.prefix = "Genre",
    title.text = "juxtaposition (`ggstatsplot` implementation in `grouped_` functions)",
    title.size = 12
  ),
  # combine for comparison
  title.text = "Two ways to compare different aspects of data",
  nrow = 2,
  labels = c("(a)", "(b)")
)
```

The `grouped_` plots follow the *Shrink Principle* (Tufte, 2001, p.166-7) for
high-information graphics, which dictates that the data density and the size of
the data matrix can be maximized to exploit maximum resolution of the available
data-display technology. Given the large maximum resolution afforded by most
computer monitors today, saving `grouped_` plots with appropriate resolution
ensures no loss in legibility with reduced graphics area.

# Graphical integrity (and clean design)
   
Graphical excellence consists of communicating complex ideas with clarity and in
a way that the viewer understands the greatest number of ideas in a short amount
of time all the while not quoting the data out of context. The package follows
the principles for **graphical integrity** (as outlined in Tufte, 2001):

  - The physical representation of numbers is proportional to the numerical
    quantities they represent (e.g., Figure-1 and Figure-2 show how means (in
    `ggbetweenstats`) or percentages (`ggpiestats`) are proportional to the
    vertical distance or the area, respectively).
  
  - All important events in the data have clear, detailed, and thorough labeling
    (e.g., Figure-1 plot shows how `ggbetweenstats` labels means, sample size
    information, outliers, and pairwise comparisons; same can be appreciated for
    `ggpiestats` in Figure-2 and `gghistostats` in Figure-5). Note that data
    labels in the data region are designed in a way that they don't interfere
    with our ability to assess the overall pattern of the data (Cleveland, 1985;
    p.44-45). This is achieved by using `ggrepel` package to place labels in a
    way that reduces their visual prominence.
  
  - None of the plots have *design* variation (e.g., abrupt change in scales)
    over the surface of a same graphic because this can lead to a false
    impression about variation in *data*.
  
  - The number of information-carrying dimensions never exceed the number of
    dimensions in the data (e.g., using area to show one-dimensional data).

  - All plots are designed to have no **chartjunk** (like moiré vibrations, fake
    perspective, dark grid lines, etc.) (Tufte, 2001, Chapter 5).

There are some instances where `ggstatsplot` graphs don't follow principles of
clean graphics, as formulated in the Tufte theory of data graphics (Tufte, 2001,
Chapter 4). The theory has four key principles:

  1. Above all else show the data.
  2. Maximize the data-ink ratio.
  3. Erase non-data-ink.
  4. Erase redundant data-ink, within reason.

In particular, default plots in `ggstatsplot` can sometimes violate one of the
principles from 2-4. According to these principles, every bit of ink should have
reason for its inclusion in the graphic and should convey some new information
to the viewer. If not, such ink should be removed. One instance of this is
bilateral symmetry of data measures. For example, in Figure-1, we can see that
both the box and violin plots are mirrored, which consumes twice the space in
the graphic without adding any new information. But this redundancy is tolerated
for the sake of beauty that such symmetrical shapes can bring to the graphic.
Even Tufte admits that efficiency is but one consideration in the design of
statistical graphics (Tufte, 2001, p. 137). Additionally, these principles were
formulated in an era in which computer graphics had yet to revolutionize the
ease with which graphics could be produced and thus some of the concerns about
minimizing data-ink for easier production of graphics are not as relevant as
they were.


# Statistical analysis

As an extension of `ggplot2`, `ggstatsplot` has the same expectations about the
structure of the data. More specifically,

  - The `data` should be an object of class `data.frame` (a `tibble` dataframe
    will also work).
    
  - The data should be organized following the principles of *tidy data*, which
    specify how statistical structure of a data frame (variables and
    observations) should be mapped to physical structure (columns and rows).
    More specifically, tidy data means all variables have their own columns and
    each row corresponds to a unique observation (Wickham, 2014).
    
  - All `ggstatsplot` functions remove `NA`s from variables of interest (similar
    to `ggplot2`; Wickham, 2016, p.207) in the data and display total sample
    size (*n*) in the subtitle to inform the user/reader about the number of
    observations included for both the statistical analysis and the
    visualization. But, when sample sizes differ *across* tests in the same
    function, `ggstatsplot` makes an effort to inform the user of this aspect.
    For example, `ggcorrmat` features several correlation test pairs and,
    depending on variables in a given pair, the sample sizes may vary
    (Figure-4).

```{r example4, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 10, fig.cap = "**Figure-4**. `ggstatsplot` functions remove `NA`s from variables of interest and display total sample size *n*, but they can give more nuanced information about sample sizes when *n* differs across tests. For example, `ggcorrmat` will display (a) only one total sample size once when no `NA`s present, but (b) will instead show minimum, median, and maximum sample sizes across all correlation tests when `NA`s are present across correlation variables."}

# creating a new dataset without any NAs in variables of interest
msleep_no_na <-
  dplyr::filter(
    .data = ggplot2::msleep,
    !is.na(sleep_rem),
    !is.na(awake),
    !is.na(brainwt),
    !is.na(bodywt)
  )

# variable names vector
var_names <- c(
  "REM sleep",
  "time awake",
  "brain weight",
  "body weight"
)

# combining two plots
ggstatsplot::combine_plots(
  # plot *without* any NAs
  ggstatsplot::ggcorrmat(
    data = msleep_no_na,
    corr.method = "kendall",
    sig.level = 0.001,
    p.adjust.method = "holm",
    cor.vars = c(sleep_rem, awake:bodywt),
    cor.vars.names = var_names,
    matrix.type = "upper",
    colors = c("#B2182B", "white", "#4D4D4D"),
    title = "Correlalogram for mammals sleep dataset",
    subtitle = "sleep units: hours; weight units: kilograms",
    messages = FALSE
  ),
  # plot *with* NAs
  ggstatsplot::ggcorrmat(
    data = ggplot2::msleep,
    corr.method = "kendall",
    sig.level = 0.001,
    p.adjust.method = "holm",
    cor.vars = c(sleep_rem, awake:bodywt),
    cor.vars.names = var_names,
    matrix.type = "upper",
    colors = c("#B2182B", "white", "#4D4D4D"),
    title = "Correlalogram for mammals sleep dataset",
    subtitle = "sleep units: hours; weight units: kilograms",
    messages = FALSE
  ),
  labels = c("(a)", "(b)"),
  nrow = 1
)
```
   
## Types of statistics supported

Functions | Description | Parametric | Non-parametric | Robust | Bayes Factor
------- | ------------------ | ---- | ----- | ----| ----- 
`ggbetweenstats` | Between group/condition comparisons | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font>
`ggwithinstats` | Within group/condition comparisons | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font>
`gghistostats`, `ggdotplotstats` | Distribution of a numeric variable | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font>
`ggcorrmat` | Correlation matrix | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="red">$\times$</font>
`ggscatterstats` | Correlation between two variables | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font>
`ggpiestats`, `ggbarstats` | Association between categorical variables | <font color="green">$\checkmark$</font> | `NA` | `NA` | <font color="green">$\checkmark$</font>
`ggpiestats`, `ggbarstats` | Equal proportions for categorical variable levels | <font color="green">$\checkmark$</font> | `NA` | `NA` | <font color="red">$\times$</font>
`ggcoefstats` | Regression model coefficients | <font color="green">$\checkmark$</font> | <font color="red">$\times$</font>| <font color="green">$\checkmark$</font> | <font color="red">$\times$</font>

## Types of statistical tests supported

Functions | Type | Test | Effect size | 95% CI available? 
----------- | ----------- | ------------------ | ------------------ | -----  
`ggbetweenstats` | Parametric | Student's and Welch's *t*-test | Cohen's *d*, Hedge's *g* | <font color="green">$\checkmark$</font> 
`ggbetweenstats` | Parametric | Fisher's and Welch's one-way ANOVA | $$\eta^2, \eta^2_p, \omega^2, \omega^2_p$$ | <font color="green">$\checkmark$</font> 
`ggbetweenstats` | Non-parametric | Mann-Whitney *U*-test | *r* | <font color="green">$\checkmark$</font> 
`ggbetweenstats` | Non-parametric | Kruskal-Wallis Rank Sum Test | $$\epsilon^2$$ | <font color="green">$\checkmark$</font> 
`ggbetweenstats` | Robust | Yuen's test for trimmed means | $$\xi$$ | <font color="green">$\checkmark$</font> 
`ggbetweenstats` | Robust | Heteroscedastic one-way ANOVA for trimmed means | $$\xi$$ | <font color="green">$\checkmark$</font> 
`ggwithinstats` | Parametric | Student's *t*-test | Cohen's *d*, Hedge's *g* | <font color="green">$\checkmark$</font> 
`ggwithinstats` | Parametric | Fisher's one-way repeated measures ANOVA | $$\eta^2_p, \omega^2$$ | <font color="green">$\checkmark$</font> 
`ggwithinstats` | Non-parametric | Wilcoxon signed-rank test | *r* | <font color="green">$\checkmark$</font> 
`ggwithinstats` | Non-parametric | Friedman test | $$W_{Kendall}$$ | <font color="green">$\checkmark$</font>
`ggwithinstats` | Robust | Yuen's test on trimmed means for dependent samples | $$\xi$$ | <font color="green">$\checkmark$</font> 
`ggwithinstats` | Robust | Heteroscedastic one-way repeated measures ANOVA for trimmed means | <font color="red">$\times$</font> | <font color="red">$\times$</font>
`ggpiestats` | Parametric | $$\text{Pearson's}~ \chi^2 ~\text{test}$$ | Cramér's *V* | <font color="green">$\checkmark$</font>
`ggpiestats` | Parametric | McNemar's test | Cohen's *g* | <font color="green">$\checkmark$</font>
`ggpiestats` | Parametric | One-sample proportion test | Cramér's *V* | <font color="green">$\checkmark$</font>
`ggscatterstats`/`ggcorrmat` | Parametric | Pearson's *r* | *r* | <font color="green">$\checkmark$</font>
`ggscatterstats`/`ggcorrmat` | Non-parametric | $$\text{Spearman's}~ \rho$$ | $$\rho$$ | <font color="green">$\checkmark$</font>
`ggscatterstats`/`ggcorrmat` | Robust | Percentage bend correlation | *r* | <font color="green">$\checkmark$</font>
`gghistostats`/`ggdotplotstats` | Parametric | One-sample *t*-test | Cohen's *d*, Hedge's *g* | <font color="green">$\checkmark$</font>
`gghistostats` | Non-parametric | One-sample Wilcoxon signed rank test | *r* | <font color="green">$\checkmark$</font> 
`gghistostats`/`ggdotplotstats` | Robust | One-sample percentile bootstrap | robust estimator | <font color="green">$\checkmark$</font>
`gghistostats`/`ggdotplotstats` | Parametric | Regression models | $$\beta$$ | <font color="green">$\checkmark$</font>

For the `ggbetweenstats` function, the following post-hoc tests are available
for (adjusted) pairwise multiple comparisons:

Type | Design | Equal variance assumed? |  Pairwise comparison test | *p*-value adjustment? 
----------- | ----------- | --------- | ----------------------- | -----
Parametric | between-subjects | No | Games-Howell test | <font color="green">$\checkmark$</font> 
Parametric | between-subjects | Yes | Student's *t*-test | <font color="green">$\checkmark$</font> 
Parametric | within-subjects | `NA` | Student's *t*-test | <font color="green">$\checkmark$</font> 
Non-parametric | between-subjects | No | Dwass-Steel-Crichtlow-Fligner test | <font color="green">$\checkmark$</font> 
Non-parametric | within-subjects | No | Durbin-Conover test | <font color="green">$\checkmark$</font> 
Robust | between-subjects | No | Yuen's two-sample trimmed means *t*-test | <font color="green">$\checkmark$</font> 
Robust | within-subjects | `NA` | Yuen's trimmed means test | <font color="green">$\checkmark$</font>
Bayes Factor | between-subjects | No | <font color="red">$\times$</font> | <font color="red">$\times$</font>
Bayes Factor | between-subjects | Yes | <font color="red">$\times$</font> | <font color="red">$\times$</font>
Bayes Factor | within-subjects | `NA` | <font color="red">$\times$</font> | <font color="red">$\times$</font>

*Note*- 

  - `NA`: not applicable
  - available methods for *p*-value adjustment: "holm", "hochberg", "hommel",
    "bonferroni", "BH", "BY", "fdr", "none"

## Statistical variation

One of the important functions of a plot is to show the variation in the data,
which comes in two forms:

  - **Measurement noise**: In `ggstatsplot`, the actual variation in
    measurements is shown by plotting a combination of (jittered) raw data
    points with a boxplot laid on top (Figure-1) or a histogram (Figure-5). None
    of the plots, where empirical distribution of the data is concerned, show
    the sample standard deviation because they are poor at conveying information
    about limits of the sample and presence of outliers (Cleveland, 1985,
    p.220).

```{r example5, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8, fig.cap = "**Figure-5**. Distribution of a variable shown using `gghistostats`."}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::gghistostats(
  data = morley,
  x = Speed,
  test.value = 792,
  test.value.line = TRUE,
  xlab = "Speed of light (km/sec, with 299000 subtracted)",
  title = "Figure-5: Distribution of Speed of light",
  caption = "Note: Data collected across 5 experiments (20 measurements each)",
  messages = FALSE
)
```

  - **Sample-to-sample statistic variation**: Although, traditionally, this
    variation has been shown using the standard error of the mean (SEM) of the
    statistic, `ggstatsplot` plots instead use 95% confidence intervals (e.g.,
    Figure-6). This is because the interval formed by error bars correspond to
    a 68% confidence interval, which is not a particularly interesting interval
    (Cleveland, 1985, p.222-225).

```{r example6, fig.height = 5, fig.width = 5, fig.cap = "**Figure-6**. Sample-to-sample variation in regression estimates is displayed using confidence intervals in `ggcoefstats`."}
# for reproducibility
set.seed(123)

# creating model object
mod <- lme4::lmer(
  formula = total.fruits ~ nutrient + rack + (nutrient | popu / gen),
  data = lme4::Arabidopsis
)

# plot
ggstatsplot::ggcoefstats(
  x = mod,
  p.kr = FALSE
)
```

## Reporting results

The default setting in `ggstatsplot` is to produce plots with statistical
details included. Most often than not, the results are displayed as a `subtitle`
in the plot. Great care has been taken into which details are included in
statistical reporting and why.

1. **APA guidelines** (APA, 2009) are followed (for the most part) by default:   
  - Percentages are displayed with no decimal places (Figure-2).
  - Correlations, *t*-tests, and chi-squared tests are reported with the degrees
    of freedom in parentheses and the significance level (Figure-2, Figure-3b,
    Figure-5).
  - ANOVAs are reported with two degrees of freedom and the significance level
    (Figure-1).
  - Regression results are presented with the unstandardized or standardized
    estimate (beta), whichever was specified by the user, along with the
    statistic (depending on the model, this can be a *t* or *z* statistic) and
    the corresponding significance level (Figure-6).
  - With the exception of *p*-values, most statistics are rounded to two decimal
    places.

2. Default statistical tests: 

3. Dealing with **null results**: 

4.  Avoiding the **"p-value error"**:  
    The *p*-value indexes the probability that the researchers have falsely
    rejected a true null hypothesis (Type I error, i.e.) and can rarely be
    *exactly* 0. And yet over 97,000 manuscripts on Google Scholar report the
    *p*-value to be `p = 0.000` (Lilienfeld et al., 2015), putatively due to
    relying on default computer outputs. All *p*-values displayed in
    `ggstatsplot` plots avoid this mistake. Anything less than `p < 0.001` is
    displayed as such (e.g, Figure-1). The package deems it unimportant how
    infinitesimally small the *p*-values are and, instead, puts emphasis on the
    effect size magnitudes and their 95% CIs.

# Overall consistency in API

Attempt has been made to make the application program interface (API) consistent
enough that no struggle is expected while thinking about specifying function
calls-

  - When a given function depends on variables in a dataframe, `data` argument
    must always be specified.
  - Often, package functions relevant for between-subjects versus
    within-subjects design expect tidy/long versus Cartesian/wide format data,
    respectively. `ggstatsplot` functions consistently expect tidy/long form
    data. 
  - All functions accept both quoted (`x = "var1"`) and unquoted (`x = var1`)
    arguments.

# Conclusion

# Acknowlegdments



# References
   
# Appendix
   
## Appendix A: Documentation

There are three main documents one can rely on to learn how to use
`ggstatsplot`:

  - **Presentation**: 
    The quickest (and the most fun) way to get an overview of
    the philosophy behind this package and the offered functionality is to go
    through the following slides:
    <https://indrajeetpatil.github.io/ggstatsplot_slides/slides/ggstatsplot_presentation.html#1>
  
  - **Manual**:  
    The `CRAN` reference manual provides detailed documentation about arguments
    for each function and examples:
    <https://cran.r-project.org/web/packages/ggstatsplot/ggstatsplot.pdf>

  - **README**:  
    The GitHub `README` document provides a quick summary of all available
    functionality without going too much into details:
    <https://github.com/IndrajeetPatil/ggstatsplot/blob/master/README.md>

  - **Vignettes**:  
    Vignettes contain probably the most detailed exposition. Every single
    function in `ggstatsplot` has an associated vignette which describes in
    depth how to use the function and modify the defaults to customize the plot
    to your liking. All these vignettes can be accessed from the package
    website: <https://indrajeetpatil.github.io/ggstatsplot/articles/>

## Appendix B: Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub` repository for this package:
<https://github.com/IndrajeetPatil/ggstatsplot/issues>

## Appendix C: Session information

Summarizing session information for reproducibility.

```{r session_info}
options(width = 200)
devtools::session_info()
```
