---
title: "ggwithinstats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ggwithinstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE

source("../setup.R")
```

```{r}
#| label = "suggested_pkgs",
#| include = FALSE

pkgs <- c(
  "afex",
  "PMCMRplus",
  "WRS2"
)

successfully_loaded <- purrr::map_lgl(pkgs, requireNamespace, quietly = TRUE)
can_evaluate <- all(successfully_loaded)

if (can_evaluate) {
  purrr::walk(pkgs, library, character.only = TRUE)
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

---

Lifecycle: [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)

The function `ggwithinstats` is designed to facilitate 
**data exploration**, and for making highly customizable **publication-ready plots**,
with relevant statistical details included in the plot itself if desired. We
will see examples of how to use this function in this vignette.

To begin with, here are some instances where you would want to use
`ggwithinstats`-

 - to check if a continuous variable differs across multiple groups/conditions

 - to compare distributions visually

**Note**: This vignette uses the pipe operator (`%>%`), if you are not
familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Comparisons between groups with `ggwithinstats`

To illustrate how this function can be used, we will use the `bugs` dataset
throughout this vignette. This data set, "Bugs", provides the extent to which
men and women want to kill arthropods that vary in freighteningness (low, high)
and disgustingness (low, high). Each participant rates their attitudes towards
all anthropods. Subset of the data reported by [Ryan et al. (2013)](https://www.sciencedirect.com/science/article/pii/S0747563213000277). 
Note that this is a repeated measures design because the same participant gave
four different ratings across four different conditions (LDLF, LDHF, HDLF,
HDHF).

Suppose the first thing we want to inspect is the distribution of desire to kill
across all conditions (disregarding the factorial structure of the experiment).
We also want to know if the mean differences in this desire across conditions is
statistically significant.

The simplest form of the function call is-

```{r}
#| label = "ggwithinstats1",
#| fig.height = 6,
#| fig.width = 8

ggwithinstats(
  data = bugs_long,
  x = condition,
  y = desire
)
```

**Note**:

  - The function automatically decides whether a dependent samples test is
    preferred (for 2 groups) or an ANOVA (3 or more groups). based on the number
    of levels in the grouping variable.
    
  - The output of the function is a `ggplot` object which means that it can be
    further modified with `{ggplot2}` functions.

As can be seen from the plot, the function by default returns Bayes Factor for
the test. If the null hypothesis can't be rejected with the null hypothesis
significance testing (NHST) approach, the Bayesian approach can help index
evidence in favor of the null hypothesis (i.e., $BF_{01}$).

By default, natural logarithms are shown because Bayes Factor values can
sometimes be pretty large. Having values on logarithmic scale also makes it easy
to compare evidence in favor alternative ($BF_{10}$) versus null ($BF_{01}$)
hypotheses (since $log_{e}(BF_{01}) = - log_{e}(BF_{10})$).

We can make the output much more aesthetically pleasing as well as informative
by making use of the many optional parameters in `ggwithinstats`. We'll add a
title and caption, better `x` and `y` axis labels. We can and will change the overall theme as well as the
color palette in use.

```{r}
#| label = "ggwithinstats2",
#| fig.height = 6,
#| fig.width = 8

ggwithinstats(
  data = bugs_long,
  x = condition,
  y = desire,
  type = "nonparametric", ## type of statistical test
  xlab = "Condition", ## label for the x-axis
  ylab = "Desire to kill an artrhopod", ## label for the y-axis
  effsize.type = "biased", ## type of effect size
  sphericity.correction = FALSE, ## don't display sphericity corrected dfs and p-values
  pairwise.comparisons = TRUE, ## display pairwise comparisons
  mean.plotting = TRUE, ## whether the mean is to be displayed
  mean.color = "darkblue", ## color for mean
  package = "yarrr", ## package from which color palette is to be taken
  palette = "info2", ## choosing a different color palette
  title = "Comparison of desire to kill bugs",
  caption = "Source: Ryan et al., 2013"
) + ## modifying the plot further
  ggplot2::scale_y_continuous(
    limits = c(0, 10),
    breaks = seq(from = 0, to = 10, by = 1)
  )
```

As can be appreciated from the effect size (partial eta squared) of 0.18, there
are small differences in the mean desire to kill across conditions.
Importantly, this plot also helps us appreciate the distributions within any
given condition. 

So far we have only used a classic parametric test, but we can also use other
available options: The `type` (of test) argument also accepts the following
abbreviations: `"p"` (for *parametric*), `"np"` (for *nonparametric*), `"r"`
(for *robust*), `"bf"` (for *Bayes Factor*).

Let's use the `combine_plots` function to make one plot from four separate plots
that demonstrates all of these options. Let's compare desire to kill bugs only
for low versus high disgust conditions to see how much of a difference whether a
bug is disgusting-looking or not makes to the desire to kill that bug. We will
generate the plots one by one and then use `combine_plots` to merge them into
one plot with some common labeling. It is possible, but not necessarily
recommended, to make each plot have different colors or themes.

For example,

```{r}
#| label = "ggwithinstats3",
#| fig.height = 14,
#| fig.width = 14

## selecting subset of the data
df_disgust <- dplyr::filter(bugs_long, condition %in% c("LDHF", "HDHF"))

## parametric t-test
p1 <- ggwithinstats(
  data = df_disgust,
  x = condition,
  y = desire,
  type = "p",
  effsize.type = "d",
  conf.level = 0.99,
  title = "Parametric test",
  package = "ggsci",
  palette = "nrc_npg"
)

## Mann-Whitney U test (nonparametric test)
p2 <- ggwithinstats(
  data = df_disgust,
  x = condition,
  y = desire,
  xlab = "Condition",
  ylab = "Desire to kill bugs",
  type = "np",
  conf.level = 0.99,
  title = "Non-parametric Test",
  package = "ggsci",
  palette = "uniform_startrek"
)

## robust t-test
p3 <- ggwithinstats(
  data = df_disgust,
  x = condition,
  y = desire,
  xlab = "Condition",
  ylab = "Desire to kill bugs",
  type = "r",
  conf.level = 0.99,
  title = "Robust Test",
  package = "wesanderson",
  palette = "Royal2"
)

## Bayes Factor for parametric t-test
p4 <- ggwithinstats(
  data = df_disgust,
  x = condition,
  y = desire,
  xlab = "Condition",
  ylab = "Desire to kill bugs",
  type = "bayes",
  title = "Bayesian Test",
  package = "ggsci",
  palette = "nrc_npg"
)

## combining the individual plots into a single plot
combine_plots(
  plotlist = list(p1, p2, p3, p4),
  plotgrid.args = list(nrow = 2),
  annotation.args = list(
    title = "Effect of disgust on desire to kill bugs ",
    caption = "Source: Bugs dataset from `jmv` R package"
  )
)
```

## Grouped analysis with `grouped_ggwithinstats`

What if we want to carry out this same analysis but for each region (or gender)?

`{ggstatsplot}` provides a special helper function for such instances:
`grouped_ggwithinstats`. This is merely a wrapper function around
`combine_plots`. It applies `ggwithinstats` across all **levels**
of a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc.

Let's focus on the two regions and for years: 1967, 1987, 2007. Also,
let's carry out pairwise comparisons to see if there differences between every
pair of continents. 

```{r}
#| label = "grouped1",
#| fig.height = 14,
#| fig.width = 8

grouped_ggwithinstats(
  ## arguments relevant for ggwithinstats
  data = bugs_long,
  x = condition,
  y = desire,
  grouping.var = gender,
  xlab = "Continent",
  ylab = "Desire to kill bugs",
  type = "nonparametric", ## type of test
  pairwise.display = "significant", ## display only significant pairwise comparisons
  p.adjust.method = "BH", ## adjust p-values for multiple tests using this method
  # ggtheme = ggthemes::theme_tufte(),
  package = "ggsci",
  palette = "default_jco",
  k = 3,
  ## arguments relevant for combine_plots
  annotation.args = list(title = "Desire to kill bugs across genders"),
  plotgrid.args = list(ncol = 1)
)
```

## Grouped analysis with `ggwithinstats` + `{purrr}` 

Although this grouping function provides a quick way to explore the data, it
leaves much to be desired. For example, the same type of test and theme is
applied for all genders, but maybe we want to change this for different genders,
or maybe we want to gave different effect sizes for different years. This type
of customization for different levels of a grouping variable is not possible
with `grouped_ggwithinstats`, but this can be easily achieved using the `{purrr}`
package.

See the associated vignette here:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html>

## Between-subjects designs

For independent measures designs, `ggbetweenstats` function can be used:
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggbetweenstats.html>

## Summary of graphics and tests

Details about underlying functions used to create graphics and statistical tests carried out can be found in the function documentation:
<https://indrajeetpatil.github.io/ggstatsplot/reference/ggwithinstats.html>

## Reporting

```{asis, file="../../man/md-fragments/reporting.md"}
```

For example, let's see the following example:

```{r}
#| label = "reporting",
#| fig.height = 6,
#| fig.width = 8
library(WRS2) # for data
ggwithinstats(WineTasting, Wine, Taste)
```

The narrative context (assuming `type = "parametric"`) can complement this plot
either as a figure caption or in the main text-

> Fisher's repeated measures one-way ANOVA revealed that, across 22 friends to
taste each of the three wines, there was a statistically significant difference
across persons preference for each wine. The effect size $(\omega_{p} = 0.02)$
was medium, as per Field’s (2013) conventions. The Bayes Factor for the same
analysis revealed that the data were `r round(exp(2.11), 2)` times more probable
under the alternative hypothesis as compared to the null hypothesis. This can be
considered moderate evidence (Jeffreys, 1961) in favor of the alternative
hypothesis. This global effect was carried out by post hoc pairwise *t*-tests,
which revealed that Wine C was preferred across participants to be the least
desirable compared to Wines A and B.

Similar reporting style can be followed when the function performs *t*-test
instead of a one-way ANOVA.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
