---
title: "ggwithinstats"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ggwithinstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE

source("../setup.R")
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

---

Lifecycle: [![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html)

The function `ggwithinstats` is designed to facilitate
**data exploration**, and for making highly customizable **publication-ready plots**,
with relevant statistical details included in the plot itself if desired. We
will see examples of how to use this function in this vignette.

To begin with, here are some instances where you would want to use
`ggwithinstats`-

 - to check if a continuous variable differs across multiple conditions measured
   on the same subjects (repeated measures or within-subjects designs)

 - to compare distributions visually

To illustrate how this function can be used, we will use the `bugs_long` dataset
throughout this vignette. This data set, "Bugs", provides the extent to which
men and women want to kill arthropods that vary in frighteningness (low, high)
and disgustingness (low, high). Each participant rates their attitudes towards
all arthropods. Subset of the data reported by [Ryan et al. (2013)](https://www.sciencedirect.com/science/article/pii/S0747563213000277).
Note that this is a repeated measures design because the same participant gave
four different ratings across four different conditions (LDLF, LDHF, HDLF,
HDHF).

## Data format

`ggwithinstats()` expects data in the **long** format: one row per
observation, with one column for the condition (`x`), one for the measurement
(`y`), and, ideally, one identifying the subject (`subject.id`). This is how
`bugs_long` is organized:

```{r}
#| label = "bugs_long"
dplyr::glimpse(bugs_long)
```

If your data are in the **wide** format (one row per subject and one column per
condition), first reshape them with `tidyr::pivot_longer()`:

```{r}
#| label = "wide_to_long"
# a data frame in the wide format
df_wide <- tidyr::pivot_wider(bugs_long, names_from = condition, values_from = desire)
head(df_wide)

# converting it to the long format
df_long <- tidyr::pivot_longer(
  df_wide,
  cols = c(LDLF, LDHF, HDLF, HDHF),
  names_to = "condition",
  values_to = "desire"
)
head(df_long)
```

Supplying `subject.id` is strongly recommended: it is used to pair
observations of the same subject across conditions. If it is omitted, the
function assumes that the rows are already sorted in the same subject order
within every condition. Subjects with missing values in any condition are
excluded from the statistical analysis.

## Comparisons between conditions with `ggwithinstats`

Suppose the first thing we want to inspect is the distribution of desire to kill
across all conditions (disregarding the factorial structure of the experiment).
We also want to know if the mean differences in this desire across conditions is
statistically significant.

The simplest form of the function call is-

```{r}
#| label = "ggwithinstats1",
#| fig.height = 6,
#| fig.width = 8

ggwithinstats(
  data       = bugs_long,
  x          = condition,
  y          = desire,
  subject.id = subject
)
```

**Note**:

  - The function automatically decides whether a paired samples test (for 2
    conditions) or a repeated measures ANOVA (3 or more conditions) is carried
    out, based on the number of levels in the `x` variable.

  - The output of the function is a `ggplot` object which means that it can be
    further modified with `{ggplot2}` functions.

As can be seen from the plot, the function by default also returns Bayes Factor
for the test in the caption. If the null hypothesis can't be rejected with the null hypothesis
significance testing (NHST) approach, the Bayesian approach can help index
evidence in favor of the null hypothesis (i.e., $BF_{01}$).

By default, natural logarithms are shown because Bayes Factor values can
sometimes be pretty large. Having values on logarithmic scale also makes it easy
to compare evidence in favor of alternative ($BF_{10}$) versus null ($BF_{01}$)
hypotheses (since $log_{e}(BF_{01}) = - log_{e}(BF_{10})$).

We can make the output much more aesthetically pleasing as well as informative
by making use of the many optional parameters in `ggwithinstats`. We'll add a
title and caption, better `x` and `y` axis labels. We can and will change the
color palette in use as well. This time, let's also use a nonparametric test.

```{r}
#| label = "ggwithinstats2",
#| fig.height = 6,
#| fig.width = 8

ggwithinstats(
  data       = bugs_long,
  x          = condition,
  y          = desire,
  subject.id = subject,
  type       = "nonparametric", ## type of statistical test
  xlab       = "Condition", ## label for the x-axis
  ylab       = "Desire to kill an arthropod", ## label for the y-axis
  palette    = "yarrr::info2", ## choosing a different color palette
  title      = "Comparison of desire to kill bugs",
  caption    = "Source: Ryan et al., 2013"
) + ## modifying the plot further
  ggplot2::scale_y_continuous(
    limits = c(0, 10),
    breaks = seq(from = 0, to = 10, by = 1)
  )
```

As can be appreciated from the effect size (Kendall's *W*) of 0.21, there are
small differences in the desire to kill across conditions.
Importantly, this plot also helps us appreciate the distributions within any
given condition.

We can also use other available options: The `type` (of test) argument also accepts the following
abbreviations: `"p"` (for *parametric*), `"np"` (for *nonparametric*), `"r"`
(for *robust*), `"bf"` (for *Bayes Factor*).

Let's use the `combine_plots` function to make one plot from four separate plots
that demonstrates all of these options. Let's compare desire to kill bugs only
for low versus high disgust conditions to see how much of a difference whether a
bug is disgusting-looking or not makes to the desire to kill that bug. We will
generate the plots one by one and then use `combine_plots` to merge them into
one plot with some common labeling. It is possible, but not necessarily
recommended, to make each plot have different colors or themes.

For example,

```{r}
#| label = "ggwithinstats3",
#| fig.height = 14,
#| fig.width = 14

## selecting subset of the data
df_disgust <- dplyr::filter(bugs_long, condition %in% c("LDHF", "HDHF"))

## parametric t-test
p1 <- ggwithinstats(
  data = df_disgust,
  x = condition,
  y = desire,
  subject.id = subject,
  xlab = "Condition",
  ylab = "Desire to kill bugs",
  type = "p",
  conf.level = 0.99,
  title = "Parametric test",
  palette = "ggsci::nrc_npg"
)

## Wilcoxon signed-rank test (nonparametric test)
p2 <- ggwithinstats(
  data       = df_disgust,
  x          = condition,
  y          = desire,
  subject.id = subject,
  xlab       = "Condition",
  ylab       = "Desire to kill bugs",
  type       = "np",
  conf.level = 0.99,
  title      = "Non-parametric Test",
  palette    = "ggsci::uniform_startrek"
)

## Yuen's paired trimmed means test (robust test)
p3 <- ggwithinstats(
  data       = df_disgust,
  x          = condition,
  y          = desire,
  subject.id = subject,
  xlab       = "Condition",
  ylab       = "Desire to kill bugs",
  type       = "r",
  conf.level = 0.99,
  title      = "Robust Test",
  palette    = "wesanderson::Royal2"
)

## Bayes Factor for parametric t-test
p4 <- ggwithinstats(
  data       = df_disgust,
  x          = condition,
  y          = desire,
  subject.id = subject,
  xlab       = "Condition",
  ylab       = "Desire to kill bugs",
  type       = "bayes",
  title      = "Bayesian Test",
  palette    = "ggsci::nrc_npg"
)

## combining the individual plots into a single plot
combine_plots(
  plotlist = list(p1, p2, p3, p4),
  plotgrid.args = list(nrow = 2L),
  annotation.args = list(
    title = "Effect of disgust on desire to kill bugs",
    caption = "Source: Bugs dataset from `jmv` R package"
  )
)
```

## Grouped analysis with `grouped_ggwithinstats`

What if we want to carry out this same analysis but for each region (or gender)?

`{ggstatsplot}` provides a special helper function for such instances:
`grouped_ggwithinstats`. This is merely a wrapper function around
`combine_plots`. It applies `ggwithinstats` across all **levels**
of a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc.

Let's carry out the analysis separately for each gender. Also, let's carry out
pairwise comparisons to see if there are differences between every pair of
conditions.

```{r}
#| label = "grouped1",
#| fig.height = 14,
#| fig.width = 8

grouped_ggwithinstats(
  ## arguments relevant for ggwithinstats
  data             = bugs_long,
  x                = condition,
  y                = desire,
  subject.id       = subject,
  grouping.var     = gender,
  xlab             = "Condition",
  ylab             = "Desire to kill bugs",
  type             = "nonparametric", ## type of test
  pairwise.display = "significant", ## display only significant pairwise comparisons
  pairwise.alpha   = 0.01, ## use a stricter alpha threshold to reduce clutter
  p.adjust.method  = "BH", ## adjust p-values for multiple tests using this method
  palette          = "ggsci::default_jco",
  digits           = 3,
  ## arguments relevant for combine_plots
  annotation.args  = list(title = "Desire to kill bugs across genders"),
  plotgrid.args    = list(ncol = 1)
)
```

## Grouped analysis with `ggwithinstats` + `{purrr}`

Although this grouping function provides a quick way to explore the data, it
leaves much to be desired. For example, the same type of test and theme is
applied for all genders, but maybe we want to change this for different genders,
or maybe we want to have different types of tests for different genders. This type
of customization for different levels of a grouping variable is not possible
with `grouped_ggwithinstats`, but this can be easily achieved using the `{purrr}`
package.

See the associated vignette here:
<https://www.indrapatil.com/ggstatsplot/articles/web_only/purrr_examples.html>

## Between-subjects designs

For independent measures designs, `ggbetweenstats` function can be used:
<https://www.indrapatil.com/ggstatsplot/articles/web_only/ggbetweenstats.html>

## Summary of graphics and tests

```{r child="../../man/rmd-fragments/ggwithinstats_graphics.Rmd"}
```

The statistical tests and effect sizes carried out for each `type` are listed
in the function documentation:
<https://www.indrapatil.com/ggstatsplot/reference/ggwithinstats.html>

## Extracting statistical details

All statistical details shown in the plot are also available as data frames,
which can be extracted with `extract_stats()`. The returned list contains
results from the test in the subtitle (`subtitle_data`), the Bayesian test in
the caption (`caption_data`), and the pairwise comparisons
(`pairwise_comparisons_data`).

```{r}
#| label = "extract_stats"
p <- ggwithinstats(bugs_long, condition, desire, subject.id = subject)

extract_stats(p)$subtitle_data

extract_stats(p)$pairwise_comparisons_data
```

For `grouped_ggwithinstats()` plots, `extract_stats()` returns one such list
for each level of the grouping variable.

## Reporting

```{asis, file="../../man/md-fragments/reporting.md"}
```

For example, let's see the following example:

```{r}
#| label = "reporting",
#| fig.height = 6,
#| fig.width = 8
ggwithinstats(WRS2::WineTasting, Wine, Taste, subject.id = Taster)
```

The narrative context (assuming `type = "parametric"`) can complement this plot
either as a figure caption or in the main text-

> Fisher's repeated measures one-way ANOVA revealed that, across 22 friends to
taste each of the three wines, there was a statistically significant difference
across persons preference for each wine. The effect size $(\omega_{p}^2 = 0.02)$
was small, as per Field’s (2013) conventions. The Bayes Factor for the same
analysis revealed that the data were `r round(exp(2.13), 2)` times more probable
under the alternative hypothesis as compared to the null hypothesis. This can be
considered moderate evidence (Jeffreys, 1961) in favor of the alternative
hypothesis. This global effect was followed by post hoc pairwise *t*-tests,
which revealed that Wine C was preferred across participants to be the least
desirable compared to Wines A and B.

Similar reporting style can be followed when the function performs *t*-test
instead of a one-way ANOVA.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
