---
title: "Pairwise comparisons with `{ggstatsplot}`"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    eval: FALSE
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{Pairwise comparisons with `{ggstatsplot}`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
## pretty tibble printing
options(
  tibble.width = Inf,
  pillar.bold = TRUE,
  pillar.neg = TRUE,
  pillar.subtle_num = TRUE,
  pillar.min_chars = Inf
)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  warning = FALSE,
  message = FALSE,
  out.width = "100%",
  comment = "#>",
  package.startup.message = FALSE
)

library(ggstatsplot)
```

---

You can cite this package/vignette as:

```{r citation, echo=FALSE, comment = ""}
citation("ggstatsplot")
```

---

## Introduction

Pairwise comparisons with `{ggstatsplot}`.

## Summary of types of statistical analyses

Following table contains a brief summary of the currently supported pairwise
comparison tests-

### Between-subjects design

Type | Equal variance? | Test | *p*-value adjustment? | Function used
----------- | --- | ------------------------- | --- | -----
Parametric | No | Games-Howell test | ✅ | `stats::pairwise.t.test`
Parametric | Yes | Student's *t*-test | ✅ | `PMCMRplus::gamesHowellTest`
Non-parametric | No | Dunn test | ✅ | `PMCMRplus::kwAllPairsDunnTest`
Robust | No | Yuen's trimmed means test | ✅ | `WRS2::lincon`
Bayesian | `NA` | Student's *t*-test | `NA` | `BayesFactor::ttestBF`

### Within-subjects design

Type | Test | *p*-value adjustment? | Function used
----------- | ---------------------------- | --- | -----
Parametric | Student's *t*-test | ✅ | `stats::pairwise.t.test`
Non-parametric | Durbin-Conover test | ✅ | `PMCMRplus::durbinAllPairsTest` 
Robust | Yuen's trimmed means test | ✅ | `WRS2::rmmcp`
Bayesian | Student's *t*-test | `NA` | `BayesFactor::ttestBF`

## Examples

Here we will see specific examples of how to use this function for different
types of

  - designs (between or within subjects)
  - statistics (parametric, non-parametric, robust, Bayesian)
  - *p*-value adjustment methods

### Between-subjects design

```{r}
## for reproducibility
set.seed(123)
library(ggstatsplot)
library(statsExpressions) ## for data

## parametric
## if `var.equal = TRUE`, then Student's *t*-test will be run
pairwise_comparisons(
  data            = ggplot2::msleep,
  x               = vore,
  y               = brainwt,
  type            = "parametric",
  var.equal       = TRUE,
  paired          = FALSE,
  p.adjust.method = "bonferroni"
)

## if `var.equal = FALSE`, then Games-Howell test will be run
pairwise_comparisons(
  data            = ggplot2::msleep,
  x               = vore,
  y               = brainwt,
  type            = "parametric",
  var.equal       = FALSE,
  paired          = FALSE,
  p.adjust.method = "bonferroni"
)

## non-parametric
pairwise_comparisons(
  data            = ggplot2::msleep,
  x               = vore,
  y               = brainwt,
  type            = "nonparametric",
  paired          = FALSE,
  p.adjust.method = "none"
)

## robust
pairwise_comparisons(
  data            = ggplot2::msleep,
  x               = vore,
  y               = brainwt,
  type            = "robust",
  paired          = FALSE,
  p.adjust.method = "fdr"
)

## Bayesian
pairwise_comparisons(
  data   = ggplot2::msleep,
  x      = vore,
  y      = brainwt,
  type   = "bayes",
  paired = FALSE
)
```


### Within-subjects design

```{r}
## for reproducibility
set.seed(123)

## parametric
pairwise_comparisons(
  data            = bugs_long,
  x               = condition,
  y               = desire,
  subject.id      = subject,
  type            = "parametric",
  paired          = TRUE,
  p.adjust.method = "BH"
)

## non-parametric
pairwise_comparisons(
  data            = bugs_long,
  x               = condition,
  y               = desire,
  subject.id      = subject,
  type            = "nonparametric",
  paired          = TRUE,
  p.adjust.method = "BY"
)

## robust
pairwise_comparisons(
  data            = bugs_long,
  x               = condition,
  y               = desire,
  subject.id      = subject,
  type            = "robust",
  paired          = TRUE,
  p.adjust.method = "hommel"
)

## Bayesian
pairwise_comparisons(
  data       = bugs_long,
  x          = condition,
  y          = desire,
  subject.id = subject,
  type       = "bayes",
  paired     = TRUE,
  bf.prior   = 0.77
)
```

## Using `pairwise_comparisons()` with `ggsignif`

### Example-1: between-subjects

```{r ggsignif, fig.height=5}
## needed libraries
set.seed(123)
library(ggplot2)
library(ggsignif)

## converting to factor
mtcars$cyl <- as.factor(mtcars$cyl)

## creating a basic plot
p <- ggplot(mtcars, aes(cyl, wt)) +
  geom_boxplot()

## using `pairwise_comparisons()` package to create a dataframe with results
set.seed(123)
(df <-
  pairwise_comparisons(mtcars, cyl, wt) %>%
  dplyr::mutate(groups = purrr::pmap(.l = list(group1, group2), .f = c)) %>%
  dplyr::arrange(group1))

## using `geom_signif` to display results
## (note that you can choose not to display all comparisons)
p +
  ggsignif::geom_signif(
    comparisons = list(df$groups[[1]]),
    annotations = df$label[[1]],
    test        = NULL,
    na.rm       = TRUE,
    parse       = TRUE
  )
```

### Example-2: within-subjects

```{r ggsignif2}
## needed libraries
library(ggplot2)
library(ggstatsplot)
library(ggsignif)

## creating a basic plot
p <- ggplot(WRS2::WineTasting, aes(Wine, Taste)) +
  geom_boxplot()

## using `pairwise_comparisons()` package to create a dataframe with results
set.seed(123)
(df <-
  pairwise_comparisons(
    WRS2::WineTasting,
    Wine,
    Taste,
    subject.id = Taster,
    type = "bayes",
    paired = TRUE
  ) %>%
  dplyr::mutate(groups = purrr::pmap(.l = list(group1, group2), .f = c)) %>%
  dplyr::arrange(group1))

## using `geom_signif` to display results
p +
  ggsignif::geom_signif(
    comparisons      = df$groups,
    map_signif_level = TRUE,
    tip_length       = 0.01,
    y_position       = c(6.5, 6.65, 6.8),
    annotations      = df$label,
    test             = NULL,
    na.rm            = TRUE,
    parse            = TRUE
  )
```

