---
title: "Pairwise comparisons with `{ggstatsplot}`"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Pairwise comparisons with `{ggstatsplot}`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE

source("../setup.R")
```

```{r}
#| label = "suggested_pkgs",
#| include = FALSE

pkgs <- "PMCMRplus"

successfully_loaded <- purrr::map_lgl(pkgs, requireNamespace, quietly = TRUE)
can_evaluate <- all(successfully_loaded)

if (can_evaluate) {
  purrr::walk(pkgs, library, character.only = TRUE)
} else {
  knitr::opts_chunk$set(eval = FALSE)
}
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

---

## Introduction

When the grouping variable `x` has more than two levels, `ggbetweenstats()` and
`ggwithinstats()` follow up the omnibus test (ANOVA or its non-parametric,
robust, or Bayesian counterpart) with pairwise comparisons between all pairs of
groups and display them using `{ggsignif}` brackets. The comparisons themselves
are carried out by `statsExpressions::pairwise_comparisons()`.

## Summary of types of statistical analyses

The tests used for each `type` (and the functions used internally to compute
them) are listed in the *Pairwise comparison tests* section of the
documentation for
[`ggbetweenstats()`](https://www.indrapatil.com/ggstatsplot/reference/ggbetweenstats.html)
(between-subjects designs) and
[`ggwithinstats()`](https://www.indrapatil.com/ggstatsplot/reference/ggwithinstats.html)
(within-subjects designs).

A few points worth noting:

- For between-subjects designs, `ggbetweenstats()` always uses the Games-Howell
  test for `type = "parametric"`, which doesn't assume equal variances. If you
  want Student's *t*-test instead, call
  `statsExpressions::pairwise_comparisons()` directly with `var.equal = TRUE`.
- *p*-values are adjusted for multiple comparisons using the method specified
  in `p.adjust.method` (default: `"holm"`); use `"none"` for no adjustment.
- `pairwise.display` decides which comparisons are shown (`"significant"`,
  `"non-significant"`, `"all"`, or `"none"`), and `pairwise.alpha` sets the
  cutoff used for this decision.
- For `type = "bayes"`, there is no *p*-value adjustment, and all comparisons
  are displayed with $\log_{e}(BF_{01})$ values unless
  `pairwise.display = "none"`.
- For within-subjects designs, specify `subject.id` and make sure that there is
  exactly one observation per subject per condition.

## Data frame outputs

The results of the pairwise comparisons shown in a plot can be extracted with
`extract_stats()`:

```{r}
#| label = "extract_stats"

p <- ggbetweenstats(mtcars, cyl, wt)

extract_stats(p)$pairwise_comparisons_data
```

For more examples of data frame outputs from
`statsExpressions::pairwise_comparisons()`, see
[here](https://www.indrapatil.com/statsExpressions/articles/web_only/dataframe_outputs.html#pairwise-comparisons-for-one-way-design).

## Using `statsExpressions::pairwise_comparisons()` with `ggsignif`

### Example-1: between-subjects

```{r}
#| label = "ggsignif",
#| fig.height = 5

library(ggplot2)
library(ggsignif)

## converting to factor
mtcars$cyl <- as.factor(mtcars$cyl)

## creating a basic plot
p <- ggplot(mtcars, aes(cyl, wt)) +
  geom_boxplot()

## using `statsExpressions::pairwise_comparisons()` function to create a data frame with results
df <-
  statsExpressions::pairwise_comparisons(mtcars, cyl, wt) |>
  dplyr::mutate(groups = purrr::pmap(.l = list(group1, group2), .f = c)) |>
  dplyr::arrange(group1)

df

## using `geom_signif` to display results
## (note that you can choose not to display all comparisons)
p +
  ggsignif::geom_signif(
    comparisons = list(df$groups[[1]]),
    annotations = as.character(df$expression)[[1]],
    test        = NULL,
    na.rm       = TRUE,
    parse       = TRUE
  )
```

### Example-2: within-subjects

```{r}
#| label = "ggsignif2",
#| fig.height = 7

library(ggplot2)
library(ggsignif)

## creating a basic plot
p <- ggplot(WRS2::WineTasting, aes(Wine, Taste)) +
  geom_boxplot()

## using `statsExpressions::pairwise_comparisons()` function to create a data frame with results
df <-
  statsExpressions::pairwise_comparisons(
    WRS2::WineTasting,
    Wine,
    Taste,
    subject.id = Taster,
    type = "bayes",
    paired = TRUE
  ) |>
  dplyr::mutate(groups = purrr::pmap(.l = list(group1, group2), .f = c)) |>
  dplyr::arrange(group1)

df

## using `geom_signif` to display results
p +
  ggsignif::geom_signif(
    comparisons      = df$groups,
    map_signif_level = TRUE,
    tip_length       = 0.01,
    y_position       = c(6.5, 6.65, 6.8),
    annotations      = as.character(df$expression),
    test             = NULL,
    na.rm            = TRUE,
    parse            = TRUE
  )
```
