---
title: "Using 'ggstatsplot' with the 'purrr' package"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Using 'ggstatsplot' with the 'purrr' package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label = "setup",
#| include = FALSE
source("../setup.R")
```

---

You can cite this package/vignette as:

```{r}
#| label = "citation",
#| echo = FALSE,
#| comment = ""
citation("ggstatsplot")
```

---

---

This is an extremely time-consuming vignette, and so it is not evaluated here.
You can still use the code as a reference for writing your own `{purrr}` code.

---

## Why use `{purrr}`?

Most of the `{ggstatsplot}` functions have `grouped_` variants, which are designed
to quickly run the same `{ggstatsplot}` function across multiple levels of a
**single** grouping variable. Although this function is useful for data
exploration, it has two strong weaknesses-

 * The arguments applied to `grouped_` function call are applied uniformly to
   all levels of the grouping variable when we might want to customize them for
   different levels of the grouping variable.

 * Only one grouping variable can be used to repeat the analysis when in reality
   there can be a combination of grouping variables and the operation needs to
   be repeated for all resulting combinations.

We will see how to overcome this limitation by combining `{ggstatsplot}` with the
`{purrr}` package.

**Note:**

 * While using `purrr::pmap()`, we **must** input the arguments as strings.

 * You can use `{ggplot2}` themes from extension packages (e.g. `ggthemes`).

 * If you'd like some more background or an introduction to the purrr package,
   please see [this chapter](https://adv-r.hadley.nz/functionals.html).

## Introduction and methodology

For all the examples in this vignette we are going to build `list`s of things
that we will pass along to `{purrr}` which will in turn return a list of plots
that will be passed to `combine_plots`. As the name implies `combine_plots`
merges the individual plots into one bigger plot with common labeling and
aesthetics.

What are these `lists` that we are building? The lists correspond to the
parameters in our `{ggstatsplot}` function like `ggbetweenstats`. If you look at
the help file for `?ggbetweenstats` for example the very first parameter it
wants is the `data` file we'll be using. We can also pass it different `titles`
of even `ggtheme` themes.

You can pass:

 * A single character string such as `xlab = "Continent"` or numeric such as
   `nboot = 25` in which case it will be reused/recycled as many times as
   needed.

 * A vector of values such as `nboot = c(50, 100, 200)` in which case it
   will be coerced to a list and checked for the right class (in this case
   integer) and the right quantity of entries in the vector i.e.,
   `nboot = c(50, 100)` will fail if we're trying to make three plots.

 * A list; either named `data = year_list` or created as you go
   `palette = list("Dark2", "Set1")`. Any list will
   be checked for the right class (in this case character) and the right
   quantity of entries in the list.

## `ggbetweenstats`

Let's start with `ggebtweenstats`. We'll use the `gapminder` dataset. We'll make
a 3 item `list` called `year_list` using `dplyr::filter` and `split`.

```r



## let's split the data frame and create a list by years of interest
year_list <- gapminder::gapminder %>%
  dplyr::filter(year %in% c(1967, 1987, 2007), continent != "Oceania") %>%
  split(f = .$year, drop = TRUE)

## checking the length of the list and the names of each element
length(year_list)
names(year_list)
```

Now that we have the data divided into the three relevant years in a list we'll
turn to `purrr::pmap` to create a list of `ggplot` objects that we'll make use of
stored in `plot_list`. When you look at the documentation for `?pmap` it will
accept `.l` which is a list of lists. The length of `.l` determines the number of
arguments that `.f` will be called with. List names will be used if present.
`.f` is the function we want to apply (here, `.f = ggbetweenstats`).

Let's keep building the list of arguments, `.l`. First is `data = year_list`,
the `x` and `y` axes are constant in all three plots so we pass the variable
name as a string `x = "continent"`.

```r
## creating a list of plots
plot_list <- purrr::pmap(
  .l = list(
    data = year_list,
    x = "continent",
    y = "lifeExp",
    xlab = "Continent",
    ylab = "Life expectancy",
    title = list(
      "Year: 1967",
      "Year: 1987",
      "Year: 2007"
    ),
    type = list("r", "bf", "np"),
    pairwise.display = list("s", "ns", "all"),
    p.adjust.method = list("hommel", "bonferroni", "BH"),
    conf.level = list(0.99, 0.95, 0.90),
    digits = list(1, 2, 3),
    effsize.type = list(
      NULL,
      "partial_omega",
      "partial_eta"
    ),
    package = list("nord", "ochRe", "awtools"),
    palette = list("aurora", "parliament", "bpalette"),
    ggtheme = list(
      ggthemes::theme_stata(),
      ggplot2::theme_classic(),
      ggthemes::theme_fivethirtyeight()
    )
  ),
  .f = ggbetweenstats
)
```

The final step is to pass the `plot_list` object we just created to the
`combine_plots` function. While each of the 3 plots already has labeling
information `combine_plots` gives us an opportunity to add additional details to
the merged plots and specify the layout in rows and columns.

```r
## combining all individual plots from the list into a single plot using combine_plots function
combine_plots(
  plotlist = plot_list,
  annotation.args = list(title = "Changes in life expectancy across continents (1967-2007)"),
  plotgrid.args = list(ncol = 1)
)
```

## `ggwithinstats`

We will be using simulated data from then Attention Network Test provided in ANT
dataset in `ez` package.

```r

library(ez)
data("ANT") ## loading data from `ez` package

## let's split the data frame and create a list by years of interest
cue_list <- ANT %>% split(f = .$cue, drop = TRUE)

## checking the length of the list and the names of each element
length(cue_list)

## creating a list of plots by applying the same function for elements of the list
plot_list <- purrr::pmap(
  .l = list(
    data = cue_list,
    x = "flank",
    y = "rt",
    xlab = "Flank",
    ylab = "Response time",
    title = list(
      "Cue: None",
      "Cue: Center",
      "Cue: Double",
      "Cue: Spatial"
    ),
    type = list("p", "r", "bf", "np"),
    pairwise.display = list("ns", "s", "ns", "all"),
    p.adjust.method = list("fdr", "hommel", "bonferroni", "BH"),
    conf.level = list(0.99, 0.99, 0.95, 0.90),
    digits = list(3, 2, 2, 3),
    effsize.type = list(
      "omega",
      "eta",
      "partial_omega",
      "partial_eta"
    ),
    package = list("ggsci", "palettetown", "palettetown", "wesanderson"),
    palette = list("lanonc_lancet", "venomoth", "blastoise", "GrandBudapest1"),
    ggtheme = list(
      ggplot2::theme_linedraw(),
      hrbrthemes::theme_ft_rc(),
      ggthemes::theme_solarized(),
      ggthemes::theme_gdocs()
    )
  ),
  .f = ggwithinstats
)

## combining all individual plots from the list into a single plot using combine_plots function
combine_plots(
  plotlist = plot_list,
  annotation.args = list(title = "Response times across flank conditions for each type of cue"),
  plotgrid.args = list(ncol = 1)
)
```

## `ggscatterstats`

For the next example lets use the same methodology on different data and using
`ggscatterstats` to produce scatterplots combined with marginal
histograms/boxplots/density plots with statistical details added as a subtitle.
For data we'll use `movies_long` which is from IMDB and part of the
`{ggstatsplot}` package. Since it's a large dataset with some relatively small
categories like **NC-17** we'll sample only one quarter of the data and
completely drop NC-17 using `dplyr`. 

This time we'll put all the code in one block-

```r
mpaa_list <- movies_long %>%
  dplyr::filter(mpaa != "NC-17") %>%
  dplyr::sample_frac(size = 0.25) %>%
  split(f = .$mpaa, drop = TRUE)

## creating a list of plots
plot_list <- purrr::pmap(
  .l = list(
    data = mpaa_list,
    x = "budget",
    y = "rating",
    xlab = "Budget (in millions of US dollars)",
    ylab = "Rating on IMDB",
    title = list(
      "MPAA Rating: PG",
      "MPAA Rating: PG-13",
      "MPAA Rating: R"
    ),
    label.var = list("title"),
    ## note that you need to quote the expressions
    label.expression = list(
      quote(rating > 7.5 & budget < 100),
      quote(rating > 8 & budget < 50),
      quote(rating > 8 & budget < 10)
    ),
    type = list("r", "np", "bf"),
    xfill = list("#009E73", "#999999", "#0072B2"),
    yfill = list("#CC79A7", "#F0E442", "#D55E00"),
    ggtheme = list(
      ggthemes::theme_tufte(),
      ggplot2::theme_classic(),
      ggplot2::theme_light()
    )
  ),
  .f = ggscatterstats
)

## combining all individual plots from the list into a single plot using combine_plots function
combine_plots(
  plotlist = plot_list,
  annotation.args = list(
    title = "Relationship between movie budget and IMDB rating",
    caption = "Source: www.imdb.com"
  ),
  plotgrid.args = list(ncol = 1)
)
```

The remainder of the examples vary in content but follow the exact same
methodology as the earlier examples.

## `ggcorrmat`

```r
## splitting the data frame by cut and creating a list
## let's leave out "fair" cut
## also, to make this fast, let's only use 5% of the sample
cut_list <- ggplot2::diamonds %>%
  dplyr::sample_frac(size = 0.05) %>%
  dplyr::filter(cut != "Fair") %>%
  split(f = .$cut, drop = TRUE)

## checking the length and names of each element
length(cut_list)
names(cut_list)

## running function on every element of this list note that if you want the same
## value for a given argument across all elements of the list, you need to
## specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = cut_list,
    cor.vars = list(c("carat", "depth", "table", "price")),
    type = list("pearson", "np", "robust", "bf"),
    partial = list(TRUE, FALSE, TRUE, FALSE),
    title = list("Cut: Good", "Cut: Very Good", "Cut: Premium", "Cut: Ideal"),
    p.adjust.method = list("hommel", "fdr", "BY", "hochberg"),
    lab.size = 3.5,
    colors = list(
      c("#56B4E9", "white", "#999999"),
      c("#CC79A7", "white", "#F0E442"),
      c("#56B4E9", "white", "#D55E00"),
      c("#999999", "white", "#0072B2")
    ),
    ggtheme = list(
      ggplot2::theme_linedraw(),
      ggplot2::theme_classic(),
      ggthemes::theme_fivethirtyeight(),
      ggthemes::theme_tufte()
    )
  ),
  .f = ggcorrmat
)

## combining all individual plots from the list into a single plot using
## `combine_plots` function
combine_plots(
  plotlist = plot_list,
  guides = "keep",
  annotation.args = list(
    title = "Relationship between diamond attributes and price across cut",
    caption = "Dataset: Diamonds from ggplot2 package"
  ),
  plotgrid.args = list(nrow = 2)
)
```

## `gghistostats`

```r
## let's split the data frame and create a list by continent
## let's leave out Oceania because it has just two data points
continent_list <-
  gapminder::gapminder %>%
  dplyr::filter(year == 2007, continent != "Oceania") %>%
  split(f = .$continent, drop = TRUE)

## checking the length and names of each element
length(continent_list)
names(continent_list)

## running function on every element of this list note that if you want the same
## value for a given argument across all elements of the list, you need to
## specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = continent_list,
      x = "lifeExp",
      xlab = "Life expectancy",
      test.value = list(35.6, 58.4, 41.6, 64.7),
      type = list("p", "np", "r", "bf"),
      bf.message = list(TRUE, FALSE, FALSE, FALSE),
      title = list(
        "Continent: Africa",
        "Continent: Americas",
        "Continent: Asia",
        "Continent: Europe"
      ),
      effsize.type = list("d", "d", "g", "g"),
      ggtheme = list(
        ggplot2::theme_classic(),
        hrbrthemes::theme_ipsum_tw(),
        ggplot2::theme_minimal(),
        hrbrthemes::theme_modern_rc()
      )
    ),
    .f = gghistostats
  )

## combining all individual plots from the list into a single plot using combine_plots function
combine_plots(
  plotlist = plot_list,
  annotation.args = list(
    title = "Improvement in life expectancy worldwide since 1950",
    caption = "Note: black line - 1950; blue line - 2007"
  ),
  plotgrid.args = list(nrow = 4)
)
```  

## `ggdotplotstats`

```r
library(ggthemes)
library(hrbrthemes)

## let's split the data frame and create a list by continent
## let's leave out Oceania because it has just two data points
continent_list <-
  gapminder::gapminder %>%
  dplyr::filter(continent != "Oceania") %>%
  split(f = .$continent, drop = TRUE)

## checking the length and names of each element
length(continent_list)
names(continent_list)

## running function on every element of this list note that if you want the same
## value for a given argument across all elements of the list, you need to
## specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = continent_list,
      x = "gdpPercap",
      y = "year",
      xlab = "GDP per capita (US$, inflation-adjusted)",
      test.value = list(2500, 9000, 9500, 10000),
      type = list("p", "np", "r", "bf"),
      title = list(
        "Continent: Africa",
        "Continent: Americas",
        "Continent: Asia",
        "Continent: Europe"
      ),
      effsize.type = list("d", "d", "g", "g"),
      centrality.line.args = list(
        list(color = "red"),
        list(color = "#0072B2"),
        list(color = "#D55E00"),
        list(color = "#CC79A7")
      ),
      ggtheme = list(
        ggplot2::theme_minimal(base_family = "serif"),
        ggthemes::theme_tufte(),
        hrbrthemes::theme_ipsum_rc(axis_title_size = 10),
        ggthemes::theme_hc(bgcolor = "darkunica")
      )
    ),
    .f = ggdotplotstats
  )

## combining all individual plots from the list into a single plot using combine_plots function
combine_plots(
  plotlist = plot_list,
  annotation.args = list(title = "Improvement in GDP per capita from 1952-2007"),
  plotgrid.args = list(nrow = 4),
  guides = "keep"
)
```  

## `ggpiestats`

```r
## let's split the data frame and create a list by passenger class
class_list <- Titanic_full %>% split(f = .$Class, drop = TRUE)

## checking the length and names of each element
length(class_list)
names(class_list)

## running function on every element of this list note that if you want the same
## value for a given argument across all elements of the list, you need to
## specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = class_list,
      x = "Survived",
      y = "Sex",
      label = list("both", "count", "percentage", "both"),
      title = list(
        "Passenger class: 1st",
        "Passenger class: 2nd",
        "Passenger class: 3rd",
        "Passenger class: Crew"
      ),
      caption = list(
        "Total: 319, Died: 120, Survived: 199, % Survived: 62%",
        "Total: 272, Died: 155, Survived: 117, % Survived: 43%",
        "Total: 709, Died: 537, Survived: 172, % Survived: 25%",
        "Data not available for crew passengers"
      ),
      package = list("RColorBrewer", "ghibli", "palettetown", "yarrr"),
      palette = list("Accent", "MarnieMedium1", "pikachu", "nemo"),
      ggtheme = list(
        ggplot2::theme_grey(),
        ggplot2::theme_bw(),
        ggthemes::theme_tufte(),
        ggthemes::theme_economist()
      ),
      proportion.test = list(TRUE, FALSE, TRUE, FALSE),
      type = list("p", "p", "bf", "p")
    ),
    .f = ggpiestats
  )

## combining all individual plots from the list into a single plot using combine_plots function
combine_plots(
  plotlist = plot_list,
  annotation.args = list(title = "Survival in Titanic disaster by gender for all passenger classes"),
  plotgrid.args = list(ncol = 1),
  guides = "keep"
)
``` 

## `ggbarstats`

```r
## let's split the data frame and create a list by passenger class
class_list <- Titanic_full %>% split(f = .$Class, drop = TRUE)

## checking the length and names of each element
length(class_list)
names(class_list)

## running function on every element of this list note that if you want the same
## value for a given argument across all elements of the list, you need to
## specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = class_list,
      x = "Survived",
      y = "Sex",
      type = "bayes",
      label = list("both", "count", "percentage", "both"),
      title = list(
        "Passenger class: 1st",
        "Passenger class: 2nd",
        "Passenger class: 3rd",
        "Passenger class: Crew"
      ),
      caption = list(
        "Total: 319, Died: 120, Survived: 199, % Survived: 62%",
        "Total: 272, Died: 155, Survived: 117, % Survived: 43%",
        "Total: 709, Died: 537, Survived: 172, % Survived: 25%",
        "Data not available for crew passengers"
      ),
      package = list("RColorBrewer", "ghibli", "palettetown", "yarrr"),
      palette = list("Accent", "MarnieMedium1", "pikachu", "nemo"),
      ggtheme = list(
        ggplot2::theme_grey(),
        ggplot2::theme_bw(),
        ggthemes::theme_tufte(),
        ggthemes::theme_economist()
      )
    ),
    .f = ggbarstats
  )

## combining all individual plots from the list into a single plot using combine_plots function
combine_plots(
  plotlist = plot_list,
  annotation.args = list(
    title = "Survival in Titanic disaster by gender for all passenger classes",
    caption = "Asterisks denote results from proportion tests: \n***: p < 0.001, ns: non-significant"
  ),
  plotgrid.args = list(ncol = 1),
  guides = "keep"
)
``` 

## `grouped_` variants

Note that although all the above examples were written with the non-grouped
variants of functions, the same rule holds true for the `grouped_` variants of
all the above functions.

For example, if we want to use the `grouped_gghistostats` across three different
datasets, you can use `purrr::pmap()` function. For the sake of brevity, the
plots are not displayed here, but you can run the following code and check the
individual `grouped_` plots (e.g., `plotlist[[1]]`).

```r
## create a list of plots
plotlist <- purrr::pmap(
    .l = list(
      data = list(mtcars, iris, ToothGrowth),
      x = alist(wt, Sepal.Length, len),
      results.subtitle = list(FALSE),
      grouping.var = alist(am, Species, supp)
    ),
    .f = grouped_gghistostats
  )

## given that we had three different datasets, we expect a list of length 3
## (each of which contains a `grouped_` plot)
length(plotlist)
```

## Repeating function execution across multiple columns in a data frame

```r

library(patchwork)

## running the same analysis on two different columns (creates a list of plots)
plotlist <- purrr::pmap(
    .l = list(
      data = list(movies_long),
      x = "mpaa",
      y = list("rating", "length"),
      title = list("IMDB score by MPAA rating", "Movie length by MPAA rating")
    ),
    .f = ggbetweenstats
  )

## combine plots using `patchwork`
plotlist[[1]] + plotlist[[2]]
```

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
