---
title: "using `ggstatsplot` with the `purrr` package"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    eval: FALSE
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{using `ggstatsplot` with the `purrr` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
# pretty tibble printing
options(
  tibble.width = Inf,
  pillar.bold = TRUE,
  pillar.neg = TRUE,
  pillar.subtle_num = TRUE,
  pillar.min_chars = Inf
)

knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  warning = FALSE,
  message = FALSE,
  out.width = "100%",
  comment = "#>",
  package.startup.message = FALSE
)

future::plan("multicore")
```

---

You can cite this package/vignette as:

```{r citation, echo=FALSE, comment = ""}
citation("ggstatsplot")
```

---

# Why use `purrr`?

Most of the `ggstatsplot` functions have `grouped_` variants, which are designed
to quickly run the same `ggstatsplot` function across multiple levels of a
**single** grouping variable. Although this function is useful for data
exploration, it has two strong weaknesses-

 * The arguments applied to `grouped_` function call are applied uniformly to
   all levels of the grouping variable when we might want to customize them for
   different levels of the grouping variable.

 * Only one grouping variable can be used to repeat the analysis when in reality
   there can be a combination of grouping variables and the operation needs to
   be repeated for all resulting combinations.

We will see how to overcome this limitation by combining `ggstatsplot` with the
`purrr` package.

**Note:**

 * While using `purrr::pmap`, we **must** input the arguments as strings.

 * You can use `{ggplot2}` themes from extension packages (e.g. `ggthemes`).

 * If you'd like some more background or an introduction to the purrr package,
   please see [this tutorial](https://jennybc.github.io/purrr-tutorial/).

# Introduction and methodology

For all the examples in this vignette we are going to build `list`s of things
that we will pass along to `purrr` which will in turn return a list of plots
that will be passed to `combine_plots`. As the name implies `combine_plots`
merges the individual plots into one bigger plot with common labeling and
aesthetics.

What are these `lists` that we are building? The lists correspond to the
parameters in our `ggstatsplot` function like `ggbetweenstats`. If you look at
the help file for `?ggbetweenstats` for example the very first parameter it
wants is the `data` file we'll be using. We can also pass it different `titles`
of even `ggtheme` themes.

You can pass:

 * A single character string such as `xlab = "Continent"` or numeric such as
   `nboot = 25` in which case it will be reused/recycled as many times as
   needed.

 * A vector of values such as `nboot = c(50, 100, 200)` in which case it
   will be coerced to a list and checked for the right class (in this case
   integer) and the right quantity of entries in the vector i.e.,
   `nboot = c(50, 100)` will fail if we're trying to make three plots.

 * A list; either named `data = year_list` or created as you go
   `palette = list("Dark2", "Set1")`. Any list will
   be checked for the right class (in this case character) and the right
   quantity of entries in the list.

# `ggbetweenstats`

Let's start with `ggebtweenstats`. We'll use the `gapminder` dataset. We'll make
a 3 item `list` called `year_list` using `dplyr::filter` and `split`.

```{r purrr_ggbetweenstats1, fig.height = 12, fig.width = 7}
# for reproducibility
library(ggstatsplot)
set.seed(123)

# let's split the dataframe and create a list by years of interest
year_list <-
  gapminder::gapminder %>%
  dplyr::filter(year %in% c(1967, 1987, 2007), continent != "Oceania") %>%
  split(f = .$year, drop = TRUE)

# checking the length of the list and the names of each element
length(year_list)
names(year_list)
```

Now that we have the data divided into the three relevant years in a list we'll
turn to `purrr::pmap` to create a list of `ggplot` objects that we'll make use of
stored in `plot_list`. When you look at the documentation for `?pmap` it will
accept `.l` which is a list of lists. The length of `.l` determines the number of
arguments that `.f` will be called with. List names will be used if present.
`.f` is the function we want to apply (here, `.f = ggstatsplot::ggbetweenstats`).

Let's keep building the list of arguments, `.l`. First is `data = year_list`,
the `x` and `y` axes are constant in all three plots so we pass the variable
name as a string `x = "continent"`.

Same with the label we'll use for outliers where needed. For demonstration
purposes let's assume we want the outliers on each plot to be a different color.
Not actually recommending it just demonstrating what's possible. The rest of the
code shows you a wide variety of possibilities and we won't catalog them here.

```{r purrr_ggbetweenstats2, fig.height = 10, fig.width = 7}
# for reproducibility
set.seed(123)
library(ggstatsplot)

# creating a list of plots
plot_list <-
  purrr::pmap(
    .l = list(
      data = year_list,
      x = "continent",
      y = "lifeExp",
      outlier.tagging = TRUE,
      outlier.label = "country",
      outlier.label.args = list(
        list(size = 3, color = "#56B4E9"),
        list(size = 2.5, color = "#009E73"),
        list(size = 3.5, color = "#F0E442")
      ),
      xlab = "Continent",
      ylab = "Life expectancy",
      title = list(
        "Year: 1967",
        "Year: 1987",
        "Year: 2007"
      ),
      type = list("r", "bf", "np"),
      pairwise.display = list("s", "ns", "all"),
      p.adjust.method = list("hommel", "bonferroni", "BH"),
      conf.level = list(0.99, 0.95, 0.90),
      k = list(1, 2, 3),
      effsize.type = list(
        NULL,
        "partial_omega",
        "partial_eta"
      ),
      plot.type = list("box", "boxviolin", "violin"),
      package = list("nord", "ochRe", "awtools"),
      palette = list("aurora", "parliament", "bpalette"),
      ggtheme = list(
        ggthemes::theme_stata(),
        ggplot2::theme_classic(),
        ggthemes::theme_fivethirtyeight()
      )
    ),
    .f = ggstatsplot::ggbetweenstats
  )
```

The final step is to pass the `plot_list` object we just created to the
`combine_plots` function. While each of the 3 plots already has labeling
information `combine_plots` gives us an opportunity to add additional details to
the merged plots and specify the layout in rows and columns.

```{r purrr_ggbetweenstats3, fig.height = 18, fig.width = 7}
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  annotation.args = list(title = "Changes in life expectancy across continents (1967-2007)"),
  plotgrid.args = list(ncol = 1)
)
```

# `ggwithinstats`

We will be using simulated data from then Attention Network Test provided in ANT
dataset in `ez` package.

```{r purrr_ggwithinstats, fig.height = 20, fig.width = 8}
# for reproducibility
set.seed(123)
library(ggstatsplot)
library(ez)
data("ANT") # loading data from `ez` package

# let's split the dataframe and create a list by years of interest
cue_list <- ANT %>% split(f = .$cue, drop = TRUE)

# checking the length of the list and the names of each element
length(cue_list)

# creating a list of plots by applying the same function for elements of the list
plot_list <-
  purrr::pmap(
    .l = list(
      data = cue_list,
      x = "flank",
      y = "rt",
      outlier.tagging = TRUE,
      outlier.label = "group",
      outlier.coef = list(2, 2, 2.5, 3),
      outlier.label.args = list(
        list(size = 3, color = "#56B4E9"),
        list(size = 2.5, color = "#009E73"),
        list(size = 4, color = "#F0E442"),
        list(size = 2, color = "red")
      ),
      xlab = "Flank",
      ylab = "Response time",
      title = list(
        "Cue: None",
        "Cue: Center",
        "Cue: Double",
        "Cue: Spatial"
      ),
      type = list("p", "r", "bf", "np"),
      pairwise.display = list("ns", "s", "ns", "all"),
      p.adjust.method = list("fdr", "hommel", "bonferroni", "BH"),
      conf.level = list(0.99, 0.99, 0.95, 0.90),
      k = list(3, 2, 2, 3),
      effsize.type = list(
        "omega",
        "eta",
        "partial_omega",
        "partial_eta"
      ),
      package = list("ggsci", "palettetown", "palettetown", "wesanderson"),
      palette = list("lanonc_lancet", "venomoth", "blastoise", "GrandBudapest1"),
      ggtheme = list(
        ggplot2::theme_linedraw(),
        hrbrthemes::theme_ft_rc(),
        ggthemes::theme_solarized(),
        ggthemes::theme_gdocs()
      )
    ),
    .f = ggstatsplot::ggwithinstats
  )

# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  annotation.args = list(title = "Response times across flank conditions for each type of cue"),
  plotgrid.args = list(ncol = 1)
)
```

# `ggscatterstats`

For the next example lets use the same methodology on different data and using
`ggscatterstats` to produce scatterplots combined with marginal
histograms/boxplots/density plots with statistical details added as a subtitle.
For data we'll use `movies_long` which is from IMDB and part of the
`ggstatsplot` package. Since it's a large dataset with some relatively small
categories like **NC-17** we'll sample only one quarter of the data and
completely drop NC-17 using `dplyr`. 

This time we'll put all the code in one block-

```{r purrr_ggscatterstats, fig.height = 14, fig.width = 7}
# for reproducibility
set.seed(123)

mpaa_list <- ggstatsplot::movies_long %>%
  dplyr::filter(mpaa != "NC-17") %>%
  dplyr::sample_frac(size = 0.25) %>%
  split(f = .$mpaa, drop = TRUE)

# creating a list of plots
plot_list <-
  purrr::pmap(
    .l = list(
      data = mpaa_list,
      x = "budget",
      y = "rating",
      xlab = "Budget (in millions of US dollars)",
      ylab = "Rating on IMDB",
      title = list(
        "MPAA Rating: PG",
        "MPAA Rating: PG-13",
        "MPAA Rating: R"
      ),
      label.var = list("title"),
      # note that you need to quote the expressions
      label.expression = list(
        quote(rating > 7.5 & budget < 100),
        quote(rating > 8 & budget < 50),
        quote(rating > 8 & budget < 10)
      ),
      type = list("r", "np", "bf"),
      xfill = list("#009E73", "#999999", "#0072B2"),
      yfill = list("#CC79A7", "#F0E442", "#D55E00"),
      ggtheme = list(
        ggthemes::theme_tufte(),
        ggplot2::theme_classic(),
        ggplot2::theme_light()
      )
    ),
    .f = ggstatsplot::ggscatterstats
  )

# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  annotation.args = list(
    title = "Relationship between movie budget and IMDB rating",
    caption = "Source: www.imdb.com"
  ),
  plotgrid.args = list(ncol = 1)
)
```

The remainder of the examples vary in content but follow the exact same
methodology as the earlier examples.

# `ggcorrmat`

```{r purrr_ggcorrmat, fig.height = 10, fig.width = 10}
# for reproducibility
set.seed(123)

# splitting the dataframe by cut and creating a list
# let's leave out "fair" cut
# also, to make this fast, let's only use 5% of the sample
cut_list <-
  ggplot2::diamonds %>%
  dplyr::sample_frac(size = 0.05) %>%
  dplyr::filter(cut != "Fair") %>%
  split(f = .$cut, drop = TRUE)

# checking the length and names of each element
length(cut_list)
names(cut_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = cut_list,
      cor.vars = list(c("carat", "depth", "table", "price")),
      type = list("pearson", "np", "robust", "bf"),
      partial = list(TRUE, FALSE, TRUE, FALSE),
      title = list("Cut: Good", "Cut: Very Good", "Cut: Premium", "Cut: Ideal"),
      p.adjust.method = list("hommel", "fdr", "BY", "hochberg"),
      lab.size = 3.5,
      colors = list(
        c("#56B4E9", "white", "#999999"),
        c("#CC79A7", "white", "#F0E442"),
        c("#56B4E9", "white", "#D55E00"),
        c("#999999", "white", "#0072B2")
      ),
      ggtheme = list(
        ggplot2::theme_linedraw(),
        ggplot2::theme_classic(),
        ggthemes::theme_fivethirtyeight(),
        ggthemes::theme_tufte()
      )
    ),
    .f = ggstatsplot::ggcorrmat
  )

# combining all individual plots from the list into a single plot using
# `combine_plots` function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  guides = "keep",
  annotation.args = list(
    title = "Relationship between diamond attributes and price across cut",
    caption = "Dataset: Diamonds from ggplot2 package"
  ),
  plotgrid.args = list(nrow = 2)
)
```

# `gghistostats`

```{r purrr_gghistostats, fig.height = 14, fig.width = 8}
# for reproducibility
set.seed(123)

# let's split the dataframe and create a list by continent
# let's leave out Oceania because it has just two data points
continent_list <-
  gapminder::gapminder %>%
  dplyr::filter(year == 2007, continent != "Oceania") %>%
  split(f = .$continent, drop = TRUE)

# checking the length and names of each element
length(continent_list)
names(continent_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = continent_list,
      x = "lifeExp",
      xlab = "Life expectancy",
      test.value = list(35.6, 58.4, 41.6, 64.7),
      type = list("p", "np", "r", "bf"),
      bf.message = list(TRUE, FALSE, FALSE, FALSE),
      title = list(
        "Continent: Africa",
        "Continent: Americas",
        "Continent: Asia",
        "Continent: Europe"
      ),
      effsize.type = list("d", "d", "g", "g"),
      normal.curve = list(TRUE, FALSE, FALSE, TRUE),
      ggtheme = list(
        ggplot2::theme_classic(),
        hrbrthemes::theme_ipsum_tw(),
        ggplot2::theme_minimal(),
        hrbrthemes::theme_modern_rc()
      )
    ),
    .f = ggstatsplot::gghistostats
  )

# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  annotation.args = list(
    title = "Improvement in life expectancy worldwide since 1950",
    caption = "Note: black line - 1950; blue line - 2007"
  ),
  plotgrid.args = list(nrow = 4)
)
```  

# `ggdotplotstats`

```{r purrr_ggdotplotstats, fig.height = 16, fig.width = 8}
# for reproducibility
set.seed(123)
library(ggthemes)
library(hrbrthemes)

# let's split the dataframe and create a list by continent
# let's leave out Oceania because it has just two data points
continent_list <-
  gapminder::gapminder %>%
  dplyr::filter(continent != "Oceania") %>%
  split(f = .$continent, drop = TRUE)

# checking the length and names of each element
length(continent_list)
names(continent_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = continent_list,
      x = "gdpPercap",
      y = "year",
      xlab = "GDP per capita (US$, inflation-adjusted)",
      test.value = list(2500, 9000, 9500, 10000),
      type = list("p", "np", "r", "bf"),
      title = list(
        "Continent: Africa",
        "Continent: Americas",
        "Continent: Asia",
        "Continent: Europe"
      ),
      effsize.type = list("d", "d", "g", "g"),
      centrality.line.args = list(
        list(color = "red"),
        list(color = "#0072B2"),
        list(color = "#D55E00"),
        list(color = "#CC79A7")
      ),
      ggtheme = list(
        ggplot2::theme_minimal(base_family = "serif"),
        ggthemes::theme_tufte(),
        hrbrthemes::theme_ipsum_rc(axis_title_size = 10),
        ggthemes::theme_hc(bgcolor = "darkunica")
      )
    ),
    .f = ggstatsplot::ggdotplotstats
  )

# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  annotation.args = list(title = "Improvement in GDP per capita from 1952-2007"),
  plotgrid.args = list(nrow = 4),
  guides = "keep"
)
```  

# `ggpiestats`

```{r purrr_ggpiestats, fig.height = 22, fig.width = 9}
# for reproducibility
set.seed(123)

# let's split the dataframe and create a list by passenger class
class_list <- ggstatsplot::Titanic_full %>% split(f = .$Class, drop = TRUE)

# checking the length and names of each element
length(class_list)
names(class_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = class_list,
      x = "Survived",
      y = "Sex",
      label = list("both", "count", "percentage", "both"),
      title = list(
        "Passenger class: 1st",
        "Passenger class: 2nd",
        "Passenger class: 3rd",
        "Passenger class: Crew"
      ),
      caption = list(
        "Total: 319, Died: 120, Survived: 199, % Survived: 62%",
        "Total: 272, Died: 155, Survived: 117, % Survived: 43%",
        "Total: 709, Died: 537, Survived: 172, % Survived: 25%",
        "Data not available for crew passengers"
      ),
      package = list("RColorBrewer", "ghibli", "palettetown", "yarrr"),
      palette = list("Accent", "MarnieMedium1", "pikachu", "nemo"),
      ggtheme = list(
        ggplot2::theme_grey(),
        ggplot2::theme_bw(),
        ggthemes::theme_tufte(),
        ggthemes::theme_economist()
      ),
      proportion.test = list(TRUE, FALSE, TRUE, FALSE),
      type = list("p", "p", "bf", "p")
    ),
    .f = ggstatsplot::ggpiestats
  )

# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  annotation.args = list(title = "Survival in Titanic disaster by gender for all passenger classes"),
  plotgrid.args = list(ncol = 1),
  guides = "keep"
)
``` 

# `ggbarstats`

```{r purrr_ggbarstats, fig.height = 24, fig.width = 6}
# for reproducibility
set.seed(123)

# let's split the dataframe and create a list by passenger class
class_list <- ggstatsplot::Titanic_full %>% split(f = .$Class, drop = TRUE)

# checking the length and names of each element
length(class_list)
names(class_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <-
  purrr::pmap(
    .l = list(
      data = class_list,
      x = "Survived",
      y = "Sex",
      type = "bayes",
      label = list("both", "count", "percentage", "both"),
      title = list(
        "Passenger class: 1st",
        "Passenger class: 2nd",
        "Passenger class: 3rd",
        "Passenger class: Crew"
      ),
      caption = list(
        "Total: 319, Died: 120, Survived: 199, % Survived: 62%",
        "Total: 272, Died: 155, Survived: 117, % Survived: 43%",
        "Total: 709, Died: 537, Survived: 172, % Survived: 25%",
        "Data not available for crew passengers"
      ),
      package = list("RColorBrewer", "ghibli", "palettetown", "yarrr"),
      palette = list("Accent", "MarnieMedium1", "pikachu", "nemo"),
      ggtheme = list(
        ggplot2::theme_grey(),
        ggplot2::theme_bw(),
        ggthemes::theme_tufte(),
        ggthemes::theme_economist()
      )
    ),
    .f = ggstatsplot::ggbarstats
  )

# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  annotation.args = list(
    title = "Survival in Titanic disaster by gender for all passenger classes",
    caption = "Asterisks denote results from proportion tests: \n***: p < 0.001, ns: non-significant"
  ),
  plotgrid.args = list(ncol = 1),
  guides = "keep"
)
``` 

# `grouped_` variants

Note that although all the above examples were written with the non-grouped
variants of functions, the same rule holds true for the `grouped_` variants of
all the above functions.

For example, if we want to use the `grouped_gghistostats` across three different
datasets, you can use `purrr::pmap()` function. For the sake of brevity, the
plots are not displayed here, but you can run the following code and check the
individual `grouped_` plots (e.g., `plotlist[[1]]`).

```{r purrr_grouped}
# create a list of plots
plotlist <-
  purrr::pmap(
    .l = list(
      data = list(mtcars, iris, ToothGrowth),
      x = alist(wt, Sepal.Length, len),
      results.subtitle = list(FALSE),
      grouping.var = alist(am, Species, supp)
    ),
    .f = ggstatsplot::grouped_gghistostats
  )

# given that we had three different datasets, we expect a list of length 3
# (each of which contains a `grouped_` plot)
length(plotlist)
```

# Repeating function execution across multiple columns in a dataframe

```{r purrr_columns, fig.width=12}
# setup
set.seed(123)
library(ggstatsplot)
library(patchwork)

# running the same analysis on two different columns (creates a list of plots)
plotlist <-
  purrr::pmap(
    .l = list(
      data = list(movies_long),
      x = "mpaa",
      y = list("rating", "length"),
      title = list("IMDB score by MPAA rating", "Movie length by MPAA rating")
    ),
    .f = ggstatsplot::ggbetweenstats
  )

# combine plots using `patchwork`
plotlist[[1]] + plotlist[[2]]
```

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
