---
title: "session information"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{session information}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Session information

This vignette provides exhaustive details about the session (attached packages,
their versions, date, source, etc.) in which the vignettes were created and the
website was generated. This is helpful information for reproducibility. If you
see any divergences between function behavior as described on the website and
what you see on your system, this information can come in handy for diagnosing
the source of those divergences.

This session information was generated on `r Sys.Date()`:

```{r include = FALSE}
library(ggstatsplot)
```

```{r session_info}
options(width = 200)
sessioninfo::session_info(include_base = TRUE)
```

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`:
<https://github.com/IndrajeetPatil/ggstatsplot/issues>
