---
title: "ggstatsplot theme"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggstatsplot theme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
# show me all columns
options(tibble.width = Inf)

knitr::opts_chunk$set(
  dpi = 300,
  out.width = "100%",
  collapse = TRUE,
  comment = "#>"
)
```

## Default theme for the package: `theme_ggstatsplot`

`ggstatsplot` uses a default theme `theme_ggstatsplot()`, which is a selected
`ggplot2` theme with few aesthetic modifications overlaid on top, that can be
used with any `ggplot2` object.

Here is a simple example:

```{r theme_ggstatsplot, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 8}
library(ggplot2)

ggstatsplot::combine_plots(
  # basic scatter plot with `theme_ggstatsplot()` added
  ggplot(mtcars, aes(x = wt, y = mpg)) +
    geom_point() +
    ggstatsplot::theme_ggstatsplot(),
  # basic scatter plot without the default theme
  ggplot(mtcars, aes(x = wt, y = mpg)) +
    geom_point(),
  nrow = 1,
  title.text = "Plot with and without the default `theme_ggstatsplot` overlaid"
)
```

All plots in this package have `theme_bw()` by default as the base on which
`theme_ggstatsplot()` is built, but this can be modified using the `ggtheme`
argument. Let's see an example with `ggcorrmat` function.

```{r theme1, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 6}
ggstatsplot::ggcorrmat(
  data = datasets::iris,
  cor.vars = c(Sepal.Length:Petal.Width),
  matrix.type = "upper",
  ggtheme = ggthemes::theme_fivethirtyeight(), # selected ggplot2 theme
  ggstatsplot.layer = FALSE # turn of default theme layer
)
```

Try modifying the theme for other functions (use themes from `ggplot2`,
`ggthemes`, `hrbrthemes`, etc.).

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

For details, see-
<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>
