---
title: "additional vignettes"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 100
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{additional vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r library, include = FALSE}
library(rlang)
library(ggstatsplot)
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Additional vignettes

Due to constraints on the size of the `R` package, all available vignettes are
not included in the package and thus can't be accessed on `CRAN`. There are few
additional vignettes that are only available on the website for this package:

## Vignettes for individual functions

  - `ggbetweenstats`:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggbetweenstats.html>)
    
  - `ggwithinstats`:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggwithinstats.html>)
    
  - `ggcorrmat`:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggcorrmat.html>)
    
  - `gghistostats`:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/gghistostats.html>)    

  - `ggpiestats`:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggpiestats.html>)
    
  - `ggscatterstats`:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggscatterstats.html>) 
    
  - `ggcoefstats`:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggcoefstats.html>) 
    
  - How to arrange multiple plots in a single plot along with annotations using
    the `combine_plots` helper function:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/combine_plots.html>)
    
  - Default theme (`theme_ggstatsplot`) used for the package and how it can be
    modified:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/theme_ggstatsplot.html>)
    
## General vignettes

  - Introduction to `ggstatsplot` (publication describing philosophy and
    principles behind this package):
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/ggstatsplot_paper.html>)
    
  - Interpreting effect sizes for different tests:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/effsize_interpretation.html>)
    
  - Gallery of `ggstatsplot` examples (shows how `ggstatsplot` can be further
    modified using `ggplot2` functions):
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/gallery.html>)

  - Examples illustrating how to use functional programming package like `purrr`
    to extend `ggstatsplot` functionality-
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/purrr_examples.html>)
    
  - Frequently Asked Questions (FAQ)-
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/faq.html>)

  - Session information:
    (<https://indrajeetpatil.github.io/ggstatsplot/articles/web_only/session_info.html>)

    
# Presentation

In addition to these vignettes, another quick way to get an overview of this
package is to go through the following slides:
<https://indrajeetpatil.github.io/ggstatsplot_slides/slides/ggstatsplot_presentation.html#1>

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on
`GitHub`:
<https://github.com/IndrajeetPatil/ggstatsplot/issues>
