---
title: "combine_plots"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{combine_plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Combining plots with `combine_plots`

`ggstatsplot` also contains a helper function `combine_plots` to combine
multiple plots. This is a wrapper around \code{\link[cowplot]{plot_grid}} 
and lets you combine multiple plots and add combination of title, caption, and
annotation texts with suitable default parameters.

## Examples with `purrr`

The full power of `ggstatsplot` can be leveraged with a functional programming
package like [`purrr`](http://purrr.tidyverse.org/) that replaces many for loops
with code that is both more succinct and easier to read and, therefore, `purrr`
should be preferrred.

An example is provided below. 

```{r ggscatterstats_purrr, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 8}
library(glue)
library(dplyr)
library(ggplot2)

### creating a list column with `ggstatsplot` plots
plots <- datasets::iris %>%
  dplyr::mutate(.data = ., Species2 = Species) %>% # just creates a copy of this variable
  dplyr::group_by(.data = ., Species) %>%                
  tidyr::nest(data = .) %>%                        # creates a nested dataframe with list column called `data`
  dplyr::mutate(                                   # creating a new list column of ggstatsplot outputs
    .data = .,
    plot = data %>%
      purrr::map(
        .x = .,
        .f = ~ ggstatsplot::ggscatterstats(
          data = .,
          x = Sepal.Length,
          y = Sepal.Width,
          messages = FALSE,                        # turns off all the warnings, notes, and reference messages   
          marginal.type = "boxplot",
          title =
            glue::glue("Species: {.$Species2} (n = {length(.$Sepal.Length)})")
        )
      )
  )

### display the new object (notice that the class of the `plot` list column is S3: gg)
plots

### creating a grid with cowplot
ggstatsplot::combine_plots(
  plotlist = plots$plot,                           # list column containing all ggstatsplot objects
  labels = c("(a)", "(b)", "(c)"),
  nrow = 3,
  ncol = 1,
  title.text = "Relationship between sepal length and width for all Iris species",
  title.size = 14,
  title.color = "black",
  caption.text = expression(
    paste(
      italic("Note"),
      ": Iris flower dataset was collected by Edgar Anderson."
    ),
    caption.size = 10
  )
)
```

Here is another example with `ggbetweenstats`-

```{r ggbetweenstats_purrr, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 8}
library(dplyr)
library(glue)

### creating a list column with `ggstatsplot` plots
plots <- datasets::mtcars %>%
  dplyr::mutate(.data = ., cyl2 = cyl) %>%        # just creates a copy of this variable
  dplyr::group_by(.data = ., cyl) %>%             # 
  tidyr::nest(data = .) %>%                       # creates a nested dataframe with list column called `data`
  dplyr::mutate(                                  # creating a new list column of ggstatsplot outputs
    .data = .,
    plot = data %>%
      purrr::map(
        .x = .,
        .f = ~ ggstatsplot::ggbetweenstats(
          data = .,
          x = am,
          y = mpg,
          plot.type = "box",                      # type of plot needed
          messages = FALSE,                       # turns off all the warnings, notes, and reference messages
          xlab = "Transmission",
          ylab = "Miles/(US) gallon",
          title = glue::glue(
            "Number of cylinders: {.$cyl2}"       # this is where the duplicated cyl2 column is useful
            ) 
        )
      )
  )

### display the new object (notice that the class of the `plot` list column is S3: gg)
plots

### creating a grid with cowplot
ggstatsplot::combine_plots(
  plotlist = plots$plot,       # list column containing all ggstatsplot objects
  nrow = 3,
  ncol = 1,
  labels = c("(a)","(b)","(c)"),
  title.text = "MPG and car transmission relationship (for each cylinder count)",
  title.size = 13,
  title.color = "black",
  caption.text = expression(
    paste(
      italic("Transmission"),
      ": 0 = automatic, 1 = manual"
    ),
    caption.size = 10
  )
)
```

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
