---
title: "combine_plots"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{combine_plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Combining plots with `combine_plots`

`ggstatsplot` also contains a helper function `combine_plots` to combine
multiple plots. This is a wrapper around `cowplot::plot_grid()` and it helps you
combine multiple plots and add combination of title, caption, and annotation
texts with suitable default parameters. Let's see some examples below.

**Note before**: The codes below illustrates the utility of `combine_plots` for
combining multiple plots created with `ggstatsplot` functions. But, if you have
just one grouping variable, it's not even necessary to use `purrr` or `plyr`
since the `grouped_` variants
(<https://indrajeetpatil.github.io/ggstatsplot/reference/index.html>) of all
functions will take care of this for you and rely on the `combine_plots`
function behind the curtains.

## Combining plots: Examples with `purrr`

The full power of `ggstatsplot` can be leveraged with a functional programming
package like [`purrr`](http://purrr.tidyverse.org/) that replaces many `for` loops
with code that is both more succinct and easier to read and, therefore, `purrr`
should be preferrred.

An example is provided below. 

```{r ggscatterstats_purrr, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 8}
library(glue)
library(dplyr)
library(ggplot2)

### creating a list column with `ggstatsplot` plots
plots <- datasets::iris %>%
  dplyr::mutate(.data = ., Species2 = Species) %>% # just creates a copy of this variable
  dplyr::group_by(.data = ., Species) %>%                
  tidyr::nest(data = .) %>%                        # creates a nested dataframe with list column called `data`
  dplyr::mutate(                                   # creating a new list column of ggstatsplot outputs
    .data = .,
    plot = data %>%
      purrr::map(
        .x = .,
        .f = ~ ggstatsplot::ggscatterstats(
          data = .,
          x = Sepal.Length,
          y = Sepal.Width,
          label.var = Species2,
          label.expression = Sepal.Length > 7,
          xfill = "#0072B2",
          yfill = "#009E73",
          ggtheme = ggthemes::theme_fivethirtyeight(),
          ggstatsplot.layer = FALSE,
          messages = FALSE,                        # turns off all the warnings, notes, and reference messages   
          marginal.type = "boxplot",
          title =
            glue::glue("Species: {.$Species2} (n = {length(.$Sepal.Length)})")
        )
      )
  )

### display the new object (notice that the class of the `plot` list column is S3: gg)
plots

### creating a grid with cowplot
ggstatsplot::combine_plots(
  plotlist = plots$plot,                           # list column containing all ggstatsplot objects
  nrow = 3,
  ncol = 1,
  title.text = "Relationship between sepal length and width for all Iris species",
  title.size = 14,
  caption.text = expression(
    paste(
      italic("Note"),
      ": Iris flower dataset was collected by Edgar Anderson.",
      sep = ""
    ),
    caption.size = 12
  )
)
```

## Combining plots: Example with `plyr`

Another popular package for handling big datasets is `plyr`, where we can
repeatedly apply a common function on smaller pieces and then combine the
results.

Let's see another example on how to use `plyr` to conveniently to repeat the
same operation and then use `combine_plots`. Here we will investigate how Gross
Domestic Product (per capita) of a country is related to the life expectancy of
her citizens in 2007. We will also see which countries still have very low life
expectancy across different continents.

```{r ggscatterstats_plyr, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}
library(plyr)
library(gapminder)

# for reproducibility
set.seed(123)

# let's have a look at the structure of the data
dplyr::glimpse(x = gapminder::gapminder)

# creating a list of plots
plots <- plyr::dlply(
  .data = dplyr::filter(gapminder::gapminder, year == 2007, continent != "Oceania"),
  .variables = .(continent),
  .fun = function(data)
    ggstatsplot::ggscatterstats(
      data = data,
      x = gdpPercap,
      y = lifeExp,
      xfill = "#0072B2",
      yfill = "#009E73",
      label.var = country,
      label.expression = lifeExp < 45,
      title = glue::glue("Continent: {data$continent}"),
      marginal = FALSE
    ) +
    ggplot2::scale_x_continuous(labels = scales::comma)
)

# combining individual plots
ggstatsplot::combine_plots(plotlist = plots, 
                           title.text = "Relationship between GDP (per capita) and life expectancy",
                           nrow = 2,
                           ncol = 2)
```

## Combining plot with additional text 

This function can also be useful adding some additional text information that
can't be contained in either title, subtitle, or caption. Here is an example:
We want to run a polynomial regression and want to annotate the formula.

```{r ggbetweenstats_subtext, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 8}
library(ggstatsplot)

ggstatsplot::combine_plots(
  # preparing the plot with ggstatsplot function
  # let's use only 20% of data to speed up the process
  ggstatsplot::ggcoefstats(
    x = stats::lm(
      formula = rating ~ stats::poly(budget, degree = 3),
      data = dplyr::sample_frac(tbl = ggstatsplot::movies_long, size = 0.2),
      na.action = na.omit
    ),
    exclude.intercept = FALSE,
    title = "Relationship between movie budget and IMDB rating",
    subtitle = "Source: Internet Movie Database",
    ggtheme = ggplot2::theme_gray(),
    stats.label.color = c("#CC79A7", "darkgreen", "#0072B2", "red")
  ) +
    # modifying the plot outside of ggstatsplot using ggplot2 functions
    ggplot2::scale_y_discrete(
      labels = c(
        "Intercept (c)",
        "1st degree (b1)",
        "2nd degree (b2)",
        "3rd degree (b3)"
      )
    ) + 
    ggplot2::labs(y = "term (polynomial regression)"),
  # adding additional text element to the plot since title, subtitle, caption are all already occupied
  sub.text = expression(
    paste(
      "linear model: ", bolditalic(y),
      " ~ ",
      italic(c) + italic(b)[1] * bolditalic(x) + italic(b)[2] * bolditalic(x) ^
        2 + italic(b)[3] * bolditalic(x) ^ 3,
      sep = ""
    )
  ),
  sub.size = 12
)
```

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>
