---
title: "ggbetweenstats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggbetweenstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::ggbetweenstats` is designed not just to facilitate
**data exploration**, but also for making **publication-ready box-violin plot**,
with all statistical details included in the plot itself. We will see examples
of how to use this function in this vignette.

To begin with, here are some instances where you would want to use
`ggbetweenstats`-

  - to check if a continuous variable differs between two groups or conditions
  - to check for outliers

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Between-subjects comparisons with `ggbetweenstats`

To illustrate how this function can be used, we will use the `gapminder`
dataset. This dataset provides values for life expectancy, GDP per capita, and
population, every five years, from 1952 to 2007, for each of 142 countries and
was collected by the Gapminder Foundation. Let's have a look at the data-

```{r gapminder, warning = FALSE, message = FALSE}
library(gapminder)
library(dplyr)

dplyr::glimpse(x = gapminder::gapminder)
```

Suppose the first thing we want to check is the distribution of life expectancy
worldwide (across continents, i.e.) in 2007. That is, we want to see if the
average (across countries in a given continent) life expectancy differs
significantly across five continents.

The simplest form of the function call is-
```{r ggbetweenstats1, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 8}
# loading the necessary libraries
library(ggstatsplot)
library(gapminder)

# since the confidence intervals for the effect sizes are computed using
# bootstrapping, important to set a seed for reproducibility
set.seed(123)

# function call
ggstatsplot::ggbetweenstats(
  data = dplyr::filter(.data = gapminder, year == 2007),
  x = continent,
  y = lifeExp,
  messages = FALSE
)
```

Note that the test automatically figures out whether independent t-test is to be
run or an ANOVA based on the number of levels in the grouping variable.
Additionally, the function output a `ggplot` object which means that it can be
further modified.

We will see how this basic call can be further modified with additional
arguments-

```{r ggbetweenstats2, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 8}
library(ggstatsplot)
library(gapminder)

# for reproducibility
set.seed(123)

ggstatsplot::ggbetweenstats(
  data = dplyr::filter(.data = gapminder, year == 2007),      # dataframe
  x = continent,                                              # grouping/independent variable
  y = lifeExp,                                                # dependent variables
  xlab = "Continent",                                         # label for the x-axis
  ylab = "Life expectancy",                                   # label for the y-axis
  plot.type = "boxviolin",                                    # type of plot
  type = "parametric",                                        # type of statistical test  
  effsize.type = "biased",                                    # type of effect size
  outlier.tagging = TRUE,                                     # whether outliers should be flagged
  outlier.coef = 1.5,                                         # coefficient for Tukey's rule
  outlier.label = country,                                    # label to attacht to outlier values
  outlier.label.color = "red",                                # outlier point label color
  mean.plotting = TRUE,                                       # whether the mean is to be displayed
  mean.color = "darkblue",                                    # color for mean
  messages = FALSE,                                           # turn off messages
  ggtheme = ggthemes::theme_economist(),                      # a different theme
  package = "yarrr",                                          # package from which color palette is to be taken
  palette = "info2",                                          # choosing a different color palette
  title = "Comparison of life expectancy across continents (Year: 2007)",
  caption = "Source: Gapminder Foundation"
) +                                                           # modifying the plot further
  ggplot2::scale_y_continuous(limits = c(35,85), breaks = seq(from = 35, to = 85, by = 5))
```

As can be appreciated from the effect size of 0.635, there are big differences
in the observed life expectancy across continents. Importantly, this plot also
helps us appreciate the differences within any given continent. For example,
although Asian countries are doing much better than African countries, on
average, Afghanistan has a particularly grim average for the Asian continent,
possibly reflecting the war and the political turmoil.

Out of curiosity, we can repeat the same analysis with other available feature of
`ggstatsplot`:
  - The `type` (of test) argument also accepts the following
abbreviations: `"p"` (for *parametric*), `"np"` (for *nonparametric*), `"r"`
(for *robust*). 
  - The type of plot to be displayed can also be
modified (`"box"`, `"violin"`, or `"boxviolin"`). Let's produce all of these
variations in the plot below.
  - The color palettes can be modified.

Let's try out both of these features by plotting continent-level differences for
three different years, separated by a decade. Also, since there are just two
data points for the continent of Oceania, let's leave out this continent from
our analysis.

For example,
```{r ggbetweenstats3, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 12}
library(ggstatsplot)
library(gapminder)

# selecting subset of the data
df_year <- dplyr::filter(.data = gapminder::gapminder, year == 2007 | year == 1957)

# for reproducibility
set.seed(123)

# parametric ANOVA and box plot
p1 <- ggstatsplot::ggbetweenstats(
  data = df_year,
  x = year,
  y = lifeExp,
  plot.type = "box",
  type = "p",
  effsize.type = "d",
  title = "parametric test",
  package = "ggsci",
  palette = "nrc_npg",
  messages = FALSE
)

# Kruskal-Wallis test (nonparametric ANOVA) and violin plot
p2 <- ggstatsplot::ggbetweenstats(
  data = df_year,
  x = year,
  y = lifeExp,
  plot.type = "violin",
  type = "np",
  title = "non-parametric test",
  package = "ggsci",
  palette = "uniform_startrek",
  messages = FALSE
)

# robust ANOVA and boxviolin plot
p3 <- ggstatsplot::ggbetweenstats(
  data = df_year,
  x = year,
  y = lifeExp,
  plot.type = "boxviolin",
  type = "r",
  title = "robust test",
  tr = 0.005,
  package = "wesanderson",
  palette = "Royal2",
  messages = FALSE
)

# robust ANOVA and boxviolin plot
p4 <- ggstatsplot::ggbetweenstats(
  data = df_year,
  x = year,
  y = lifeExp,
  type = "bf",
  title = "bayesian test",
  package = "palettetown",
  palette = "natu",
  messages = FALSE
)

# combining the individual plots into a single plot
ggstatsplot::combine_plots(
  p1, p2, p3, p4, 
  nrow = 2, 
  ncol = 2, 
  labels = c("(a)", "(b)", "(c)"),
  title.text = "Comparison of life expectancy between 1957 and 2007",
  caption.text = "Note: Comparing results from parametric, non-parametric, robust, and bayesian tests",
  title.size = 14,
  caption.size = 12
)
```

## Grouped analysis with `grouped_ggbetweenstats`

What if we want to do the same analysis separately for each year for which the
data is available, i.e. checking how the differences in life expectancy have
changed since this data collection started in 1952 until 2007? In that case, we
will have to either write a `for` loop or use `purrr`, both of which are time
consuming and can be a bit of a struggle.

`ggstatsplot` provides a special helper function for such instances:
`grouped_ggbetweenstats`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `ggbetweenstats` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

Let's focus on the following years to see these changes for every 10
years: 1957, 1967, 1977, 1987, 1997, 2007. 

```{r grouped1, warning = FALSE, message = FALSE, fig.height = 22, fig.width = 7}
# for reproducibility
set.seed(123)

ggstatsplot::grouped_ggbetweenstats(
  # arguments relevant for ggstatsplot::ggbetweenstats
  data = dplyr::filter(
    .data = gapminder::gapminder,
    year == 1957 |
    year == 1967 |
    year == 1977 |
    year == 1987 |
    year == 1997 |
    year == 2007, continent != "Oceania"
  ),
  x = continent,
  y = lifeExp,
  # number of decimal places in results
  k = 2,
  ggtheme = ggthemes::theme_tufte(),
  package = "ggsci",
  palette = "default_jco",
  outlier.tagging = TRUE,
  ggstatsplot.layer = FALSE,
  outlier.label = country,
  grouping.var = year,
  title.prefix = "Year",
  messages = FALSE,
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Changes in life expectancy across continents (1957-2007)",
  nrow = 6,
  ncol = 1,
  labels = c("(a)","(b)","(c)", "(d)", "(e)", "(f)")
)
```

As seen from the plot, although the life expectancy has been improving steadily
across all continents as we go from 1957 to 2007, this improvement has not been
happening at the same rate for all continents. Additionally, irrespective of
which year we look at, we still find significant differences in life expectancy
across continents which have been surprisingly consistent across five decades
(based on the observed effect sizes).

## Grouped analysis with `ggbetweenstats` + `purrr` 

Although this grouping function provides a quick way to explore the data, it
leaves much to be desired. For example, the same type of plot and test is
applied for all years, but maybe we want to change this for different years, or
maybe we want to gave different effect sizes for different years. This type of
customization for different levels of a grouping variable is not possible with
`grouped_ggbetweenstats`, but we will see how this can be easily achieved using
the `purrr` package.

**Note before**:
  * Unlike the function call so far, while using `purrr::pmap`, we will need to *quote* the arguments.
  * You can use `ggplot2` themes from extension packages (like `ggthemes`).


```{r grouped2, warning = FALSE, message = FALSE, fig.height = 24, fig.width = 8}
# for reproducibility
set.seed(123)

# let's split the dataframe and create a list by years of interest
year_list <- gapminder::gapminder %>%
  dplyr::filter(
    .data = .,
    year == 1957 |
    year == 1967 |
    year == 1977 |
    year == 1987 |
    year == 1997 |
    year == 2007, continent != "Oceania"
  ) %>%
  base::split(x = ., f = .$year, drop = TRUE)

# this created a list with 4 elements, one for each mpaa rating
# you can check the structure of the file for yourself
# str(year_list)

# checking the length and names of each element
length(year_list)
names(year_list)

# running function on every element of this list; note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = year_list,
    x = "continent",
    y = "lifeExp",
    outlier.label = "country",
    outlier.label.color = list(
      "#56B4E9",
      "#009E73",
      "#F0E442",
      "#0072B2",
      "#D55E00",
      "#CC79A7"
    ),
    xlab = "Continent",
    ylab = "Life expectancy",
    title = list(
      "Year: 1957",
      "Year: 1967",
      "Year: 1977",
      "Year: 1987",
      "Year: 1997",
      "Year: 2007"
    ),
    type = list("r", "p", "np", "p", "p", "r"),
    k = list(1, 2, 3, 3, 2, 1),
    effsize.type = list(
      NULL,
      "partial_omega",
      NULL,
      "partial_omega",
      "partial_eta",
      NULL
    ),
    plot.type = list("box", "boxviolin", "box", "boxviolin", "box", "violin"),
    mean.ci = list(TRUE, FALSE, FALSE, FALSE, TRUE, TRUE),
    package = list("nord", "ochRe", "awtools", "ggsci", "yarrr", "RColorBrewer"),
    palette = list("aurora", "parliament", "ppalette", "default_nejm", "basel", "Set1"),
    ggtheme = list(
      ggthemes::theme_stata(),
      ggplot2::theme_classic(),
      ggthemes::theme_fivethirtyeight(),
      ggplot2::theme_minimal(),
      ggthemes::theme_wsj(),
      ggthemes::theme_calc()
    ),
    ggstatsplot.layer = list(FALSE, FALSE, FALSE, FALSE, TRUE, FALSE),
    sample.size.label = list(TRUE, FALSE, TRUE, FALSE, FALSE, TRUE),
    messages = FALSE
  ),
  .f = ggstatsplot::ggbetweenstats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Changes in life expectancy across continents (1957-2007)",
  title.color = "red",
  nrow = 6,
  ncol = 1,
  labels = c("(a)","(b)","(c)","(d)", "(e)", "(f)")
)
```

## Within-subjects designs

Variant of this function `ggwithinstats` is currently under work. You *can*
still use this function just to prepare the **plot** for exploratory data
analysis, but the statistical details displayed in the subtitle will be
incorrect. You can remove them by adding `+ ggplot2::labs(subtitle = NULL)`.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub:
<https://github.com/IndrajeetPatil/ggstatsplot/issues>
