---
title: "ggbetweenstats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggbetweenstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::ggbetweenstats` is designed with a publication-ready
comparison plot in mind, with all statistical details included in the plot itself. We will see
examples of how to use this function in this vignette.

To begin with, here are some instances where you would want to use
`ggbetweenstats`-

  - to check if a continuous (numeric) variable differs between two groups or conditions
  - to check for outliers

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Group comparison with `ggbetweenstats`

To illustrate how this function can be used, we will use the `gapminder`
dataset. This dataset (available in eponymous
[package](https://CRAN.R-project.org/package=gapminder) on CRAN) provides values
for life expectancy, GDP per capita, and population, every five years, from 1952
to 2007, for each of 142 countries and was collected by the Gapminder
Foundation. Let's have a look at the data-

```{r gapminder, warning = FALSE, message = FALSE}
library(gapminder)
library(dplyr)

dplyr::glimpse(x = gapminder::gapminder)
```

Suppose the first thing we want to check is the distribution of life expectancy
worldwide (across continents, i.e.) in 2007. That is, we want to see if the
average (across countries in a given continent) life expectancy differs
significantly across five continents.

The simplest form of the function call is-
```{r ggbetweenstats1, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 6}
library(ggstatsplot)
library(gapminder)

ggstatsplot::ggbetweenstats(
  data = dplyr::filter(.data = gapminder, year == 2007),
  x = continent,
  y = lifeExp
)
```

Note that the test automatically figures out whether independent t-test is to be
run or an ANOVA based on the number of levels in the grouping variable.
Additionally, the function output a `ggplot` object which means that it can be
further modified.

We will see how this basic call can be further modified with additional arguments-

```{r ggbetweenstats2, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 7}
library(ggstatsplot)
library(gapminder)

ggstatsplot::ggbetweenstats(
  data = dplyr::filter(.data = gapminder, year == 2007),      # dataframe
  x = continent,                                              # grouping/independent variable
  y = lifeExp,                                                # dependent variables
  plot.type = "boxviolin",                                    # type of plot
  type = "parametric",                                        # type of statistical test  
  effsize.type = "biased",                                    # type of effect size
  outlier.tagging = TRUE,                                     # whether outliers should be flagged
  outlier.coef = 1.5,                                         # coefficient for Tukey's rule
  outlier.label = country,                                    # label to attacht to outlier values
  outlier.label.color = "red",                                # outlier point label color
  mean.plotting = TRUE,                                       # whether the mean is to be displayed
  mean.color = "darkblue",                                    # color for mean
  messages = FALSE,                                           # turn off messages
  title = "Comparison of life expectancy across continents (Year: 2007)",
  caption = "Source: Gapminder Foundation"
) +                                                           # modifying the plot further
  ggplot2::scale_y_continuous(limits = c(35,85), breaks = seq(from = 35, to = 85, by = 5))
```


The `type` (of test) argument also accepts the following abbreviations: `"p"`
(for *parametric*), `"np"` (for *nonparametric*), `"r"` (for *robust*).
Additionally, the type of plot to be displayed can also be modified (`"box"`,
`"violin"`, or `"boxviolin"`). Let's produce all of these variations in the plot
below.

For example,
```{r ggbetweenstats3, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 7}
library(ggstatsplot)
library(gapminder)

# parametric ANOVA and box plot
p1 <- ggstatsplot::ggbetweenstats(
  data = dplyr::filter(.data = gapminder, year == 2007),
  x = continent,
  y = lifeExp,
  plot.type = "box",
  type = "p",
  messages = FALSE
)

# Kruskal-Wallis test (nonparametric ANOVA) and violin plot
p2 <- ggstatsplot::ggbetweenstats(
  data = dplyr::filter(.data = gapminder, year == 2007),
  x = continent,
  y = lifeExp,
  plot.type = "violin",
  type = "np",
  messages = FALSE
)

# robust ANOVA and boxviolin plot
p3 <- ggstatsplot::ggbetweenstats(
  data = dplyr::filter(.data = gapminder, year == 2007),
  x = continent,
  y = lifeExp,
  plot.type = "boxviolin",
  type = "r",
  messages = FALSE
)

# combining the individual plots into a single plot
ggstatsplot::combine_plots(
  p1, p2, p3, 
  nrow = 3, 
  ncol = 1, 
  labels = c("(a)", "(b)", "(c)"),
  title.text = "Comparison of life expectancy across continents (Year: 2007)",
  caption.text = "Note: Comparing results from parametric, non-parametric, and robust tests",
  title.size = 14,
  caption.size = 12
)
```

## Within-subjects designs?

Variant of this function `ggwithinstats` is currently under work. You *can*
still use this function just to prepare the **plot** for exploratory data
analysis, but the statistical details displayed in the subtitle will be
incorrect. You can remove them by adding `+ ggplot2::labs(subtitle = NULL)`.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
