---
title: "ggcorrmat"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggcorrmat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::ggcorrmat` provides a quick way to produce
**publication-ready correlation matrix** (aka correlalogram) plot. The function
can also be used for quick **data exploration**. In addition to the plot, it can
also be used to get a correlation coefficient matrix or the associated p-value
matrix. Currently, the plot can display Pearson's *r*, Spearman's *rho*, and
Kendall's *tau*. Robust correlation coefficient option is available only to
output coefficients and p-values. The percentage bend correlation is used as a
robust correlation. Future release will also support robust correlation matrix.
This function is a convenient wrapper around `ggcorrplot` function with some
additional functionality, so its documentation will be helpful
(<http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2>).

We will see examples of how to use this function in this vignette with the
`gapminder` dataset.

To begin with, here are some instances where you would want to use
`ggcorrmat`-

  - to easily visualize a correlation matrix using `ggplot2`
  - to quickly explore correlation between numeric variables in the dataset

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Correlation matrix plot with `ggcorrmat`

For the first example, we will use the `gapminder` dataset (available in
eponymous [package](https://CRAN.R-project.org/package=gapminder) on CRAN)
provides values for life expectancy, Gross Domestic Product (GDP) per capita,
and population, every five years, from 1952 to 2007, for each of 142 countries
and was collected by the Gapminder Foundation. Let's have a look at the data-

```{r gapminder, warning = FALSE, message = FALSE}
library(gapminder)
library(dplyr)

dplyr::glimpse(x = gapminder)
```

Let's say we are interested in studying correlation between population of a
country, average life expectancy, and GDP per capita across countries only for
the year 2007.

The simplest way to get a correlation matrix is to stick to the defaults-
```{r ggcorrmat1, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
library(ggstatsplot)

# select data only from the year 2007
gapminder_2007 <- dplyr::filter(.data = gapminder::gapminder, year == 2007)

# producing the correlation matrix
ggstatsplot::ggcorrmat(
  data = gapminder_2007,             # data from which variable is to be taken
  cor.vars = lifeExp:gdpPercap       # specifying correlation matrix variables
)
```

This plot can be further modified with additional arguments-
```{r ggcorrmat2, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 6}
ggstatsplot::ggcorrmat(
  data = gapminder_2007,                      # data from which variable is to be taken
  cor.vars = lifeExp:gdpPercap,               # specifying correlation matrix variables
  cor.vars.names = c("Life Expectancy", "population", "GDP (per capita)"),
  corr.method = "kendall",                    # which correlation coefficient is to be computed
  lab.col = "red",                            # label color
  ggtheme = ggplot2::theme_light,             # selected ggplot2 theme
  ggstatsplot.theme = FALSE,                  # turn off default ggestatsplot theme overlay
  type = "lower",                             # type of correlation matrix
  colors = c("green", "white", "yellow"),     # selecting color combination
  title = "Gapminder correlation matrix",     # custom title
  subtitle = "Source: Gapminder Foundation"   # custom subtitle
)
```

As seen from this correlation matrix, although there is no relationship between
population and life expectancy worldwide, at least in 2007, there is a strong
positive relationship between GDP, a well-established indicator of a country's
economic performance.

Given that there were only three variables, this doesn't look that impressive.
So let's work with another example from `ggplot2` package: the `diamonds`
[dataset](http://ggplot2.tidyverse.org/reference/diamonds.html). This dataset
contains the prices and other attributes of almost 54,000 diamonds.

Let's have a look at the data-

```{r diamonds, warning = FALSE, message = FALSE}
library(ggplot2)

dplyr::glimpse(x = diamonds)
```

Let's see the correlation matrix between different attributes of the diamond and
the price.

```{r ggcorrmat3, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 7}
ggstatsplot::ggcorrmat(
  data = diamonds,             
  cor.vars = c(carat, depth:z),        # note how the variables are getting selected
  cor.vars.names = c("carat", "total depth", "table", "price", "length (in mm)", "width (in mm)", "depth (in mm)"),
  hc.order = TRUE                      # use hierarchical clustering
)
```

We can make a number of changes to this basic correlation matrix. For example,
since we were interested in relationship between price and other attributes,
let's make the `price` column to the the first column. Additionally, since we are
running 6 correlations that are of *a priori* interest to us, we can adjust our
threshold of significance to (0.05/6 ~ 0.008). Additionally, let's use a
non-parametric correlation coefficient. Please note that it is **important** to
always make sure that the order in which `cor.vars` and `cor.vars.names` are
entered is in sync. Otherwise, wrong column labels will be displayed.

```{r ggcorrmat4, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 7}
ggstatsplot::ggcorrmat(
  data = diamonds,             
  cor.vars = c(price, carat, depth:table, x:z),    # note how the variables are getting selected
  cor.vars.names = c("price", "carat", "total depth", "table",  "length (in mm)", "width (in mm)", "depth (in mm)"),
  corr.method = "spearman",
  sig.level = 0.008,
  type = "lower",
  title = "Relationship between diamond attributes and price",
  subtitle = "Dataset: Diamonds from ggplot2 package",
  colors = c("#0072B2", "#D55E00", "#CC79A7"),
  lab.col = "yellow",
  lab.size = 6,
  pch = 7,
  pch.col = "white",
  pch.cex = 14,
  caption = expression(                            # changing the default caption text for the plot 
    paste(italic("Note"), ": Point shape denotes correlation non-significant at p < 0.008; adjusted for 6 comparisons")
  )
)
```

As seen here, and unsurprisingly, the strongest predictor of the diamond price is its carat value, which a unit of mass equal to 200 mg. In other words, the heavier the diamond, the more expensive it is going to be.

## Correlation statistics matrix with `ggcorrmat`

Another utility of `ggcorrmat` is in obtaining matrix of correlation
coefficients and their p-values for a quick and dirty exploratory data analysis.
For example, for the correlation matrix we just ran, we can get a coefficient
matrix and a p-value matrix. We will use robust correlation for this
illustration as this correlation is supported only to get correlation
coefficients and p-values.

```{r ggcorrmat5, warning = FALSE, message = FALSE}
# to get correlations
ggstatsplot::ggcorrmat(
  data = diamonds,             
  cor.vars = c(price, carat, depth:table, x:z),
  output = "correlations",
  corr.method = "robust",
  digits = 3
)

# to get p-values
ggstatsplot::ggcorrmat(
  data = diamonds,             
  cor.vars = c(price, carat, depth:table, x:z),
  output = "p-values",
  corr.method = "robust",
  digits = 3
)
```

## Grouped analysis with `grouped_ggcorrmat`

What if we want to do the same analysis separately for each type of quality of
the diamond `cut` (Fair, Good, Very Good, Premium, Ideal)? In that case, we will
have to either write a `for` loop or use `purrr`, none of which seem like an
exciting prospect.

`ggstatsplot` provides a special helper function for such instances:
`grouped_ggcorrmat`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `ggcorrmat` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

```{r ggcorrmat6, warning = FALSE, message = FALSE, fig.height = 16, fig.width = 10}
ggstatsplot::grouped_ggcorrmat(
  # arguments relevant for ggstatsplot::ggcorrmat
  data = ggplot2::diamonds,
  grouping.var = cut,
  title.prefix = "Quality of cut",
  cor.vars = c(carat, depth:z),
  cor.vars.names = c(
    "carat",
    "total depth",
    "table",
    "price",
    "length (in mm)",
    "width (in mm)",
    "depth (in mm)"
  ),
  lab.size = 3.5,
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Relationship between diamond attributes and price across cut",
  title.size = 16,
  title.color = "red",
  caption.text = "Dataset: Diamonds from ggplot2 package",
  caption.size = 14,
  caption.color = "blue",
  labels = c("(a)","(b)","(c)","(d)","(e)"),
  nrow = 3,
  ncol = 2
)
```

Note that this function also makes it easy to run the same correlation matrix
across different levels of a factor/grouping variable. For example, if we wanted
to get the same correlation coefficient matrix for `color` of the diamond, we
can do the following-

```{r ggcorrmat7, warning = FALSE, message = FALSE}
ggstatsplot::grouped_ggcorrmat(
  data = ggplot2::diamonds,
  grouping.var = cut,
  cor.vars = c(price, carat, depth:table, x:z),
  output = "correlations",
  corr.method = "robust",
  digits = 3
)
```

As this example illustrates, there is a minimal coding overhead to explore
correlations in your dataset with the `grouped_ggcorrmat` function.

## Grouped analysis with `ggcorrmat` + `purrr`

Although `grouped_` function is good for quickly exploring the data, it reduces
the flexibility with which this function can be used. This is the because the
common parameters used are applied to plots corresponding to all levels of the
grouping variable and there is no way to adapt them based on the level of the
grouping variable. We will see how this can be done using the `purrr` package
from tidyverse. 

**Note before**: Unlike the function call so far, while using `purrr::pmap`, we
will need to *quote* the arguments.

```{r ggcorrmat8, warning = FALSE, message = FALSE, fig.height = 16, fig.width = 10}
# splitting the dataframe by cut and creting a list
cut_list <- ggplot2::diamonds %>%
  base::split(x = ., f = .$cut, drop = TRUE)

# this created a list with 5 elements, one for each quality of cut
str(cut_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = cut_list,
    cor.vars = list(c("carat", "depth", "table",
                 "price", "x", "y", "z")),
    cor.vars.names = list(c(
      "carat",
      "total depth",
      "table",
      "price",
      "length (in mm)",
      "width (in mm)",
      "depth (in mm)"
    )),
    corr.method = list("pearson", "spearman", "spearman", "pearson", "pearson"),
    sig.level = list(0.05, 0.001, 0.01, 0.05, 0.003),
    lab.size = 3.5,
    colors = list(
      c("#56B4E9", "white", "#999999"),
      c("#0072B2", "white", "#D55E00"),
      c("#CC79A7", "white", "#F0E442"),
      c("#56B4E9", "white", "#D55E00"),
      c("#999999", "white", "#0072B2")
    ),
    ggstatsplot.theme = list(FALSE),
    ggtheme = list(
      ggplot2::theme_grey,
      ggplot2::theme_classic,
      ggplot2::theme_minimal,
      ggplot2::theme_bw,
      ggplot2::theme_dark
    )
  ),
  .f = ggstatsplot::ggcorrmat
)

# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Relationship between diamond attributes and price across cut",
  title.size = 16,
  title.color = "red",
  caption.text = "Dataset: Diamonds from ggplot2 package",
  caption.size = 14,
  caption.color = "blue",
  labels = c("(a)", "(b)", "(c)", "(d)", "(e)"),
  nrow = 3,
  ncol = 2
)
```

As can be seen from this example, combination of `purrr` and `ggstatsplot` much
more flexibility in analyzing the data and preparing a combined plot across
studies or conditions.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>
