---
title: "ggcorrmat"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggcorrmat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::ggcorrmat` provides a quick way to produce
**publication-ready correlation matrix** (aka correlalogram) plot. In addition
to the plot, it can also be used to get a correlation coefficient matrix or the
associated p-value matrix. Currently, the plot can display Pearson's *r*,
Spearman's *rho*, and Kendall's *tau*. Robust correlation coefficient option is
available only to output coefficients and p-values. The percentage bend
correlation is used as a robust correlation. Future release will also support
robust correlation matrix. This function is a convenient wrapper around
`ggcorrplot` function with some additional functionality, so its documentation
will be helpful
(<http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2>).

We will see examples of how to use this function in this vignette with the
`gapminder` dataset.

To begin with, here are some instances where you would want to use
`ggcorrmat`-

  - to easily visualize a correlation matrix using `ggplot2`
  - to quickly explore correlation between numeric variables in the dataset

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Correlation matrix plot with `ggcorrmat`

For the first example, we will use the `gapminder` dataset (available in
eponymous [package](https://CRAN.R-project.org/package=gapminder) on CRAN)
provides values for life expectancy, Gross Domestic Product (GDP) per capita,
and population, every five years, from 1952 to 2007, for each of 142 countries
and was collected by the Gapminder Foundation. Let's have a look at the data-

```{r gapminder, warning = FALSE, message = FALSE}
library(gapminder)
library(dplyr)

dplyr::glimpse(x = gapminder)
```

Let's say we are interested in studying correlation between population of a
country, average life expectancy, and GDP per capita across countries only for
the year 2007.

The simplest way to get a correlation matrix is to stick to the defaults-
```{r ggcorrmat1, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 6}
library(ggstatsplot)

# select data only from the year 2007
gapminder_2007 <- dplyr::filter(.data = gapminder::gapminder, year == 2007)

# producing the correlation matrix
ggstatsplot::ggcorrmat(
  data = gapminder_2007,             # data from which variable is to be taken
  cor.vars = lifeExp:gdpPercap       # specifying correlation matrix variables
)
```

This plot can be further modified with additional arguments-
```{r ggcorrmat2, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 6}
ggstatsplot::ggcorrmat(
  data = gapminder_2007,                      # data from which variable is to be taken
  cor.vars = lifeExp:gdpPercap,               # specifying correlation matrix variables
  cor.vars.names = c("Life Expectancy", "population", "GDP (per capita)"),
  corr.method = "kendall",                    # which correlation coefficient is to be computed
  lab.col = "red",                            # label color
  ggtheme = ggplot2::theme_light,             # selected ggplot2 theme
  ggstatsplot.theme = FALSE,                  # turn off default ggestatsplot theme overlay
  type = "lower",                             # type of correlation matrix
  colors = c("green", "white", "yellow"),     # selecting color combination
  title = "Gapminder correlation matrix",     # custom title
  subtitle = "Source: Gapminder Foundation"   # custom subtitle
)
```

As seen from this correlation matrix, although there is no relationship between
population and life expectancy worldwide, at least in 2007, there is a strong
positive relationship between GDP, a well-established indicator of a country's
economic performance.

Given that there were only three variables, this doesn't look that impressive.
So let's work with another example from `ggplot2` package: the `diamonds`
[dataset](http://ggplot2.tidyverse.org/reference/diamonds.html). This dataset
contains the prices and other attributes of almost 54,000 diamonds.

Let's have a look at the data-

```{r diamonds, warning = FALSE, message = FALSE}
library(ggplot2)

dplyr::glimpse(x = diamonds)
```

Let's see the correlation matrix between different attributes of the diamond and
the price.

```{r ggcorrmat3, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 7}
ggstatsplot::ggcorrmat(
  data = diamonds,             
  cor.vars = c(carat, depth:z),        # note how the variables are getting selected
  cor.vars.names = c("carat", "total depth", "table", "price", "length (in mm)", "width (in mm)", "depth (in mm)"),
  hc.order = TRUE                      # use hierarchical clustering
)
```

We can make a number of changes to this basic correlation matrix. For example,
since we were interested in relationship between price and other attributes,
let's make the `price` column to te the first column. Additionally, since we are
running 6 correlations that are of *a priori* interest to us, we can adjust our
threshold of significance to (0.05/6 ~ 0.008). Additionally, let's use a
non-parametric correlation coefficient. Please note that it is **important** to
always make sure that the order in which `cor.vars` and `cor.vars.names` are
entered is in sync. Otherwise, wrong column labels will be displayed.

```{r ggcorrmat4, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 7}
ggstatsplot::ggcorrmat(
  data = diamonds,             
  cor.vars = c(price, carat, depth:table, x:z),    # note how the variables are getting selected
  cor.vars.names = c("price", "carat", "total depth", "table",  "length (in mm)", "width (in mm)", "depth (in mm)"),
  corr.method = "spearman",
  sig.level = 0.008,
  type = "lower",
  title = "Relationship between diamond attributes and price",
  subtitle = "Dataset: Diamonds from ggplot2 package",
  colors = c("#0072B2", "#D55E00", "#CC79A7"),
  lab.col = "yellow",
  lab.size = 6,
  pch = 7,
  pch.col = "white",
  pch.cex = 14,
  caption = expression(                            # changing the default caption text for the plot 
    paste(italic("Note"), ": Point shape denotes correlation non-significant at p < 0.008; adjusted for 6 comparisons")
  )
)
```

As seen here, and unsurprisingly, the strongest predictor of the diamond price is its carat value, which a unit of mass equal to 200 mg. In other words, the heavier the diamond, the more expensive it is going to be.

## Correlation statistics matrix with `ggcorrmat`

Another utility of `ggcorrmat` is in obtaining matrix of correlation
coefficients and their p-values for a quick and dirty exploratory data analysis.
For example, for the correlation matrix we just ran, we can get a coefficient
matrix and a p-value matrix. We will use robust correlation for this
illustration as this correlation is supported only to get correlation
coeffcients and p-values.

```{r ggcorrmat5, warning = FALSE, message = FALSE}
# to get correlations
ggstatsplot::ggcorrmat(
  data = diamonds,             
  cor.vars = c(price, carat, depth:table, x:z),
  output = "correlations",
  corr.method = "robust",
  digits = 3
)

# to get p-values
ggstatsplot::ggcorrmat(
  data = diamonds,             
  cor.vars = c(price, carat, depth:table, x:z),
  output = "p-values",
  corr.method = "robust",
  digits = 3
)
```

Note that this function also makes it easy to run the same correlation matrix
across different levels of a factor/grouping variable. For example, if we wanted
to get the same correlation coefficient matrix for `color` of the diamond, we
can do the following-

```{r ggcorrmat6, warning = FALSE, message = FALSE}
# splitting the dataframe by color and creting a list
color_list <- ggplot2::diamonds %>%
  base::split(x = ., f = .$color, drop = TRUE)

# running the same function for all elements of the list
purrr::map_dfr(
  .x = color_list,                                  # list on which map operation needs to be carried out
  .f = ~ ggstatsplot::ggcorrmat(
    data = .,                                       # `.` is just a placeholder for list element
    cor.vars = c(price, carat, depth:table, x:z),
    output = "correlations",
    corr.method = "robust",
    digits = 3
  ),
  .id = "color"                                      # identity/grouping variable
)
```

As this example illustrates, there is a minimal coding overhead to exlore
correlations in your dataset with the `ggcorrmat` function.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
