---
title: "gghistostats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 100
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::gghistostats` is meant to provide a publication-ready
histogram with all statistical details included in the plot itself. We will see
examples of how to use this function in this vignette with the `gapminder`
dataset.

To begin with, here are some instances where you would want to use
`gghistostats`-

  - to check distribution of a continuous variable
  - to check if the mean of variable is different from a specified value

## gapminder dataset

This dataset (available in eponymous
[package](https://CRAN.R-project.org/package=gapminder) on CRAN)
provides values for life expectancy, GDP per capita, and population, every five
years, from 1952 to 2007, for each of 142 countries and was collected by the
Gapminder Foundation. Let's have a look at the data-

```{r gapminder, warning = FALSE, message = FALSE}
library(gapminder)
library(dplyr)
library(magrittr)

gapminder::gapminder %>%
  dplyr::glimpse(x = .)
```

## Distribution with `gghistostats`

Suppose the first thing we want to check is the distribution of population
worldwide in 2007. In this case, we are not interested in any statistics and,
therefore, can set the `results.subtitle` argument to `FALSE`.

```{r age_distribution1, warning = FALSE, message = FALSE, fig.height = 7}
library(ggstatsplot)

gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = pop,                                            # numeric variable
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "Population",                                # x-axis label
    title = "Distribution of population worldwide",     # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation"  # caption for the plot
  )
```

Although this plot is useful, it is still not satisfactory as most of the mass
seems to be concentrated at 0 due to the large range of numbers. We can remedy
this by converting population to logarithmic scale. We can additionally adjust
binwidth so that we have bins for every increase in order of magnitude.

```{r age_distribution2, warning = FALSE, message = FALSE, fig.height = 7}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  dplyr::mutate(.data = ., pop_log = log10(pop)) %>%    # creating new population variable
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = pop_log,                                        # numeric variable
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "Population (logarithmic)",                  # x-axis label
    title = "Distribution of population worldwide",     # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    binwidth.adjust = TRUE,                             # adjust binwidth
    binwidth = 1                                        # new binwidth
  )
```

## Statistical analysis with `gghistostats`

Let's say we are now interested in investigating whether the mean life
expectancy in 2007 across the world has improved during the 20th-Century.
In 1950, it was [48](https://ourworldindata.org/life-expectancy), so this is the
`test.value` we are going to use.

```{r stats1, warning = FALSE, message = FALSE, fig.height = 7}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = lifeExp,                                        # numeric variable
    messages = FALSE,                                   # turn off messages
    test.value = 48,                                    # test value for one-sample t-test
    xlab = "Life expectancy",                           # x-axis label
    title = "Life expectancy worldwide",                # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    centrality.para = "mean"                            # plotting centrality parameter (mean)
  )
```

Although there are still some countries where the life expectancy is low, on
average, the life expectancy worldwide has improved compared to what it was
in 1950.

## Grouped analysis with `gghistostats`

What if we want to do the same analysis separately for all five continents? In
that case, we will have to either write a `for` loop or use `purrr`. There is
also a helper funtion that does this for you: `grouped_gghistostats`. It applied
`gghistostats` across all specified grouping variables and then combines list of
plots with the help of `ggstatsplot::combine_plots`.  

```{r grouped1, warning = FALSE, message = FALSE, fig.height = 12, fig.width = 10}
ggstatsplot::grouped_gghistostats(
  # arguments relevant for gghistostats
  data = gapminder::gapminder,
  x = lifeExp,
  xlab = "Life expectancy",
  test.value = 48,
  test.value.line = TRUE,
  messages = FALSE,
  centrality.para = "mean",
  grouping.var = continent,
  # arguments for combine_plots
  title.text = "Life expectancy change in different continents since 1950",
  caption.text = "Note: black line - 1950; blue line - 2007",
  nrow = 3,
  ncol = 2,
  labels = c("(a)","(b)","(c)","(d)","(e)")
)
```

As can be seen from these plots, life expectancy has improved in all continents
in 2007 as compared to the global average of 1950.
