---
title: "gghistostats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{gghistostats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::gghistostats` can be used during **data exploration**
phase and is also meant to provide an easy way to make **publication-ready
histogram** with all statistical details included in the plot itself. We will
see examples of how to use this function in this vignette with the `gapminder`
dataset.

To begin with, here are some instances where you would want to use
`gghistostats`-

  - to check distribution of a continuous variable
  - to check if the mean of variable is different from a specified value

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Distribution with `gghistostats`

To illustrate how this function can be used, we will use the `gapminder`
dataset. This dataset (available in eponymous
[package](https://CRAN.R-project.org/package=gapminder) on CRAN) provides values
for life expectancy, GDP per capita, and population, every five years, from 1952
to 2007, for each of 142 countries and was collected by the Gapminder
Foundation. Let's have a look at the data-

```{r gapminder, warning = FALSE, message = FALSE}
library(gapminder)
library(dplyr)

dplyr::glimpse(x = gapminder::gapminder)
```

Suppose the first thing we want to check is the distribution of population
worldwide in 2007. In this case, we are not interested in any statistics and,
therefore, can set the `results.subtitle` argument to `FALSE`.

```{r age_distribution1, warning = FALSE, message = FALSE, fig.height = 6}
library(ggstatsplot)

gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = pop,                                            # numeric variable
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "Population",                                # x-axis label
    title = "Distribution of population worldwide",     # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation"  # caption for the plot
  )
```

Although this plot is useful, it is still not satisfactory as most of the mass
seems to be concentrated at 0 due to the large range of numbers. We can remedy
this by converting population to logarithmic scale. We can additionally adjust
binwidth so that we have bins for every increase in order of magnitude.

```{r age_distribution2, warning = FALSE, message = FALSE, fig.height = 6}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  dplyr::mutate(.data = ., pop_log = log10(pop)) %>%    # creating new population variable
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = pop_log,                                        # numeric variable
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "Population (logarithmic)",                  # x-axis label
    title = "Distribution of population worldwide",     # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    binwidth = 1                                        # new binwidth
  )
```

So far we have been showing the count information with the bar chart. Another
option included is `density`. Showing `count` gives an idea about *raw* counts,
while `density` gives information about *proportional* prevalence of values in a
certain range.

For example,
```{r age_distribution3, warning = FALSE, message = FALSE, fig.height = 6}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  dplyr::mutate(.data = ., pop_log = log10(pop)) %>%    # creating new population variable
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = pop_log,                                        # numeric variable
    bar.measure = "density",                            # bar height measure
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "Population (logarithmic)",                  # x-axis label
    title = "Distribution of population worldwide",     # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    binwidth = 1,                                       # new binwidth
    low.color = "#009E73",                              # color for the lower end of the colorbar
    high.color = "#F0E442"                              # color for the upper end of the colorbar
  )
```

And yet another option is to show relative frequencies that denote percentage
`"proportion"` of the total observations that fall in a given bin.

```{r age_distribution4, warning = FALSE, message = FALSE, fig.height = 6}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = lifeExp,                                        # numeric variable
    bar.measure = "proportion",                         # bar height measure
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "Life expectancy",                           # x-axis label
    title = "Distribution of life expectancy",          # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    binwidth = 5,                                       # new binwidth
    low.color = "#009E73",                              # color for the lower end of the colorbar
    high.color = "#F0E442"                              # color for the upper end of the colorbar
  )
```

This shows the utility of `gghistostats` in case of data exploration.

## Statistical analysis with `gghistostats`

Let's say we are now interested in investigating whether the mean life
expectancy in 2007 across the world has improved during the 20th-Century.
In 1950, it was [48](https://ourworldindata.org/life-expectancy), so this is the
`test.value` we are going to use.

```{r stats1, warning = FALSE, message = FALSE, fig.height = 6}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = lifeExp,                                        # numeric variable
    messages = FALSE,                                   # turn off messages
    test.value = 48,                                    # test value against which sample mean is to be compared
    xlab = "Life expectancy",                           # x-axis label
    title = "Life expectancy worldwide",                # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    centrality.para = "mean"                            # plotting centrality parameter (mean)
  )
```

Although there are still some countries where the life expectancy is low, on
average, the life expectancy worldwide has improved compared to what it was
in 1950.

`gghistostats` also provides the opportunity to compute Bayes Factors to
quantify evidence in favor of the **alternative** (BF10) or the **null**
hypothesis (BF01). In practice, you need to compute only one and the other will
just be the inverse. In the current example, let's say we want to quantify
evidence in favor of the alternative hypothesis (H1) that the life expectancy
in 2007 has improved significantly worldwide since 1957. The
null, in this case, will of course be that there is no improvement. 

```{r stats_bf, warning = FALSE, message = FALSE, fig.height = 6}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%
  ggstatsplot::gghistostats(
    data = .,                                              # data from which variable is to be taken
    x = lifeExp,                                           # numeric variable
    messages = FALSE,                                      # turn off messages
    type = "bf",                                           # bayesian one sample t-test
    test.value = 48,                                       # test value 
    xlab = "Life expectancy",                              # x-axis label
    title = "Life expectancy worldwide",                   # title for the plot
    subtitle = "Year: 2007",                               # subtitle for the plot
    caption = "Note: black line - 1950; blue line - 2007", # caption for the plot
    test.value.line = TRUE,                                # show a vertical line at `test.value`
    centrality.para = "mean"                               # plotting centrality parameter (mean)
  )
```

As this analysis shows, Bayes Factor value provides [**conclusive** evidence](http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0149794) in favor of
the alternative hypothesis: Life expectancy worldwide has improved significantly since 1957.

## Grouped analysis with `grouped_gghistostats`

What if we want to do the same analysis separately for all five continents? In
that case, we will have to either write a `for` loop or use `purrr`, none of
which seem like an exciting prospect.

`ggstatsplot` provides a special helper function for such instances:
`grouped_gghistostats`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `gghistostats` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

Let's see how we can use this function to apply `gghistostats` for all five
continents. We will be running parametric tests (one sample t-test, i.e.). If
you set `type = "np"`, results from non-parametric test will be displayed.

```{r grouped1, warning = FALSE, message = FALSE, fig.height = 12, fig.width = 10}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%
ggstatsplot::grouped_gghistostats(
  # arguments relevant for ggstatsplot::gghistostats
  data = .,                                     # `.` is placeholder for data plugged by %>%
  x = lifeExp,
  xlab = "Life expectancy",
  title.prefix = "Continent",                   # prefix for the fixed title
  type = "robust",                              # robust test: one-sample percentile bootstrap
  robust.estimator = "mom",                     # the modified one-step M-estimator of location
  test.value = 48,                              # test value against which sample mean is to be compared
  test.value.line = TRUE,                       # show a vertical line at `test.value`
  messages = FALSE,                             # turn off messages
  centrality.para = "mean",                     # plotting centrality parameter (mean)
  grouping.var = continent,                     # grouping variable with multiple levels
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Life expectancy change in different continents since 1950",
  caption.text = "Note: black line - 1950; blue line - 2007",
  nrow = 3,
  ncol = 2,
  labels = c("(a)","(b)","(c)","(d)","(e)")
)
```

As can be seen from these plots, life expectancy has improved in all continents
in 2007 as compared to the global average of 1950. Additionally, we see the
benefits of plotting this data separately for each continent. If we look at the
standardized effect sizes (Cohen's *d*), it is apparent that the biggest
improvements in life expectancy outcomes were seen on the continents of Europe,
Americas, and Oceania (just one data point is available here), while Asia and
Africa exhibit the lowest improvements.

Although this is a quick and dirty way to explore large amount of data with
minimal effort, it does come with an important limitation: reduced flexibility.
For example, if we wanted to add, let's say, a separate `test.value` argument
for each continent, this is not possible with `grouped_gghistostats`. For cases
like these, it would be better to use a function like
[`purrr::pmap`](https://purrr.tidyverse.org/reference/map2.html).

## Grouped analysis with `gghistostats` + `purrr`

So far we have been comparing life expectancy in 2007 for a particular continent
to the global average from 1957. But what if we want to compare to
continent-specific life expectancy from 1957
(<https://ourworldindata.org/life-expectancy>), or run separate kinds of tests
(robust for some, parametric for other, while Bayesian for some other levels of
the group). This is not possible `grouped_gghistostats` function, but can be
easily achieved with `purrr` package from tidyverse.

**Note before**: Unlike the function call so far, while using `purrr::pmap`, we
will need to *quote* the arguments.

```{r grouped2, warning = FALSE, message = FALSE, fig.height = 14, fig.width = 10}
# let's split the dataframe and create a list by continent
continent_list <- gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%
  base::split(x = ., f = .$continent, drop = TRUE)

# this created a list with 5 elements, one for each continent
str(continent_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = continent_list,
    x = "lifeExp",
    xlab = "Life expectancy",
    test.value = list(35.6, 58.4, 41.6, 64.7, 63.4),
    type = list("p", "np", "r", "np", "p"),
    title = list(
      "Continent: Africa",
      "Continent: Americas",
      "Continent: Asia",
      "Continent: Europe",
      "Continent: Oceania"
    ),
    messages = FALSE,
    test.value.line = TRUE,
    test.value.color = "black",
    centrality.para = "mean",
    centrality.color = "blue",
    low.color = list("#56B4E9", "#009E73", "#999999", "#0072B2", "#D55E00"),
    high.color = list("#D55E00", "#CC79A7", "#F0E442", "#D55E00", "#56B4E9"),
    ggtheme = list(
      ggplot2::theme_grey(),
      ggplot2::theme_classic(),
      ggplot2::theme_light(),
      ggplot2::theme_minimal(),
      ggplot2::theme_bw()
    )
  ),
  .f = ggstatsplot::gghistostats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Improvement in life expectancy worldwide since 1950",
  caption.text = "Note: black line - 1950; blue line - 2007",
  nrow = 3,
  ncol = 2,
  labels = c("(a)", "(b)", "(c)", "(d)", "(e)")
)
```  

This shows a much more detailed account of changes in life expectancy as
compared to the previous plot. Compared to their respective average life
expectancies in 1950's, the continent that has had the highest improvement is
Oceania (Australia and New Zealand), while the continent with the least
improvement is Africa (as seen by Cohen's *d* values). This again shows the ease
with which publication-ready plots or plots for exploratory data analysis can be
prepared if `ggstatsplot` is coupled with a functional programming package like
`purrr`.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>
