---
title: "gghistostats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{gghistostats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::gghistostats` can be used for **data exploration**
and to provide an easy way to make **publication-ready histograms** with appropriate
and selected statistical details embedded in the plot itself. In this vignette we will explore
several examples of how to use it.

Some instances where you would want to use `gghistostats`-

  - to inspect distribution of a continuous variable
  - to test if the mean of a sample variable is different from a specified value (population parameter)

**Note before**: The examples make extensive use of the pipe operator (`%>%`), if you need a 
review, here is a good explanation: <http://r4ds.had.co.nz/pipes.html>

## Distribution of a sample with `gghistostats`

Let's begin with a very simple example from the `psych` package a sample of 700 self-reported scores on the SAT Verbal, SAT Quantitative and ACT tests ([psych](https://CRAN.R-project.org/package=gapminder) on CRAN). ACT composite scores may range from 1 - 36. National norms have a mean of 20.

```{r psychact, warning = FALSE, message = FALSE}
library(psych)
library(dplyr)
dplyr::glimpse(x = psych::sat.act)
```

To get a simple histogram with no statistics and no special information. `gghistostats` will by default choose a binwidth `max(x) - min(x) / sqrt(N)`. You should always check this value and explore multiple widths to find the best to illustrate the stories in your data since histograms are sensitive to binwidth.

```{r psychact2, warning = FALSE, message = FALSE}
library(ggstatsplot)
ggstatsplot::gghistostats(
    data = psych::sat.act,                              # data from which variable is to be taken
    x = ACT,                                            # numeric variable
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "ACT Score",                                 # x-axis label
    title = "Distribution of ACT Scores",               # title for the plot
    subtitle = "N = 700",                               # subtitle for the plot
    caption = "Data courtesy of: SAPA project (https://sapa-project.org)", # caption for the plot
    centrality.k = 1                                    # show 1 decimal places for centrality label
  )
```

The authors note that "the score means are higher than national norms suggesting both self selection for people taking on line personality and ability tests and a self reporting bias in scores."  Let's display the national norms and test the hypothesis that our sample mean is the same as our national population mean of 20. 

```{r psychact3, warning = FALSE, message = FALSE}
library(ggstatsplot)
ggstatsplot::gghistostats(
    data = psych::sat.act,                              # data from which variable is to be taken
    x = ACT,                                            # numeric variable
    results.subtitle = TRUE,                            # Run statistical tests
    messages = TRUE,                                    # turn on messages
    bar.measure = "mix",                                # counts and proportions
    xlab = "ACT Score",                                 # x-axis label
    title = "Distribution of ACT Scores",               # title for the plot
    subtitle = "N = 700",                               # subtitle for the plot
    type = "p",                                         # one sample t-test
    bf.message = TRUE,
    ggtheme = ggplot2::theme_gray(),                       # changing default theme
    bar.fill = "#D55E00",                                  # uniform fill color
    test.value = 20,                                       # test value 
    test.value.line = TRUE,                                 # show a vertical line at `test.value`
    caption = "Data courtesy of: SAPA project (https://sapa-project.org)", # caption for the plot
    centrality.k = 1                                    # show 1 decimal places for centrality label
  )
```





To illustrate how this function can be used, we will use the `gapminder`
dataset. This dataset (available in eponymous
[package](https://CRAN.R-project.org/package=gapminder) on CRAN) provides values
for life expectancy, GDP per capita, and population, every five years, from 1952
to 2007, for each of 142 countries and was collected by the Gapminder
Foundation. Let's have a look at the data-

```{r gapminder, warning = FALSE, message = FALSE}
library(gapminder)
library(dplyr)

dplyr::glimpse(x = gapminder::gapminder)
```

Suppose the first thing we want to check is the distribution of population
worldwide in 2007. In this case, we are not interested in any statistics and,
therefore, can set the `results.subtitle` argument to `FALSE`.

```{r age_distribution1, warning = FALSE, message = FALSE, fig.height = 6}
library(ggstatsplot)

gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = pop,                                            # numeric variable
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "Population",                                # x-axis label
    title = "Distribution of population worldwide",     # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    centrality.k = 0                                    # show 0 decimal places for centrality label
  )
```

Although this plot is useful, it is still not satisfactory as most of the mass
seems to be concentrated at 0 due to the large range of numbers. We can remedy
this by converting population to logarithmic scale. We can additionally adjust
binwidth so that we have bins for every increase in order of magnitude.

```{r age_distribution2, warning = FALSE, message = FALSE, fig.height = 6}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  dplyr::mutate(.data = ., pop_log = log10(pop)) %>%    # creating new population variable
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = pop_log,                                        # numeric variable
    results.subtitle = FALSE,                           # don't run statistical tests
    messages = FALSE,                                   # turn off messages
    xlab = "Population (logarithmic)",                  # x-axis label
    title = "Distribution of population worldwide",     # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    binwidth = 1                                        # new binwidth
  )
```

So far we have been showing both the count and proportion information with the
bar chart: showing `count` gives an idea about *raw* counts, while `proportion`
gives information about *proportional* prevalence of values in a certain range.

Other possible options are: (only) `"count"`, (only) `"proportion"`, or
`"density"` information.

This shows the utility of `gghistostats` in case of data exploration.

## Statistical analysis with `gghistostats`

Let's say we are now interested in investigating whether the mean life
expectancy in 2007 across the world has improved during the 20th-Century.
In 1950, it was [48](https://ourworldindata.org/life-expectancy), so this is the
`test.value` we are going to use.

```{r stats1, warning = FALSE, message = FALSE, fig.height = 6}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%            # select data only from the year 2007
  ggstatsplot::gghistostats(
    data = .,                                           # data from which variable is to be taken
    x = lifeExp,                                        # numeric variable
    messages = FALSE,                                   # turn off messages
    test.value = 48,                                    # test value against which sample mean is to be compared
    xlab = "Life expectancy",                           # x-axis label
    title = "Life expectancy worldwide",                # title for the plot
    subtitle = "Year: 2007",                            # subtitle for the plot
    caption = "Data courtesy of: Gapminder Foundation", # caption for the plot
    centrality.para = "mean",                           # plotting centrality parameter
    ggtheme = ggthemes::theme_wsj(),                    # change the default theme
    fill.gradient = FALSE                               # turn off color fill gradient
  )
```

Although there are still some countries where the life expectancy is low, on
average, the life expectancy worldwide has improved compared to what it was
in 1950.

`gghistostats` also provides the opportunity to compute Bayes Factors to
quantify evidence in favor of the **alternative** (BF10) or the **null**
hypothesis (BF01). In practice, you need to compute only one and the other will
just be the inverse. In the current example, let's say we want to quantify
evidence in favor of the alternative hypothesis (H1) that the life expectancy
in 2007 has improved significantly worldwide since 1957. The
null, in this case, will of course be that there is no improvement. 

```{r stats_bf, warning = FALSE, message = FALSE, fig.height = 6}
gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007) %>%
  ggstatsplot::gghistostats(
    data = .,                                              # data from which variable is to be taken
    x = lifeExp,                                           # numeric variable
    messages = FALSE,                                      # turn off messages
    type = "bf",                                           # bayesian one sample t-test
    ggtheme = ggplot2::theme_gray(),                       # changing default theme
    fill.gradient = FALSE,                                 # no color gradient (default)
    bar.fill = "#D55E00",                                  # uniform fill color
    test.value = 48,                                       # test value 
    xlab = "Life expectancy",                              # x-axis label
    title = "Life expectancy worldwide",                   # title for the plot
    subtitle = "Year: 2007",                               # subtitle for the plot
    caption = "Note: black line - 1950; blue line - 2007", # caption for the plot
    test.value.line = TRUE                                 # show a vertical line at `test.value`
  )
```

Observed Bayes Factor value provides
[**conclusive**](http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0149794)
evidence in favor of the alternative hypothesis: Life expectancy worldwide has
improved significantly since 1957.

## Grouped analysis with `grouped_gghistostats`

What if we want to do the same analysis separately for all five continents? In
that case, we will have to either write a `for` loop or use `purrr`, none of
which seem like an exciting prospect.

`ggstatsplot` provides a special helper function for such instances:
`grouped_gghistostats`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `gghistostats` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

Let's see how we can use this function to apply `gghistostats` for all five
continents. We will be running parametric tests (one sample t-test, i.e.). If
you set `type = "np"`, results from non-parametric test will be displayed.

```{r grouped1, warning = FALSE, message = FALSE, fig.height = 12, fig.width = 12}
gapminder::gapminder %>%                        # select data only for the year 2007
  dplyr::filter(.data = ., year == 2007) %>%
ggstatsplot::grouped_gghistostats(
  # arguments relevant for ggstatsplot::gghistostats
  data = .,                                     # `.` is placeholder for data plugged by %>%
  x = lifeExp,
  xlab = "Life expectancy",
  grouping.var = continent,                     # grouping variable with multiple levels
  title.prefix = "Continent",                   # prefix for the fixed title
  type = "robust",                              # robust test: one-sample percentile bootstrap
  k = 2,                                        # number of decimal places in results
  robust.estimator = "mom",                     # the modified one-step M-estimator of location
  test.value = 48,                              # test value against which sample mean is to be compared
  test.value.line = TRUE,                       # show a vertical line at `test.value`
  centrality.para = "mean",                     # plotting centrality parameter
  centrality.color = "#D55E00",                 # color for centrality line and label
  test.value.color = "#009E73",                 # color for test line and label
  messages = FALSE,                             # turn off messages
  ggtheme = ggthemes::theme_stata(),            # changing default theme
  ggstatsplot.layer = FALSE,                    # turn off ggstatsplot theme layer
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Life expectancy change in different continents since 1950",
  caption.text = "Note: green line - 1950; orange line - 2007",
  nrow = 3,
  ncol = 2,
  labels = c("(a)","(b)","(c)","(d)","(e)")
)
```

As can be seen from these plots, life expectancy has improved in all continents
in 2007 as compared to the global average of 1950. Additionally, we see the
benefits of plotting this data separately for each continent. If we look at the
standardized effect sizes (Cohen's *d*), it is apparent that the biggest
improvements in life expectancy outcomes were seen on the continents of Europe,
Americas, and Oceania (just one data point is available here), while Asia and
Africa exhibit the lowest improvements.

Although this is a quick and dirty way to explore large amount of data with
minimal effort, it does come with an important limitation: reduced flexibility.
For example, if we wanted to add, let's say, a separate `test.value` argument
for each continent, this is not possible with `grouped_gghistostats`. For cases
like these, it would be better to use \code{\link[purrr]{pmap}} (e.g.).

## Grouped analysis with `gghistostats` + `purrr`

So far we have been comparing life expectancy in 2007 for a particular continent
to the global average from 1957. But what if we want to compare to
continent-specific life expectancy from 1957
(<https://ourworldindata.org/life-expectancy>), or run separate kinds of tests
(robust for some, parametric for other, while Bayesian for some other levels of
the group). This is not possible `grouped_gghistostats` function, but can be
easily achieved with `purrr` package from tidyverse. See the associated vignette here:
<https://indrajeetpatil.github.io/ggstatsplot/articles/purrr_examples.html>

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

Summarizing session information for reproducibility.

```{r session_info, eval = FALSE}
options(width = 200)
devtools::session_info()
```

