---
title: "ggpiestats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggpiestats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The function `ggstatsplot::ggpiestats` can be used for quick **data exploration** 
and/or to prepare **publication-ready pie charts** to summarize the statistical relationship
between two categorical variables. We will see examples of how to use this
function in this vignette.

To begin with, here are some instances where you would want to use `ggpiestats`-

  - to see if the frequency distribution of two categorical variables are
    independent of each other using the contingency table analysis
  - to check if the proportion of observations at each level of a categorical
    variable is equal

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Statistical independence of categorical variables with `ggpiestats`

To demonstrate how `ggpiestats` can be used to we will be using the `Titanic`
dataset that is included in the `datasets` library. Titanic Passenger Survival
Data Set provides information "on the fate of passengers on the fatal maiden
voyage of the ocean liner *Titanic*, summarized according to economic status
(class), sex, age, and survival."

Let's have a look at the structure of this table and also convert it into a
tibble while we are at it.

```{r titanic1, warning = FALSE, message = FALSE}
library(datasets)
library(dplyr)

# looking at the table
dplyr::glimpse(x = Titanic)
```

Note that the last column in this dataframe contains count information, which
means we will have to modify it to reflect this count structure. This has
already been carried out and the final dataset is included in the `ggstatsplot`
package in `Titanic_full`. This is not necessary as `ggpiestats` **can** handle
table structures as well (see examples below).

Let's have a look at this dataset.

```{r titanic2, warning = FALSE, message = FALSE}
library(ggstatsplot)

# looking at the final dataset
dplyr::glimpse(ggstatsplot::Titanic_full)
```

First, let's see if the proportion of people who survived was different between
sexes using `ggpiestats`.

```{r ggpiestats1, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8}
# since effect size confidence intervals are computed using bootstrapping, let's
# set seed for reproducibility
set.seed(123)

ggstatsplot::ggpiestats(data = ggstatsplot::Titanic_full,
                        condition = Sex,
                        main = Survived) 
```

A number of arguments can be modified to change the appearance of this plot:

```{r ggpiestats2, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8}
library(ggplot2)

# for reproducibility
set.seed(123)

ggstatsplot::ggpiestats(
  data = ggstatsplot::Titanic_full,             # dataframe (matrix or table will not be accepted)
  main = Survived,                              # rows in the contingency table
  condition = Sex,                              # columns in the contingecy table
  title = "Passengar survival by gender",       # title for the entire plot
  caption = "Source: Titanic survival dataset", # caption for the entire plot
  legend.title = "Survived?",                   # legend title
  facet.wrap.name = "Gender",                   # changing the facet wrap title
  facet.proptest = TRUE,                        # proportion test for each facet
  stat.title = "survival x gender: ",           # title for statistical test
  palette = "Set1",                             # changing the color palette
  ggtheme = ggplot2::theme_classic()            # changing plot theme 
) +                                             # further modification with ggplot2 commands
  ggplot2::theme(plot.subtitle = ggplot2::element_text(
    color = "black",
    size = 10,
    face = "bold",
    hjust = 0.5
  ))
```

As seen from this plot, the Pearson's chi-square test of independence shows that
the distribution of survival was different across males and females.
Additionally, among both males and females, the proportion of survival was not
equally likely (at 50%, i.e.), as shown by significant results (`***`) from one-sample
proportion tests for each facet.

In case the `condition` argument is not specified, instead of chi-square test of
independence, a proportion test will be carried out. For example, let's see if
there were equal proportions of different age groups.

```{r ggpiestats3, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
ggstatsplot::ggpiestats(
  data = ggstatsplot::Titanic_full,                          
  main = Age
)
```

As this plot shows there were overwhelmingly more number of adults than children
on the boat and the proportion test attests to this.

## Grouped analysis with `grouped_ggpiestats`

What if we want to do the same analysis separately for the four different Class
on the Titanic (1st, 2nd, 3rd, Crew), i.e. checking how the survival-by-gender
interaction changes by the passenger class in which the people were traveling?
In that case, we will have to either write a `for` loop or use `purrr`, both of
which are time consuming and can be a bit of a struggle.

`ggstatsplot` provides a special helper function for such instances:
`grouped_ggpiestats`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `ggpiestats` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

```{r ggpiestats4, warning = FALSE, message = FALSE, fig.height = 20, fig.width = 9}
ggstatsplot::grouped_ggpiestats(
  # arguments relevant for ggstatsplot::gghistostats
  data = ggstatsplot::Titanic_full,
  grouping.var = Class,
  title.prefix = "Passenger class",
  stat.title = "survival x gender: ",
  main = Survived,
  condition = Sex,
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Survival in Titanic disaster by gender for all passenger classes",
  caption.text = "Asterisks denote results from proportion tests; ***: p < 0.001, ns: non-significant",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)", "(d)")
)
```

As seen from this quick exploratory analysis, across all passenger classes, the
proportion of survived to non-survived individuals differed across genders: Men
were more likely to perish than survive, whereas women were more likely to
survive than perish. The only exception was the 3rd Class passengers where women
were as likely to survive as to perish.

This will work even if the condition argument is not specified:

```{r ggpiestats5, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10}
ggstatsplot::grouped_ggpiestats(
  data = ggstatsplot::Titanic_full,
  main = Age,
  grouping.var = Class,
  title.prefix = "Passenger Class"
) 
```

## Grouped analysis with `ggpiestats` + `purrr` 

Although this grouping function provides a quick way to explore the data, it
leaves much to be desired. For example, we may want to add different captions,
titles, themes, or palettes for each level of the grouping variable, etc. For
cases like these, it would be better to use a function like
[`purrr::pmap`](https://purrr.tidyverse.org/reference/map2.html).

**Note before**: Unlike the function call so far, while using `purrr::pmap`, we
will need to *quote* the arguments.

```{r ggpiestats6, warning = FALSE, message = FALSE, fig.height = 20, fig.width = 9}
# let's split the dataframe and create a list by passenger class
class_list <- ggstatsplot::Titanic_full %>%
  base::split(x = ., f = .$Class, drop = TRUE)

# this created a list with 4 elements, one for each class
# you can check the structure of the file for yourself
# str(class_list)

# checking the length and names of each element
length(class_list)
names(class_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = class_list,
    main = "Survived",
    condition = "Sex",
    facet.wrap.name = "Gender",
    title = list(
      "Passenger class: 1st",
      "Passenger class: 2nd",
      "Passenger class: 3rd",
      "Passenger class: Crew"
    ),
    caption = list(
      "Total: 319, Died: 120, Survived: 199, % Survived: 62%",
      "Total: 272, Died: 155, Survived: 117, % Survived: 43%",
      "Total: 709, Died: 537, Survived: 172, % Survived: 25%",
      "Not available"
    ),
    palette = list("Accent", "Paired", "Pastel1", "Set2"),
    ggtheme = list(
      ggplot2::theme_grey(),
      ggplot2::theme_classic(),
      ggplot2::theme_light(),
      ggplot2::theme_minimal()
    ),
    sample.size.label = list(TRUE, FALSE, TRUE, FALSE),
    messages = FALSE
  ),
  .f = ggstatsplot::ggpiestats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Survival in Titanic disaster by gender for all passenger classes",
  caption.text = "Asterisks denote results from proportion tests; ***: p < 0.001, ns: non-significant",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)", "(d)")
)
``` 

As can be appreciated from this example, although `grouped_ggpiestats` provides
a quick way to explore data, `purrr::pmap` lets us utilize the full
functionality of this function and `ggplot2`.

## Working with `counts` data

`ggpiestats` can also work with dataframe containing counts (aka tabled data),
i.e., when each row doesn't correspond to a unique observation. For example,
consider the following `fishing` dataframe containing data from two boats (`A`
and `B`) about the number of different types fish they caught in the months of
`February` and `March`. In this dataframe, each row doesn't equal a unique
observation. In such cases, we can use `counts` argument. Let's say we want to
investigate if the frequency of different types of fish caught differs across
the two months:

```{r ggpiestats7, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 9}
# for reproducibility
set.seed(123)

# creating a dataframe
# (this is completely fictional; I don't know first thing about fishing!)
(
  fishing <- data.frame(
    Boat = c(rep("B", 4), rep("A", 4), rep("A", 4), rep("B", 4)),
    Month = c(rep("February", 2), rep("March", 2), rep("February", 2), rep("March", 2)),
    Fish = c(
      "Bass",
      "Catfish",
      "Cod",
      "Haddock",
      "Cod",
      "Haddock",
      "Bass",
      "Catfish",
      "Bass",
      "Catfish",
      "Cod",
      "Haddock",
      "Cod",
      "Haddock",
      "Bass",
      "Catfish"
    ),
    SumOfCaught = c(25, 20, 35, 40, 40, 25, 30, 42, 40, 30, 33, 26, 100, 30, 20, 20)
  ) %>% # converting to a tibble dataframe
    tibble::as_data_frame(x = .)
)

# running `ggpiestats` with counts information
ggstatsplot::ggpiestats(
  data = fishing,
  main = Fish,
  condition = Month,
  counts = SumOfCaught
)

```

We just verified that the frequency of different types of fish caught differs
across the two months, but what if we further want to know if this difference is
present for both boats (since they are fishing in different parts of the sea)?
For this, we can again utilize `grouped_ggpiestats`:

```{r ggpiestats8, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 8}
# running the grouped variant of the function
ggstatsplot::grouped_ggpiestats(
  data = fishing,
  main = Fish,
  condition = Month,
  counts = SumOfCaught,
  grouping.var = Boat,
  title.prefix = "Boat",
  nrow = 2
)
```

As seen from these charts, this difference is found only for the location in
which the boat `B` has been fishing. Additionally, faceted proportion tests also
reveal that all fish are not equally likely to be caught at this location.

## Within-subjects designs

Variant of this function for within-subjects designs, which will display results
from McNemar test, is currently under work. You *can* still use this function
just to prepare the **plot** for exploratory data analysis, but the statistical
details displayed in the subtitle will be incorrect. You can remove them by
adding `+ ggplot2::labs(subtitle = NULL)`.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub:
<https://github.com/IndrajeetPatil/ggstatsplot/issues>

