---
title: "ggpiestats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggpiestats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The function `ggstatsplot::ggpiestats` can be used to prepare
**publication-ready pie charts** to summarize the statistical relationship
between two categorical variables. We will see examples of how to use this
function in this vignette.

To begin with, here are some instances where you would want to use `ggpiestats`-

  - to see if the frequency distribution of two categorial variables are
    independent of each other using the contingency table analysis
  - to check if the proportion of observations at each level of a categorial
    variable is equal

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Statistical independence of categorical variables with `ggpiestats`

To demonstrate how `ggpiestats` can be used to we will be using the `Titanic`
dataset that is included in the `datasets` library. Titanic Passenger Survival
Data Set provides information "on the fate of passengers on the fatal maiden
voyage of the ocean liner *Titanic*, summarized according to economic status
(class), sex, age, and survival."

Let's have a look at the structure of this table and also convert it into a
tibble while we are at it.

```{r titanic1, warning = FALSE, message = FALSE}
library(datasets)
library(dplyr)

# looking at the table
dplyr::glimpse(x = Titanic)

# converting to tibble
tibble::as_data_frame(x = Titanic)
```

Note that the last column in this dataframe contains count information, which
means we will have to modify it to reflect this count structure.

```{r titanic2, warning = FALSE, message = FALSE}

# a custom function to repeat dataframe `rep` number of times, which is going to
# be count data for us
rep_df <- function(df, rep) {
  df[rep(1:nrow(df), rep), ]
}

# converting dataframe to full length based on count information
Titanic_full <- tibble::as_data_frame(datasets::Titanic) %>%
  tibble::rowid_to_column(df = ., var = "id") %>%
  dplyr::mutate_at(
    .tbl = .,
    .vars = dplyr::vars("id"),
    .funs = ~ as.factor(.)
  ) %>%
  base::split(x = ., f = .$id) %>%
  purrr::map_dfr(.x = ., .f = ~ rep_df(df = ., rep = .$n)) %>%
  dplyr::mutate_at(
    .tbl = .,
    .vars = dplyr::vars("id"),
    .funs = ~ as.numeric(as.character(.))
  ) %>%
  dplyr::mutate_if(
    .tbl = .,
    .predicate = is.character,
    .funs = ~ base::as.factor(.)
  ) %>%
  dplyr::mutate_if(
    .tbl = .,
    .predicate = is.factor,
    .funs = ~ base::droplevels(.)
  ) %>%
  dplyr::arrange(.data = ., id)

# reordering the Class variables
Titanic_full$Class <-
  base::factor(x = Titanic_full$Class,
  levels = c("1st", "2nd", "3rd", "Crew", ordered = TRUE))

# looking at the final dataset
dplyr::glimpse(Titanic_full)
```

Notice that our final dataset contains information about over 2000 passangers,
while the original dataset with counts information had only 32 rows. Now we can
start asking interesting question from this dataset.

First, let's see if the proportion of people who survived was different between
sexes using `ggpiestats`.

```{r ggpiestats1, cache.extra = Titanic_full, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8}
ggstatsplot::ggpiestats(data = Titanic_full,
                        condition = Sex,
                        main = Survived) 
```

A number of arguments can be modified to change the appearance of this plot:

```{r ggpiestats2, cache.extra = Titanic_full, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8}
library(ggstatsplot)

ggstatsplot::ggpiestats(
  data = Titanic_full,                          # dataframe
  main = Survived,                              # rows in the contingency table
  condition = Sex,                              # columns in the contingecy table
  title = "Passengar survival by gender",       # title for the entire plot
  caption = "Source: Titanic survival dataset", # caption for the entire plot
  legend.title = "Survived?",                   # legend title
  facet.wrap.name = "Gender",                   # changing the facet wrap title
  facet.proptest = TRUE,                        # proportion test for each facet
  stat.title = "survival x gender"              # title for statistical test
) +                                             # further modification outside of ggstatsplot
  ggplot2::scale_fill_brewer(palette = "Dark2")
```

As seen from this plot, the Pearson's chi-square test of independence shows that
the distribution of survival was different across males and females.
Additionally, among both males and females, the proportion of survival was not
equally likely (at 50%, i.e.), as shown by significant results (`***`) from one-sample
proportion tests for each facet.

In case the `condition` argument is not specified, instead of chi-square test of
independence, a proportion test will be carried out. For example, let's see if
there were equal proportions of different age groups.

```{r ggpiestats3, cache.extra = Titanic_full, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 6}
library(ggstatsplot)

ggstatsplot::ggpiestats(
  data = Titanic_full,                          
  main = Age
  ) + 
  ggplot2::scale_fill_brewer(palette = "Set2")
```

As this plot shows there were overwhelmingly more number of adults than children
on the boat and the proportion test attests to this.

## Grouped analysis with `grouped_ggpiestats`

What if we want to do the same analysis separately for the four different Class
on the Titanic (1st, 2nd, 3rd, Crew), i.e. checking how the survival-by-gender
interaction changes by the passenger class in which the people were traveling?
In that case, we will have to either write a `for` loop or use `purrr`, both of
which are time consuming and can be a bit of a struggle.

`ggstatsplot` provides a special helper function for such instances:
`grouped_ggpiestats`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `ggpiestats` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

```{r ggpiestats4, cache.extra = Titanic_full, warning = FALSE, message = FALSE, fig.height = 20, fig.width = 9}
library(ggstatsplot)

ggstatsplot::grouped_ggpiestats(
  # arguments relevant for ggstatsplot::gghistostats
  data = Titanic_full,
  grouping.var = Class,
  title.prefix = "Passenger class",
  stat.title = "survival x gender",
  main = Survived,
  condition = Sex,
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Survival in Titanic disaster by gender for all passenger classes",
  caption.text = "Asterisks denote results from proportion tests; ***: p < 0.001, ns: non-significant",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)", "(d)")
)
```

As seen from this quick exploratory analysis, across all passenger classes, the
proportion of survived to non-survived individuals differed across genders: Men
were more likely to perish than survive, whereas women were more likely to
survive than perish. The only exception was the 3rd Class passangers where women
were as likely to survive as to perish.

Although this grouping function provides a quick way to explore the data, it
leaves much to be desired. For example, the color palette can't be further
modified, the legend color combination differs across different levels of the
grouping variable based on the frequencies, etc. For cases like these, it would
be better to use a function like
[`purrr::pmap`](https://purrr.tidyverse.org/reference/map2.html).

## Grouped analysis with `ggpiestats` + `purrr` 


```{r ggpiestats5, cache.extra = Titanic_full, warning = FALSE, message = FALSE, fig.height = 20, fig.width = 9}
# let's split the dataframe and create a list by passenger class
class_list <- Titanic_full %>%
  base::split(x = ., f = .$Class, drop = TRUE)

# this created a list with 4 elements, one for each class
str(class_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = class_list,
    main = "Survived",
    condition = "Sex",
    facet.wrap.name = "Gender",
    title = list(
      "Passenger class: 1st",
      "Passenger class: 2nd",
      "Passenger class: 3rd",
      "Passenger class: Crew"
    ),
    caption = list(
      "Total: 319, Died: 120, Survived: 199, % Survived: 62%",
      "Total: 272, Died: 155, Survived: 117, % Survived: 43%",
      "Total: 709, Died: 537, Survived: 172, % Survived: 25%",
      "Not available"
    ),
    messages = FALSE
  ),
  .f = ggstatsplot::ggpiestats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plot_list$`1st` + ggplot2::scale_fill_brewer(palette = "Dark2"),
  plot_list$`2nd` + ggplot2::scale_fill_brewer(palette = "Dark2"),
  plot_list$`3rd` + ggplot2::scale_fill_manual(values = c("#D95F02", "#1B9E77")), # to be consistent with other legends
  plot_list$Crew + ggplot2::scale_fill_brewer(palette = "Dark2"),
  title.text = "Survival in Titanic disaster by gender for all passenger classes",
  caption.text = "Asterisks denote results from proportion tests; ***: p < 0.001, ns: non-significant",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)", "(d)")
)
``` 

As can be appreciated from this example, although `grouped_ggpiestats` provides
a quick way to explore data, `purrr::pmap` lets us utilize the full
functionality of this function and `ggplot2`.

## Within-subjects designs

Variant of this function for within-subjects designs, which will display results
from McNemar test, is currently under work. You *can* still use this function
just to prepare the **plot** for exploratory data analysis, but the statistical
details displayed in the subtitle will be incorrect. You can remove them by
adding `+ ggplot2::labs(subtitle = NULL)`.

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>

