---
title: "ggscatterstats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggscatterstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::ggscatterstats` is meant to provide a
**publication-ready scatterplot** with all statistical details included in the
plot itself to show association between two continuous variables. We will see
examples of how to use this function in this vignette with the `ggplot2movies`
dataset.

To begin with, here are some instances where you would want to use
`ggscatterstats`-

  - to check linear association between two continuous variables
  - to check distribution of two continuous variables

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Correlation plot with `ggscatterstats`

To illustrate how this function can be used, we will use the `ggplot2movies`
dataset. This dataset (available in
[package](https://CRAN.R-project.org/package=ggplot2movies) on CRAN) provides a
dataset about movies scraped from [IMDB](https://www.imdb.com/). Let's have a
look at the data-

```{r ggplot2movies1, warning = FALSE, message = FALSE}
library(ggplot2movies)
library(dplyr)

dplyr::glimpse(x = ggplot2movies::movies)
```

We will be using cleaned version of this dataset included in the `ggstatsplot`
package itself.

```{r ggplot2movies2, warning = FALSE, message = FALSE}
library(ggstatsplot)

# see the selected data (we have data from 1813 movies)
dplyr::glimpse(x = ggstatsplot::movies_wide)
```

Now that we have a clean dataset, we can start asking some interesting
questions. For example, let's see if the average rating a movie has depends on its budget.

```{r ggscatterstats1, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8}

ggstatsplot::ggscatterstats(
  data = ggstatsplot::movies_wide,                             # dataframe from which variables are to be taken
  x = budget,                                                  # predictor/independent variable 
  y = rating,                                                  # dependent variable
  xlab = "Budget (in millions of US dollars)",                 # label for the x-axis
  ylab = "Rating on IMDB",                                     # label for the y-axis
  marginal = TRUE,                                             # show marginal distribution 
  marginal.type = "histogram",                                 # type of plot for marginal distribution
  centrality.para = "mean",                                    # if and which type of centrality parameter to be plotted
  margins = "both",                                            # marginal distribution on both axes
  xfill = "#CC79A7",                                           # fill for marginal distributions on the x-axis
  yfill = "#009E73",                                           # fill for marginal distributions on the y-axis
  type = "pearson",                                            # type of linear association
  title = "Relationship between movie budget and IMDB rating",
  caption = "Source: www.imdb.com",
  messages = FALSE
)
```

There is indeed a significant, positive correlation between the amount of money
studio invests in a movie and the ratings given by the audiences. We should also
note that this is a really small correlation and only about 1% of variation in
ratings is explained by budget.

The `type` (of test) argument also accepts the following abbreviations: `"p"`
(for *parametric*/pearson's), `"np"` (for *nonparametric*/spearman), `"r"` (for
*robust*).

**Important**: 
In contrast to all other functions in this package, the
`ggscatterstats` function returns object that is **not** further modifiable
with `ggplot2`. This can be avoided by not plotting the marginal distributions
(`marginal = FALSE`). Currently trying to find a workaround this problem.

**Using `ggscatterstats()` in R Notebooks or Rmarkdown**

If you try including a `ggscatterstats()` plot inside an R Notebook or
Rmarkdown code chunk, you'll notice that the plot doesn't get output. In
order to get a `ggscatterstats()` to show up in an these contexts, you need
to save the ggscatterstats plot as a variable in one code chunk, and
explicitly print it using the `grid` package in another chunk, like
this:

```{r ggscatterstats2, eval = FALSE}
# include the following code in your code chunk inside R Notebook or Markdown
grid::grid.newpage()
grid::grid.draw(
  ggstatsplot::ggscatterstats(
    data = ggstatsplot::movies_wide,
    x = budget,
    y = rating,
    marginal = TRUE,
    messages = FALSE
  )
)
```

## Grouped analysis with `grouped_ggscatterstats`

What if we want to do the same analysis do the same analysis for movies with
different MPAA (Motion Picture Association of America) film ratings (NC-17, PG,
PG-13, R)? In that case, we will have to either write a `for` loop or use
`purrr`, none of which seem like an exciting prospect.

`ggstatsplot` provides a special helper function for such instances:
`grouped_ggstatsplot`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `ggstatsplot` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

Let's see how we can use this function to apply `ggscatterstats` for all MPAA
ratings. We will be running parametric tests (Pearson's *r*, i.e.). If you set
`type = "np"` or `type = "r"`, results from non-parametric or robust test will
be displayed.

```{r grouped1, warning = FALSE, message = FALSE, fig.height = 14, fig.width = 8}
ggstatsplot::grouped_ggscatterstats(
  # arguments relevant for ggstatsplot::ggscatterstats
  data = ggstatsplot::movies_wide,
  title.prefix = "MPAA Rating",
  x = budget,
  y = rating,
  grouping.var = mpaa,
  marginal.type = "boxplot",
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Relationship between movie budget and IMDB rating",
  caption.text = "Source: www.imdb.com",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)","(d)")
)
```

As seen from the plot, this analysis has revealed something interesting: The
relationship we found between budget and IMDB rating holds only for PG-13 and
R-rated movies. Indeed, the relationship even reverses for non-rated or NC-17
rated films.

Although this is a quick and dirty way to explore large amount of data with
minimal effort, it does come with an important limitation: reduced flexibility.
For example, if we wanted to add, let's say, a separate type of marginal
distribution plot for each MPAA rating or if we wanted to use different types of
correlations across different levels of MPAA ratings (NC-17 has only 6 movies,
so a robust correlation would be a good idea), this is not possible. But this
can be easily done using `purrr`.

## Grouped analysis with `ggscatterstats` + `purrr`

Let's run the same analysis using `purrr::pmap`.

**Note before**: Unlike the function call so far, while using `purrr::pmap`, we
will need to *quote* the arguments.

```{r grouped2, warning = FALSE, message = FALSE, fig.height = 16, fig.width = 8}
# let's split the dataframe and create a list by mpaa rating
mpaa_list <- ggstatsplot::movies_wide %>%
  base::split(x = ., f = .$mpaa, drop = TRUE)

# this created a list with 4 elements, one for each mpaa rating
str(mpaa_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = mpaa_list,
    x = "budget",
    y = "rating",
    xlab = "Budget (in millions of US dollars)",
    ylab = "Rating on IMDB",
    title = list(
      "MPAA Rating: NC-17",
      "MPAA Rating: PG",
      "MPAA Rating: PG-13",
      "MPAA Rating: R"
    ),
    type = list("r", "np", "np", "np"),
    marginal.type = list("histogram", "boxplot", "density", "violin"),
    centrality.para = "mean",
    xfill = list("#56B4E9", "#009E73", "#999999", "#0072B2"),
    yfill = list("#D55E00", "#CC79A7", "#F0E442", "#D55E00"),
    messages = FALSE
  ),
  .f = ggstatsplot::ggscatterstats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Relationship between movie budget and IMDB rating",
  caption.text = "Source: www.imdb.com",
  caption.size = 16,
  title.color = "red",
  caption.color = "blue",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)","(d)")
)
```

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
