---
title: "ggscatterstats"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{ggscatterstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The function `ggstatsplot::ggscatterstats` is meant to provide a
**publication-ready scatterplot** with all statistical details included in the
plot itself to show association between two continuous variables. This function
is also helpful during the **data exploration** phase. We will see examples of how
to use this function in this vignette with the `ggplot2movies` dataset.

To begin with, here are some instances where you would want to use
`ggscatterstats`-

  - to check linear association between two continuous variables
  - to check distribution of two continuous variables

**Note before**: The following demo uses the pipe operator (`%>%`), so in case
you are not familiar with this operator, here is a good explanation:
<http://r4ds.had.co.nz/pipes.html>

## Correlation plot with `ggscatterstats`

To illustrate how this function can be used, we will use the `ggplot2movies`
dataset. This dataset provides information about movies scraped from
[IMDB](https://www.imdb.com/). Let's have a look at the data-

```{r ggplot2movies1, warning = FALSE, message = FALSE}
library(ggplot2movies)
library(dplyr)

dplyr::glimpse(x = ggplot2movies::movies)
```

We will be using cleaned version of this dataset included in the `ggstatsplot`
package itself.

```{r ggplot2movies2, warning = FALSE, message = FALSE}
library(ggstatsplot)

# see the selected data (we have data from 1813 movies)
dplyr::glimpse(x = ggstatsplot::movies_wide)
```

Now that we have a clean dataset, we can start asking some interesting
questions. For example, let's see if the average IMDB rating for a movie has any
relationship to its budget. Additionally, let's also see which movies had a high
budget but low IMDB rating by labeling those data points.

```{r ggscatterstats1, warning = FALSE, message = FALSE, fig.height = 6, fig.width = 8}
# for reproducibility
set.seed(123)

# plot
ggstatsplot::ggscatterstats(
  data = ggstatsplot::movies_wide,                             # dataframe from which variables are to be taken
  x = budget,                                                  # predictor/independent variable 
  y = rating,                                                  # dependent variable
  xlab = "Budget (in millions of US dollars)",                 # label for the x-axis
  ylab = "Rating on IMDB",                                     # label for the y-axis
  label.var = title,                                           # variable to use for labeling data points
  label.expression = rating < 5 & budget > 100,                # expression for deciding which points to label
  marginal = TRUE,                                             # show marginal distribution 
  marginal.type = "density",                                   # type of plot for marginal distribution
  centrality.para = "mean",                                    # if and which type of centrality parameter to be plotted
  margins = "both",                                            # marginal distribution on both axes
  xfill = "#CC79A7",                                           # fill for marginal distributions on the x-axis
  yfill = "#009E73",                                           # fill for marginal distributions on the y-axis
  xalpha = 0.5,                                                # changing transparency for the x-axis marginals
  yalpha = 0.75,                                               # changing transparency for the y-axis marginals
  xsize = 1,                                                   # changing size for the x-axis marginals
  ysize = 1,                                                   # changing size for the y-axis marginals
  type = "pearson",                                            # type of linear association
  title = "Relationship between movie budget and IMDB rating",
  caption = "Source: www.imdb.com",
  messages = FALSE
)
```

There is indeed a significant, positive correlation between the amount of money
studio invests in a movie and the ratings given by the audiences. We should also
note that this is a really small correlation and only about 1% of variation in
ratings is explained by budget.

The `type` (of test) argument also accepts the following abbreviations: `"p"`
(for *parametric*/pearson's), `"np"` (for *nonparametric*/spearman), `"r"` (for
*robust*). 

**Important**: 
In contrast to all other functions in this package, the
`ggscatterstats` function returns object that is **not** further modifiable
with `ggplot2`. This can be avoided by not plotting the marginal distributions
(`marginal = FALSE`). Currently trying to find a workaround this problem.

**Using `ggscatterstats()` in R Notebooks or Rmarkdown**

If you try including a `ggscatterstats()` plot inside an R Notebook or
Rmarkdown code chunk, you'll notice that the plot doesn't get output. In
order to get a `ggscatterstats()` to show up in an these contexts, you need
to save the ggscatterstats plot as a variable in one code chunk, and
explicitly print it using the `grid` package in another chunk, like
this:

```{r ggscatterstats2, eval = FALSE}
# include the following code in your code chunk inside R Notebook or Markdown
grid::grid.newpage()
grid::grid.draw(
  ggstatsplot::ggscatterstats(
    data = ggstatsplot::movies_wide,
    x = budget,
    y = rating,
    marginal = TRUE,
    messages = FALSE
  )
)
```

## Grouped analysis with `grouped_ggscatterstats`

What if we want to do the same analysis do the same analysis for movies with
different MPAA (Motion Picture Association of America) film ratings (NC-17, PG,
PG-13, R)? In that case, we will have to either write a `for` loop or use
`purrr`, none of which seem like an exciting prospect.

`ggstatsplot` provides a special helper function for such instances:
`grouped_ggstatsplot`. This is merely a wrapper function around
`ggstatsplot::combine_plots`. It applies `ggstatsplot` across all **levels** of
a specified **grouping variable** and then combines list of individual plots
into a single plot. Note that the grouping variable can be anything: conditions
in a given study, groups in a study sample, different studies, etc. 

Let's see how we can use this function to apply `ggscatterstats` for all MPAA
ratings. We will be running parametric tests (Pearson's *r*, i.e.). If you set
`type = "np"` or `type = "r"`, results from non-parametric or robust test will
be displayed.

```{r grouped1, warning = FALSE, message = FALSE, fig.height = 14, fig.width = 8}
ggstatsplot::grouped_ggscatterstats(
  # arguments relevant for ggstatsplot::ggscatterstats
  data = ggstatsplot::movies_wide,
  title.prefix = "MPAA Rating",
  x = budget,
  y = rating,
  grouping.var = mpaa,
  label.var = title,
  label.expression = rating < 5 & budget > 100,
  marginal.type = "boxplot",
  ggtheme = ggthemes::theme_tufte(),
  ggstatsplot.layer = FALSE,
  # number of decimal places in results
  k = 2,
  # arguments relevant for ggstatsplot::combine_plots
  title.text = "Relationship between movie budget and IMDB rating",
  caption.text = "Source: www.imdb.com",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)","(d)")
)
```

As seen from the plot, this analysis has revealed something interesting: The
relationship we found between budget and IMDB rating holds only for PG-13 and
R-rated movies. Indeed, the relationship even reverses for non-rated or NC-17
rated films.

Although this is a quick and dirty way to explore large amount of data with
minimal effort, it does come with an important limitation: reduced flexibility.
For example, if we wanted to add, let's say, a separate type of marginal
distribution plot for each MPAA rating or if we wanted to use different types of
correlations across different levels of MPAA ratings (NC-17 has only 6 movies,
so a robust correlation would be a good idea), this is not possible. But this
can be easily done using `purrr`.

## Grouped analysis with `ggscatterstats` + `purrr`

Let's run the same analysis using `purrr::pmap`.

**Note before**: Unlike the function call so far, while using `purrr::pmap`, we
will need to *quote* the arguments.

```{r grouped2, warning = FALSE, message = FALSE, fig.height = 16, fig.width = 8}
# for reproducibility
set.seed(123)

# let's split the dataframe and create a list by mpaa rating
mpaa_list <- ggstatsplot::movies_wide %>%
  base::split(x = ., f = .$mpaa, drop = TRUE)

# this created a list with 4 elements, one for each mpaa rating
# you can check the structure of the file for yourself
# str(mpaa_list)

# checking the length and names of each element
length(mpaa_list)
names(mpaa_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list1 <- purrr::pmap(
  .l = list(
    data = mpaa_list,
    x = "budget",
    y = "rating",
    xlab = "Budget (in millions of US dollars)",
    ylab = "Rating on IMDB",
    title = list(
      "MPAA Rating: NC-17",
      "MPAA Rating: PG",
      "MPAA Rating: PG-13",
      "MPAA Rating: R"
    ),
    # label.var = list("title", "year", "votes", "genre"),
    # label.expression = list(
    #   ("rating" > 8.5 &
    #     "budget" < 50),
    #   ("rating" > 8.5 &
    #     "budget" < 100),
    #   ("rating" > 8 & "budget" < 50),
    #   ("rating" > 9 & "budget" < 10)
    # ),
    type = list("r", "np", "p", "np"),
    method = list(MASS::rlm, "lm", "lm", "lm"),
    marginal.type = list("histogram", "boxplot", "density", "violin"),
    centrality.para = "mean",
    xfill = list("#56B4E9", "#009E73", "#999999", "#0072B2"),
    yfill = list("#D55E00", "#CC79A7", "#F0E442", "#D55E00"),
    ggtheme = list(
      ggplot2::theme_grey(),
      ggplot2::theme_classic(),
      ggplot2::theme_light(),
      ggplot2::theme_minimal()
    ),
    messages = TRUE
  ),
  .f = ggstatsplot::ggscatterstats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list1,
  title.text = "Relationship between movie budget and IMDB rating",
  caption.text = "Source: www.imdb.com",
  caption.size = 16,
  title.color = "red",
  caption.color = "blue",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)","(d)")
)
```

## Different smoothing methods

Additionally, different smoothing methods can be specified. For example, if a
robust correlation (percentage bend correlation coefficient) is used, we can use
a robust smoothing function (`MASS::rlm`). Additionally, we can also specify
different formulas to use for smoothing function. It is **important** that you
set `results.subtitle = FALSE` since the results will no longer be relevant for
the smoothing function used. Below, four different examples are given for how to
use different smoothing functions.

```{r grouped3, warning = FALSE, message = FALSE, fig.height = 12, fig.width = 12}
library(mgcv)

# for reproducibility
set.seed(123)

# creating a list of plots with different smoothing functions
plot_list2 <- purrr::pmap(
  .l = list(
    data = list(dplyr::sample_frac(tbl = ggstatsplot::movies_wide, size = 0.10)),
    x = "budget",
    y = "rating",
    title = list(
      "Robust linear model using an M estimator (rlm)",
      "Generalized additive model (GAM) with a penalized smoother",
      "Local Polynomial Regression Fitting",
      "Quadratic fit"
    ),
    method = list(MASS::rlm, 
                  "gam", 
                  "loess", 
                  "lm"),
    formula = list(y ~ x, 
                   y ~ s(x, k = 3), 
                   y ~ x, 
                   y ~ x + I(x ^ 2)),
    line.color = list("#009E73", "#F0E442", "#0072B2", "#D55E00"),
    marginal = FALSE,
    results.subtitle = FALSE,
    messages = FALSE
  ),
  .f = ggstatsplot::ggscatterstats
)

# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list2,
  title.text = "Trying out different smoothing functions with ggscatterstats",
  caption.text = "Source: www.imdb.com",
  nrow = 2,
  ncol = 2,
  labels = c("(a)", "(b)", "(c)", "(d)")
)
```

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: 
<https://github.com/IndrajeetPatil/ggstatsplot/issues>

## Session Information

Summarizing session information for reproducibility.

```{r session_info}
options(width = 200)
devtools::session_info()
```

