---
title: "graphics design"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{graphics design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `ggstatsplot` package is an opinionated collection of plots made with
`ggplot2` and is designed for exploratory data analysis or for producing
publication-ready. All plots share an underlying principle of displaying
information-rich plots with all necessary statistical details included in the
plots themselves. Although the plots produced by `ggstatsplot` are still
`ggplot` objects and can thus be further modified using `ggplot2` commands,
there is a limit to how many such modifications can be made. That is, it is less
flexible than `ggplot2`, but that's a feature and not a bug. The original intent
behind this package is to offload struggles associated with *constructing* the
plot and focus more on the *interpretation* of that data displayed in the plot.

(**This vignette is still a work in progress**)

## Clean design

```{r example1, fig.height = 8, fig.width = 7}
ggstatsplot::ggbetweenstats(
  data = ggplot2::mpg,
  x = cyl,
  y = cty,
  title = "Figure-1: Fuel efficiency by type of cylinder",
  xlab = "number of cylinders",
  ylab = "city miles per gallon",
  outlier.tagging = TRUE,
  outlier.label = manufacturer,
  messages = FALSE
)
```

* The package follows two principles for graphical integrity (Tufte, 2001, Chapter 2):

  + The physical representation of numbers is proportional to the numerical
  quantities they represent (e.g., Figure-1 and Figure-2 show how means (in
  `ggbetweenstats`) or percentages (`ggpiestats`) are proportional to the
  vertical distance or the area, respectively).
  
  + All important events in the data have clear, detailed, and thorough labeling
  (e.g., Figure-1 plot shows how `ggbetweenstats` labels means, sample size
  information, and outliers; same can be appreciated for `ggpiestats` in
  Figure-2).

* All plots are designed to have no **chartjunk** (like moiré vibrations, fake
perspective, dark grid lines, etc.) (Tufte, 2001, Chapter 5).

```{r example2, fig.height = 5, fig.width = 5}
ggstatsplot::ggpiestats(
  data = ggplot2::mpg,
  main = drv,
  title = "Figure-2: Distribution of layouts",
  legend.title = "layout",
  caption = "f = front-wheel drive, r = rear wheel drive, 4 = 4wd",
  messages = FALSE
)
```

## Graphical perception

Graphical perception involves visual decoding the encoded information in graphs.
`ggstatsplot` incorporates the paradigm proposed in Cleveland (1985, Chapter 4) to
facilitate making visual judgments about quantitative information effortless and
almost instantaneous.

There are few instances where `ggstatsplot` diverges from recommendations made in Cleveland's paradigm:
*  

## Statistical details

* As Lilienfeld and colleagues report (Lilienfeld et al., 2015):

> **p = 0.000**. Even though this statistical expression, used in over 97,000
manuscripts according to Google Scholar, makes regular cameo appearances in our
computer printouts, we should assiduously avoid inserting it in our Results
sections. This expression implies erroneously that there is a zero probability
that the investigators have committed a Type I error, that is, a false rejection
of a true null hypothesis.

All p-values displayed in `ggstatsplot` plots avoid this mistake. Anything less
  than `p < 0.001` is displayed as such. The package doesn't care how
  infinitesimally small the *p*-values are. Instead, the emphasis is put more on
  the effect size magnitudes and their 95% CIs.
  

