---
title: "plot design"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    toc: true
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{plot design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `ggstatsplot` package is an opinionated collection of plots made with
`ggplot2` and is designed for exploratory data analysis or for producing
publication-ready. All plots share an underlying principle of displaying
information-rich plots with all necessary statistical details included in the
plots themselves. Although the plots produced by `ggstatsplot` are still
`ggplot` objects and can thus be further modified using `ggplot2` commands,
there is a limit to how many such modifications can be made. That is, it is less
flexible than `ggplot2`, but that's a feature and not a bug. The original intent
behind this package is to offload struggles associated with *constructing* the
plot and focus more on the *interpretation* of that data displayed in the plot.

(**This vignette is still a work in progress**)

# Graphical perception

Graphical perception involves visual decoding of the encoded information in
graphs. `ggstatsplot` incorporates the paradigm proposed in Cleveland (1985,
Chapter 4) to facilitate making visual judgments about quantitative information
effortless and almost instantaneous. Based on experiments, Cleveland proposes
that there are ten elementary graphical-perception tasks that we perform to
visually decode quantitative information in graphs (organized from most to least
accurate [^1])-
 
 [^1]: "The ordering is based on the theory of visual perception, on experiments
 in graphical perception, and on informal experimentation." (Cleveland, 1985,
 p.254)

* Position along a common scale
* Position along identical, non-aligned scales
* Length
* Angle (Slope)
* Area
* Volume
* Color hue - Color saturation - Density

So the key principle of Cleveland's paradigm for data display is- 

> "We should encode data on a graph so that the visual decoding involves
[graphical-perception] tasks as high in the ordering as possible."

For example, decoding the data point values in `ggbetweenstats` requires
position judgments along a common scale (Figure-1):

```{r example1, fig.height = 8, fig.width = 7, fig.cap = "**Figure-1**. Note that assessing differences in mean values between groups has been made easier with the help of *position* of data points along a common scale (the Y-axis) and labels."}
ggstatsplot::ggbetweenstats(
  data = ggplot2::mpg,
  x = cyl,
  y = cty,
  title = "Figure-1: Fuel efficiency by type of cylinder",
  xlab = "number of cylinders",
  ylab = "city miles per gallon",
  ggtheme = ggthemes::theme_fivethirtyeight(),
  ggstatsplot.layer = FALSE,
  outlier.tagging = TRUE,
  outlier.label = manufacturer,
  messages = FALSE
)
```

There are few instances where `ggstatsplot` diverges from recommendations made
in Cleveland's paradigm:

* For the categorical/nominal data, `ggstatsplot` uses pie charts (see Figure-2)
which rely on *angle* judgments, which are less accurate (as compared to bar
graphs, e.g., which require *position* judgments). This shortcoming is assuaged
to some degree by using plenty of labels that describe percentages for all
slices. This makes angle judgment unnecessary and pre-vacates any concerns about
inaccurate judgments about percentages.

```{r example2, fig.height = 6, fig.width = 10, fig.cap = "Figure-2. Pie charts don't follow Cleveland's paradigm to data display because they rely on less accurate angle judgments. `ggstatsplot` sidesteps this issue by always labelling percentages for pie slices, which makes angle judgments unnecessary."}
ggstatsplot::ggpiestats(
  data = ggstatsplot::movies_long,
  main = genre,
  condition = mpaa,
  title = "Figure-2: Distribution of MPAA ratings by film genre",
  legend.title = "layout",
  caption = "MPAA: Motion Picture Association of America",
  package = "ggsci",
  palette = "default_jama",
  messages = FALSE
)
```

* Cleveland's paradigm also emphasizes that *superposition* of data is better
than *juxtaposition* (Cleveland, 1985, p.201) because this allows for a more
incisive comparison of the values from different parts of the dataset. This
recommendation is violated in all `grouped_` variants of the function (see
Figure-3). Note that the range for Y-axes are no longer the same across
juxtaposed subplots and so visually comparing the data becomes difficult. On the
other hand, in the superposed plot, all data have the same range and coloring
different parts makes the visual discrimination of different components of the
data, and their comparison, even easier. But the goal of `grouped_` variants of
functions is to not only show different aspects of the data but also to run
statistical tests and showing detailed results for all aspects of the data in
a superposed plot is difficult.

```{r example3, fig.height = 12, fig.width = 10, fig.cap = "Figure-3. Comparing different aspects of data is much more accurate in a superposed plot (b), which is recommended in Cleveland's paradigm, than in a juxtaposed plot, which is how it's implemented in `ggstatsplot` because displaying detailed results from statistical tests would be difficult otherwise."}
ggstatsplot::combine_plots(
  # plot 1: juxtaposition
  ggstatsplot::grouped_ggscatterstats(
    data = dplyr::filter(ggstatsplot::movies_long, genre == "Comedy" |
                           genre == "Drama"),
    x = length,
    y = rating,
    grouping.var = genre,
    marginal = FALSE,
    title.prefix = "Genre",
    title.text = "juxtaposition (`ggstatsplot` implementation in `grouped_` functions)",
    title.size = 12
  ),
  # plot2: superposition
  ggplot2::ggplot(
    data = dplyr::filter(ggstatsplot::movies_long, genre == "Comedy" |
                           genre == "Drama"),
    mapping = ggplot2::aes(x = length,
                           y = rating,
                           color = genre)
  ) +
    ggplot2::geom_jitter(size = 3, alpha = 0.5) +
    ggplot2::geom_smooth(method = "lm") +
    ggplot2::labs(title = "superposition (recommended in Cleveland's paradigm)") +
    ggstatsplot::theme_ggstatsplot(),
  # combine for comparison
  title.text = "Two ways to compare different aspects of data",
  nrow = 2,
  labels = c("(a)", "(b)")
)
```

# Graphical integrity (and clean design)

The package follows the principles for **graphical integrity** (as outlined in
Tufte, 2001):

  * The physical representation of numbers is proportional to the numerical
  quantities they represent (e.g., Figure-1 and Figure-2 show how means (in
  `ggbetweenstats`) or percentages (`ggpiestats`) are proportional to the
  vertical distance or the area, respectively).
  
  * All important events in the data have clear, detailed, and thorough labeling
  (e.g., Figure-1 plot shows how `ggbetweenstats` labels means, sample size
  information, and outliers; same can be appreciated for `ggpiestats` in
  Figure-2).
  
  * None of the plots have *design* variation (e.g., abrupt change in scales)
  over the surface of a same graphic because this can lead to a false impression
  about variation in *data*.
  
  * The number of information-carrying dimensions never exceed the number of
  dimensions in the data (e.g., using area to show one-dimensional data).

  * All plots are designed to have no **chartjunk** (like moiré vibrations, fake
  perspective, dark grid lines, etc.) (Tufte, 2001, Chapter 5).

# Statistical details


## Types of tests supported in each function

Functions | Description | Parametric | Non-parametric | Robust | Bayes Factor
------- | ------------------ | ---- | ----- | ----| ----- 
`ggbetweenstats` | Between group/condition comparisons | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font>
`gghistostats` | Distribution of a variable | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font>
`ggcorrmat` | Correlation matrix | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="red">$\times$</font>
`ggscatterstats` | Correlation between two variables | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="green">$\checkmark$</font> | <font color="red">$\times$</font>
`ggpiestats` | Association between two categorical variables | <font color="green">$\checkmark$</font> | <font color="red">$\times$</font> | <font color="red">$\times$</font> | <font color="red">$\times$</font>
`ggcoefstats` | Regression model coefficients | <font color="green">$\checkmark$</font> | <font color="red">$\times$</font>| <font color="green">$\checkmark$</font> | <font color="red">$\times$</font>

## Statistical variation

One of the important functions of a plot is to show the variation in the data,
which comes in two forms:

* *Measurement noise*: In `ggstatsplot`, the actual variation in measurements is
shown by plotting a combination of (jittered) raw data points with a boxplot
laid on top (Figure-1) or a histogram (Figure-4). None of the plots, where
empirical distribution of the data is concerned, show the sample standard
deviation because they are poor at conveying information about limits of the
sample and presence of outliers (Cleveland, 1985, p.220).

```{r example4, fig.height = 6, fig.width = 8, fig.cap = "**Figure-4**. Distribution of a variable shown using `gghistostats`."}
ggstatsplot::gghistostats(
  data = morley,
  x = Speed,
  test.value = 792,
  test.value.line = TRUE,
  xlab = "Speed of light (km/sec, with 299000 subtracted)",
  title = "Figure-4: Distribution of Speed of light",
  caption = "Note: Data collected across 5 different experiments (20 measurements per study)",
  messages = FALSE
)
```

* *Sample-to-sample statistic variation*: Although, traditionally, this
variation has been shown using the standard error of the mean (SEM) of the
statistic, `ggstatsplot` plots instead use 95% confidence intervals (e.g,
Figure-5). This is because the interval formed by error bars correspond to a 68%
confidence interval, which is not a particularly interesting interval
(Cleveland, 1985, p.222-225).

```{r example5, fig.height = 5, fig.width = 5, fig.cap = "**Figure-5**. Sample-to-sample variation in regression estimates is displayed using confidence intervals in `ggcoefstats`."}
ggstatsplot::ggcoefstats(x = lme4::lmer(
  total.fruits ~ nutrient + rack + (nutrient |
                               popu / gen),
  data = lme4::Arabidopsis
))
```

## p-values

* As Lilienfeld and colleagues report (Lilienfeld et al., 2015):

> **p = 0.000**. Even though this statistical expression, used in over 97,000
manuscripts according to Google Scholar, makes regular cameo appearances in our
computer printouts, we should assiduously avoid inserting it in our Results
sections. This expression implies erroneously that there is a zero probability
that the investigators have committed a Type I error, that is, a false rejection
of a true null hypothesis.

All p-values displayed in `ggstatsplot` plots avoid this mistake. Anything less
  than `p < 0.001` is displayed as such. The package doesn't care how
  infinitesimally small the *p*-values are. Instead, the emphasis is put more on
  the effect size magnitudes and their 95% CIs.
  
# References
