---
title: "using `ggstatsplot` with `purrr` package"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 150
    toc: true
    eval: FALSE
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{using `ggstatsplot` with `purrr` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Why `purrr`?

Most of `ggstatsplot` functions have `grouped_` variants, which are designed to
quickly run the same `ggstatsplot` function across multiple levels of a single
grouping variable. Although this function has its utility for quick data
exploration, it has two strong weaknesses-

  * The arguments applied to `grouped_` function call are applied uniformly to
  all levels of the grouping variable when we might want to customize them for
  different levels of the grouping variable.
  
  * Only one grouping variable can be used to repeat the analysis when in
  reality there can be a combination of grouping variables and the operation
  needs to be repeated for all resulting combinations.

We will see how to overcome this limitation by combining `ggstatsplot` with the
`purrr` package. Although output from only one example is shown here, the users
are encouraged to execute the other examples.

**Note before**:

  * Unlike the typical function call for `ggstatsplot` functions where arguments
  can be quoted (`"x"`) or unquoted (`x`), while using `purrr::pmap`, we **must**
  *quote* the arguments.
  * You can use `ggplot2` themes from extension packages (like `ggthemes`).

# `ggbetweenstats`

```{r purrr_ggbetweenstats, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 7}
library(ggstatsplot)

# for reproducibility
set.seed(123)

# let's split the dataframe and create a list by years of interest
year_list <- gapminder::gapminder %>%
  dplyr::filter(
    .data = .,
    year == 1967 |
    year == 1987 |
    year == 2007, 
    continent != "Oceania"
  ) %>%
  base::split(x = ., f = .$year, drop = TRUE)

# this created a list with 3 elements, one for each mpaa rating
# you can check the structure of the file for yourself
# str(year_list)

# checking the length and names of each element
length(year_list)
names(year_list)

# running function on every element of this list; note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = year_list,
    x = "continent",
    y = "lifeExp",
    outlier.label = "country",
    outlier.label.color = list(
      "#56B4E9",
      "#009E73",
      "#F0E442"
    ),
    xlab = "Continent",
    ylab = "Life expectancy",
    title = list(
      "Year: 1967",
      "Year: 1987",
      "Year: 2007"
    ),
    type = list("r", "p", "np"),
    nboot = 25,
    k = list(1, 2, 3),
    effsize.type = list(
      NULL,
      "partial_omega",
       "partial_eta"
    ),
    plot.type = list("box", "boxviolin", "violin"),
    mean.ci = list(TRUE, FALSE, FALSE),
    package = list("nord", "ochRe", "awtools"),
    palette = list("aurora", "parliament", "ppalette"),
    ggtheme = list(
      ggthemes::theme_stata(),
      ggplot2::theme_classic(),
      ggthemes::theme_fivethirtyeight()
    ),
    ggstatsplot.layer = list(FALSE, FALSE, FALSE),
    sample.size.label = list(TRUE, FALSE, TRUE),
    messages = FALSE
  ),
  .f = ggstatsplot::ggbetweenstats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Changes in life expectancy across continents (1967-2007)",
  title.color = "red",
  nrow = 3,
  ncol = 1
)
```

# `ggscatterstats`

```{r purrr_ggscatterstats, warning = FALSE, message = FALSE, fig.height = 12, fig.width = 7}
# for reproducibility
set.seed(123)

# let's split the dataframe and create a list by mpaa rating
# let's use only 25% of the data
# also let's leave out movies with NC-17 rating because there are so few of them
mpaa_list <- ggstatsplot::movies_wide %>%
  dplyr::filter(.data = ., mpaa != "NC-17") %>%
  dplyr::sample_frac(tbl = ., size = 0.25) %>%
  base::split(x = ., f = .$mpaa, drop = TRUE)

# this created a list with 3 elements, one for each mpaa rating
# you can check the structure of the file for yourself
# str(mpaa_list)

# checking the length and names of each element
length(mpaa_list)
names(mpaa_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = mpaa_list,
    x = "budget",
    y = "rating",
    xlab = "Budget (in millions of US dollars)",
    ylab = "Rating on IMDB",
    title = list(
      "MPAA Rating: PG",
      "MPAA Rating: PG-13",
      "MPAA Rating: R"
    ),
    label.var = list("title", "year", "length"),
    label.expression = list(
       "rating > 8.5 &
         budget < 100",
       "rating > 8 & budget < 50",
       "rating > 9 & budget < 10"
     ),
    type = list("r", "np", "p"),
    method = list(MASS::rlm, "lm", "lm"),
    nboot = 25,
    marginal.type = list("boxplot", "density", "violin"),
    centrality.para = list("mean", "median", "mean"),
    xfill = list("#009E73", "#999999", "#0072B2"),
    yfill = list("#CC79A7", "#F0E442", "#D55E00"),
    ggtheme = list(
      ggthemes::theme_tufte(),
      ggplot2::theme_classic(),
      ggplot2::theme_light()
    ),
    ggstatsplot.layer = list(FALSE, TRUE, TRUE),
    messages = FALSE
  ),
  .f = ggstatsplot::ggscatterstats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Relationship between movie budget and IMDB rating",
  caption.text = "Source: www.imdb.com",
  caption.size = 16,
  title.color = "red",
  caption.color = "blue",
  nrow = 3,
  ncol = 1,
  labels = c("(a)","(b)","(c)","(d)")
)
```

# `ggcorrmat`

```{r purrr_ggcorrmat, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10}
# splitting the dataframe by cut and creting a list
# let's leave out "fair" cut
# also, to make this fast, let's only use 5% of the sample
cut_list <- ggplot2::diamonds %>%
  dplyr::sample_frac(tbl = ., size = 0.05) %>%
  dplyr::filter(.data = ., cut != "Fair") %>% 
  base::split(x = ., f = .$cut, drop = TRUE)

# this created a list with 4 elements, one for each quality of cut
# you can check the structure of the file for yourself
# str(cut_list)

# checking the length and names of each element
length(cut_list)
names(cut_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = cut_list,
    cor.vars = list(c("carat", "depth", "table", "price")),
    cor.vars.names = list(c(
      "carat",
      "total depth",
      "table",
      "price"
    )),
    corr.method = list("pearson", "np", "robust", "kendall"),
    title = list("Cut: Good", "Cut: Very Good", "Cut: Premium", "Cut: Ideal"), 
    # note that we are changing both p-value adjustment method *and*
    # significance level to display the significant correlations in the
    # visualization matrix
    p.adjust.method = list("hommel", "fdr", "BY", "hochberg"),
    sig.level = list(0.001, 0.01, 0.05, 0.003),
    lab.size = 3.5,
    colors = list(
      c("#56B4E9", "white", "#999999"),
      c("#CC79A7", "white", "#F0E442"),
      c("#56B4E9", "white", "#D55E00"),
      c("#999999", "white", "#0072B2")
    ),
    ggstatsplot.layer = FALSE,
    ggtheme = list(
      ggplot2::theme_grey(),
      ggplot2::theme_classic(),
      ggthemes::theme_fivethirtyeight(),
      ggthemes::theme_tufte()
    )
  ),
  .f = ggstatsplot::ggcorrmat
)

# combining all individual plots from the list into a single plot using
# `combine_plots` function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Relationship between diamond attributes and price across cut",
  title.size = 14,
  title.color = "red",
  caption.text = "Dataset: Diamonds from ggplot2 package",
  caption.size = 12,
  caption.color = "blue",
  nrow = 2
)
```


# `gghistostats`

```{r purrr_gghistostats, warning = FALSE, message = FALSE, fig.height = 14, fig.width = 6}
# for reproducibility
set.seed(123)

# libraries needed
library(ggthemes)

# let's split the dataframe and create a list by continent
# let's leave out Oceania because it has just two data points
continent_list <- gapminder::gapminder %>%
  dplyr::filter(.data = ., year == 2007, continent != "Oceania") %>%
  base::split(x = ., f = .$continent, drop = TRUE)

# this created a list with 4 elements, one for each continent
# you can check the structure of the file for yourself
# str(continent_list)

# checking the length and names of each element
length(continent_list)
names(continent_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = continent_list,
    x = "lifeExp",
    xlab = "Life expectancy",
    test.value = list(35.6, 58.4, 41.6, 64.7),
    type = list("p", "np", "r", "bf"),
    bf.message = list(TRUE, FALSE, FALSE, FALSE),
    title = list(
      "Continent: Africa",
      "Continent: Americas",
      "Continent: Asia",
      "Continent: Europe"
    ),
    bar.measure = list("proportion", "count", "proportion", "density"),
    fill.gradient = list(TRUE, FALSE, FALSE, TRUE),
    low.color = list("#56B4E9", "white", "#999999", "#009E73"),
    high.color = list("#D55E00", "white", "#F0E442", "#F0E442"),
    bar.fill = list("white", "red", "orange", "blue"),
    centrality.color = "black",
    test.value.line = TRUE,
    test.value.color = "black",
    centrality.para = "mean",
    ggtheme = list(
      ggplot2::theme_classic(),
      ggthemes::theme_fivethirtyeight(),
      ggplot2::theme_minimal(),
      ggthemes::theme_few()
    ),
    messages = FALSE
  ),
  .f = ggstatsplot::gghistostats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Improvement in life expectancy worldwide since 1950",
  caption.text = "Note: black line - 1950; blue line - 2007",
  nrow = 4,
  ncol = 1,
  labels = c("(a)", "(b)", "(c)", "(d)")
)
```  

# `ggpiestats`

```{r purrr_ggpiestats, warning = FALSE, message = FALSE, fig.height = 20, fig.width = 9}
# let's split the dataframe and create a list by passenger class
class_list <- ggstatsplot::Titanic_full %>%
  base::split(x = ., f = .$Class, drop = TRUE)

# this created a list with 4 elements, one for each class
# you can check the structure of the file for yourself
# str(class_list)

# checking the length and names of each element
length(class_list)
names(class_list)

# running function on every element of this list note that if you want the same
# value for a given argument across all elements of the list, you need to
# specify it just once
plot_list <- purrr::pmap(
  .l = list(
    data = class_list,
    main = "Survived",
    condition = "Sex",
    nboot = 10,
    facet.wrap.name = "Gender",
    title = list(
      "Passenger class: 1st",
      "Passenger class: 2nd",
      "Passenger class: 3rd",
      "Passenger class: Crew"
    ),
    caption = list(
      "Total: 319, Died: 120, Survived: 199, % Survived: 62%",
      "Total: 272, Died: 155, Survived: 117, % Survived: 43%",
      "Total: 709, Died: 537, Survived: 172, % Survived: 25%",
      "Data not available for crew passengers"
    ),
    package = list("RColorBrewer", "ghibli", "palettetown", "yarrr"),
    palette = list("Accent", "MarnieMedium1", "pikachu", "nemo"),
    ggtheme = list(
      ggplot2::theme_grey(),
      ggplot2::theme_bw(),
      ggthemes::theme_tufte(),
      ggthemes::theme_economist()
    ),
    ggstatsplot.layer = list(TRUE, TRUE, FALSE, FALSE),
    sample.size.label = list(TRUE, FALSE, TRUE, FALSE),
    messages = FALSE
  ),
  .f = ggstatsplot::ggpiestats
)
  
# combining all individual plots from the list into a single plot using combine_plots function
ggstatsplot::combine_plots(
  plotlist = plot_list,
  title.text = "Survival in Titanic disaster by gender for all passenger classes",
  caption.text = "Asterisks denote results from proportion tests: \n***: p < 0.001, ns: non-significant",
  nrow = 4,
  ncol = 1,
  labels = c("(a)","(b)","(c)", "(d)")
)
``` 

# Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub:
<https://github.com/IndrajeetPatil/ggstatsplot/issues>

# Session Information

Summarizing session information for reproducibility.

```{r session_info}
options(width = 200)
devtools::session_info()
```
