---
title: "Default theme (theme_mprl)"
author: "Indrajeet Patil"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 6
    fig.align: 'center'
    fig.asp: 0.618
    dpi: 300
    warning: FALSE
    message: FALSE
vignette: >
  %\VignetteIndexEntry{theme_mprl}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Default theme for the package: `theme_mprl`

`ggstatsplot` uses a default theme `theme_mprl()` that can be used with any
`ggplot2` object.

Here is a simple example:

```{r theme_mprl, message = FALSE, warning = FALSE, fig.height = 4, fig.width = 4}
library(ggplot2)

# Basic scatter plot
ggplot2::ggplot(
  data = datasets::mtcars, 
  mapping = ggplot2::aes(x = wt, y = mpg)
) + 
  ggplot2::geom_point()

# Basic scatter plot with theme_mprl() added
ggplot2::ggplot(
  data = datasets::mtcars, 
  mapping = ggplot2::aes(x = wt, y = mpg)
) + 
  ggplot2::geom_point() + 
  ggstatsplot::theme_mprl()
```

All plots in this package have this theme by default. For example, since the
`ggcorrmat` allows you to use different `ggplot2` themes, it contains an
argument to prevent overlaying the default ggstatsplot theme. Otherwise,
whichever `ggtheme` you chose will just be overridden by the ggstatsplot theme.

```{r ggcorrmat_theme1, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 6}
ggstatsplot::ggcorrmat(
  data = datasets::iris,
  cor.vars = c(Sepal.Length:Petal.Width),
  type = "upper",
  ggtheme = ggplot2::theme_dark,          # selected ggplot2 theme
  ggstatsplot.theme = FALSE               # turn off overlaying theme_mprl on selected ggplot2 theme
)
```

Contrast this what it looks like if you don't turn off the default theme overlay:

```{r ggcorrmat_theme2, message = FALSE, warning = FALSE, fig.height = 6, fig.width = 6}
ggstatsplot::ggcorrmat(
  data = datasets::iris,
  cor.vars = c(Sepal.Length:Petal.Width),
  type = "upper",
  ggtheme = ggplot2::theme_dark,         # selected ggplot2 theme
  ggstatsplot.theme = TRUE                # overlaying theme_mprl on selected ggplot2 theme
)
```

## Suggestions

If you find any bugs or have any suggestions/remarks, please file an issue on GitHub: <https://github.com/IndrajeetPatil/ggstatsplot/issues>
